### 2022-10-19 latex/supplementary.tex
Add files via upload

\documentclass[11pt]{article}
\usepackage{times}
\usepackage{amsmath,amsthm,amssymb,mathtools,setspace,enumitem,epsfig,titlesec,verbatim,color,array,multirow,comment,graphicx,hyperref,blkarray}
%\usepackage[sort&compress]{natbib} % ProcB
\usepackage[super,sort&compress,comma]{natbib} % NComms
\usepackage[bf,small]{caption}
\usepackage[export]{adjustbox}
\usepackage[top=2.5cm,left=2.8cm,right=2.8cm,bottom=3.2cm]{geometry} 
\smallskip

\definecolor{darkred}{rgb}{0.6,0,0}
\definecolor{darkblue}{rgb}{0,0.3,0.8}

\newcommand{\christian}[1]{\textcolor{blue}{{\bf CH:} #1}}

\titleformat{\section}{\sffamily \fontsize{12}{20}\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\sffamily \fontsize{11}{20}\bfseries}{\thesubsection}{1em}{}

\renewcommand{\figurename}{Supplementary Figure}

\newcommand{\FigIllustration}{{\bf Fig.~1}}

\newtheoremstyle{plainCl1}% name
{9pt}%      Space above, empty = 'usual value'
{15pt}%      Space below
{\it}% 	   Body font
{}%         Indent amount (empty = no indent, \parindent = para indent)
{\bfseries}% Thm head font
{.}%        Punctuation after thm head
{2mm}% Space after thm head: \newline = linebreak
{}%         Thm head spec

\newtheoremstyle{plainCl2}% name
{9pt}%      Space above, empty = 'usual value'
{15pt}%      Space below
{\it}% 	   Body font
{}%         Indent amount (empty = no indent, \parindent = para indent)
{\bfseries}% Thm head font
{.}%        Punctuation after thm head
{4mm}% Space after thm head: \newline = linebreak
{}%         Thm head spec

\theoremstyle{plainCl1}
\newtheorem{theorem}{Theorem}
\newtheorem{Prop}{Proposition}

\theoremstyle{plainCl2}
\newtheorem{lemma}{Lemma}
\newtheorem{Cor}{Corollary}

\newcommand{\ALLD}{\emph{D}}

\newcommand{\ai}{\mathbf{A}^i}

\title{\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}}
\date{\empty}
\author{\parbox[c]{16cm}{\centering \onehalfspacing \fontsize{11}{12}\selectfont Marta Couto$^1$ and Saptarshi Pal$^1$\\[0.2cm]
$^1$Max Planck Research Group Dynamics of Social Behavior, Max Planck Institute for Evolutionary Biology, 24306~Ploen, Germany}}

\begin{document}
\maketitle
\onehalfspacing
\section*{The general model for introspection dynamics}
We consider an asymmetric normal form game with $N (>2)$ players. Each player, $i$, has access to their action set, $\ai$, in which there are $m_i$ possible actions that they can play, $\ai = \{a^i_i, a^i_2, ..., a^i_{m_i}\}$. The payoff for an individual $i$ depends on what everyone plays and is represented by $\pi^i(a^1, a^2, ..., a^N)$, where $(a^1, a^2,...,a^N) \in \mathbf{A}^1 \times \mathbf{A}^2 \times ... \times \mathbf{A}^N$. In this model we only consider pure strategies for players. So, player $i$ has only $m_i$ possible strategies.

\noindent The players update their strategies over time using the introspection dynamics \cite{couto2022introspection}.

\section*{Examples of multiplayer games and results}

\section*{Supplementary References}
\bibliographystyle{unsrt}
\bibliography{bibliography.bib }
\end{document}

### 2022-11-07 latex/supplementary.tex
additions to the latex SI with some formalizations and proofs

@@
 \newtheorem{Prop}{Proposition}
+\newtheorem{definition}{Definition}
 
@@
 \newtheorem{lemma}{Lemma}
+\newtheorem{proposition}{Proposition}
 \newtheorem{Cor}{Corollary}
@@
 
-\newcommand{\ai}{\mathbf{A}^i}
+\newcommand{\A}{\mathbf{A}}
+\newcommand{\abf}{\mathbf{a}}
+\newcommand{\T}{\mathbf{T}}
+\newcommand{\ubf}{\mathbf{u}}
 
@@
 We consider an asymmetric normal form game with $N (>2)$ players.
-Each player, $i$, has access to their action set, $\ai$, in which there are $m_i$ possible actions that they can play, $\ai = \{a^i_i, a^i_2, ..., a^i_{m_i}\}$.
-The payoff for an individual $i$ depends on what everyone plays and is represented by $\pi^i(a^1, a^2, ..., a^N)$, where $(a^1, a^2,...,a^N) \in \mathbf{A}^1 \times \mathbf{A}^2 \times ...
-\times \mathbf{A}^N$.
+Each player, $i$, has access to their action set, $\A^i$, in which there are $m_i$ possible actions that they can play, $\A^i = \{a^i_i, a^i_2, ..., a^i_{m_i}\}$.
+The payoff for an individual $i$ depends on what everyone plays and is represented by $\pi^i(\abf^1, \abf^2, ..., \abf^N)$, where $\abf := (\abf^1, \abf^2,...,\abf^N) \in \A^1 \times \A^2 \times ...
+\times \A^N$ represents a state of the game.
 In this model we only consider pure strategies for players.
 So, player $i$ has only $m_i$ possible strategies.
+Therefore, the total number of states possible for the game is the product of all $m_i$.
+\\ \\
+\noindent We represent a state of the game, $\abf$, from the perspective of player $j$ as $\abf =: (\abf^j, \abf^{-j})$.
+In the state $(\abf^j, \abf^{-j})$, player $j$ plays the action $\abf^j \in \A^j$ and all the other co-players of $j$ play $\abf^{-j} \in \Pi_{k \neq j} \A^k$.
+The payoff of player $j$ in this state is also represented as $\pi^j(\abf^j, \abf^{-j})$.
+\\ \\
+\noindent The players update their strategies over time using the introspection dynamics \cite{couto2022introspection}.
+At every time step, one randomly chosen player can update their strategy.
+The randomly chosen player, say $j$, currently playing strategy $a^j_k$, compares their current payoff to all the payoffs they can achieve if they played an alternate action from their action set $\A^j$.
+This comparison is done while assuming that the co-players do not change from $\abf^{-j}$.
+Then, they adopt a new strategy $a^j_l \neq a^j_k$ with the probability:
 
-\noindent The players update their strategies over time using the introspection dynamics \cite{couto2022introspection}.
+\begin{equation}
+ p^j_{a^j_k \to a^j_l} (\abf^{-j})= \frac{1}{1 + e^{\displaystyle -\beta(\pi^j(a^j_l, \abf^{-j}) - \pi^j(a^j_k, \abf^{-j}))}}
+ \label{Eq:introspection-update}
+\end{equation}
+\\
+\noindent Where $\beta$ is the selection parameter. The probability that no update is made by the randomly chosen player is given by the normalization condition:
+
+\begin{equation}
+ p^j_{a^j_k \to a^j_k} (\abf^{-j}) = 1 - \sum_{k \neq l} p^j_{a^j_k \to a^j_l} (\abf^{-j})
+ \label{Eq:introspection-normalization}
+\end{equation}
+\\ 
+\noindent Now, with the help of Eq.
+\ref{Eq:introspection-update} and \ref{Eq:introspection-normalization}, we can define the transition matrix $\T$ of the process.
+The transition matrix is a square matrix of size $\Pi_i m_i$.
+The element $\T_{\abf_p, \abf_q}$ of the matrix represents the probability that the game will go to state $\abf_q$ from state $\abf_p$ in a time step.
+Before defining the transition matrix, we define the notion of neighbouring states.
+
+\begin{definition}
+\textbf{Neighbouring states}: \\ The state $\abf_q \in \mathit{Neb}(\abf_p)$, the neighbourhood of state $\abf_p$, if and only if $\exists j$ such that $\abf_p^{-j} = \abf_q^{-j}$ and $\abf_p^{j} \neq \abf_q^{j}$.
+\label{Def:neighbourhood-states}
+\end{definition}
+\noindent Note that if $\abf_q \in \mathit{Neb}(\abf_p)$ then by definition $\abf_p \in \mathit{Neb}(\abf_q)$.
+We give an example to explain the notion of neighbourhood.
+Consider three players, player $1,2$ and $3$.
+Each of these players choose actions from an identical binary action set $\{\mathit{0},\mathit{1}\}$.
+In this example, the state $(\mathit{0}, \mathit{0}, \mathit{0})$ is a neighbour of $(\mathit{0}, \mathit{0}, \mathit{1})$ and vice versa.
+The index of difference between the two states is player $3$.
+The states  $(\mathit{0}, \mathit{0}, \mathit{0})$ and $(\mathit{0}, \mathit{1}, \mathit{1})$ are not neighbouring states because more than one player's action are changed.
+
+\begin{definition}
+\textbf{Index of difference for neighbouring states}: \\ \\ If the states $\abf_p$ and $\abf_q$ are neighbours then, the unique $j$ for which $\abf_p^{j} \neq \abf_q^{j}$, is called the index of difference.
+Or $I(\abf_p,\abf_q) := j$
+\label{Def:index-of-difference}
+\end{definition}
+\noindent For the earlier example, let $\abf_p = (\mathit{0}, \mathit{0}, \mathit{0})$ and $\abf_q = (\mathit{0}, \mathit{0}, \mathit{1})$. Then, $I(\abf_p,\abf_q) = 3$. 
+\\ \\ 
+Using the above definitions of neighbourhood and index of difference, we can define the transition matrix $\T$ for the process as the follows: 
+\begin{align}
+\T_{\abf_p,\abf_q} = 
+\begin{cases}
+\frac{1}{N}  \cdot p^j_{\abf^j_p \to \abf^j_q} (\abf_p^{-j}) \quad  \quad &\abf_p \in \mathit{Neb}(\abf_q) \quad \text{and,} \quad j = I(\abf_p,\abf_q)\\ \\ 
+0 \quad & \abf_{p} \notin \mathit{Neb}(\abf_q) \\ \\
+1 - \sum_{\forall \abf_k \neq \abf_p} \T_{\abf_p,\abf_k} \quad &\abf_p = \abf_q
+\end{cases}
+\label{Eq:transition-matrix}
+\end{align}
+\noindent The stochastic transition matrix $\T$ is row-stochastic.
+This implies that its stationary distribution is a left eigenvector of $\T$ corresponding to eigenvalue $1$.
+We denote the stationary distribution of $\T$ as $\ubf$.
+Furthermore, since no state of the process is isolated (i.e., every state has atleast one neighbour), a finite $\beta$ assures that a state is reachable from any other state with positive probability in a finite number of steps.
+Therefore, $\T$ is also primitive.
+The stationary distribution $\ubf$ is unique and strictly positive (from the Perron-Frobenius Theorem).
+The following conditions are satisfied by the stationary distribution $\ubf$ when it is additionally also a probability distribution.
+
+\begin{eqnarray}
+\label{Eq:lefteigenvector}
+\ubf \T = \ubf \\ 
+\label{Eq:normalizationcondition}
+\ubf \cdot \mathbf{1} = 1
+\end{eqnarray}
 
 \section*{Examples of multiplayer games and results} 
+\subsection*{Linear public goods game}
+We consider the linear public goods game with $N$ asymmetric players.
+Each player has two possible actions, to contribute ($a=1$), or to not contribute ($a=0$).
+The players differ in their cost of cooperation and their productivities.
+The cost of cooperation and the productivity of a player $i$ are denoted by $c_i$ and $r_i$.
+The payoff for player $i$ when the state of the game is $\abf$ is given by:
+
+\begin{equation}
+\pi^i(\abf) = \sum_{j=1}^N \frac{\displaystyle r_j a_j c_j}{N} - a_i c_i
+\label{Eq:linear-pgg-payoff}
+\end{equation}
+
+\noindent The difference in payoffs between playing the two actions in a linear public goods game is independent of what the other co-players play in the game. That is,
+
+\begin{equation}
+\pi^i(\abf^i = 0, \abf^{-i}) - \pi^i(\abf^i = 1, \abf^{-i}) = c_i \left(1 - \frac{r_i}{N} \right) =: f(c_i, r_i) 
+\label{Eq:difference-payoffs-lpgg}
+\end{equation}
+
+\noindent is independent of $\abf^{-i}$.
+This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r_i$ and number of players $N$.
+When $r_i < N$, the action of not contributing ($a = 0$) dominates the action of contributing ($a = 1$) and vice-versa.
+
+\begin{proposition}
+\label{prop:stationary-dist-lpgg}
+When $\beta$ is finite, the unique stationary distribution of an asymmetric linear public goods game under introspection dynamics is given by:
+
+\begin{equation}
+\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^j)\beta f(c_j, r_j )}} \quad ,\forall \abf \in \{0,1\}^N
+\label{Eq:stationary_dist_lpgg}
+\end{equation}
+where, 
+\begin{equation}
+\mathit{sign}(a) = 2a - 1
+\end{equation}
+\end{proposition}
+
+\section*{Appendix: Proofs}
+\begin{proof}
+\textbf{Proof of Proposition} \ref{prop:stationary-dist-lpgg} \\ 
+The stationary transition matrix $\T$ for the linear public goods game is primitive when $\beta$ is finite (i.e., there is a positive power $k$ such that $\T^k$ is a strictly positive matrix).
+Therefore, the stationary distribution of $\T$ will always be unique.
+We define the following short cut notations for the ease of the proof:
+\begin{eqnarray}
+&\bar{\abf}^j := \{0,1\} \setminus \abf^j  \\ 
+&p^j := \frac{1}{1 + \displaystyle e^{\beta f(c_j, r_j)}}
+\end{eqnarray}
+Using these notations and Eq.
+\ref{Eq:introspection-update} and \ref{Eq:difference-payoffs-lpgg} we can write the probability that a player $j$ updates from $\abf^j$ to $\bar{\abf}^j$ while their co-players play $\abf^{-j}$ as:
+\begin{equation}
+p^j_{\displaystyle \bar{\abf}^j  \to \abf^j} (\abf^{-j}) = p^j \mathit{sign}(\abf^j) + \bar{\abf}^j \\ \\
+\end{equation}
+The candidate stationary distribution $\ubf$ given in Eq \ref{Eq:stationary_dist_lpgg} can be written down using our shortcut notation as: 
+\begin{equation}
+\label{Eq:stationary-dist-shortcut}
+\ubf_\abf = \prod_{k = 1}^{N}  p^k \mathit{sign}(\abf^k) + \bar{\abf}^k \quad ,\forall \abf \in \{0,1\}^N
+\end{equation}
+This stationary distribution must satisfy the following properties, which are also given in Eq  \ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}:
+\begin{align}
+\label{Eq:transition-in-proof}
+&\ubf_a = \T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\ 
+\label{Eq:normalization-in-proof}
+&\sum_{\forall \abf_q} u_{\abf_q}= 1
+\end{align}
+Where, the terms in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified using Eq \ref{Eq:introspection-update} and \ref{Eq:transition-matrix} as follows:
+\begin{eqnarray}
+\T_{\abf,\abf} = 1 - \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}), (\bar{\abf}^k,\abf^{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \abf^k 
+\label{Eq:first-term-rhs-proof}
+\end{eqnarray} 
+and additionally, also using Eq. \ref{Eq:stationary-dist-shortcut} the second term can be simplified too:
+\begin{align}
+\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k = 1}^N \T_{(\bar{\abf}^k,\abf^{-k}), (\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k,\abf^{-k})} \\
+&= \frac{1}{N} \sum_{k = 1}^N \left(p^k \textit{sign}(\abf^k) + \bar{\abf}^k \right) \ubf_{(\bar{\abf}^k,\abf^{-k})} \\ 
+\label{Eq:second-term-rhs-proof}
+&= \frac{\ubf_\abf}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \abf^k 
+\end{align}
+Now, using Eq.
+\ref{Eq:first-term-rhs-proof}, \ref{Eq:second-term-rhs-proof} one can show that the right hand side of Eq.
+\ref{Eq:transition-in-proof} is the element of the stationary distribution, corresponding to the state $\abf$, $\ubf_a$.
+Now, to complete the proof, we must show that Eq.
+\ref{Eq:normalization-in-proof} is also true for our candidate stationary distribution.
+This can be done by decomposing the sum of the elements of the stationary distribution as follows:
+\begin{eqnarray}
+\sum_{\forall \abf_q} u_{\abf_q} =& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^N p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k \\
+=& \displaystyle \displaystyle \sum_{\forall \abf_q} (1-p^N)  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k  + p^N  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k \\ 
+=& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k
+\end{eqnarray}
+When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also normalized. 
+\end{proof}
 

### 2022-11-11 latex/supplementary.tex
proofs of the additive games added

@@
 The payoff for an individual $i$ depends on what everyone plays and is represented by $\pi^i(\abf^1, \abf^2, ..., \abf^N)$, where $\abf := (\abf^1, \abf^2,...,\abf^N) \in \A^1 \times \A^2 \times ...
-\times \A^N$ represents a state of the game.
+\times \A^N =: \A$ represents a state of the game.
 In this model we only consider pure strategies for players.
@@
 This implies that its stationary distribution is a left eigenvector of $\T$ corresponding to eigenvalue $1$.
-We denote the stationary distribution of $\T$ as $\ubf$.
+We denote the stationary distribution of $\T$ as $\ubf := (\ubf_{\abf})_{\abf \in \A}$.
 Furthermore, since no state of the process is isolated (i.e., every state has atleast one neighbour), a finite $\beta$ assures that a state is reachable from any other state with positive probability in a finite number of steps.
@@
 \end{eqnarray}
+
+\noindent The marginal distribution over the strategies of a player $j$ at the stationary distribution is given by $\mathbf{\xi}^j := (\mathbf{\xi}^j_{a^j_1}, \mathbf{\xi}^j_{a^j_2}, ..., \mathbf{\xi}^j_{a^j_{m_j}})$.
+This distribution indicates the probability with which player $j$ plays strategies from their action set $\A^j$ at the stationary distribution.
+The relationship between the marginal distribution and the stationary distribution is given by:
+
+\begin{equation}
+\mathbf{\xi}^j_{a^j_k} := \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(a^j_k, \mathbf{b})}
+\label{Eq:marginal-definition}
+\end{equation}
+
+\noindent Where, $\A^{-j} = \prod_{l \neq j} \A^l$. One can note that the marginal distribution is also a probability distribution. That is, for all $j$:
+
+\begin{equation}
+\sum_{a' \in \A^j} \xi^j_{a'}= 1
+\label{Eq:marginal-prob-dist}
+\end{equation}
+
+\subsection*{Additive games and their properties under introspection dynamics}
+
+In this subsection we discuss a special class of general multiplayer games: additive games \cite{mcavoy2015asymmetric} and some of their properties under the introspection dynamics.
+Additive games are games where the payoff earned by a player $j$ in the state $\abf$ can be broken down into two-components - one which is only dependent on what player $j$ played in the state: $\abf^j$ and the other which only depends on what their co-players $-j$ played in the state: $\abf^{-j}$ .
+That is, for all players $j$,
+
+\begin{equation}
+\pi^j(\abf) = \pi^j_{\abf^j} + \pi^j_{\abf^{-j}}
+\label{Eq:additive games}
+\end{equation}
+
+\noindent holds.
+In additive games, the payoff difference earned by a player when they switch between two strategies in their action set is independent of what other co-players are playing (given all other co-players do not change their strategies).
+That is, for all $j$ and any pair of strategies $a^j_p, a^j_q\in \A^j$,
+
+\begin{equation}
+\pi^j(a^j_p, \mathbf{b}) - \pi^j(a^j_q, \mathbf{b}) = \pi^j_{a^j_p} - \pi^j_{a^j_q}
+\label{Eq:additive games property}
+\end{equation}
+
+\noindent holds for any $\mathbf{b} \in \prod_{l \neq j} \A^l$. 
+\\ \\
+We see an example of additive game in the next section.
+Under introspection dynamics, stationary distribution and marginal distributions from additive games show interesting properties.
+They are discussed in the theorems below:
+
+\begin{theorem}
+When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of an N-player additive game under the introspection dynamics is given by: 
+\begin{equation}
+\ubf_a = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
+\label{Eq:additive-game-stationary-distribution}
+\end{equation}
+where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they switch their play to $a'$ from $\abf^j$ while their co-players do not change their respective plays.
+\label{Th:additive-games-stationary-dist}
+\end{theorem}
+
+\begin{theorem}
+Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of an N-player additive game under the introspection dynamics with finite $\beta$.
+Then, $\ubf_\abf$ is the product of elements of the marginal distributions that correspond to the actions that the players play in state $\abf$.
+That is,
+
+\begin{equation}
+\ubf_\abf = \prod_{j = 1}^N \xi^j_{\abf^j}
+\label{Eq:additive-game-products}
+\end{equation}
+
+\noindent and, the marginal $\xi^j_{\abf^j}$ is given by:
+
+\begin{equation}
+\xi^j_{\abf_j} = \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
+\label{Eq:marginal-at-additive-game}
+\end{equation}
+\noindent where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they switch their play to $a'$ from $\abf^j$ while their co-players do not change their respective plays.
+\label{Th:additive-game-product-of-marginals}
+\end{theorem}
+
+\noindent In other words, the above theorem states that for additive games, the frequency that the game will be in state $\abf = (\abf^1, \abf^2, ...,\abf^N)$ under the finite selection introspection dynamics, is the product of the probabilities that the players respectively adopt the action $\abf^j$ which appear in this state $\abf$.
+\\ \\
+\noindent To elucidate this result further, we use an example of a 2-player additive game where each player has three possible actions from the action set $\{\mathit{0},\mathit{1},\mathit{2}\}$.
+The result says that the expected frequency of the state $(\mathit{0,2})$, say, where player 1 and player 2 simultaneously play $\mathit{0}$ and $\mathit{2}$ respectively: $\ubf_{(\mathit{0,2})}$, is the product of the marginal probabilities that the first player plays $\mathit{0}$ and the second player plays $\mathit{2}$ in the game.
+That is,
+
+\begin{equation}
+\ubf_{(\mathit{0,2})} = \xi^1_{\mathit{0}}  \xi^2_{\mathit{2}} = (\ubf_{(\mathit{0,0})} + \ubf_{(\mathit{0,1})} + \ubf_{(\mathit{0,2})})(\ubf_{(\mathit{0,2})} + \ubf_{(\mathit{1,2})} + \ubf_{(\mathit{2,2})})
+\label{Eq:additive-stationary-dist-example}
+\end{equation}
+\\
+\noindent As stated in the theorem above, this result holds for any additive game with arbitrary number of players and each player having arbitrary action sets.
 
@@
 \noindent is independent of $\abf^{-i}$.
+The linear public goods game is therefore an example of an additive game.
 This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r_i$ and number of players $N$.
@@
 
-\begin{proposition}
+\begin{lemma}
 \label{prop:stationary-dist-lpgg}
@@
 \end{equation}
-\end{proposition}
+\end{lemma}
 
 \section*{Appendix: Proofs}
+
 \begin{proof}
-\textbf{Proof of Proposition} \ref{prop:stationary-dist-lpgg} \\ 
+\textbf{Proof of Theorem} \ref{Th:additive-games-stationary-dist} \\ \\ 
+Since $\beta$ is finite, the transition matrix of the process $\T$ given by Eq.
+\ref{Eq:transition-matrix} is primitive and therefore, the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the row-stochastic transition matrix is unique and satisfies the conditions laid out in Eq.
+\ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}.
+To continue for the rest of the proof, we introduce some short-cut notation that will be of use later in the proof:\\
+\begin{align}
+I_{q} &:= I(\abf_q,\abf), \quad \mathit{iff} \quad \abf_q \in \mathit{Neb}(\abf) \\ \notag \\ 
+\label{Eq:shortcut-tau}
+\tau^j_{\abf^j} &:= \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
+\end{align}
+\noindent In order to show that the candidate stationary distribution, as proposed in Eq.
+\ref{Eq:additive-game-stationary-distribution} is the stationary distribution of the process, we need to show that the following are true:
+\begin{eqnarray}
+\label{step-one}
+\T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} = \ubf_a \quad \forall \abf \in \A \\ 
+\label{step-two}
+\sum_{\abf \in \A} \ubf_\abf  = 1
+\end{eqnarray}
+The Eq \ref{step-one} can be simplified further with the steps: 
+\begin{align}
+&\T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} = \\
+& \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)} p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
+\label{eq:important-step}
+& \ubf_\abf +  \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \left( \prod_{k \neq I_q} \tau^k_{\abf^k} \right) \left( p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} \right)
+\end{align}
+\\ Using the definition of probability of update of the introspection dynamics, as given by Eq. \ref{Eq:introspection-update} and Eq. \ref{Eq:shortcut-tau}, it can be shown that: 
+\begin{equation}
+p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} = 0
+\label{important-step-is-zero}
+\end{equation}
+\\ \noindent Plugging the equality in Eq.
+\ref{important-step-is-zero} into Eq.
+\ref{eq:important-step}, we can see that the left hand side of Eq.
+\ref{step-one} indeed simplifies to $\ubf_{\abf}$.
+Now, to confirm that the candidate $\ubf$ is the unique stationary distribution we need to check if Eq.
+\ref{step-two} holds.
+Simplifying the left hand side of this equation shows that:
+\begin{align}
+\sum_{\abf \in \A} \ubf_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau^k_{\abf^k} \\ \notag \\
+\label{step-prod-sum-sum-prod}
+&= \left( \prod_{k=1}^N \sum_{\abf' \in \A} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\abf \in \A} \prod_{k=1}^N \displaystyle e^{\beta \pi^k_{\abf^k}} \right) \\ \notag \\
+\label{step-prod-is-one}
+&= 1
+\end{align}
+\noindent The step from Eq.
+\ref{step-prod-sum-sum-prod} to Eq \ref{step-prod-is-one} is possible because the sum and product in Eq.
+\ref{step-prod-sum-sum-prod} are interchangeable for both the terms.
+Therefore, condition Eq.
+\ref{step-two} is satisfied too.
+\end{proof}
+
+\begin{proof}
+\textbf{Proof of Theorem} \ref{Th:additive-game-product-of-marginals} \\ \\ 
+If $\ubf$ is the unique stationary distribution of the additive game with $N-$players under finite selection introspection dynamics, it is given by the expression in Eq.
+\ref{Eq:additive-game-stationary-distribution}.
+We calculate the marginal distribution of any arbitrary state $\abf$, $\xi_{\abf} = (\xi^j_{\abf^j})_{j = 1,2,...,N}$ by using the definition of marginal distribution in Eq.
+\ref{Eq:marginal-definition}.
+It follows that:
+\begin{align}
+\xi^j_{\abf^j} &= \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(\abf^j,\mathbf{b})} \\ \notag \\
+&= \left( \prod_{k=1}^N \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
+&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \prod_{k\neq j} \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
+&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\abf' \in \A^{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
+&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \left( \pi^j_{\abf'} - \pi^j_{\abf^j}\right)}\right)^{-1}
+\end{align}
+\noindent Therefore, the marginal distribution follows Eq.
+\ref{Eq:marginal-at-additive-game}.
+Now since we also additionally know that the stationary distribution follows the form Eq.
+\ref{Eq:additive-game-stationary-distribution}, we can conclude that for additive games, under introspection dynamics with finite selection, Eq.
+\ref{Eq:additive-game-products} holds.
+\end{proof}
+\clearpage
+\newpage
+\begin{proof}
+\textbf{Proof of lemma} \ref{prop:stationary-dist-lpgg} \\ 
 The stationary transition matrix $\T$ for the linear public goods game is primitive when $\beta$ is finite (i.e., there is a positive power $k$ such that $\T^k$ is a strictly positive matrix).

### 2022-11-14 latex/supplementary.tex
fixed the supplementary by adding normalization to transition matrices - Sap

@@
 At every time step, one randomly chosen player can update their strategy.
-The randomly chosen player, say $j$, currently playing strategy $a^j_k$, compares their current payoff to all the payoffs they can achieve if they played an alternate action from their action set $\A^j$.
+The randomly chosen player, say $j$, currently playing strategy $a^j_k$, compares their current payoff to the payoff that they would obtain if they played a randomly selected strategy,  $a^j_l \neq a^j_k$, from their action set $\A^j$.
 This comparison is done while assuming that the co-players do not change from $\abf^{-j}$.
-Then, they adopt a new strategy $a^j_l \neq a^j_k$ with the probability:
+Then, they adopt this new strategy  with the probability:
 
@@
 \begin{cases}
-\frac{1}{N}  \cdot p^j_{\abf^j_p \to \abf^j_q} (\abf_p^{-j}) \quad  \quad &\abf_p \in \mathit{Neb}(\abf_q) \quad \text{and,} \quad j = I(\abf_p,\abf_q)\\ \\ 
+\frac{1}{N(m_j-1)}  \cdot p^j_{\abf^j_p \to \abf^j_q} (\abf_p^{-j}) \quad  \quad &\abf_p \in \mathit{Neb}(\abf_q) \quad \text{and,} \quad j = I(\abf_p,\abf_q)\\ \\ 
 0 \quad & \abf_{p} \notin \mathit{Neb}(\abf_q) \\ \\
@@
 &\T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} = \\
-& \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)} p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
+& \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)}  \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
 \label{eq:important-step}
-& \ubf_\abf +  \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \left( \prod_{k \neq I_q} \tau^k_{\abf^k} \right) \left( p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} \right)
+& \ubf_\abf +  \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \left( \prod_{k \neq I_q} \tau^k_{\abf^k} \right) \left( p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} \right) \cdot \left(  \frac{1}{m^{I_q}-1} \right)
 \end{align}
@@
 \end{proof}
-\clearpage
-\newpage
+
 \begin{proof}
-\textbf{Proof of lemma} \ref{prop:stationary-dist-lpgg} \\ 
-The stationary transition matrix $\T$ for the linear public goods game is primitive when $\beta$ is finite (i.e., there is a positive power $k$ such that $\T^k$ is a strictly positive matrix).
+\textbf{Proof of lemma} \ref{prop:stationary-dist-lpgg} \\ \\
+Since we have demonstrated that the linear public goods game is an additive game, the proof of this theorem can be performed by directly using Theorem \ref{Th:additive-games-stationary-dist}.
+Here, we provide an independent proof.
+The idea behind this proof is identical to the proof of Theorem \ref{Th:additive-games-stationary-dist}.
+\\ \\
+\noindent The stationary transition matrix $\T$ for the linear public goods game is primitive when $\beta$ is finite (i.e., there is a positive power $k$ such that $\T^k$ is a strictly positive matrix).
 Therefore, the stationary distribution of $\T$ will always be unique.

### 2023-01-23 latex/supplementary.tex
Latex and Notebook changes till 23rd Jan

@@
 \newcommand{\ubf}{\mathbf{u}}
+\newcommand{\C}{\mathrm{C}}
+\newcommand{\D}{\mathrm{D}}
 
@@
 \section*{The general model for introspection dynamics}
-We consider an asymmetric normal form game with $N (>2)$ players.
-Each player, $i$, has access to their action set, $\A^i$, in which there are $m_i$ possible actions that they can play, $\A^i = \{a^i_i, a^i_2, ..., a^i_{m_i}\}$.
+We consider a normal form game with $N (>2)$ players.
+Each player, $i$, has access to their action set, $\A^i$, in which there are $m^i$ possible actions that they can play, $\A^i = \{a^i_1, a^i_2, ..., a^i_{m^i}\}$.
 The payoff for an individual $i$ depends on what everyone plays and is represented by $\pi^i(\abf^1, \abf^2, ..., \abf^N)$, where $\abf := (\abf^1, \abf^2,...,\abf^N) \in \A^1 \times \A^2 \times ...
@@
 In this model we only consider pure strategies for players.
-So, player $i$ has only $m_i$ possible strategies.
-Therefore, the total number of states possible for the game is the product of all $m_i$.
+So, player $i$ has only $m^i$ possible strategies.
+Therefore, the total number of states possible for the game is the product of all $m^i$.
 \\ \\
@@
 \ref{Eq:introspection-update} and \ref{Eq:introspection-normalization}, we can define the transition matrix $\T$ of the process.
-The transition matrix is a square matrix of size $\Pi_i m_i$.
+The transition matrix is a square matrix of size $M = m^1 \times m^2 \times ...
+\times m^N$.
 The element $\T_{\abf_p, \abf_q}$ of the matrix represents the probability that the game will go to state $\abf_q$ from state $\abf_p$ in a time step.
@@
 \begin{theorem}
-When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of an N-player additive game under the introspection dynamics is given by: 
+When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
 \begin{equation}
@@
 \end{equation}
-where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they switch their play to $a'$ from $\abf^j$ while their co-players do not change their respective plays.
+where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$.
 \label{Th:additive-games-stationary-dist}
 \end{theorem}
+\noindent The above theorem gives a closed form expression of the stationary distribution of the introspection dynamics for additive multiplayer games.
+For any finite value of the selection parameter, $\beta$, the stationary distribution can be analytically calculated using the expression in Eq.
+(\ref{Eq:additive-game-stationary-distribution}).
+The expression is derived by assuming that the update process of the introspection dynamics is governed by Eq.
+(\ref{Eq:introspection-update}) and (\ref{Eq:introspection-normalization}).
+For proof, see Appendix \ref{Section:Appendix}.
 
 \begin{theorem}
-Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of an N-player additive game under the introspection dynamics with finite $\beta$.
-Then, $\ubf_\abf$ is the product of elements of the marginal distributions that correspond to the actions that the players play in state $\abf$.
+Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game.
+Then, $\ubf_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$.
 That is,
@@
 
-\noindent and, the marginal $\xi^j_{\abf^j}$ is given by:
+\noindent where the marginal probability, $\xi^j_{\abf^j}$, is the cumulative probability that player $j$ plays $\abf^j$ at the stationary distribution. The marginal probability is given by:
 
@@
 \end{equation}
-\noindent where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they switch their play to $a'$ from $\abf^j$ while their co-players do not change their respective plays.
+\noindent where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$ in an additive game.
 \label{Th:additive-game-product-of-marginals}
@@
 
-\noindent In other words, the above theorem states that for additive games, the frequency that the game will be in state $\abf = (\abf^1, \abf^2, ...,\abf^N)$ under the finite selection introspection dynamics, is the product of the probabilities that the players respectively adopt the action $\abf^j$ which appear in this state $\abf$.
+\noindent In other words, the above theorem states for additive games, the probability that the game will be in state $\abf = (\abf^1, \abf^2, ...,\abf^N)$ in the long run (considering a finite selection strength introspection dynamics) is the product of the cumulative probabilities that each player $j$ respectively adopts the action $\abf^j$ in the stationary distribution.
 \\ \\
@@
 
-\section*{Examples of multiplayer games and results} 
-\subsection*{Linear public goods game}
+\subsection*{Example of multiplayer additive game: linear public goods game}
 We consider the linear public goods game with $N$ asymmetric players.
-Each player has two possible actions, to contribute ($a=1$), or to not contribute ($a=0$).
+Each player has two possible actions, to contribute (action, $\C$), or to not contribute (action, $\D$).
 The players differ in their cost of cooperation and their productivities.
-The cost of cooperation and the productivity of a player $i$ are denoted by $c_i$ and $r_i$.
+The cost of cooperation and the productivity of a player $i$ are denoted by $c^i$ and $r^i$.
 The payoff for player $i$ when the state of the game is $\abf$ is given by:
@@
 \begin{equation}
-\pi^i(\abf) = \sum_{j=1}^N \frac{\displaystyle r_j a_j c_j}{N} - a_i c_i
+\pi^i(\abf) = \sum_{j=1}^N \frac{\displaystyle r^j a^j c^j}{N} - a^i c^i
 \label{Eq:linear-pgg-payoff}
 \end{equation}
-
+\\
 \noindent The difference in payoffs between playing the two actions in a linear public goods game is independent of what the other co-players play in the game. That is,
@@
 \begin{equation}
-\pi^i(\abf^i = 0, \abf^{-i}) - \pi^i(\abf^i = 1, \abf^{-i}) = c_i \left(1 - \frac{r_i}{N} \right) =: f(c_i, r_i) 
+\pi^i(\abf^i = \D, \abf^{-i}) - \pi^i(\abf^i = \C, \abf^{-i}) = c^i \left(1 - \frac{r^i}{N} \right) =: f(c^i, r^i) 
 \label{Eq:difference-payoffs-lpgg}
 \end{equation}
-
+\\
 \noindent is independent of $\abf^{-i}$.
 The linear public goods game is therefore an example of an additive game.
-This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r_i$ and number of players $N$.
-When $r_i < N$, the action of not contributing ($a = 0$) dominates the action of contributing ($a = 1$) and vice-versa.
-
+This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r^i$ and number of players $N$.
+When $r^i < N$, the action of not contributing ($\D$) dominates the action of contributing ($\C$) and vice-versa.
+\\
 \begin{lemma}
 \label{prop:stationary-dist-lpgg}
-When $\beta$ is finite, the unique stationary distribution of an asymmetric linear public goods game under introspection dynamics is given by:
-
+When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for an asymmetric linear public goods game under introspection dynamics is given by: 
+\\
 \begin{equation}
-\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^j)\beta f(c_j, r_j )}} \quad ,\forall \abf \in \{0,1\}^N
+\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^j)\beta f(c^j, r^j )}} \quad ,\forall \abf \in \{\C, \D\}^N
 \label{Eq:stationary_dist_lpgg}
@@
 \begin{equation}
-\mathit{sign}(a) = 2a - 1
+\label{Eq:sign-function}
+\mathit{sign}(a) =
+\begin{cases}
+1& \quad \text{if} \quad a = \C \\
+-1& \quad \text{if} \quad a = \D
+\end{cases}
+\end{equation}
+\end{lemma}
+
+\section*{Symmetric multiplayer games with two strategies}
+
+In the previous section we looked at properties of the stationary distribution of the introspection dynamics for additive games.
+In this section we look at properties of the stationary distribution for any multiplayer game where players are symmetric and have two actions in their action set.
+A $N-$player symmetric normal form game satisfies the following properties:
+
+\begin{enumerate}
+\item $\A^1 = \A^2 = ... = \A^N = \mathcal{A}$, and
+\item For any $i, j \in \{1,2,...,N\}, a \in \mathcal{A}$ and $\mathbf{b} \in \displaystyle \prod_{k=1}^{N-1} \mathcal{A}$: 
+\begin{equation}
+\pi^i(a, \mathbf{b}) = \pi^j(a, \mathbf{b})
+\end{equation}
+\end{enumerate}
+
+\noindent In addition, when there are only two actions in the action set of players we define the action set in the same way as we did in the section of linear public goods game: $\mathcal{A} := \{\C, \D\}$.
+Since all players are symmetric in the two-action game, the number of states of the game can be reduced from  $2^N$ to $N+1$.
+Now, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
+For the sake of notational simplicity, we denote the payoffs of a $\C$ and $\D$ player in the state $k$ as $\pi^{\C}(k)$ and $\pi^{\D}(k)$ respectively.
+
+%We define following mapping function:  
+%
+%\begin{equation}
+%e(a^i):= 
+%\begin{cases}
+%1 \quad \text{if} \quad a^i = a_\C \\
+%0 \quad \text{if} \quad a^i = a_\D  
+%\end{cases}
+%\end{equation}
+%\\
+%We define $N_\C(\abf)$ as the number of $\C$ players in a state $\abf$. That is, 
+%
+%\begin{equation}
+%N_\C(\abf) := \sum_{i = 1}^N e(\abf^i)
+%\end{equation}
+%\noindent 
+%\\
+\begin{lemma}
+When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{a_\C, a_\D \}$, is given by:
+\begin{equation}
+\label{Eq:stationary-dist-symm-2-stgs}
+\ubf_k = \frac{1}{T(k)} \cdot {N \choose k} \cdot \displaystyle \prod_{j=0}^{k} \displaystyle e^{\beta f(j-1)}
+\end{equation}
+where, $f(j) := \pi^\D(k+1) - \pi^\C(k)$ and $T(k)$ is the normalization factor, given by,
+\begin{equation}
+\label{Eq:normalization-Tk}
+T(k) = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=0}^{k} \displaystyle e^{\beta f(j-1)}
 \end{equation}
@@
 \section*{Appendix: Proofs}
-
+\label{Section:Appendix}
 \begin{proof}
@@
 \label{step-one}
-\T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} = \ubf_a \quad \forall \abf \in \A \\ 
+\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \ubf_a \quad \forall \abf \in \A \\ 
 \label{step-two}
@@
 \begin{align}
-&\T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} = \\
+&\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \\
 & \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)}  \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
@@
 \textbf{Proof of Theorem} \ref{Th:additive-game-product-of-marginals} \\ \\ 
-If $\ubf$ is the unique stationary distribution of the additive game with $N-$players under finite selection introspection dynamics, it is given by the expression in Eq.
+If $\ubf$ is the unique stationary distribution of the $N-$player additive game with under the finite selection introspection dynamics, it is given by the expression in Eq.
 \ref{Eq:additive-game-stationary-distribution}.
@@
 \begin{eqnarray}
-&\bar{\abf}^j := \{0,1\} \setminus \abf^j  \\ 
-&p^j := \frac{1}{1 + \displaystyle e^{\beta f(c_j, r_j)}}
+&\bar{\abf}^j := \{a_\D,a_\C\} \setminus \abf^j  \\ 
+&p^j := \frac{1}{1 + \displaystyle e^{\beta f(c^j, r^j)}}
 \end{eqnarray}
@@
 \label{Eq:transition-in-proof}
-&\ubf_a = \T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\ 
+&\ubf_\abf = \T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\ 
 \label{Eq:normalization-in-proof}
@@
 \end{eqnarray}
-When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also normalized. 
+When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also a probability distribution.
 \end{proof}

### 2023-01-30 latex/supplementary.tex
added proofs for symmetric games 2 strategies

@@
 \newtheorem{proposition}{Proposition}
-\newtheorem{Cor}{Corollary}
+\newtheorem{Corollary}{Corollary}
 
@@
 
-\begin{theorem}
+\begin{Prop}
 When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
@@
 \label{Th:additive-games-stationary-dist}
-\end{theorem}
+\end{Prop}
 \noindent The above theorem gives a closed form expression of the stationary distribution of the introspection dynamics for additive multiplayer games.
@@
 
-\begin{theorem}
+\begin{Prop}
 Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game.
@@
 \label{Th:additive-game-product-of-marginals}
-\end{theorem}
+\end{Prop}
 
@@
 \\
-\begin{lemma}
+\begin{Prop}
 \label{prop:stationary-dist-lpgg}
@@
 \end{equation}
-\end{lemma}
+\end{Prop}
 
@@
 \noindent In addition, when there are only two actions in the action set of players we define the action set in the same way as we did in the section of linear public goods game: $\mathcal{A} := \{\C, \D\}$.
-Since all players are symmetric in the two-action game, the number of states of the game can be reduced from  $2^N$ to $N+1$.
+\subsection*{Notations}
+We introduce some notations before presenting the results
+\begin{enumerate}
+
+\item We denote the payoffs of a $\C$ and $\D$ player when they have $j$ co-players playing $\C$, as $\pi^{\C}(j)$ and $\pi^{\D}(j)$ respectively. 
+\item We define a simple mapping function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to $0$. That is, 
+\begin{equation}
+\alpha(a):= 
+\begin{cases}
+1 \quad \text{if} \quad a = \C \\
+0 \quad \text{if} \quad a = \D  
+\end{cases}
+\end{equation}
+\item For every state $\abf \in \mathcal{A}^N$, we count the number of $\C$ players in the state and denote it with $\mathcal{C}(\abf)$. That is, 
+\begin{equation}
+\mathcal{C}(\abf) := \sum_{j=1}^N \alpha(\abf^j)
+\end{equation}
+\end{enumerate}
+\newpage
+\begin{Prop}
+\label{Prop:Symmetric-2-strategies-state}
+When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\ubf_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
+\begin{equation}
+\label{Eq:stationary-dist-symm-2-stgs-state}
+\ubf_\abf = \frac{1}{\Gamma} \displaystyle \prod_{j=1}^{\mathcal{C}(\abf)} \displaystyle e^{-\beta f(j-1)}
+\end{equation}
+where $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$. The term $\Gamma$ is the normalization factor given by:
+\begin{equation}
+\label{Eq:stationary-dist-normalization-symm-2-stgs-state}
+\Gamma = \displaystyle \sum_{\forall \abf' \in \mathcal{A}^N} \prod_{j = 1}^{\mathcal{C}(\abf')} \displaystyle e^{-\beta f(j-1)}
+\end{equation}
+\end{Prop}
+
+\noindent The above proposition gives an exact closed form expression for the steady state distribution of the introspection dynamics for symmetric games with two strategies.
+Since all players are symmetric in this two strategy game, the number of unique states of the game can be reduced to $N+1$ from $2^N$.
 Now, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
-For the sake of notational simplicity, we denote the payoffs of a $\C$ and $\D$ player in the state $k$ as $\pi^{\C}(k)$ and $\pi^{\D}(k)$ respectively.
+Then, Proposition \ref{Prop:Symmetric-2-strategies-state} can be simplified by accounting for states with number of $\C$ players as follows:
 
-%We define following mapping function:  
-%
-%\begin{equation}
-%e(a^i):= 
-%\begin{cases}
-%1 \quad \text{if} \quad a^i = a_\C \\
-%0 \quad \text{if} \quad a^i = a_\D  
-%\end{cases}
-%\end{equation}
-%\\
-%We define $N_\C(\abf)$ as the number of $\C$ players in a state $\abf$. That is, 
-%
-%\begin{equation}
-%N_\C(\abf) := \sum_{i = 1}^N e(\abf^i)
-%\end{equation}
-%\noindent 
-%\\
-\begin{lemma}
-When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{a_\C, a_\D \}$, is given by:
+\begin{Corollary}
+\label{Lemma: Symmetric-2-stg}
+When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
 \begin{equation}
 \label{Eq:stationary-dist-symm-2-stgs}
-\ubf_k = \frac{1}{T(k)} \cdot {N \choose k} \cdot \displaystyle \prod_{j=0}^{k} \displaystyle e^{\beta f(j-1)}
-\end{equation}
-where, $f(j) := \pi^\D(k+1) - \pi^\C(k)$ and $T(k)$ is the normalization factor, given by,
+\ubf_k = \frac{1}{\Gamma} \cdot {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
+\end{equation} \\ 
+where, $k$ represents the number of $\C$ players in the state and $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$.
+The term $\Gamma$ is the normalization factor, given by, \\
 \begin{equation}
 \label{Eq:normalization-Tk}
-T(k) = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=0}^{k} \displaystyle e^{\beta f(j-1)}
+\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k+1  } \displaystyle e^{-\beta f(j-1)}
 \end{equation}
-\end{lemma}
-
+\end{Corollary}
+\noindent The above lemma follows directly from Proposition \ref{Prop:Symmetric-2-strategies-state}.
+The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$, $\C$ players and $N-k$, $\D$ players.
+This count is simply the binomal coefficient $N \choose k$.
+For details see the proof in the Appendix.
+\newpage 
 \section*{Appendix: Proofs}
@@
 \begin{proof}
-\textbf{Proof of Theorem} \ref{Th:additive-games-stationary-dist} \\ \\ 
+\textbf{Proof of Proposition} \ref{Th:additive-games-stationary-dist} \\ \\ 
 Since $\beta$ is finite, the transition matrix of the process $\T$ given by Eq.
@@
 \noindent The step from Eq.
-\ref{step-prod-sum-sum-prod} to Eq \ref{step-prod-is-one} is possible because the sum and product in Eq.
+\ref{step-prod-sum-sum-prod} to Eq.
+\ref{step-prod-is-one} is possible because the sum and product in Eq.
 \ref{step-prod-sum-sum-prod} are interchangeable for both the terms.
@@
 \begin{proof}
-\textbf{Proof of Theorem} \ref{Th:additive-game-product-of-marginals} \\ \\ 
+\textbf{Proof of Proposition} \ref{Th:additive-game-product-of-marginals} \\ \\ 
 If $\ubf$ is the unique stationary distribution of the $N-$player additive game with under the finite selection introspection dynamics, it is given by the expression in Eq.
@@
 \begin{proof}
-\textbf{Proof of lemma} \ref{prop:stationary-dist-lpgg} \\ \\
+\textbf{Proof of Proposition} \ref{prop:stationary-dist-lpgg} \\ \\
 Since we have demonstrated that the linear public goods game is an additive game, the proof of this theorem can be performed by directly using Theorem \ref{Th:additive-games-stationary-dist}.
@@
 \begin{eqnarray}
-&\bar{\abf}^j := \{a_\D,a_\C\} \setminus \abf^j  \\ 
-&p^j := \frac{1}{1 + \displaystyle e^{\beta f(c^j, r^j)}}
+\bar{\abf}^j &:= \{\D,\C\} \setminus \abf^j  \\ 
+p^j &:= \frac{1}{1 + \displaystyle e^{\beta f(c^j, r^j)}} 
 \end{eqnarray}
+In addition we introduce a mapping function $\alpha(.)$ which maps the action $\C$ to 1 and the action $\D$ to 0.
+That is $\alpha(\C) := 1$ and $\alpha(\D) := 0$.
 Using these notations and Eq.
-\ref{Eq:introspection-update} and \ref{Eq:difference-payoffs-lpgg} we can write the probability that a player $j$ updates from $\abf^j$ to $\bar{\abf}^j$ while their co-players play $\abf^{-j}$ as:
+\ref{Eq:introspection-update} and \ref{Eq:difference-payoffs-lpgg} we can write the probability that a player $j$ updates from $\abf^j$ to $\bar{\abf}^j$ while their co-players play $\abf^{-j}$ as: \\
 \begin{equation}
-p^j_{\displaystyle \bar{\abf}^j  \to \abf^j} (\abf^{-j}) = p^j \mathit{sign}(\abf^j) + \bar{\abf}^j \\ \\
+p^j_{\displaystyle \bar{\abf}^j  \to \abf^j} (\abf^{-j}) = p^j \mathit{sign}(\abf^j) + \alpha(\bar{\abf}^j) \\ \\
 \end{equation}
@@
 \label{Eq:stationary-dist-shortcut}
-\ubf_\abf = \prod_{k = 1}^{N}  p^k \mathit{sign}(\abf^k) + \bar{\abf}^k \quad ,\forall \abf \in \{0,1\}^N
+\ubf_\abf = \prod_{k = 1}^{N}  p^k \mathit{sign}(\abf^k) + \alpha(\bar{\abf}^k) \quad ,\forall \abf \in \{0,1\}^N
 \end{equation}
@@
 \label{Eq:transition-in-proof}
-&\ubf_\abf = \T_{\abf,\abf} \ubf_a  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\ 
+&\ubf_\abf = \T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\[10pt] 
 \label{Eq:normalization-in-proof}
-&\sum_{\forall \abf_q} u_{\abf_q}= 1
+&\sum_{\forall \abf_q} \ubf_{\abf_q}= 1
 \end{align}
@@
 \begin{eqnarray}
-\T_{\abf,\abf} = 1 - \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}), (\bar{\abf}^k,\abf^{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \abf^k 
+\T_{\abf,\abf} = 1 - \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}), (\bar{\abf}^k,\abf^{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \alpha(\abf^k)
 \label{Eq:first-term-rhs-proof}
@@
 \begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k = 1}^N \T_{(\bar{\abf}^k,\abf^{-k}), (\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k,\abf^{-k})} \\
-&= \frac{1}{N} \sum_{k = 1}^N \left(p^k \textit{sign}(\abf^k) + \bar{\abf}^k \right) \ubf_{(\bar{\abf}^k,\abf^{-k})} \\ 
+\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k = 1}^N \T_{(\bar{\abf}^k,\abf^{-k}), (\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k,\abf^{-k})} \\[10pt]
+&= \frac{1}{N} \sum_{k = 1}^N \left(p^k \textit{sign}(\abf^k) +\alpha(\bar{\abf}^k) \right) \ubf_{(\bar{\abf}^k,\abf^{-k})} \\[10pt] 
 \label{Eq:second-term-rhs-proof}
-&= \frac{\ubf_\abf}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \abf^k 
+&= \frac{\ubf_\abf}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \alpha(\abf^k) 
 \end{align}
@@
 This can be done by decomposing the sum of the elements of the stationary distribution as follows:
-\begin{eqnarray}
-\sum_{\forall \abf_q} u_{\abf_q} =& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^N p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k \\
-=& \displaystyle \displaystyle \sum_{\forall \abf_q} (1-p^N)  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k  + p^N  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k \\ 
-=& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \bar{\abf}_q^k
-\end{eqnarray}
+\begin{align}
+\sum_{\forall \abf_q} u_{\abf_q} =& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^N p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k) \\[10pt]
+=& \displaystyle \displaystyle \sum_{\forall \abf_q} (1-p^N)  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k)  + p^N  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k) \\[10pt]
+=& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k)
+\end{align}
 When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also a probability distribution.
@@
 
+\begin{proof}
+\textbf{Proof of Proposition} \ref{Prop:Symmetric-2-strategies-state} \\ \\
+By construction, the candidate stationary distribution given by Eq.
+\ref{Eq:stationary-dist-symm-2-stgs-state} and Eq.
+\ref{Eq:stationary-dist-normalization-symm-2-stgs-state} is a probability distribution since it satisfies the condition in Eq.
+\ref{Eq:normalizationcondition} and for any state $\abf'$, $\ubf_{\abf'}$ is between 0 and 1.
+Moreover, since $\beta$ is finite, the transition matrix of the process $\T$ is primitive and therefore, it will have a unique stationary distribution.
+To show that the candidate stationary distribution is the unique stationary distribution, we need to check if for this process, $\ubf \T= \ubf$.
+That is, the Eq.
+\ref{Eq:transition-in-proof} must hold.
+We re-introduce some notations that we will use in this proof:
+\begin{align}
+\bar{\abf}^j &:= \{\D,\C\} \setminus \abf^j \\[10pt]
+\alpha(a)&:= 
+\begin{cases}
+1 \quad \text{if} \quad a = \C \\[10pt]
+0 \quad \text{if} \quad a = \D 
+\end{cases}\\[10pt]
+\mathcal{C}(\abf) &= \sum_{j=1}^N \alpha(\abf^j)
+\end{align}
+For this process, the first term in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified as: 
+\begin{align}
+\ubf_{\abf} \T_{\abf,\abf}  &= \ubf_\abf - \ubf_{\abf} \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}),(\bar{\abf}^{k}, \abf^{-k})} \\[10pt]
+&= \ubf_{\abf} - \frac{\ubf_{\abf}}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}^{k}) \beta f(N_k)}}
+\label{Eq:T_aa_u_a term}
+\end{align}
+\\ \noindent Where, the function $\mathit{sign}(.)$ is  defined in Eq.
+\ref{Eq:sign-function} and$f(j)$ is the difference in payoffs between playing $\D$ and $\C$ when there are $j$ co-players playing $\C$.
+The term $N_k$ is the number of co-players of $k$ that play $\C$ in state $\abf_\C$.
+That is,
+\begin{equation}
+N_k := \sum_{j \neq k} \alpha(\abf^l)
+\end{equation}
+The second term in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified as, 
+\begin{align}
+\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k, \abf^{-k})} \\[10pt]
+\label{Eq:step-single-product}
+&= \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \prod_{j=1}^{\mathcal{C}((\bar{\abf}^k, \abf^{-k}))} e^{-\beta f(j-1)}\\[10pt]
+&=  \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \left( \prod_{j=1}^{\sum_{j \neq k} \alpha(\abf^l)}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ \sum_{j \neq k} \abf^l)}
+\label{Eq:step-product-broken}
+\end{align}
+Between the steps, Eq.
+\ref{Eq:step-single-product} and \ref{Eq:step-product-broken}, we took out one term from the product that is present in our candidate distribution.
+This term accounts for the $k^{th}$ players action in the state $(\bar{\abf}^k, \abf^{-k})$.
+For simplicity, we replace $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ with just $\T$ in the next steps and also denote the number of co-players of $k$ that play $\C$ in the state $\abf$ as $N_k$.
+\noindent We continue the simplification of Eq. \ref{Eq:step-product-broken} in the later steps by introducing terms that cancel each other. \\[10pt]
+\begin{align}
+\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \cdot e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) + N_k)}
+\label{Eq:new-cancelable-term-introduced}
+\end{align}
+\\ \noindent The newly introduced term in Eq.
+\ref{Eq:new-cancelable-term-introduced} can be taken inside the product.
+Note that this term is 0 if the $k^{th}$ player plays $\D$ in the state $\abf$.
+When this term is taken inside the product bracket, products of exponent $e^{-\beta f(j-1)}$ can be performed where $j$ ranges from $1$ to the number of cooperators in state $\abf$, $\mathcal{C}(\abf)$.
+This product is then the stationary distribution probability $\ubf_\abf$.
+That is,
+\begin{align}
+\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \cdot e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) + N_k)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \\[10pt]
+&= \frac{1}{N} \sum_{k=1}^N  \T \cdot \left( \frac{1}{\Gamma} \prod_{j=1}^{\mathcal{C}(\abf)} e^{-\beta f(j-1)}\right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \\[10pt]
+&= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \cdot \ubf_\abf \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \label{Eq: last-step-w-fraction}
+\end{align}
+\\ \noindent The fraction inside the sum in  Eq. \ref{Eq: last-step-w-fraction} can be simplified as follows leading to further simplification of Eq. \ref{Eq: last-step-w-fraction}:
+\begin{align}
+\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \cdot \ubf_\abf \cdot e^{sign(\abf^k) \beta f(N_k)} 
+\label{Eq:only-need-to-replace-T-now}
+\end{align}
+\\ \noindent In Eq. \ref{Eq:only-need-to-replace-T-now} we can replace the element of the transition matrix $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ by using the following: 
+\begin{equation}
+\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} = \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^k) \beta f(N_k)}} 
+\label{Eq:transition-matrix-T-symm-2-stgs}
+\end{equation}
+\\ \noindent Using the expression for the transition matrix element from Eq.
+\ref{Eq:transition-matrix-T-symm-2-stgs} into Eq.
+\ref{Eq:only-need-to-replace-T-now} and by using Eq.
+\ref{Eq:T_aa_u_a term}, we can simplify further:
+\begin{align}
+\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^k) \beta f(N_k)}} \cdot  e^{sign(\abf^k) \beta f(N_k)} \\[10pt]
+&= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}^k) \beta f(N_k)}}  \\[10pt]
+&= \ubf_\abf - \ubf_\abf \T_{\abf,\abf}
+\end{align}
+\\ \noindent The final step in the previous simplification shows that Eq.
+\ref{Eq:transition-in-proof} holds for any $\abf \in \{\C,\D\}^N$.
+Therefore, the candidate distribution we propose in Eq.
+\ref{Eq:stationary-dist-symm-2-stgs-state} is the unique stationary distribution of the symmetric $N$-player game with two strategies.
+\end{proof}
+
+\begin{proof}
+\textbf{Proof of Corollary} \ref{Lemma: Symmetric-2-stg} \\ \\
+
+\end{proof}
+\newpage
 \section*{Supplementary References}

### 2023-02-03 latex/supplementary.tex

@@
 \label{Eq:normalization-Tk}
-\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k+1  } \displaystyle e^{-\beta f(j-1)}
+\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
 \end{equation}
@@
 To show that the candidate stationary distribution is the unique stationary distribution, we need to check if for this process, $\ubf \T= \ubf$.
-That is, the Eq.
-\ref{Eq:transition-in-proof} must hold.
+That is, the condition in Eq.
+\ref{Eq:transition-in-proof} must hold for all states $\abf$.
 We re-introduce some notations that we will use in this proof:
@@
 \end{align}
-\\ \noindent Where, the function $\mathit{sign}(.)$ is  defined in Eq.
+\\ \noindent Where, the function $\mathit{sign}(.)$ is  defined as in Eq.
 \ref{Eq:sign-function} and$f(j)$ is the difference in payoffs between playing $\D$ and $\C$ when there are $j$ co-players playing $\C$.
-The term $N_k$ is the number of co-players of $k$ that play $\C$ in state $\abf_\C$.
+The term $N_k$ is the number of co-players of $k$ that play $\C$ in state $\abf$.
 That is,
 \begin{equation}
-N_k := \sum_{j \neq k} \alpha(\abf^l)
+N_k := \sum_{j \neq k} \alpha(\abf^j)
 \end{equation}
@@
 &= \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \prod_{j=1}^{\mathcal{C}((\bar{\abf}^k, \abf^{-k}))} e^{-\beta f(j-1)}\\[10pt]
-&=  \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \left( \prod_{j=1}^{\sum_{j \neq k} \alpha(\abf^l)}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ \sum_{j \neq k} \abf^l)}
+&=  \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k}
 \label{Eq:step-product-broken}
@@
 \ref{Eq:step-single-product} and \ref{Eq:step-product-broken}, we took out one term from the product that is present in our candidate distribution.
-This term accounts for the $k^{th}$ players action in the state $(\bar{\abf}^k, \abf^{-k})$.
-For simplicity, we replace $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ with just $\T$ in the next steps and also denote the number of co-players of $k$ that play $\C$ in the state $\abf$ as $N_k$.
-\noindent We continue the simplification of Eq. \ref{Eq:step-product-broken} in the later steps by introducing terms that cancel each other. \\[10pt]
+This term accounts for the $k^{th}$ players action in the neighbouring state $(\bar{\abf}^k, \abf^{-k})$ of $\abf$.
+For simplicity, we replace $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ with just $\T$ in the next steps.
+We continue the simplification of Eq.
+\ref{Eq:step-product-broken} in the later steps by introducing terms that cancel each other.
+\\[10pt]
 \begin{align}
@@
 Note that this term is 0 if the $k^{th}$ player plays $\D$ in the state $\abf$.
-When this term is taken inside the product bracket, products of exponent $e^{-\beta f(j-1)}$ can be performed where $j$ ranges from $1$ to the number of cooperators in state $\abf$, $\mathcal{C}(\abf)$.
+When this term is taken inside the product bracket, products of exponent $e^{-\beta f(j-1)}$ can be performed for $j$ ranging from $1$ to the number of cooperators in state $\abf$, $\mathcal{C}(\abf)$.
 This product is then the stationary distribution probability $\ubf_\abf$.
@@
 \end{proof}
-
+\newpage
 \begin{proof}
 \textbf{Proof of Corollary} \ref{Lemma: Symmetric-2-stg} \\ \\
-
+To show this result we count how many states are identical to a state $\abf \in \{\C,\D\}^N$ in a symmetric game.
+When players are symmetric in a two-strategy game, states can be enumerated by counting the number of $\C$ players in that state.
+This can also be confirmed by the expression of the stationary distribution in Eq.
+\ref{Eq:stationary-dist-symm-2-stgs-state}.
+Two distinct states $\abf, \abf'$ having the same number of cooperators (i.e., $\mathcal{C}(\abf') = \mathcal{C}(\abf)$), have the same stationary distribution probability (i.e., $\ubf_{\abf'} = \ubf_{\abf}$).
+\\ \\ 
+\noindent In a game with $N$ players, there can be $k$ players playing $\C$ in exactly $N \choose k$ ways.
+As argued before, all of these states are identical and are also equiprobable in the stationary distribution.
+Therefore, the stationary distribution probability of having $k$, $\C$ players, $\ubf_{k}$, is,
+\begin{equation}
+\ubf_{k} = \sum_{\forall \abf,  \mathcal{C(\abf)} = k} \ubf_\abf = \frac{1}{\Gamma} {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)} \\[10pt]
+\end{equation} 
+\noindent Where the normalization factor $\Gamma$ can also be simplified as: 
+\begin{equation}
+\Gamma = \sum_{k=0}^N {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)}
+\end{equation}
 \end{proof}

### 2023-02-06 latex/article.tex
added the file article.tex

--- 2023-02-03 latex/supplementary.tex
@@
 \onehalfspacing
-\section*{The general model for introspection dynamics}
-We consider a normal form game with $N (>2)$ players.
-Each player, $i$, has access to their action set, $\A^i$, in which there are $m^i$ possible actions that they can play, $\A^i = \{a^i_1, a^i_2, ..., a^i_{m^i}\}$.
-The payoff for an individual $i$ depends on what everyone plays and is represented by $\pi^i(\abf^1, \abf^2, ..., \abf^N)$, where $\abf := (\abf^1, \abf^2,...,\abf^N) \in \A^1 \times \A^2 \times ...
-\times \A^N =: \A$ represents a state of the game.
-In this model we only consider pure strategies for players.
-So, player $i$ has only $m^i$ possible strategies.
-Therefore, the total number of states possible for the game is the product of all $m^i$.
-\\ \\
-\noindent We represent a state of the game, $\abf$, from the perspective of player $j$ as $\abf =: (\abf^j, \abf^{-j})$.
-In the state $(\abf^j, \abf^{-j})$, player $j$ plays the action $\abf^j \in \A^j$ and all the other co-players of $j$ play $\abf^{-j} \in \Pi_{k \neq j} \A^k$.
-The payoff of player $j$ in this state is also represented as $\pi^j(\abf^j, \abf^{-j})$.
-\\ \\
-\noindent The players update their strategies over time using the introspection dynamics \cite{couto2022introspection}.
-At every time step, one randomly chosen player can update their strategy.
-The randomly chosen player, say $j$, currently playing strategy $a^j_k$, compares their current payoff to the payoff that they would obtain if they played a randomly selected strategy,  $a^j_l \neq a^j_k$, from their action set $\A^j$.
-This comparison is done while assuming that the co-players do not change from $\abf^{-j}$.
-Then, they adopt this new strategy  with the probability:
-
-\begin{equation}
- p^j_{a^j_k \to a^j_l} (\abf^{-j})= \frac{1}{1 + e^{\displaystyle -\beta(\pi^j(a^j_l, \abf^{-j}) - \pi^j(a^j_k, \abf^{-j}))}}
- \label{Eq:introspection-update}
-\end{equation}
-\\
-\noindent Where $\beta$ is the selection parameter. The probability that no update is made by the randomly chosen player is given by the normalization condition:
-
-\begin{equation}
- p^j_{a^j_k \to a^j_k} (\abf^{-j}) = 1 - \sum_{k \neq l} p^j_{a^j_k \to a^j_l} (\abf^{-j})
- \label{Eq:introspection-normalization}
-\end{equation}
-\\ 
-\noindent Now, with the help of Eq.
-\ref{Eq:introspection-update} and \ref{Eq:introspection-normalization}, we can define the transition matrix $\T$ of the process.
-The transition matrix is a square matrix of size $M = m^1 \times m^2 \times ...
-\times m^N$.
-The element $\T_{\abf_p, \abf_q}$ of the matrix represents the probability that the game will go to state $\abf_q$ from state $\abf_p$ in a time step.
-Before defining the transition matrix, we define the notion of neighbouring states.
-
-\begin{definition}
-\textbf{Neighbouring states}: \\ The state $\abf_q \in \mathit{Neb}(\abf_p)$, the neighbourhood of state $\abf_p$, if and only if $\exists j$ such that $\abf_p^{-j} = \abf_q^{-j}$ and $\abf_p^{j} \neq \abf_q^{j}$.
-\label{Def:neighbourhood-states}
-\end{definition}
-\noindent Note that if $\abf_q \in \mathit{Neb}(\abf_p)$ then by definition $\abf_p \in \mathit{Neb}(\abf_q)$.
-We give an example to explain the notion of neighbourhood.
-Consider three players, player $1,2$ and $3$.
-Each of these players choose actions from an identical binary action set $\{\mathit{0},\mathit{1}\}$.
-In this example, the state $(\mathit{0}, \mathit{0}, \mathit{0})$ is a neighbour of $(\mathit{0}, \mathit{0}, \mathit{1})$ and vice versa.
-The index of difference between the two states is player $3$.
-The states  $(\mathit{0}, \mathit{0}, \mathit{0})$ and $(\mathit{0}, \mathit{1}, \mathit{1})$ are not neighbouring states because more than one player's action are changed.
-
-\begin{definition}
-\textbf{Index of difference for neighbouring states}: \\ \\ If the states $\abf_p$ and $\abf_q$ are neighbours then, the unique $j$ for which $\abf_p^{j} \neq \abf_q^{j}$, is called the index of difference.
-Or $I(\abf_p,\abf_q) := j$
-\label{Def:index-of-difference}
-\end{definition}
-\noindent For the earlier example, let $\abf_p = (\mathit{0}, \mathit{0}, \mathit{0})$ and $\abf_q = (\mathit{0}, \mathit{0}, \mathit{1})$. Then, $I(\abf_p,\abf_q) = 3$. 
-\\ \\ 
-Using the above definitions of neighbourhood and index of difference, we can define the transition matrix $\T$ for the process as the follows: 
-\begin{align}
-\T_{\abf_p,\abf_q} = 
-\begin{cases}
-\frac{1}{N(m_j-1)}  \cdot p^j_{\abf^j_p \to \abf^j_q} (\abf_p^{-j}) \quad  \quad &\abf_p \in \mathit{Neb}(\abf_q) \quad \text{and,} \quad j = I(\abf_p,\abf_q)\\ \\ 
-0 \quad & \abf_{p} \notin \mathit{Neb}(\abf_q) \\ \\
-1 - \sum_{\forall \abf_k \neq \abf_p} \T_{\abf_p,\abf_k} \quad &\abf_p = \abf_q
-\end{cases}
-\label{Eq:transition-matrix}
-\end{align}
-\noindent The stochastic transition matrix $\T$ is row-stochastic.
-This implies that its stationary distribution is a left eigenvector of $\T$ corresponding to eigenvalue $1$.
-We denote the stationary distribution of $\T$ as $\ubf := (\ubf_{\abf})_{\abf \in \A}$.
-Furthermore, since no state of the process is isolated (i.e., every state has atleast one neighbour), a finite $\beta$ assures that a state is reachable from any other state with positive probability in a finite number of steps.
-Therefore, $\T$ is also primitive.
-The stationary distribution $\ubf$ is unique and strictly positive (from the Perron-Frobenius Theorem).
-The following conditions are satisfied by the stationary distribution $\ubf$ when it is additionally also a probability distribution.
-
-\begin{eqnarray}
-\label{Eq:lefteigenvector}
-\ubf \T = \ubf \\ 
-\label{Eq:normalizationcondition}
-\ubf \cdot \mathbf{1} = 1
-\end{eqnarray}
-
-\noindent The marginal distribution over the strategies of a player $j$ at the stationary distribution is given by $\mathbf{\xi}^j := (\mathbf{\xi}^j_{a^j_1}, \mathbf{\xi}^j_{a^j_2}, ..., \mathbf{\xi}^j_{a^j_{m_j}})$.
-This distribution indicates the probability with which player $j$ plays strategies from their action set $\A^j$ at the stationary distribution.
-The relationship between the marginal distribution and the stationary distribution is given by:
-
-\begin{equation}
-\mathbf{\xi}^j_{a^j_k} := \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(a^j_k, \mathbf{b})}
-\label{Eq:marginal-definition}
-\end{equation}
-
-\noindent Where, $\A^{-j} = \prod_{l \neq j} \A^l$. One can note that the marginal distribution is also a probability distribution. That is, for all $j$:
-
-\begin{equation}
-\sum_{a' \in \A^j} \xi^j_{a'}= 1
-\label{Eq:marginal-prob-dist}
-\end{equation}
-
-\subsection*{Additive games and their properties under introspection dynamics}
-
-In this subsection we discuss a special class of general multiplayer games: additive games \cite{mcavoy2015asymmetric} and some of their properties under the introspection dynamics.
-Additive games are games where the payoff earned by a player $j$ in the state $\abf$ can be broken down into two-components - one which is only dependent on what player $j$ played in the state: $\abf^j$ and the other which only depends on what their co-players $-j$ played in the state: $\abf^{-j}$ .
-That is, for all players $j$,
-
-\begin{equation}
-\pi^j(\abf) = \pi^j_{\abf^j} + \pi^j_{\abf^{-j}}
-\label{Eq:additive games}
-\end{equation}
-
-\noindent holds.
-In additive games, the payoff difference earned by a player when they switch between two strategies in their action set is independent of what other co-players are playing (given all other co-players do not change their strategies).
-That is, for all $j$ and any pair of strategies $a^j_p, a^j_q\in \A^j$,
-
-\begin{equation}
-\pi^j(a^j_p, \mathbf{b}) - \pi^j(a^j_q, \mathbf{b}) = \pi^j_{a^j_p} - \pi^j_{a^j_q}
-\label{Eq:additive games property}
-\end{equation}
-
-\noindent holds for any $\mathbf{b} \in \prod_{l \neq j} \A^l$. 
-\\ \\
-We see an example of additive game in the next section.
-Under introspection dynamics, stationary distribution and marginal distributions from additive games show interesting properties.
-They are discussed in the theorems below:
-
-\begin{Prop}
-When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
-\begin{equation}
-\ubf_a = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
-\label{Eq:additive-game-stationary-distribution}
-\end{equation}
-where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$.
-\label{Th:additive-games-stationary-dist}
-\end{Prop}
-\noindent The above theorem gives a closed form expression of the stationary distribution of the introspection dynamics for additive multiplayer games.
-For any finite value of the selection parameter, $\beta$, the stationary distribution can be analytically calculated using the expression in Eq.
-(\ref{Eq:additive-game-stationary-distribution}).
-The expression is derived by assuming that the update process of the introspection dynamics is governed by Eq.
-(\ref{Eq:introspection-update}) and (\ref{Eq:introspection-normalization}).
-For proof, see Appendix \ref{Section:Appendix}.
-
-\begin{Prop}
-Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game.
-Then, $\ubf_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$.
-That is,
-
-\begin{equation}
-\ubf_\abf = \prod_{j = 1}^N \xi^j_{\abf^j}
-\label{Eq:additive-game-products}
-\end{equation}
-
-\noindent where the marginal probability, $\xi^j_{\abf^j}$, is the cumulative probability that player $j$ plays $\abf^j$ at the stationary distribution. The marginal probability is given by:
-
-\begin{equation}
-\xi^j_{\abf_j} = \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
-\label{Eq:marginal-at-additive-game}
-\end{equation}
-\noindent where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$ in an additive game.
-\label{Th:additive-game-product-of-marginals}
-\end{Prop}
-
-\noindent In other words, the above theorem states for additive games, the probability that the game will be in state $\abf = (\abf^1, \abf^2, ...,\abf^N)$ in the long run (considering a finite selection strength introspection dynamics) is the product of the cumulative probabilities that each player $j$ respectively adopts the action $\abf^j$ in the stationary distribution.
-\\ \\
-\noindent To elucidate this result further, we use an example of a 2-player additive game where each player has three possible actions from the action set $\{\mathit{0},\mathit{1},\mathit{2}\}$.
-The result says that the expected frequency of the state $(\mathit{0,2})$, say, where player 1 and player 2 simultaneously play $\mathit{0}$ and $\mathit{2}$ respectively: $\ubf_{(\mathit{0,2})}$, is the product of the marginal probabilities that the first player plays $\mathit{0}$ and the second player plays $\mathit{2}$ in the game.
-That is,
-
-\begin{equation}
-\ubf_{(\mathit{0,2})} = \xi^1_{\mathit{0}}  \xi^2_{\mathit{2}} = (\ubf_{(\mathit{0,0})} + \ubf_{(\mathit{0,1})} + \ubf_{(\mathit{0,2})})(\ubf_{(\mathit{0,2})} + \ubf_{(\mathit{1,2})} + \ubf_{(\mathit{2,2})})
-\label{Eq:additive-stationary-dist-example}
-\end{equation}
-\\
-\noindent As stated in the theorem above, this result holds for any additive game with arbitrary number of players and each player having arbitrary action sets.
-
-\subsection*{Example of multiplayer additive game: linear public goods game}
-We consider the linear public goods game with $N$ asymmetric players.
-Each player has two possible actions, to contribute (action, $\C$), or to not contribute (action, $\D$).
-The players differ in their cost of cooperation and their productivities.
-The cost of cooperation and the productivity of a player $i$ are denoted by $c^i$ and $r^i$.
-The payoff for player $i$ when the state of the game is $\abf$ is given by:
-
-\begin{equation}
-\pi^i(\abf) = \sum_{j=1}^N \frac{\displaystyle r^j a^j c^j}{N} - a^i c^i
-\label{Eq:linear-pgg-payoff}
-\end{equation}
-\\
-\noindent The difference in payoffs between playing the two actions in a linear public goods game is independent of what the other co-players play in the game. That is,
-
-\begin{equation}
-\pi^i(\abf^i = \D, \abf^{-i}) - \pi^i(\abf^i = \C, \abf^{-i}) = c^i \left(1 - \frac{r^i}{N} \right) =: f(c^i, r^i) 
-\label{Eq:difference-payoffs-lpgg}
-\end{equation}
-\\
-\noindent is independent of $\abf^{-i}$.
-The linear public goods game is therefore an example of an additive game.
-This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r^i$ and number of players $N$.
-When $r^i < N$, the action of not contributing ($\D$) dominates the action of contributing ($\C$) and vice-versa.
-\\
-\begin{Prop}
-\label{prop:stationary-dist-lpgg}
-When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for an asymmetric linear public goods game under introspection dynamics is given by: 
-\\
-\begin{equation}
-\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^j)\beta f(c^j, r^j )}} \quad ,\forall \abf \in \{\C, \D\}^N
-\label{Eq:stationary_dist_lpgg}
-\end{equation}
-where, 
-\begin{equation}
-\label{Eq:sign-function}
-\mathit{sign}(a) =
-\begin{cases}
-1& \quad \text{if} \quad a = \C \\
--1& \quad \text{if} \quad a = \D
-\end{cases}
-\end{equation}
-\end{Prop}
-
-\section*{Symmetric multiplayer games with two strategies}
-
-In the previous section we looked at properties of the stationary distribution of the introspection dynamics for additive games.
-In this section we look at properties of the stationary distribution for any multiplayer game where players are symmetric and have two actions in their action set.
-A $N-$player symmetric normal form game satisfies the following properties:
-
-\begin{enumerate}
-\item $\A^1 = \A^2 = ... = \A^N = \mathcal{A}$, and
-\item For any $i, j \in \{1,2,...,N\}, a \in \mathcal{A}$ and $\mathbf{b} \in \displaystyle \prod_{k=1}^{N-1} \mathcal{A}$: 
-\begin{equation}
-\pi^i(a, \mathbf{b}) = \pi^j(a, \mathbf{b})
-\end{equation}
-\end{enumerate}
-
-\noindent In addition, when there are only two actions in the action set of players we define the action set in the same way as we did in the section of linear public goods game: $\mathcal{A} := \{\C, \D\}$.
-\subsection*{Notations}
-We introduce some notations before presenting the results
-\begin{enumerate}
-
-\item We denote the payoffs of a $\C$ and $\D$ player when they have $j$ co-players playing $\C$, as $\pi^{\C}(j)$ and $\pi^{\D}(j)$ respectively. 
-\item We define a simple mapping function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to $0$. That is, 
-\begin{equation}
-\alpha(a):= 
-\begin{cases}
-1 \quad \text{if} \quad a = \C \\
-0 \quad \text{if} \quad a = \D  
-\end{cases}
-\end{equation}
-\item For every state $\abf \in \mathcal{A}^N$, we count the number of $\C$ players in the state and denote it with $\mathcal{C}(\abf)$. That is, 
-\begin{equation}
-\mathcal{C}(\abf) := \sum_{j=1}^N \alpha(\abf^j)
-\end{equation}
-\end{enumerate}
+\section*{Abstract}
 \newpage
-\begin{Prop}
-\label{Prop:Symmetric-2-strategies-state}
-When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\ubf_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
-\begin{equation}
-\label{Eq:stationary-dist-symm-2-stgs-state}
-\ubf_\abf = \frac{1}{\Gamma} \displaystyle \prod_{j=1}^{\mathcal{C}(\abf)} \displaystyle e^{-\beta f(j-1)}
-\end{equation}
-where $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$. The term $\Gamma$ is the normalization factor given by:
-\begin{equation}
-\label{Eq:stationary-dist-normalization-symm-2-stgs-state}
-\Gamma = \displaystyle \sum_{\forall \abf' \in \mathcal{A}^N} \prod_{j = 1}^{\mathcal{C}(\abf')} \displaystyle e^{-\beta f(j-1)}
-\end{equation}
-\end{Prop}
-
-\noindent The above proposition gives an exact closed form expression for the steady state distribution of the introspection dynamics for symmetric games with two strategies.
-Since all players are symmetric in this two strategy game, the number of unique states of the game can be reduced to $N+1$ from $2^N$.
-Now, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
-Then, Proposition \ref{Prop:Symmetric-2-strategies-state} can be simplified by accounting for states with number of $\C$ players as follows:
-
-\begin{Corollary}
-\label{Lemma: Symmetric-2-stg}
-When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
-\begin{equation}
-\label{Eq:stationary-dist-symm-2-stgs}
-\ubf_k = \frac{1}{\Gamma} \cdot {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
-\end{equation} \\ 
-where, $k$ represents the number of $\C$ players in the state and $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$.
-The term $\Gamma$ is the normalization factor, given by, \\
-\begin{equation}
-\label{Eq:normalization-Tk}
-\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
-\end{equation}
-\end{Corollary}
-\noindent The above lemma follows directly from Proposition \ref{Prop:Symmetric-2-strategies-state}.
-The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$, $\C$ players and $N-k$, $\D$ players.
-This count is simply the binomal coefficient $N \choose k$.
-For details see the proof in the Appendix.
+\section*{Introduction}
+\section*{Model}
 \newpage
@@
 \newpage
-\section*{Supplementary References}
+%\section*{Supplementary References}
 \bibliographystyle{unsrt}

### 2023-02-06 latex/article.tex
prop 1 change

@@
 \section*{Model}
+We consider the normal form game with $N$ players where $N > 2$.
+In the game, player $i$ can play an action from their action set, $\A^i := \{a^i_1, a^i_2, ..., a^i_{m^i}\}$.
+The action set of player $i$ has $m^i$ actions.
+There are, therefore, $m^1 \times m^2 \times ...
+\times m^N$ distinct states of the game.
+We denote a state of the game with $\abf$ where $\abf := (\abf^1, \abf^2, ..., \abf^N) \in \A^1 \times \A^2 \times ...
+\times \A^N$.
+We also use the notation, $\abf := (\abf^i, \abf^{-i})$ to denote the state from the perspective of player $i$.
+In the state $\abf$, player $i$ plays the action $\abf^i \in \A^i$ and their co-players play the action $\abf^{-i} \in \prod_{j \neq i} \A^j$.
+\\ \\
+\noindent The payoffs of a player depends on the state of the game. We denote the payoff of player $i$ in the state $\abf$ with $\pi^i(\abf)$.
+
 \newpage

### 2023-02-06 latex/supplementary.tex
prop 1 change

@@
 \begin{equation}
-\ubf_a = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
+\ubf_\abf = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
 \label{Eq:additive-game-stationary-distribution}
@@
 \end{Prop}
-\noindent The above theorem gives a closed form expression of the stationary distribution of the introspection dynamics for additive multiplayer games.
+\noindent The above proposition gives a closed form expression of the stationary distribution of the introspection dynamics for additive multiplayer games.
 For any finite value of the selection parameter, $\beta$, the stationary distribution can be analytically calculated using the expression in Eq.
@@
 \end{equation}
-where $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$. The term $\Gamma$ is the normalization factor given by:
+where $f(j) := \pi^\D(j) - \pi^\C(j)$ is the payoff difference earned by switching the play from $\D$ and $\C$ when there are $j$ co-players playing $\C$.
+The term $\Gamma$ is the normalization factor given by:
 \begin{equation}
@@
 \end{equation} \\ 
-where, $k$ represents the number of $\C$ players in the state and $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$.
+where, $k$ represents the number of $\C$ players in the state and $f(j) := \pi^\D(j) - \pi^\C(j)$ is the payoff difference earned by switching the play $\D$ and $\C$ when there are $j$ co-players playing $\C$.
 The term $\Gamma$ is the normalization factor, given by, \\
@@
 \noindent The above lemma follows directly from Proposition \ref{Prop:Symmetric-2-strategies-state}.
-The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$, $\C$ players and $N-k$, $\D$ players.
+The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$, $\C$ players (and therefore $N-k$, $\D$ players).
 This count is simply the binomal coefficient $N \choose k$.

### 2023-02-07 latex/article.tex
Tuesday before lunch 7th Feb, additive games done, proofs still need to be checked

--- 2023-02-06 latex/article.tex
@@
 \usepackage{times}
-\usepackage{amsmath,amsthm,amssymb,mathtools,setspace,enumitem,epsfig,titlesec,verbatim,color,array,multirow,comment,graphicx,hyperref,blkarray}
+\usepackage{amsmath,amsthm,amssymb,bbold, mathtools,setspace,enumitem,epsfig,titlesec,verbatim,color,array,multirow,comment,graphicx,hyperref,blkarray}
 %\usepackage[sort&compress]{natbib} % ProcB
@@
 \newcommand{\abf}{\mathbf{a}}
+\newcommand{\bbf}{\mathbf{b}}
+\newcommand{\cbf}{\mathbf{c}}
 \newcommand{\T}{\mathbf{T}}
@@
 \section*{Model}
+We consider the normal form game with $N$ players where $N > 2$.
+In the game, a player, say player $i$, can play actions from their action set, $\A_i := \{a_{i,1}, a_{i,2}, ..., a_{i,m_i} \}$.
+The action set of player $i$ has $m_i$ actions.
+There are, therefore, $m_i \times m_2 \times ...
+\times m_N$ distinct states of the game.
+We denote a state of the game by collecting the actions of all the players in the game in a vector, $\abf := (\abf_1, \abf_2, ..., \abf_N)$ where $\abf \in \A := \A_1 \times \A_2 \times ...
+\times \A_N$.
+We also use the notation, $\abf := (\abf_i, \abf_{-i})$ to denote the state from the perspective of player $i$.
+In the state $(\abf_i, \abf_{-i})$, player $i$ plays the action $\abf_i \in \A_i$ and their co-players play the action $\abf_{-i} \in \A_{-i} := \prod_{j \neq i} \A_j$.
+The payoff of a player depends on the state of the game.
+We denote the payoff of player $i$ in the state $\abf$ with $\pi_i(\abf)$ or $\pi_i(\abf_i, \abf_{-i})$.
+\\ \\
+\noindent The players update their strategies over time using the introspection dynamics \cite{couto2022introspection}.
+At every time step, one randomly chosen player can update their strategy.
+The randomly chosen player, say $i$, currently playing strategy $a_{i,k}$, compares their current payoff to the payoff that they would obtain if they played a randomly selected strategy,  $a_{i,l} \neq a_{i,k}$, from their action set $\A_i$.
+This comparison is done while assuming that the co-players do not change their respective plays.
+When the co-players of player $i$ play $\abf_{-i}$, player $i$ changes to the new strategy $a_{i,l}$ from $a_{i,k}$ with the probability, \\
+\begin{equation}
+ p_{a_{i,k} \to a_{i,l}} (\abf_{-i})= \frac{1}{1 + e^{\displaystyle -\beta(\pi_i(a_{i,l}, \abf_{-i}) - \pi_i(a_{i,k}, \abf_{i}))}}
+ \label{Eq:introspection-update}
+\end{equation}
+\\ \\ \noindent in the next round.
+Here $\beta \in [0,\infty)$ is the selection strength parameter that represents the importance that players give to payoff differences while updating their strategies.
+At $\beta = 0$, players update to a randomly chosen strategy with probablity $0.5$.
+For $\beta > 0$, players update to new strategy with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
+The probability that the chosen player makes no-update is then, \\
+\begin{equation}
+ p_{a_{i,k} \to a_{i,k}} (\abf_{-i}) = 1 - \sum_{k \neq l} p_{a_{i,k} \to a_{i,l}} (\abf_{-i})
+ \label{Eq:introspection-normalization}
+\end{equation}
+\\ 
+Introspection dynamics can be studied by analyzing properties of the resulting transition matrix, $\T$.
+The transition matrix element $\T_{\abf,\bbf}$ denotes the conditional probability that the game goes to the state $\bbf$ in the next round if it is in state $\abf$ in the current round.
+We define the neighbourhood set of $\abf$ as the following:
 \newpage
+\begin{definition}[Neighbourhood set of a state] The neighbourhood set of state $\abf$, $\mathrm{Neb}(\abf)$, is defined as the following:
+\begin{equation}
+\mathrm{Neb}(\abf) := \{\bbf \in \A \setminus \{ \abf \}  : (\exists j) [ \bbf_{-j} = \abf_{-j} \land  \bbf_{j} \neq \abf_{j}] \}
+\label{Eq:neighbourhood-states}
+\end{equation} 
+\label{Def:neighbourhood-states}
+\end{definition} 
+\noindent In other words, a state in $\mathrm{Neb}(\abf)$ is a state that has exactly one player playing a different action than in state $\abf$.
+Consider the game where there are  three players and each player has the identical action set $\{\C, \D \}$.
+The state $(\C,\C,\C)$ is in the neighbouring set of $(\C,\C,\D)$ whereas the state $(\C,\D,\D)$ is not in the neighbourhood set of $(\C,\C, \C)$.
+Two states that belong in each other's neighbourhood set only differ in exactly a single player's (that we call as the index of difference) action.
+
+\begin{definition} [Index of difference between neighbouring states] If two states, $\abf$ and $\bbf$, satisfy $\abf \in \mathrm{Neb}(\bbf)$, the index of difference between them, $\mathrm{I}(\abf, \bbf)$, is the unique integer that satisfies:
+\begin{equation}
+\abf_{\mathrm{I}(\abf, \bbf)} \neq \bbf_{\mathrm{I}(\abf, \bbf)}
+\end{equation} 
+\label{Def:index-of-difference}
+\end{definition} 
+\noindent In the previous example, the index of difference between the neighbouring states $(\C,\C,\C)$ and $(\C,\C,\D)$ is $3$.
+The third player's action is the difference between the two neighbouring states.
+Using the above definitions, one can formally define the transition matrix of the introspection dynamics with:
+
+\begin{align}
+\T_{\abf, \bbf} = 
+\begin{cases}
+\frac{1}{N(m_j-1)}  \cdot p_{\abf_{j} \to \bbf_{j}} (\abf_{-j}) \quad  \quad &\text{ if }\bbf \in \mathrm{Neb}(\abf) \quad \text{and,} \quad j = \mathrm{I}(\abf,\bbf)\\ \\ 
+0 \quad &\text{ if } \bbf \notin \mathrm{Neb}(\abf) \\ \\
+1 - \sum_{\cbf \neq \bbf} \T_{\abf,\cbf} \quad &\text{ if } \abf = \bbf
+\end{cases}
+\label{Eq:transition-matrix}
+\end{align} \\ 
+\noindent The transition matrix is a row stochastic matrix (the sums of the rows are 1).
+This implies that the stationary distribution of $\T$: a left eigenvector of $\T$ corresponding to eigenvalue $1$, always exists.
+The following proposition introduces a sufficient condition for this stationary distribution to be unique.
+\begin{Prop} When $\beta$ is finite, the transition matrix of the introspection dynamics has a unique stationary distribution. 
+\label{Prop:unique-stationary-dist}
+\end{Prop}
+\noindent \textbf{Proof:} A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
+Since no state is isolated (i.e., every state belongs in the neighbourhood set of another state), every state is reachable in a finite number of steps from a starting point with non-zero probability.
+The transition matrix $\T$ is therefore primitive for a finite $\beta$.
+By the Perron-Frobenius theorem, a primite matrix, $\T$ will have a unique and strictly positive stationary distribution $\ubf := (\ubf_\abf)_{\abf \in \A}$ which satisfies the conditions:
+\begin{eqnarray}
+\label{Eq:lefteigenvector}
+\ubf \T = \ubf \\ 
+\label{Eq:normalizationcondition}
+\ubf \mathbf{1} = 1
+\end{eqnarray}
+\noindent where $\mathbf{1}$ is the column vector with size same as $\ubf$ and has all elements as $1$.
+The above equations only present an explicit representation of the stationary distribution $\ubf$.
+The stationary distribution can be explictly calculated by the following expression (which is derived using Eq.
+(\ref{Eq:lefteigenvector}) and (\ref{Eq:normalizationcondition}) as:
+\begin{equation}
+\ubf = \mathbf{1}^\intercal (\mathbb{1} + \mathbf{U} - \T)^{-1}
+\label{Eq:explicit-stationary-dist-representation}
+\end{equation}
+where $\mathbf{U}$ is a square matrix of size same as $\T$ with all elements 1 and $\mathbb{1}$ is the identity matrix.
+For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distribution of the processes are unique.
+The stationary distribution element $\ubf_\abf$ is the probability that state $\abf$ will be played by the players in the long run.
+Using the stationary distribution, one can calculate the marginal probabilities corresponding to each player's actions.
+For example, the probability that player $i$ plays action $a_{i,k}$ in the long run, $\xi_{i:a_{i,k}}$, can be computed as,
+\begin{equation}
+\mathbf{\xi}_{i:a_{i,k}} := \sum_{\mathbf{b} \in \A_{-i}} \ubf_{(a_{i,k}, \bbf)}
+\label{Eq:marginal-definition}
+\end{equation}
+\noindent Since the stationary distribution is a probability distribution, marginal distributions also have the same property. That is, for a player $i$, 
+\begin{equation}
+\sum_{k = 1}^{m_i} \xi_{i:a_{i,k}}= 1
+\label{Eq:marginal-prob-dist}
+\end{equation}
+\section*{Additive games and their properties under introspection dynamics}
+In this section we discuss the stationary properties of introspection dynamics on a special class of games - the additive games \cite{pena2014gains, mcavoy2015asymmetric}.
+In an additive game, the payoff difference that a player earns by making a switch in their actions is independent of what their co-players play while they make this switch.
+In other words, if none of the co-players change their strategy, the payoff difference earned by making a particular switch is \emph{only} determined by the switch and not on the co-players' play.
+This property is sometimes called the \emph{equal gains from switching} \cite{pena2014gains} property of a game.
+That is, for any player $i$, any pair of actions $x,y \in \A_i$, and any $\bbf \in A_{-i}$,
+\begin{equation}
+\pi_i(x, \bbf) - \pi_i(y, \bbf) =: f_i(x,y) 
+\end{equation}
+\noindent For games with this property, the stationary distribution takes a simple form as shown in the proposition below.
+
+ \begin{Prop}
+When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
+\begin{equation}
+\ubf_\abf = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a', \abf_j)}} 
+\label{Eq:additive-game-stationary-distribution}
+\end{equation}
+where, $f_j(a', \abf_j) = \pi_j(a', \bbf) - \pi_j(\abf_j, \bbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf_j$.
+\label{Th:additive-games-stationary-dist}
+\end{Prop}
+\noindent The above proposition gives a closed form expression of the stationary distribution of the introspection dynamics for additive games.
+For any finite value of the selection parameter, $\beta$, the stationary distribution can be computed using the expression in Eq.
+(\ref{Eq:additive-game-stationary-distribution}).
+For proof, see Appendix \ref{Section:Appendix}.
+Additive games are particularly interesting under the introspection dynamics because of the following relationship between the stationary distribution and marginal distributions,
+
+\begin{Prop}
+Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game.
+Then, $\ubf_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$.
+That is,
+
+\begin{equation}
+\ubf_\abf = \prod_{j = 1}^N \xi_{j:\abf_j}
+\label{Eq:additive-game-products}
+\end{equation}
+
+\noindent where the marginal probability, $\xi_{j:\abf_j}$, is the cumulative probability that player $j$ plays $\abf_j$ at the stationary distribution. The marginal probability is given by:
+
+\begin{equation}
+\xi_{j:\abf_j} = \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a', \abf_j)}} 
+\label{Eq:marginal-at-additive-game}
+\end{equation}
+\noindent where, $f_j(a', \abf_j) = \pi_j(a', \bbf) - \pi_j(\abf_j, \bbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf_j$.
+\label{Th:additive-game-product-of-marginals}
+\end{Prop}
+\noindent The above proposition states that for additive games under introspection dynamics, the stationary distribution can be factorized into its corresponding marginals.
+In the long run, the probability that players simultaneously play ($\abf_1, \abf_2, ...,\abf_N$) is the product of the cumulative probabilities that player 1 plays $\abf_1$, player 2 plays $\abf_2$ and so on.
+In the following subsection we study a classical additve game - the linear public goods game under the introspection dynamics and discuss the results.
 \section*{Appendix: Proofs}
@@
 Since $\beta$ is finite, the transition matrix of the process $\T$ given by Eq.
-\ref{Eq:transition-matrix} is primitive and therefore, the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the row-stochastic transition matrix is unique and satisfies the conditions laid out in Eq.
+(\ref{Eq:transition-matrix}) is primitive and therefore, the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the row-stochastic transition matrix is unique and satisfies the conditions laid out in Eq.
 \ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}.
@@
 \newpage
-%\section*{Supplementary References}
+\section*{Supplementary References}
 \bibliographystyle{unsrt}

### 2023-02-08 latex/article.tex
did the proof 1 changes in notation

@@
 \newcommand{\cbf}{\mathbf{c}}
+\newcommand{\qbf}{\mathbf{q}}
 \newcommand{\T}{\mathbf{T}}
@@
 \begin{equation}
- p_{a_{i,k} \to a_{i,l}} (\abf_{-i})= \frac{1}{1 + e^{\displaystyle -\beta(\pi_i(a_{i,l}, \abf_{-i}) - \pi_i(a_{i,k}, \abf_{i}))}}
+ p_{a_{i,k} \to a_{i,l}} (\abf_{-i})= \frac{1}{1 + e^{\displaystyle -\beta(\pi_i(a_{i,l}, \abf_{-i}) - \pi_i(a_{i,k}, \abf_{-i}))}}
  \label{Eq:introspection-update}
@@
 \begin{equation}
-\mathbf{\xi}_{i:a_{i,k}} := \sum_{\mathbf{b} \in \A_{-i}} \ubf_{(a_{i,k}, \bbf)}
+\mathbf{\xi}_{i:a_{i,k}} := \sum_{\qbf \in \A_{-i}} \ubf_{(a_{i,k}, \qbf)}
 \label{Eq:marginal-definition}
@@
 This property is sometimes called the \emph{equal gains from switching} \cite{pena2014gains} property of a game.
-That is, for any player $i$, any pair of actions $x,y \in \A_i$, and any $\bbf \in A_{-i}$,
+That is, for any player $i$, any pair of actions $x,y \in \A_i$, and any $\qbf \in A_{-i}$,
 \begin{equation}
-\pi_i(x, \bbf) - \pi_i(y, \bbf) =: f_i(x,y) 
+\pi_i(x, \qbf) - \pi_i(y, \qbf) =: f_i(x,y) 
 \end{equation}
@@
 \end{equation}
-where, $f_j(a', \abf_j) = \pi_j(a', \bbf) - \pi_j(\abf_j, \bbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf_j$.
+where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf_j$.
 \label{Th:additive-games-stationary-dist}
@@
 \end{equation}
-\noindent where, $f_j(a', \abf_j) = \pi_j(a', \bbf) - \pi_j(\abf_j, \bbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf_j$.
+\noindent where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf_j$.
 \label{Th:additive-game-product-of-marginals}
@@
 In the following subsection we study a classical additve game - the linear public goods game under the introspection dynamics and discuss the results.
+
+\subsection*{Example of an additive game: linear public goods game with 2 actions}
+Here, we analyze the linear public goods game with $N$-players.
+Each player has two possible actions, to contribute (action, $\C$), or to not contribute (action, $\D$).
+The players differ in their cost of cooperation and the benefit they provide to the public goods.
+The cost of cooperation for player $i$ and the benefit they provide to the public goods are denoted with $c_i$ and $b_i$ respectively.
+The payoff of player $i$ when the state of the game is $\abf$ is given by: \\
+\begin{equation}
+\pi_i(\abf) = \sum_{j=1}^N \frac{\displaystyle \abf_j b_j}{N} - \abf_i c_i
+\label{Eq:linear-pgg-payoff}
+\end{equation}
+\\
+\noindent The payoff difference that a player earns by unilaterally switching from $\C$ to $\D$ (or \emph{vice-versa}) in the linear public goods game is independent of what the other co-players play in the game.
+That is, for every player $i$,
+\begin{equation}
+\pi_i(\D, \qbf) - \pi_i(\C, \qbf) = c_i - \frac{b_i}{N} =: f_i(\D, \C) 
+\label{Eq:difference-payoffs-lpgg}
+\end{equation}\\
+\noindent is independent of any $\qbf \in \A_{-i}$ that the co-players of $i$ play.
+The linear public goods game is therefore an example of an additive game.
+This property of the game results in dominated strategies for player $i$ depending on the relationship between the benefits $b_i$, number of players $N$, and cost of cooperation $c_i$.
+When $c_i > b_i/N$, the action of not contributing ($\D$) dominates the action of contributing ($\C$) and \emph{vice-versa}.
+Using proposition \ref{Th:additive-games-stationary-dist}, we derive the following closed form expression for the stationary distribution of a $N-$player linear public goods game with two strategies.
+\begin{Prop}
+\label{prop:stationary-dist-lpgg}
+When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for a $N-$player linear public goods game is given by: 
+\\
+\begin{equation}
+\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf_j)\beta f_j(\D, \C )}} 
+\label{Eq:stationary_dist_lpgg}
+\end{equation}
+where, 
+\begin{equation}
+\label{Eq:sign-function}
+\mathit{sign}(a) =
+\begin{cases}
+1 &\quad \text{if} \quad a = \C \\
+-1 &\quad \text{if} \quad a = \D
+\end{cases}
+\end{equation}
+\end{Prop}
+\newpage
 \section*{Appendix: Proofs}
@@
 \textbf{Proof of Proposition} \ref{Th:additive-games-stationary-dist} \\ \\ 
-Since $\beta$ is finite, the transition matrix of the process $\T$ given by Eq.
-(\ref{Eq:transition-matrix}) is primitive and therefore, the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the row-stochastic transition matrix is unique and satisfies the conditions laid out in Eq.
-\ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}.
-To continue for the rest of the proof, we introduce some short-cut notation that will be of use later in the proof:\\
+Since $\beta$ is finite,the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the process is unique by Proposition \ref{Prop:unique-stationary-dist}.
+The stationary distribution also satisfies the equalities in Eq.
+(\ref{Eq:lefteigenvector}) and (\ref{Eq:normalizationcondition}).
+Before continuing through the remainder of the proof, we introduce some short-cut notation that we will be using:\\
 \begin{align}
-I_{q} &:= I(\abf_q,\abf), \quad \mathit{iff} \quad \abf_q \in \mathit{Neb}(\abf) \\ \notag \\ 
+\mathrm{I}_{\bbf} &:= \mathrm{I}(\bbf,\abf), \quad \mathit{iff} \quad \bbf \in \mathrm{Neb}(\abf) \\ \notag \\ 
 \label{Eq:shortcut-tau}
-\tau^j_{\abf^j} &:= \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
+\tau_{j:\abf_j} &:= \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a',  \abf_j)}} 
 \end{align}
 \noindent In order to show that the candidate stationary distribution, as proposed in Eq.
-\ref{Eq:additive-game-stationary-distribution} is the stationary distribution of the process, we need to show that the following are true:
-\begin{eqnarray}
+(\ref{Eq:additive-game-stationary-distribution}) is the stationary distribution of the process, we need to show that the following are true:
+\begin{align}
 \label{step-one}
-\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \ubf_a \quad \forall \abf \in \A \\ 
+\T_{\abf,\abf} \ubf_\abf  + &\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} = \ubf_\abf \quad \forall \abf \in \A \\[10pt]
 \label{step-two}
-\sum_{\abf \in \A} \ubf_\abf  = 1
-\end{eqnarray}
-The Eq \ref{step-one} can be simplified further with the steps: 
+&\sum_{\abf \in \A} \ubf_\abf  = 1
+\end{align} 
+Using our short-cut notation $\tau$ and the expression for our candidate stationary distribution in Eq.
+(\ref{Eq:additive-game-stationary-distribution}), we can express the stationary distribution as:
+\begin{equation}
+\ubf_\abf = \prod_{j=1}^N \tau_{j:\abf_j}
+\label{Eq:additive-stat-shortcut}
+\end{equation} \\ 
+Using this expression, the left hand side of Eq. (\ref{step-one}) can be simplified further with the steps: 
 \begin{align}
-&\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \\
-& \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)}  \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
+&\T_{\abf,\abf} \ubf_\abf  + \sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf}\\
+&= \left( 1 - \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} \cdot \ubf_{\abf} \right) + \sum_{\bbf \in \mathrm{Neb}(\abf)}  \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{\bbf_{\mathrm{I}_\bbf} \to \abf_{\mathrm{I}_\bbf}} \cdot \ubf_{\bbf}\\ \notag \\
 \label{eq:important-step}
-& \ubf_\abf +  \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \left( \prod_{k \neq I_q} \tau^k_{\abf^k} \right) \left( p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} \right) \cdot \left(  \frac{1}{m^{I_q}-1} \right)
+&= \ubf_\abf +  \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \left( \prod_{k \neq I_\bbf} \tau_{k:\abf_k} \right) \left( p_{\bbf_{I_\bbf} \to \abf_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf: \abf_{\mathrm{I}_\bbf}} -  p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf: \bbf_{\mathrm{I}_\bbf}} \right) \cdot \left(  \frac{1}{m_{\mathrm{I}_\bbf}-1} \right)
 \end{align}
-\\ Using the definition of probability of update of the introspection dynamics, as given by Eq. \ref{Eq:introspection-update} and Eq. \ref{Eq:shortcut-tau}, it can be shown that: 
+\noindent For an additive game, the expressions for $p_{\bbf_{I_\bbf} \to \abf_{\mathrm{I}_\bbf}}$ and $p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}}$ can be simply written as: 
+\begin{align}
+p_{\bbf_{I_\bbf} \to \abf_{\mathrm{I}_\bbf}} &=\frac{1}{1 + \displaystyle e^{\beta f_{\mathrm{I}_\bbf}(\bbf_{\mathrm{I}_\bbf}, \abf_{\mathrm{I}_\bbf})}} \\[10pt] 
+p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} &= \frac{1}{1 + \displaystyle e^{\beta f_{\mathrm{I}_\bbf}(\abf_{\mathrm{I}_\bbf}, \bbf_{\mathrm{I}_\bbf})}} 
+\end{align} \\
+Using the above expressions and the expression for $\tau$ in Eq. (\ref{Eq:shortcut-tau}), it can be shown that: 
 \begin{equation}
-p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} = 0
+\left( p_{\bbf_{I_\bbf} \to \abf_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf: \abf_{\mathrm{I}_\bbf}} -  p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf: \bbf_{\mathrm{I}_\bbf}} \right) = 0
 \label{important-step-is-zero}
 \end{equation}
-\\ \noindent Plugging the equality in Eq.
-\ref{important-step-is-zero} into Eq.
-\ref{eq:important-step}, we can see that the left hand side of Eq.
-\ref{step-one} indeed simplifies to $\ubf_{\abf}$.
-Now, to confirm that the candidate $\ubf$ is the unique stationary distribution we need to check if Eq.
-\ref{step-two} holds.
-Simplifying the left hand side of this equation shows that:
+\\ \noindent After plugging the equality in Eq.
+(\ref{important-step-is-zero}) into Eq.
+(\ref{eq:important-step}), we see that the left hand side of Eq.
+(\ref{step-one}) simplifies to $\ubf_{\abf}$.
+Now, to complete the proof we must check if Eq.
+(\ref{step-two}) holds for our candidate distribution.
+Summing up the elements of the stationary distribution $\ubf_\abf$ for all states $\abf \in \A$: \\
 \begin{align}
-\sum_{\abf \in \A} \ubf_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau^k_{\abf^k} \\ \notag \\
-\label{step-prod-sum-sum-prod}
-&= \left( \prod_{k=1}^N \sum_{\abf' \in \A} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\abf \in \A} \prod_{k=1}^N \displaystyle e^{\beta \pi^k_{\abf^k}} \right) \\ \notag \\
-\label{step-prod-is-one}
-&= 1
+\sum_{\abf \in \A} \ubf_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau_{k:\abf_k} = \sum_{\abf \in \A} \frac{\displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}}{\displaystyle \quad \prod_{k=1}^N \sum_{a' \in \A_k} e^{\beta \pi_k(a',\qbf_{-k})}}
 \end{align}
-\noindent The step from Eq.
-\ref{step-prod-sum-sum-prod} to Eq.
-\ref{step-prod-is-one} is possible because the sum and product in Eq.
-\ref{step-prod-sum-sum-prod} are interchangeable for both the terms.
-Therefore, condition Eq.
-\ref{step-two} is satisfied too.
+%\\ \notag \\
+%\label{step-prod-sum-sum-prod}
+%&= \left( \prod_{k=1}^N \sum_{\abf' \in \A} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\abf \in \A} \prod_{k=1}^N \displaystyle e^{\beta \pi^k_{\abf^k}} \right) \\ \notag \\
+%\label{step-prod-is-one}
+%&= 1
+\noindent \\ \\ where $\qbf_{-1}, \qbf_{-2},...,\qbf_{-N}$ are fixed tuples from $\A_{-1}, \A_{-2},...,\A_{-N}$ respectively.
+The denominator in the above expression can be taken out completely from the first sum.
+That is,
+\begin{align}
+\sum_{\abf \in \A} \ubf_\abf = &\sum_{\abf \in \A} \frac{\displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}}{\displaystyle \quad \prod_{k=1}^N \sum_{a' \in \A_k} e^{\beta \pi_k(a',\qbf_{-k})}} \\[15pt]
+=& \left( \displaystyle \prod_{k=1}^N \left( e^{\beta \pi_k(a_{k,1}, \qbf_{-k})}+...
++ e^{\beta \pi_k(a_{k,m_k}, \qbf_{-k})} \right) \right)^{-1} \cdot \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})} \right) \\
+\end{align} \\
+\noindent Multiplying out the sums in the denominator of the above expression, we get that:
+\begin{align}
+\sum_{\abf \in \A} \ubf_\abf =& \left( \displaystyle \prod_{k=1}^N \left( e^{\beta \pi_k(a_{k,1}, \qbf_{-k})}+...
++ e^{\beta \pi_k(a_{k,m_k}, \qbf_{-k})} \right) \right)^{-1} \cdot \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})} \right) \\[10pt]
+=& \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}  \right)^{-1} \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}  \right) = 1
+\end{align}
+\noindent Therefore, the stationary distribution sums up to 1. The candidate distribution we propose for the additive game is the unique stationary distribution of the process.
 \end{proof}

### 2023-02-08 latex/article.tex
proposition 2 and 3 proofs checked

@@
 \newcommand{\qbf}{\mathbf{q}}
+\newcommand{\pbf}{\mathbf{p}}
 \newcommand{\T}{\mathbf{T}}
@@
 The denominator in the above expression can be taken out completely from the first sum.
-That is,
+That is, \\
 \begin{align}
@@
 =& \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}  \right)^{-1} \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}  \right) = 1
-\end{align}
+\end{align} \\ 
 \noindent Therefore, the stationary distribution sums up to 1. The candidate distribution we propose for the additive game is the unique stationary distribution of the process.
@@
 \textbf{Proof of Proposition} \ref{Th:additive-game-product-of-marginals} \\ \\ 
-If $\ubf$ is the unique stationary distribution of the $N-$player additive game with under the finite selection introspection dynamics, it is given by the expression in Eq.
-\ref{Eq:additive-game-stationary-distribution}.
-We calculate the marginal distribution of any arbitrary state $\abf$, $\xi_{\abf} = (\xi^j_{\abf^j})_{j = 1,2,...,N}$ by using the definition of marginal distribution in Eq.
-\ref{Eq:marginal-definition}.
-It follows that:
+Just like the previous proof, we will denote $\pbf_{-1}, \pbf_{-2},...,\pbf_{-N} $ as fixed tuples from $\A_{-1}, \A_{-2},...,\A_{-N}$ respectively.
+In the steps below, we always decompose the expression $f_j(a,b)$ to $\pi_j(a,\pbf_{-j}) - \pi_j(b,\pbf_{-j})$.
+When $\ubf = (\ubf_\abf)_{\abf \in \A}$ is the unique stationary distribution of the $N-$player additive game under finite selection introspection dynamics, it is given by the closed form expression in Eq.
+(\ref{Eq:additive-game-stationary-distribution}).
+We use this expression to calculate the marginal distribution of actions played at a particular state $\abf$, $(\xi_{j:\abf_j})_{j \in \{1,2,...,N\}}$.
+\newpage
 \begin{align}
-\xi^j_{\abf^j} &= \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(\abf^j,\mathbf{b})} \\ \notag \\
-&= \left( \prod_{k=1}^N \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
-&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \prod_{k\neq j} \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
-&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\abf' \in \A^{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
-&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \left( \pi^j_{\abf'} - \pi^j_{\abf^j}\right)}\right)^{-1}
-\end{align}
-\noindent Therefore, the marginal distribution follows Eq.
-\ref{Eq:marginal-at-additive-game}.
-Now since we also additionally know that the stationary distribution follows the form Eq.
-\ref{Eq:additive-game-stationary-distribution}, we can conclude that for additive games, under introspection dynamics with finite selection, Eq.
-\ref{Eq:additive-game-products} holds.
+\xi_{j:\abf_j} &= \sum_{\qbf \in \A_{-j}} \ubf_{(\abf_j,\qbf)} \\ \notag \\
+&= \sum_{\qbf \in \A_{-j}} \left( \sum_{a' \in \A_j} \displaystyle e^{\beta f_j(a',\abf_j)}\right)^{-1} \prod_{k \neq j} \left( \sum_{a' \in \A_k} \displaystyle e^{\beta f_k(a',\qbf_k)}\right)^{-1} \\ \notag \\
+&= \left( \prod_{k=1}^N \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k (a', \pbf_{-k})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k, l_{-k})} \right) \\ \notag \\
+\label{step-prod-sum}
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})}\cdot \left( \prod_{k\neq j} \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k(a',\pbf_{-k})}\right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k,\pbf_{-k})} \right) \\ \notag \\
+\label{step-sum-prod}
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})}\cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi_k(\qbf_k,\pbf_{-k})} \right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k,\pbf_{-k})}  \right) \\ \notag \\
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \left( \pi_j(a',\pbf_{-j}) - \pi_j(\abf_j,\pbf_{-j})\right)} \right)^{-1}\\ \notag \\
+\label{final-expression}
+&= \sum_{a' \in \A_j} \displaystyle e^{\beta f_j(a',\abf_j)}
+\end{align} \\
+\noindent The interchange of the sum and the product between the expressions in Eq.
+(\ref{step-prod-sum}) and Eq.
+(\ref{step-sum-prod}) can be carried out by observing that when all the sums are multiplied out, one is left with sums of terms, each of which is a exponential with power equal to sum of payoffs that co-players of $j$ (here $k$) receive when they play their respective strategies from $\qbf$ (that is $\qbf_k$) against co-players that play $\pbf_{-k}$.
+Using the expression in Eq.
+(\ref{final-expression}), we can confirm that for additive games, the product of the marginals is the stationary distribution,
+\begin{equation}
+\prod_{j=1}^N \xi_{j:\abf_j} = \ubf_\abf
+\end{equation} 
 \end{proof}
@@
 \textbf{Proof of Proposition} \ref{prop:stationary-dist-lpgg} \\ \\
-Since we have demonstrated that the linear public goods game is an additive game, the proof of this theorem can be performed by directly using Theorem \ref{Th:additive-games-stationary-dist}.
+Since we have demonstrated that the linear public goods game is an additive game, the proof of this theorem can be performed by directly using proposition \ref{Th:additive-games-stationary-dist}.
 Here, we provide an independent proof.
-The idea behind this proof is identical to the proof of Theorem \ref{Th:additive-games-stationary-dist}.
+The idea behind this proof is identical to the proof of proof\ref{Th:additive-games-stationary-dist}.
 \\ \\
-\noindent The stationary transition matrix $\T$ for the linear public goods game is primitive when $\beta$ is finite (i.e., there is a positive power $k$ such that $\T^k$ is a strictly positive matrix).
-Therefore, the stationary distribution of $\T$ will always be unique.
-We define the following short cut notations for the ease of the proof:
-\begin{eqnarray}
-\bar{\abf}^j &:= \{\D,\C\} \setminus \abf^j  \\ 
-p^j &:= \frac{1}{1 + \displaystyle e^{\beta f(c^j, r^j)}} 
-\end{eqnarray}
+\noindent Using proposition \ref{Prop:unique-stationary-dist}, we can confirm that since $\beta$ is finite, the process will have a unique stationary distribution.
+Before continuing with the rest of the proof where we show that our candidate stationary distribution is \emph{the} unique stationary distribution, we define the following short-cut notations for the ease of the proof:
+\begin{align}
+\bar{\abf}_j &:= \{\D,\C\} \setminus \{\abf_j\}  \\ \notag \\ 
+p_j &:= \frac{1}{1 + \displaystyle e^{\beta f_j(\D, \C)}} 
+\end{align} \\
 In addition we introduce a mapping function $\alpha(.)$ which maps the action $\C$ to 1 and the action $\D$ to 0.
@@
 Using these notations and Eq.
-\ref{Eq:introspection-update} and \ref{Eq:difference-payoffs-lpgg} we can write the probability that a player $j$ updates from $\abf^j$ to $\bar{\abf}^j$ while their co-players play $\abf^{-j}$ as: \\
+(\ref{Eq:introspection-update}) and (\ref{Eq:difference-payoffs-lpgg}) and utilizing our shortcut notation from above, we can write the probability that a player $j$ updates to $\abf_j$ from $\bar{\abf}_j$ while their co-players play $\abf_{-j}$ as: \\
 \begin{equation}
-p^j_{\displaystyle \bar{\abf}^j  \to \abf^j} (\abf^{-j}) = p^j \mathit{sign}(\abf^j) + \alpha(\bar{\abf}^j) \\ \\
-\end{equation}
-The candidate stationary distribution $\ubf$ given in Eq \ref{Eq:stationary_dist_lpgg} can be written down using our shortcut notation as: 
+p_{\displaystyle \bar{\abf}_j  \to \abf_j} (\abf_{-j}) = p_j \mathit{sign}(\abf_j) + \alpha(\bar{\abf}_j) 
+\end{equation}\\
+The candidate stationary distribution $\ubf$ given in Eq. (\ref{Eq:stationary_dist_lpgg}) can be written down using our short-cut notation as: \\
 \begin{equation}
 \label{Eq:stationary-dist-shortcut}
-\ubf_\abf = \prod_{k = 1}^{N}  p^k \mathit{sign}(\abf^k) + \alpha(\bar{\abf}^k) \quad ,\forall \abf \in \{0,1\}^N
-\end{equation}
-This stationary distribution must satisfy the following properties, which are also given in Eq  \ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}:
+\ubf_\abf = \prod_{k = 1}^{N}  p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k)
+\end{equation}\\
+This stationary distribution must satisfy the following properties, which are also given in Eq  (\ref{Eq:lefteigenvector}) and (\ref{Eq:normalizationcondition}):
 \begin{align}
 \label{Eq:transition-in-proof}
-&\ubf_\abf = \T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\[10pt] 
+&\ubf_\abf = \T_{\abf,\abf} \ubf_\abf  + \sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf}  \\[10pt] 
 \label{Eq:normalization-in-proof}
-&\sum_{\forall \abf_q} \ubf_{\abf_q}= 1
+&\sum_{\abf \in \A} \ubf_{\abf}= 1
 \end{align}

### 2023-02-16 latex/article.tex
abstract intro sections new bibliography

@@
 \section*{Abstract}
+
+% 150 to 250 words
+% 4 to 6 keywords: multiplayer games, asymmetric games, non-linear interactions, learning model, introspection dynamics, strategy abundance
+
+The simplest form of social interaction occurs between two nearly similar individuals. This scenario can be stylized in a pairwise symmetric game. 
+More complex behavior emerges when instead we consider multiple interacting individuals, and they may differ significantly among themselves.
+This case can be captured by a multiplayer asymmetric game.
+The complexity of these games increases both with the number and diversity of players.
+From evolutionary dynamics to learning models, game theoretic frameworks have been widely used to study strategic behavior. 
+Introspection dynamics has proven to be a useful learning model for tackling complex games. 
+It provides a simple way to compute the average abundance of each combination of strategies (or actions), that is, the stationary distribution of strategies.
+Here, our aim is to analyse multiplayer and (a)symmetric games.
+We extend previous analytical results on pairwise games under introspection dynamics to multiplayer games. 
+For general games, we obtain the analytical stationary distribution for 2 strategies, symmetric games.
+Moreover, we consider a particular class of games -- additive games. 
+In additive games, for any player, the difference between the payoffs provided by any two actions is constant, regardless of the co-players' actions. 
+For these games, we derive the stationary distribution analytically, for any number of players and strategies, with no restriction to symmetric games. 
+To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas. 
+In general, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
+% 244 words
+
+%In addition, we find that the frequency of a state (a combination of actions played by each player) corresponds to the product of the frequencies of each player playing their respective strategy.
+
+\begin{comment}
+The simplest form of social interaction occurs between two nearly similar individuals. This scenario can be stylized in a pairwise symmetric game. 
+More complex behavior emerges when instead we consider multiple interacting individuals, and they may differ significantly among themselves.
+This case, in turn, can be captured by a multiplayer asymmetric game.
+The complexity of these games increases both with the number and diversity of players.
+From evolutionary dynamics to learning models, game theoretic frameworks have been widely used to study strategic behavior. 
+Introspection dynamics has proven to be a useful learning model to tackle complex games.
+%To analyse more complex games, reserachers typically use approximations, e.g. weak selection, small mutation. 
+Here, our aim is to analyse multiplayer and (a)symmetric games. We extend previous analytical results of pairwise games under introspection dynamics to multiplayer games. 
+We divide games in two main categories: additive and non-additive (or general) games.
+In additive games, for any player, the difference between the payoffs provided by any two actions (or strategies) is constant, regardless of the co-players' actions. 
+Non-additive are all games that do not hold this property; hence, general games.
+For additive games, we derive the stationary distribution of strategies analitically, for any number of players and strategies. 
+%Additionally, we find that the joint distribution of strategies factorizes over the marginal distribution of strategies.
+Additionally, we find that the frequency of a state (a combination of actions played by each player) corresponds to the product of the frequencies of each player playing their respective strategy.
+For non-additive games, we obtain the analytical stationary distribution for 2-strategies symmetric games. For other cases, we provide numerical results. 
+To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas. 
+In general, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
+%add rewarding game
+\end{comment}
 \newpage
 \section*{Introduction}
+
+%[Multiplayer games]
+
+% Pairwise vs Multiplayer Games
+The simplest form of social interaction occurs between two individuals.
+These pairwise interactions have been studied extensively \cite{bibid}.
+Despite their simplicity, they provide important insights, e.g., on how social species can maintain cooperation \cite{bibid}.
+An ubiquitous example of a model game for two players is the prisoner's dilemma.
+There, the two individuals have a temptation to cheat on each other, while both would be better off by offering mutual help.
+Solving this apparent paradox has been the focus of many studies, where various explanations were proposed \cite{bibid}.
+%some references
+\\ \\
+% non-linearity
+\noindent Yet, many interesting collective behavior occur when multiple individuals interact simultaneously \cite{Palm:JMB:1984, Skyrms:book:2003, Pacheco:PRSB:2009, Archetti:EL:2011, Archetti:JTB:2012, Gokhale:DGAA:2014, Hilbe:JTB:2015, Venkateswaran:PRSB:2019}.
+% + refs!
+Notably, most of these situations cannot be captured by the sum of several pairwise interactions.
+Thus, to account for such non-linearities we need to consider multiplayer games \cite{Gokhale:DGAA:2014}.
+One well-known effect that only emerges when more than two players are present is the second-order free riding problem \cite{Pal:NatCom:2022}.
+A natural solution to maintain pro-social behavior in a community is to monitor and punish defectors (and/or reward cooperators).
+However, most forms of sanctioning are considerably costly \cite{bibid}.
+Therefore, an additional (second-order) dilemma is at stake: deterring defection is beneficial for all, but an individual that does not pay the associated cost has an advantage over the ones that do.
+As such, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms or a suitable design \cite{Couto:JTB:2020}.
+%refs
+\\ \\
+\noindent 
+% size
+Another interesting aspect of multiplayer games is the scale or size of the interaction itself.
+Are many-player social dilemmas harder to solve than small-groups'?
+\cite{Skyrms:book:2003}.
+Indeed, in situations that require some sort of coordination and expectations on others play an important role in one's decisions (like in stag-hunt games), it is easy to see how a growing group size might hinder the optimal outcome -- it is hard to cooperate in large groups \cite{bibid}.
+% need ref here!
+\cite{Hilbe:JTB:2015}
+This is not a general effect, though.
+It can happen that adding more players actually promotes cooperation.
+As a biological example, consider a task allocation problem in a bacterial system.
+A strain of bacteria can do any of three actions: to specialize in producing one of two kinds of enzymes (at some personal cost) or not to produce any enzyme.
+The bacteria need the two different types of enzymes at the same time to obtain resources from the environment.
+In \cite{gokhale:JTB:2011}, authors investigate both the 2-player and 3-player cases of this scenario.
+Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, and hence the outcomes.
+With three players, the production of one of the enzymes increases while freeloading decreases, comparing to the 2-player case.
+Additionally, not only the average group size can have an important effect, but also the variance of the group size distribution \cite{Pena:Evolution:2011, Broom:BMB:2019}.
+\\ \\ 
+%[Asymmetric (multiplayer) games]
+\noindent Complexity further increases when players differ significantly among themselves.
+This diversity can be captured by asymmetric games \cite{Taylor:JAP:1979, Schuster:AB:1981, Gaunersdorfer:TPB:1991, Hofbauer:JMB:1996, Hofbauer:GEB:2005, Ohtsuki:JTB:2010, McAvoy:PlosCB:2015, Veller:JET:2016, Hauser:Nature:2019}.
+In symmetric games, all players are indistinguishable.
+Thus, to fully characterise a state of the game, we only require to know the number of players playing each strategy.
+Conversely, in asymmetric games, players can be different in several ways.
+We say they are of different types or roles, which can differ in payoffs and strategies.
+Therefore, they can have uneven effects on others' payoffs too.
+For example, in a public goods game, even if every player chooses to cooperate, their contributions to the common good or, alternatively, the cost they pay might be diverse \cite{Hauser:Nature:2019}.
+Hence, to fully describe a state of the game, we need to know which of the players is doing what.
+This greatly increases the size of the game's state space; even more so, for more than two players.
+\\ \\
+%meta communication; lit gap; our aim
+\noindent From this, we see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
+Perhaps for that reason, there are not many studies on multiplayer asymmetric games, compared to their simpler counterparts.
+Some exceptions are \cite{Hauser:Nature:2019}.
+%refs
+Still, we believe a general approach is lacking.
+As such, our aim here is to narrow that gap, by studying multiplayer, (a)symmetric games.
+In the following, we discuss several canonical frameworks from the literature that have been used to study both multiplayer and asymmetric games.%, pointing out the gaps.
+
+%possibly new section \section*{Background} but then where to put "proposal"?
+
+\section*{Related Work}
+
+%[Frameworks]
+
+% deterministic EGT
+From evolutionary game theory \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior.
+In evolutionary game theory, we assume a population of players and a mechanism by which strategies evolve over time.
+More successfull strategies tend to persist in the population, either by genetic or cultural inheritance.
+The first key concept in evolutionary game theory is ``evolutionary stable strategy" (ESS),  introduced in 1973, in the seminal paper of John Maynard Smith and George Price \cite{Maynard-Smith:Nature:1973}.
+A monomorphic population playing an ESS cannot be invaded by mutants.
+The concept of ESS, originally proposed for parwise encounters, was already extended for multiplayer games in \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}.
+Although suggestive of an evolutionary process, ESS does not really describe a dynamical system.
+In the more classical infinite population models, ordinary differential equations are the central mathematical tools \cite{Hofbauer:book:1998}.
+One of the most famous of these dynamics is the replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998}.
+Replicator equation has been widely used and easily comprises multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Pena:Evolution:2011, Cressman:PNAS:2014, Pena:JTB:2014}.
+More recently, also the replicator-mutator equation was applied to study the dynamics of multiplayer games \cite{Duong:DGAA:2020}.
+As for asymmetric games, a few additional assumptions are needed.
+For example, if there are two different types of players, typically, either there are two populations co-evolving (``bimatrix games" \cite{Hofbauer:book:1998, Tuyls:SciRep:2018}) or there is a single population of players where each can play the two types or roles (``role games") \cite{Hofbauer:book:1998}.
+In the latter kind of model, a strategy must include the action played in each of the two roles.
+% asymmetric multiplayer replicator dynamics?
+% 1+ paper for role games
+\\ \\
+% stochastic EGT
+\noindent To account for stochastic effects naturally present in finite populations, another set of tools was developed, known as stochastic evolutionary game dynamics.
+\cite{Nowak:Nature:2004, Traulsen:bookchapter:2009}.
+Besides the finiteness of population sizes, it also considers random mutations.
+Here, the quantitites of interest are fixation probabilities and fixation times (i.e., the probability and average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{bibid}, or average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}.
+\\ \\
+%When deriving fixation probabilities and times, it is assumed that mutations are rare, such that, no new mutant arises between the very first and its eventual fixation \cite{}. 
+%\cite{Chalub:BMB:2019}
+\noindent 
+These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types.
+Fixation probabilities for asymmetric 2-player \cite{Sekiguchi:DGA:2017} and 3-player games \cite{Sekiguchi:DGA:2022} were recently derived.
+Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:PNAS:2010, gokhale:JTB:2011, Wu:Games:2013}.
+For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to \cite{Gokhale:DGAA:2014}.\\
+%comment on pervasiveness of weak selection
+%strategy abundance papers (intermediate mutation or mutation-selection equilibrium)
+%2-player symmetric and asymmetric games, any number of strategies, Birth-death process \cite{ohtsuki:JTB:2010}
+%2-player symmetric and asymmetric games, any number of strategies, Death-birth process \cite{Sekiguchi:PA:2013}
+
+% multiplayer 
+%\cite{gokhale:PNAS:2010}
+%\cite{gokhale:JTB:2011} extends the approach in \cite{antal:JTB:2009b} for 2-player to multiplayer (symmetric) games. 
+%\cite{Wu:Games:2013} symmetric, any number of strategies, Birth-death process (equations connections?)
+%\cite{Gokhale:DGAA:2014} review on evolutionary multiplayer games both for infinitely large populations as well as finite population
+
+% nice multiplayer applications
+
+%[Learning models]
+%learning models in general
+\noindent Different from evolutionary game theory, learning models (of strategic behavior) take another approach \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Hofbauer:GEB:2005, Tuyls:bookchapter:2005, Galla:PNAS:2013, Barfuss:PRE:2019, Barfuss:PNAS:2020, Pangallo:GEB:2022}.
+There is no evolution of strategies in a population necessarily, but a process by which individuals learn strategies dynamically.
+Despite of the conceptual disparities, there have been some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005}.
+\\ \\
+\noindent Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from classical game theory itself \cite{fudenberg:book:1998b}.
+The ``theory of learning in games" was proposed as a refinement of classical equilibrium concepts, like Nash equilibrium, where strict assumptions of common knowledge of rationality are made.
+Instead, learning consists of ``\textit{an alternative explanation that equilibrium arises as the long-run outcome of a process in which less than fully rational players grope for optimality over time}" \cite{fudenberg:book:1998b}.
+In this context, several learning models were introduced, such as fictitious play \cite{bibid}.
+\\  \\
+%learning models for asymmetric and multiplayer games? fictious play for multiplayer games \cite{fudenberg:book:1998b} 
+%can we say most of learning models have no analytical or exact results?
+%quantal response equilibrium
+%introspection dynamics
+\noindent Introspection dynamics has proven to be a useful learning model for tackling 2-player, asymmetric games \cite{Couto:NJP:2022}.
+This feature comes from the fact that players update their strategies by exploring their own set of strategies in the following simple way: at each time, after a round of the game, a player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, the player more likely adopts it on the next round.
+While in \cite{Couto:NJP:2022} only 2-player games were considered, this framework is general enough to account for multiple players.
+Indeed, as each player assumes that all others remain the same when doing the counterfactual comparison, introspection dynamics is an appropriate model to deal with the complexity introduced by multiple players.
+\\ \\
+%[Our proposal]
+\noindent Here, we extend previous analytical results of pairwise games under introspection dynamics to multiplayer games. 
+For general games, we obtain the analytical stationary distribution for 2-strategies symmetric games.
+For a particularly simple class of games -- additive games -- we derive the stationary distribution of strategies analytically, for any number of players and strategies, and with no restriction to symmetric games.
+To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas, extending the framework in \cite{Hauert:JTB:2006a} to asymmetric games.
+
 \section*{Model}
@@
 \section*{Additive games and their properties under introspection dynamics}
-In this section we discuss the stationary properties of introspection dynamics on a special class of games - the additive games \cite{pena2014gains, mcavoy2015asymmetric}.
-In an additive game, the payoff difference that a player earns by making a switch in their actions is independent of what their co-players play while they make this switch.
-In other words, if none of the co-players change their strategy, the payoff difference earned by making a particular switch is \emph{only} determined by the switch and not on the co-players' play.
-This property is sometimes called the \emph{equal gains from switching} \cite{pena2014gains} property of a game.
-That is, for any player $i$, any pair of actions $x,y \in \A_i$, and any $\qbf \in A_{-i}$,
+In this section we discuss the stationary properties of the introspection dynamics when players learn to play strategies in a special class of games: the additive games \cite{pena2014gains, mcavoy2015asymmetric}.
+In an additive game, the payoff difference that a player earns by making a unilateral switch in their actions is independent of what their co-players play.
+In other words, if none of the co-players change their current actions, the payoff difference earned by making a switch in actions is \emph{only} determined by the switch and not on the actions of the co-players'.
+Formally, in additive games, for any player $i$, any pair of actions $x,y \in \A_i$, and any $\qbf \in \A_{-i}$,
 \begin{equation}
@@
 \end{equation}
-\noindent For games with this property, the stationary distribution takes a simple form as shown in the proposition below.
+\noindent is independent of $\qbf$ and only dependent on $x$ and $y$.
+In the literature, this property is sometimes called the property of \emph{equal gains from switching} \cite{pena2014gains}.
+For games with this property, the stationary distribution of introspection dynamics takes a simple form;
 
@@
 \end{equation}
-where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf_j$.
+where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play from $\abf_j$  to $a'$.
 \label{Th:additive-games-stationary-dist}
 \end{Prop}
-\noindent The above proposition gives a closed form expression of the stationary distribution of the introspection dynamics for additive games.
-For any finite value of the selection parameter, $\beta$, the stationary distribution can be computed using the expression in Eq.
+\noindent For any finite value of the selection strength parameter, $\beta$, the stationary distribution of the process for an additive game can be exactly computed using the expression in Eq.
 (\ref{Eq:additive-game-stationary-distribution}).
-For proof, see Appendix \ref{Section:Appendix}.
-Additive games are particularly interesting under the introspection dynamics because of the following relationship between the stationary distribution and marginal distributions,
+For a proof, see Appendix.
+Using the stationary distribution, one can also exactly compute the cumulative probabilities with which players play their actions in the long run (i.e., the marginal distribution) using Eq.
+(\ref{Eq:marginal-definition}).
+In this regard, introspection learning in additive games is particularly interesting.
+The stationary distribution and the marginal distributions of introspection learning in additive games are related in a special way,
 
@@
 
-\noindent where the marginal probability, $\xi_{j:\abf_j}$, is the cumulative probability that player $j$ plays $\abf_j$ at the stationary distribution. The marginal probability is given by:
+\noindent where the marginal probability, $\xi_{j:\abf_j}$, is the cumulative probability that player $j$ plays $\abf_j$ at the stationary distribution.
+The marginal probability for the $N$-player additive game is given by:
 
@@
 \end{equation}
-\noindent where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf_j$.
+\noindent where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play from $\abf_j$ to $a'$.
 \label{Th:additive-game-product-of-marginals}
 \end{Prop}
-\noindent The above proposition states that for additive games under introspection dynamics, the stationary distribution can be factorized into its corresponding marginals.
-In the long run, the probability that players simultaneously play ($\abf_1, \abf_2, ...,\abf_N$) is the product of the cumulative probabilities that player 1 plays $\abf_1$, player 2 plays $\abf_2$ and so on.
-In the following subsection we study a classical additve game - the linear public goods game under the introspection dynamics and discuss the results.
+\noindent The above proposition states that for additive games, the stationary distribution of the introspection dynamics can be factorized into its corresponding marginals.
+In the long run, the probability that players simultaneously play the state ($\abf_1, \abf_2, ...,\abf_N$) is the product of the cumulative probabilities that player 1 plays $\abf_1$, player 2 plays $\abf_2$ and so on.
+While this factorizing property of the stationary distribution appears for additive games, we do not show that this property is unique to additive games.
+We use the well-studied example of the linear public goods game to demonstrate the stationary properties of the introspection dynamics in additive games.
 
 \subsection*{Example of an additive game: linear public goods game with 2 actions}
-Here, we analyze the linear public goods game with $N$-players.
-Each player has two possible actions, to contribute (action, $\C$), or to not contribute (action, $\D$).
-The players differ in their cost of cooperation and the benefit they provide to the public goods.
-The cost of cooperation for player $i$ and the benefit they provide to the public goods are denoted with $c_i$ and $b_i$ respectively.
+In the simplest version of the linear public goods game with $N-$players, each player has two possible actions, to contribute (action, $\C$, to cooperate), or to not contribute (action, $\D$, to defect) to the public good.
+The players differ in their cost of cooperation and the benefit they provide by contributing to the public good.
+We denote the cost of cooperation for player $i$ and the benefit that they provide to the public good with $c_i$ and $b_i$ respectively.
+In addition, we define a mapping function $\alpha(.)$ to map the action of cooperation to 1 and the action of defection to 0.
+That is $\alpha(\C) = 1$ and $\alpha(\D) = 0$.
 The payoff of player $i$ when the state of the game is $\abf$ is given by: \\
 \begin{equation}
-\pi_i(\abf) = \sum_{j=1}^N \frac{\displaystyle \abf_j b_j}{N} - \abf_i c_i
+\pi_i(\abf) = \sum_{j=1}^N \frac{\displaystyle \alpha(\abf_j) b_j}{N} - \alpha(\abf_i) c_i
 \label{Eq:linear-pgg-payoff}
@@
 \end{equation}\\
-\noindent is independent of any $\qbf \in \A_{-i}$ that the co-players of $i$ play.
+\noindent is independent of co-players' actions $\qbf$.
 The linear public goods game is therefore an example of an additive game.
-This property of the game results in dominated strategies for player $i$ depending on the relationship between the benefits $b_i$, number of players $N$, and cost of cooperation $c_i$.
-When $c_i > b_i/N$, the action of not contributing ($\D$) dominates the action of contributing ($\C$) and \emph{vice-versa}.
-Using proposition \ref{Th:additive-games-stationary-dist}, we derive the following closed form expression for the stationary distribution of a $N-$player linear public goods game with two strategies.
+This property of the game results in dominated strategies for players.
+Defection dominates cooperation when $c_i > b_i/N$ while cooperation dominates defection when $c_i < b_i/N$.
+Using proposition \ref{Th:additive-games-stationary-dist}, one can derive the closed form expression for the stationary distribution of a $N-$player linear public goods game with two strategies.
 \begin{Prop}
@@
 \begin{cases}
-1 &\quad \text{if} \quad a = \C \\
--1 &\quad \text{if} \quad a = \D
+&1 \quad \text{if} \quad a = \C \\
+-&1 \quad \text{if} \quad a = \D
 \end{cases}
@@
 \end{Prop}
-\newpage
+\noindent We use a simple example to demonstrate the above result.
+Consider a 3-player linear public goods game.
+All players provide a benefit of 2 units when they contribute to the public good ($b_1 = b_2 = b_3 = 2$).
+They differ however in their cost of cooperation.
+For player 1 and 2, the cost of cooperation is 1 unit ($c_1 = c_2 = 1$) while for the third player, the cost is slightly higher at 1.5 units ($c_3 = 1.5$).
+In the stationary distribution of the process with selection strength $\beta = 1$, the state where player 1 and 2 play $\C$ and player 3 plays $\D$, $\ubf_{\C\C\D}$, occurs with probability $\approx 0.112$ (rounded up to three decimal places).
+We calculate this probability exactly with Eq.
+(\ref{Eq:stationary_dist_lpgg}).
+The marginal probabilities that in the long run player 1 (or player 2) plays cooperation and player 3 plays defection are 0.4 and 0.7 respectively.
+That is, $\xi_{1:\C} = \xi_{2:\C} \approx 0.4$ and $\xi_{3:\D} \approx 0.7$ (rounded upto a single decimal place).
+With the exact values (and also with the approximations here), one can confirm the factorizing property of the stationary distribution for additive games in this example (i.e., proposition \ref{Th:additive-game-product-of-marginals}).
+That is, $\ubf_{\C\C\D} = \xi_{1:\C} \cdot \xi_{2:\C} \cdot \xi_{3:\D}$.
+\\ \\
+\noindent First, we systematically the linear public goods game in which all players are symmetric.
+We consider a game with 4 players.
+All players have the same cost of cooperation ($c_i = c$) and they all provide the same benefit to the public goods ($b_i = b$).
+Since all players are identical, the states of the game can be enumerated by counting the number of cooperators in the state.
+There can only be 5 distinct states of the game (from 0 to 4 contributors).
+When the parameters of the game are such that defection dominates cooperation ($b = 2, c = 1$, Fig.
+\ref{}a), the stationary distribution of the process at high $\beta$ ($\beta = 5$), indicates an exponential decrease in the probability of a state with increase in the number of cooperators in the state.
+However, for intermediate and low $\beta$, the long-run outcomes of the introspection dynamics are qualitatively different to the outcomes at high $\beta$.
+Here, the state with $1$ cooperator (or even $2$ cooperators, depending on how small $\beta$ is) is the most probable state in the long-run (Fig.
+\ref{}b).
+Naturally, $\beta$ plays an important role determining the overall cooperation frequncy in the public goods game.
+When $\beta$ is low, the average cooperation frequency varies weakly with the strength of the dilemma, $b/N - c$ (Fig.
+\ref{}c).
+Even when the temptation to defect is high ($b/N - c \approx -2$), players cooperate with a non-zero probability in the long run ($\approx 0.1$).
+Similarly, when cooperation is highly beneficial ($b/N - c \approx 2$), players defect with some probability ($\approx 0.2$).
+At higher values of $\beta$, the stationary behaviour of the players is more responsive to the payoffs of the game and thus reflect an abrupt change around the parameter region where the game transitions from defection-dominating to cooperation-dominating ($b/N - c = 0$).
+\\ \\
+\noindent 
+For studying the linear public goods game with asymmetric players, we consider a setup with 3 players.
+All the players differ in their cost of cooperation and the benefit they provide to the public goods.
+In this setup, the reference player's (player 2) cost and benefit values are $1$ and $2$ units respectively.
+Player 1 and player 3 differ from the reference player in opposite directions.
+For player 1, the cost and benefit are $1 + \delta_c$ and $2 + \delta_b$ respectively while for player 3, the cost and benefit are $1 - \delta_c$ and $2 - \delta_b$, respectively.
+First, we study a simple case in which players only vary in their cost of cooperation ($\delta_b = 0$ and $\delta_c = 0.5$, Fig \ref{}a).
+In the long run, the relative cooperation frequency of players reflect their relative ability to cooperate.
+The player with the lowest cooperation cost (player 3), cooperates with the highest probability (and \emph{vice-versa}).
+Similarly, when players only differ in their ability to produce the public good ($\delta_b = 1$ and $\delta_c = 0$, Fig \ref{}b), their relative cooperation in the long run reflects the relative benefits they provide with their cooperation.
+The player with the highest benefit value (player 1) cooperates with the highest probability.
+For this particular setup with three asymmetric players, defection dominates cooperation for player 1 if and only if $\delta_b < 1 + 3\delta_c$ .
+For player 3, defection dominates cooperation only when $\delta_b > 3\delta_c - 1$.
+For the parameter values $b = 2, c = 1$, defection always dominates cooperation for the reference player.
+These regions in the $\delta_b-\delta_c$ parameter plane that correspond to defection dominating cooperation are circumscribed by white dashed lines in Fig.
+\ref{}c.
+When players learn to play at high selection strength, $\beta$, their cooperation frequency in the long-run reflect the rational play (Fig.
+\ref{}c).
+In the long run, the average cooperation frequency of the group is low if the asymmetry in the benefit value is bounded, $3\delta_c - 1 < \delta_b < 3\delta_c + 1$.
+This includes the case where players are symmetric ($\delta_b = \delta_c = 0$).
+A relatively high cooperation frequency is only assured if players are aligned in their asymmetries (i.e., either $\delta_b < 3\delta_c +1$ or $\delta_b > 3\delta_c - 1$).
+
+\section*{Games with two actions and their properties under introspection dynamics}
+
+In this section, we study the stationary properties of games with two actions.
+These games are not necessarily additive.
+First, we study the simplest case in which all players are symmetric.
+A $N$-player symmetric normal form game with two actions has the following properties:
+
+\begin{enumerate}
+\item  $\A_1 = \A_2 = ... = \A_N := \mathcal{A} := \{\C,\D\}$
+\item For any $i,j \in \{1,2,...,N\}$, $a \in \mathcal{A}$ and $\bbf \in \displaystyle \prod_{j=1}^{N} \mathcal{A}$:
+\begin{equation}
+\pi_i(a,\bbf) = \pi_j(a,\bbf)
+\end{equation} 
+\end{enumerate}
+
+\noindent Since players are symmetric, states can again be enumerated by counting the number of $\C$ players in the state.
+We denote the payoff of a $\C$ and $\D$ player in a state where there are $j$ $\C$ players with $\pi_\C(j)$ and $\pi_\D(j)$ respectively.
+From the previous section, we adopt the mapping function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to 0.
+We use the notation $\mathcal{C}(\abf)$ to denote the number of cooperators in the state $\abf$.
+That is,
+
+\begin{equation}
+\mathcal{C}(\abf) := \sum_{j=1}^N \alpha(\abf_j)
+\end{equation}
+
+\noindent 
+The stationary distribution of a two-action symmetric game under introspection dynamics can be explictly computed using the following proposition,
+
+\begin{Prop}
+\label{Prop:Symmetric-2-strategies-state}
+When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\ubf_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
+\begin{equation}
+\label{Eq:stationary-dist-symm-2-stgs-state}
+\ubf_\abf = \frac{1}{\Gamma} \displaystyle \prod_{j=1}^{\mathcal{C}(\abf)} \displaystyle e^{-\beta f(j-1)}
+\end{equation}
+where $f(j) := \pi^\D(j) - \pi^\C(j)$ is the payoff difference earned by switching the play from $\D$ and $\C$ when there are $j$ co-players playing $\C$.
+The term $\Gamma$ is the normalization factor given by:
+\begin{equation}
+\label{Eq:stationary-dist-normalization-symm-2-stgs-state}
+\Gamma = \displaystyle \sum_{\forall \abf' \in \mathcal{A}^N} \prod_{j = 1}^{\mathcal{C}(\abf')} \displaystyle e^{-\beta f(j-1)}
+\end{equation}
+\end{Prop}
+
+\noindent The number of unique states of the game can be reduced to $N+1$ from $2^N$ due to symmetry.
+In the reduced state space, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
+Then, Proposition \ref{Prop:Symmetric-2-strategies-state} can be reformulated by relabelling the states as follows,
+
+\begin{Corollary}
+\label{Lemma: Symmetric-2-stg}
+When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
+\begin{equation}
+\label{Eq:stationary-dist-symm-2-stgs}
+\ubf_k = \frac{1}{\Gamma} \cdot {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
+\end{equation} \\ 
+where, $k$ represents the number of $\C$ players in the state and $f(j) := \pi^\D(j) - \pi^\C(j)$ is the payoff difference earned by switching the play $\D$ and $\C$ when there are $j$ co-players playing $\C$.
+The term $\Gamma$ is the normalization factor, given by, \\
+\begin{equation}
+\label{Eq:normalization-Tk}
+\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
+\end{equation}
+\end{Corollary}
+\noindent The above lemma follows directly from Proposition \ref{Prop:Symmetric-2-strategies-state}.
+The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$, $\C$ players (and therefore $N-k$, $\D$ players).
+This count is simply the binomal coefficient $N \choose k$.
+For details, see the proof in the Appendix.
+In this paper, we do not derive a closed form expression for the stationary distribution of introspection dynamics in asymmetric games with two actions.
+Instead, we compute it numerically using the explicit formula in Eq.
+(\ref{Eq:explicit-stationary-dist-representation}).
+In the next section, we study the stationary behaviour of the introspection dynamics in the general public goods game (symmetric and asymmetric).
+
+\subsection*{An example of a  game with two actions: the general public goods game}
+
+To study general public goods game we adopt the framework of general social dilemmas from Hauert et al.
+\cite{Hauert:JTB:2006a}.
+This framework introduces a parametric normal form game with symmetric players.
+The players have two actions: cooperation, $\C$ and defection, $\D$.
+Here, we extend their framework to account for players with asymmetric payoffs.
+For player $i$, the cost of cooperation is $c_i$.
+The benefit that they can generate for the public good is $b_i$.
+However, in the general public goods game, the benefit of cooperation generated by a player is either synergized (or discounted) by a factor depending on the number of cooperators already in the group and the synergy/discount factor, $w$.
+If there are already $k-1$ cooperators in the group, the effective benefit provided to the public good by the $k^{th}$ cooperating player (say $i$), is $w^{k-1} b_i$.
+In this setup, we assume that all the orders in which cooperators' benefits can be synergized (or discounted) are equally likely.
+We clarify with an example.
+Consider that there are three cooperators in the group: player $i, j$ and $k$.
+The total benefit that they provide to the public good can be one of the six possibilities from $x + y w + z w^2$, where $x,y$ and $z$ are permutations  of $b_i, b_j$ and $b_k$.
+We assume that all the six possibilities are equally likely, and therefore, the expected benefit is given by $\bar{b}(1 + w + w^2)$ where $\bar{b} = (b_i + b_j + b_k)/3$.
+\\
+
+\noindent The complete state space of the game is $\A = \{\C,\D\}^N$.
+The payoff of a defector in a state $(\D, \abf_{-i})$ and that of a cooperator in state $(\C,\abf_{-i})$ where $\abf_{-i} \in \{\C,\D\}^{N-1}$ are respectively given by:
+
+\begin{align}
+\pi^{\D}_i(\D, \abf_{-i})&= \displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\D,\abf_{-i}) - 1} \right)\\[15pt]
+\pi^{\C}_i(\C, \abf_{-i}) &= \displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\C,\abf_{-i}) - 1} \right) - c_i
+\label{Eq:payoff-synergistic-asymmetric}
+\end{align} \\
+\noindent where $\mathcal{C}(a,\abf_{-i})$ is the number of cooperators in the state $(a,\abf_{-i})$ and $\alpha(.)$ is the mapping function that maps the actions $\C$ and $\D$ to 1 and 0 respectively.
+Note that the number of cooperators in the two states are related as: $\mathcal{C}(\D,\abf_{-i}) = \mathcal{C}(\C,\abf_{-i}) - 1$.
+In the symmetric case, were every player has the same cost and benefit values, the payoffs of a defector and a cooperator in a group with $k$ cooperators can be simply written as:
+
+\begin{align}
+\pi^{\D}_i(k) &= \frac{b}{N}(1 + w + w^2 + ... + w^{k-1}) \\[15pt]
+\pi^{\C}_i(k) &= \pi^{\D}_i(k) - c
+\label{Eq:payoff-synergistic-symmetric}
+\end{align}
+
+\noindent The parameter $w$ represents the nature of the public goods.
+The nature is linear when $w = 1$.
+Every additional cooperator's contribution is as valuable as the benefit that they can generate.
+When $w < 1$, the effective value of every new cooperator goes down by a factor of $w$ (compared to the last cooperator).
+The public goods is said to be discounting in that case.
+On the other hand when $w > 1$, every new contributor is more valuable than the previous one.
+These public goods are called synergistic.
+For the symmetric case, the relationship between the cost to benefit ration $cN/b$ and the discount/synergy factor determines the type of social dilemma arising from this general public goods game.
+In principle, this framework can produce generalizations of the prisoner's dilemma (defection dominating cooperation), the snowdrift game (no dominance but coexistence under the replicator dynamics), the stag-hunt game (no dominance but existence of an internal equilibrium that is unstable under the replicator dynamics) and the harmony game (cooperation dominating defection) with respect to its evolutionary trajectories.
+For more details see Hauert et al.
+\cite{Hauert:JTB:2006a}.
+We study the long term stationary behaviour of players when they learn through introspection dynamics.
+First we focus on only the symmetric version of this game.
+\\ \\ 
+\noindent To compute the stationary distribution of the symmetric general public goods game (PG), we use the closed for expression in Eq.
+(\ref{Eq:stationary-dist-symm-2-stgs}).
+We consider that every player in a 4-player game can generate a benefit $b$ of value $2$.
+We study an introspection process with selection strength $\beta = 5$.
+Before exploring the $c-w-N$ parameter space, we study four specific cases.
+In two of these cases, the public goods is discounted ($w = 0.5$) and in two other cases, the public goods is synergistic ($w = 1.5$).
+For each case we consider two sub-cases: one, in which cost is high ($c = 1$) and two, when cost is low ($c = 0.2$).
+The four parameter combinations are chosen such that each of them represents a unique social dilemma under the replicator dynamics.
+When the PG is discounted ($w = 0.5$) and costs are high ($c = 1$) defection dominates cooperation (the prisoner's dilemma).
+When the PG is discounted ($w = 0.5$) but costs are low ($c = 0.2$), the coexistence behaviour similar to the snowdrift game appears from the replicator equation.
+When the PG is synergistic ($w = 1.5$) and costs are high ($c = 1$), both cooperation and defection are locally stable equilibria.
+In addition there is also an internal equilibrium which is unstable.
+This represents the stag-hunt game.
+And finally when both the PG is synergistic and costs are low, cooperation dominates defection.
+This situation represents the harmony game.
+The stationary behaviour of the players from the introspection dynamics in these games reflect the outcomes from the replicator dynamics (Fig.
+\ref{}a).
+Since selection strength is chosen to be intermediate, in some of these cases, players play actions that are not optimal for the dilemma with positive probability in the long run.
+For example, even when the parameters of the game make cooperation to be the dominated strategy, there is a single cooperator in the group with a sizeable chance ($\approx 20\%$) in the long run.
+When the parameters of the game reflect the stag-hunt dilemma, players are more likely to coordinate their actions in the long run.
+The probabilities that the whole group plays $\C$ or $\D$ is higher than the probability that there is a group with mixed play.
+In contrast, when the parameters reflect the snowdrift game, we get the opposite effect.
+In the long run, mixed groups are more likely than homogeneous groups.
+In fact, the group with exactly 2 cooperators and 2 defectors is the most likely outcome in the long run.
+Finally, when the parameters of the game make defection the dominated action, all players in the group learn to play cooperation in the long run.
+\\ \\
+\noindent The average cooperation frequency of the group in the long run are shown in the $c-w$ and $N-w$ parameter planes in Fig \ref{}b.
+First, let us consider the case when the group size is fixed at 4 players (the $c-w$ plane in Fig\ref{}b).
+In that case if the cost of cooperation is too high, the average cooperation rate is negligible and does not change with the change in the nature of the public good.
+When the cost is not restrictively high, the discount/synergy parameter, $w$, determines the frequency with which players cooperate in the long run.
+A high $w$ for the public good would result in high cooperation in the long run (and \emph{vice-versa}).
+Next we consider the case where the cost of cooperation is fixed (the $N-w$ plane in Fig.
+\ref{}b).
+It is fixed to a value such that there is full cooperation in the long run in a group of arbitrary size when $w > 1$.
+In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run.
+For a fixed value of $w (< 1)$, cooperation rates fall with larger group sizes.
+
+\section*{Discussions and conclusion}
+
+%[Short summary]
+
+%[Comparison to other models]
+
+%[What we didn't do, limitations, further work]
+Introspection dynamics is a rather broad model.
+Here, we mainly focused on general cases to the detriment of more realistic, complex examples.
+Nevertheless, in the last section, we give one step forward in that direction, by studying a 2-stage game, where individuals are allowed to reward their co-players condition on previous actions.
+Clearly, there are a number of ways in which we can further employ our model.
+For example, other researchers recently studied multiplayer games considering multiple games played concurrentlyin \cite{Venkateswaran:PRSB:2019}, fluctuating environments \cite{Baron:JRSOP:2018}, continuous strategies \cite{Molina:JMB:2017}, or repeated interactions \cite{Hilbe:JTB:2015}.
+\\ \\
+\noindent
+Finally, for the sake of mathematical tractability, introspection dynamics, as we present it here, does not consider a population, not to mention complex population structures \cite{Broom:JTB:2012, Wu:Games:2013, Pena:JTB:2015, Pena:JRSI:2016, Pattni:JTB:2017, Su:PNAS:2022}.
+However, it can be equally applicable to population models.
+In that case, players obtain payoffs either from well-mixed or network-bounded interactions, as usual, but update their strategies introspectively.
+
+% examples
+%\cite{Baron:JRSOP:2018} multiplayer games with fluctuating environments
+%\cite{Molina:JMB:2017} multiplayer games continuous strategies
+%\cite{Venkateswaran:PRSB:2019} multiplayer in multiple games
+%\cite{Hilbe:JTB:2015} explore the evolution of direct reciprocity in groups of multiple players; in small groups, generosity allows the evolution of cooperation, whereas, in large groups, cooperation is unlikely to evolve.
+
+%networks/structure
+%\cite{Broom:JTB:2012, Wu:Games:2013, Pena:JTB:2015, Pena:JRSI:2016, Pattni:JTB:2017, Su:PNAS:2022}
+% broom territorial
+
+%\newpage
+%\begin{figure}[t!]
+%\centering
+%\includegraphics[width =  0.95\textwidth]{figures/figure1.eps}~\\[-0.4cm]
+%\caption{\onehalfspacing
+%\textbf{Symmetric linear public goods game,}
+%a) Frequency of each state in the stationary distribution of introspection dynamics.
+As players are indistinguishable here, each state can be fully defined by the number of cooperators.
+Parameters: $N = 4$, $b = 2$, $c = 1$ and $\beta = 5$.
+b) For the same game parameters ($N = 4$, $b = 2$ and $c = 1$), we now show the frequency of each state (same color code as in panel a) for varying selection strength $\beta$.
+Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators.
+Indeed, up to $\beta \approx 3$, state $0$ is not even the most frequent.
+c) Average cooperation frequency for varying dilemma strength.
+We use as a measure of the dilemma strength the marginal gain by choosing to cooperate over choosing to defect, $b/N - c$.
+When this quantity is low, we say there is a ``strong dilemma”, where there is no individual advantage to cooperate, whereas when the marginal gain is high, we say there is a ``weak dilemma” (or no dilemma), where to cooperate becomes advantageous.
+Typically, a linear public goods dilemma is defined as having a negative marginal gain (see conditions above).
+Here, we show the whole parameter range for completeness and a full grasp of this game.
+We also show the result for different values of selection strength, $\beta = 1, 5$ and $100$.
+For high $\beta$, we confirm the classical prediction that, assuming a negative marginal gain, defection is dominant.
+For low $\beta$, however, we see again that some cooperation is possible.
+}
+%\end{figure}
+
 \section*{Appendix: Proofs}
@@
 \end{align}
-Where, the terms in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified using Eq \ref{Eq:introspection-update} and \ref{Eq:transition-matrix} as follows:
+Where, the terms in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified using Eq. (\ref{Eq:introspection-update}) and (\ref{Eq:transition-matrix}) as follows:
 \begin{eqnarray}
-\T_{\abf,\abf} = 1 - \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}), (\bar{\abf}^k,\abf^{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \alpha(\abf^k)
+\T_{\abf,\abf} = 1 - \sum_{k=1}^{N} \T_{(\abf_k, \abf_{-k}), (\bar{\abf}_k,\abf_{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p_k \textit{sign}(\bar{\abf}_k) + \alpha(\abf_k)
 \label{Eq:first-term-rhs-proof}
 \end{eqnarray} 
-and additionally, also using Eq. \ref{Eq:stationary-dist-shortcut} the second term can be simplified too:
+and additionally, also using Eq. (\ref{Eq:stationary-dist-shortcut}) the second term can be simplified too:
 \begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k = 1}^N \T_{(\bar{\abf}^k,\abf^{-k}), (\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k,\abf^{-k})} \\[10pt]
-&= \frac{1}{N} \sum_{k = 1}^N \left(p^k \textit{sign}(\abf^k) +\alpha(\bar{\abf}^k) \right) \ubf_{(\bar{\abf}^k,\abf^{-k})} \\[10pt] 
+\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &= \sum_{k = 1}^N \T_{(\bar{\abf}_k,\abf_{-k}), (\abf_k, \abf_{-k})} \ubf_{(\bar{\abf}_k,\abf_{-k})} \\[10pt]
+&= \frac{1}{N} \sum_{k = 1}^N \left(p_k \textit{sign}(\abf_k) +\alpha(\bar{\abf}_k) \right) \ubf_{(\bar{\abf}_k,\abf_{-k})} \\[10pt] 
 \label{Eq:second-term-rhs-proof}
-&= \frac{\ubf_\abf}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \alpha(\abf^k) 
+&= \frac{\ubf_\abf}{N} \sum_{k=1}^{N} p_k \textit{sign}(\bar{\abf}_k) + \alpha(\abf_k) 
 \end{align}
 Now, using Eq.
-\ref{Eq:first-term-rhs-proof}, \ref{Eq:second-term-rhs-proof} one can show that the right hand side of Eq.
-\ref{Eq:transition-in-proof} is the element of the stationary distribution, corresponding to the state $\abf$, $\ubf_a$.
+(\ref{Eq:first-term-rhs-proof}) and (\ref{Eq:second-term-rhs-proof}) one can show that the right hand side of Eq.
+(\ref{Eq:transition-in-proof}) is the element of the stationary distribution, corresponding to the state $\abf$, $\ubf_a$.
 Now, to complete the proof, we must show that Eq.
-\ref{Eq:normalization-in-proof} is also true for our candidate stationary distribution.
+(\ref{Eq:normalization-in-proof}) is also true for our candidate stationary distribution.
 This can be done by decomposing the sum of the elements of the stationary distribution as follows:
 \begin{align}
-\sum_{\forall \abf_q} u_{\abf_q} =& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^N p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k) \\[10pt]
-=& \displaystyle \displaystyle \sum_{\forall \abf_q} (1-p^N)  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k)  + p^N  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k) \\[10pt]
-=& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k)
+\sum_{\abf \in \A} u_{\abf} =& \displaystyle \sum_{\abf \in \A} \prod_{k=1}^N p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k) \\[10pt]
+=& \displaystyle \displaystyle \sum_{\abf \in \A_{-\!N}} (1-p_N)  \prod_{k=1}^{N-1} p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k)  + p_N  \prod_{k=1}^{N-1} p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k) \\[10pt]
+=& \displaystyle \sum_{\abf \in \A_{-\!N}} \prod_{k=1}^{N-1} p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k)
 \end{align}
@@
 By construction, the candidate stationary distribution given by Eq.
-\ref{Eq:stationary-dist-symm-2-stgs-state} and Eq.
-\ref{Eq:stationary-dist-normalization-symm-2-stgs-state} is a probability distribution since it satisfies the condition in Eq.
-\ref{Eq:normalizationcondition} and for any state $\abf'$, $\ubf_{\abf'}$ is between 0 and 1.
-Moreover, since $\beta$ is finite, the transition matrix of the process $\T$ is primitive and therefore, it will have a unique stationary distribution.
+(\ref{Eq:stationary-dist-symm-2-stgs-state}) and Eq.
+(\ref{Eq:stationary-dist-normalization-symm-2-stgs-state}) is a probability distribution since it satisfies the condition in Eq.
+(\ref{Eq:normalizationcondition}) and for any state $\abf$, $\ubf_{\abf}$ is between 0 and 1.
+Moreover, since $\beta$ is finite, by proposition \ref{Prop:unique-stationary-dist}, the process will have a unique stationary distribution.
 To show that the candidate stationary distribution is the unique stationary distribution, we need to check if for this process, $\ubf \T= \ubf$.
 That is, the condition in Eq.
-\ref{Eq:transition-in-proof} must hold for all states $\abf$.
+(\ref{Eq:transition-in-proof}) must hold for all states $\abf$.
 We re-introduce some notations that we will use in this proof:
 \begin{align}
-\bar{\abf}^j &:= \{\D,\C\} \setminus \abf^j \\[10pt]
+\bar{\abf}^j &:= \{\D,\C\} \setminus \{\abf_j\} \\[10pt]
 \alpha(a)&:= 
@@
 \end{cases}\\[10pt]
-\mathcal{C}(\abf) &= \sum_{j=1}^N \alpha(\abf^j)
+\mathcal{C}(\abf) &= \sum_{j=1}^N \alpha(\abf_j)
 \end{align}
-For this process, the first term in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified as: 
+For this process, the first term in the right hand side of Eq. (\ref{Eq:transition-in-proof}) can be simplified as: 
 \begin{align}
-\ubf_{\abf} \T_{\abf,\abf}  &= \ubf_\abf - \ubf_{\abf} \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}),(\bar{\abf}^{k}, \abf^{-k})} \\[10pt]
-&= \ubf_{\abf} - \frac{\ubf_{\abf}}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}^{k}) \beta f(N_k)}}
+\ubf_{\abf} \T_{\abf,\abf}  &= \ubf_\abf - \ubf_{\abf} \sum_{k=1}^{N} \T_{(\abf_k, \abf_{-k}),(\bar{\abf}_{k}, \abf_{-k})} \\[10pt]
+&= \ubf_{\abf} - \frac{\ubf_{\abf}}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}_{k}) \beta f(N_k)}}
 \label{Eq:T_aa_u_a term}
@@
 \\ \noindent Where, the function $\mathit{sign}(.)$ is  defined as in Eq.
-\ref{Eq:sign-function} and$f(j)$ is the difference in payoffs between playing $\D$ and $\C$ when there are $j$ co-players playing $\C$.
-The term $N_k$ is the number of co-players of $k$ that play $\C$ in state $\abf$.
+(\ref{Eq:sign-function}) and$f(j)$ is the difference in payoffs between playing $\D$ and $\C$ when there are $j$ co-players playing $\C$.
+The term $N_k$ represents the number of co-players of $k$ that play $\C$ in state $\abf$.
 That is,
 \begin{equation}
-N_k := \sum_{j \neq k} \alpha(\abf^j)
-\end{equation}
+N_k := \sum_{j \neq k} \alpha(\abf_j)
+\end{equation} \\
 The second term in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified as, 
 \begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k, \abf^{-k})} \\[10pt]
+\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &= \sum_{k=1}^N \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \ubf_{(\bar{\abf}_k, \abf_{-k})} \\[10pt]
 \label{Eq:step-single-product}
-&= \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \prod_{j=1}^{\mathcal{C}((\bar{\abf}^k, \abf^{-k}))} e^{-\beta f(j-1)}\\[10pt]
-&=  \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k}
+&= \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \displaystyle \prod_{j=1}^{\mathcal{C}((\bar{\abf}_k, \abf_{-k}))} e^{-\beta f(j-1)}\\[10pt]
+&=  \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k})
 \label{Eq:step-product-broken}
@@
 \ref{Eq:step-single-product} and \ref{Eq:step-product-broken}, we took out one term from the product that is present in our candidate distribution.
-This term accounts for the $k^{th}$ players action in the neighbouring state $(\bar{\abf}^k, \abf^{-k})$ of $\abf$.
-For simplicity, we replace $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ with just $\T$ in the next steps.
+This term accounts for the $k^{th}$ players action in the neighbouring state $(\bar{\abf}_k, \abf_{-k})$ of $\abf$.
+For simplicity, we replace $\T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})}$ with just $\T$ in the next steps.
 We continue the simplification of Eq.
-\ref{Eq:step-product-broken} in the later steps by introducing terms that cancel each other.
+(\ref{Eq:step-product-broken})in the later steps by introducing terms that cancel each other.
 \\[10pt]
 \begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \cdot e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) + N_k)}
+\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k)}}{e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) +N_k)}} \cdot e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) + N_k)}
 \label{Eq:new-cancelable-term-introduced}
@@
 \\ \noindent The newly introduced term in Eq.
-\ref{Eq:new-cancelable-term-introduced} can be taken inside the product.
+(\ref{Eq:new-cancelable-term-introduced}) can be taken inside the product.
 Note that this term is 0 if the $k^{th}$ player plays $\D$ in the state $\abf$.
 When this term is taken inside the product bracket, products of exponent $e^{-\beta f(j-1)}$ can be performed for $j$ ranging from $1$ to the number of cooperators in state $\abf$, $\mathcal{C}(\abf)$.
-This product is then the stationary distribution probability $\ubf_\abf$.
+This product is then the candidate stationary distribution probability $\ubf_\abf$.
 That is,
 \begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \cdot e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) + N_k)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \\[10pt]
-&= \frac{1}{N} \sum_{k=1}^N  \T \cdot \left( \frac{1}{\Gamma} \prod_{j=1}^{\mathcal{C}(\abf)} e^{-\beta f(j-1)}\right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \\[10pt]
-&= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \cdot \ubf_\abf \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \label{Eq: last-step-w-fraction}
+\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \cdot e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) + N_k)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k)}}{e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) +N_k)}} \\[10pt]
+&= \frac{1}{N} \sum_{k=1}^N  \T \cdot \left( \frac{1}{\Gamma} \prod_{j=1}^{\mathcal{C}(\abf)} e^{-\beta f(j-1)}\right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k)}}{e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) +N_k)}} \\[10pt]
+&= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \cdot \ubf_\abf \cdot \frac{e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k)}}{e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) +N_k)}} \label{Eq: last-step-w-fraction}
 \end{align}
-\\ \noindent The fraction inside the sum in  Eq. \ref{Eq: last-step-w-fraction} can be simplified as follows leading to further simplification of Eq. \ref{Eq: last-step-w-fraction}:
+\\ \noindent The fraction inside the sum in  Eq. (\ref{Eq: last-step-w-fraction}) can be simplified as follows leading to further simplification of Eq. (\ref{Eq: last-step-w-fraction}):
 \begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \cdot \ubf_\abf \cdot e^{sign(\abf^k) \beta f(N_k)} 
+\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \cdot \ubf_\abf \cdot e^{sign(\abf_k) \beta f(N_k)} 
 \label{Eq:only-need-to-replace-T-now}
 \end{align}
-\\ \noindent In Eq. \ref{Eq:only-need-to-replace-T-now} we can replace the element of the transition matrix $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ by using the following: 
+\\ \noindent In Eq. (\ref{Eq:only-need-to-replace-T-now}) we can replace the element of the transition matrix $\T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})}$ by using the following: 
 \begin{equation}
-\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} = \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^k) \beta f(N_k)}} 
+\T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} = \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf_k) \beta f(N_k)}} 
 \label{Eq:transition-matrix-T-symm-2-stgs}
@@
 \\ \noindent Using the expression for the transition matrix element from Eq.
-\ref{Eq:transition-matrix-T-symm-2-stgs} into Eq.
-\ref{Eq:only-need-to-replace-T-now} and by using Eq.
-\ref{Eq:T_aa_u_a term}, we can simplify further:
+(\ref{Eq:transition-matrix-T-symm-2-stgs}) into Eq.
+(\ref{Eq:only-need-to-replace-T-now}) and by using Eq.
+(\ref{Eq:T_aa_u_a term}), we can simplify further:
 \begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^k) \beta f(N_k)}} \cdot  e^{sign(\abf^k) \beta f(N_k)} \\[10pt]
-&= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}^k) \beta f(N_k)}}  \\[10pt]
+\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf_k) \beta f(N_k)}} \cdot  e^{sign(\abf_k) \beta f(N_k)} \\[10pt]
+&= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}_k) \beta f(N_k)}}  \\[10pt]
 &= \ubf_\abf - \ubf_\abf \T_{\abf,\abf}
@@
 \\ \noindent The final step in the previous simplification shows that Eq.
-\ref{Eq:transition-in-proof} holds for any $\abf \in \{\C,\D\}^N$.
+(\ref{Eq:transition-in-proof}) holds for any $\abf \in \{\C,\D\}^N$.
 Therefore, the candidate distribution we propose in Eq.
-\ref{Eq:stationary-dist-symm-2-stgs-state} is the unique stationary distribution of the symmetric $N$-player game with two strategies.
+(\ref{Eq:stationary-dist-symm-2-stgs-state}) is the unique stationary distribution of the symmetric $N$-player game with two strategies.
 \end{proof}
-\newpage
+
 \begin{proof}
@@
 \bibliographystyle{unsrt}
-\bibliography{bibliography.bib }
+\bibliography{bibtex.bib}
 \end{document}

### 2023-02-17 latex/article.tex
changed equations and also made pgg rewards section. end of friday

@@
 \\ \\
-\noindent First, we systematically the linear public goods game in which all players are symmetric.
+\noindent First, we systematically study the linear public goods game in which all players are symmetric.
 We consider a game with 4 players.
@@
 \begin{align}
-\pi^{\D}_i(\D, \abf_{-i})&= \displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\D,\abf_{-i}) - 1} \right)\\[15pt]
-\pi^{\C}_i(\C, \abf_{-i}) &= \displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\C,\abf_{-i}) - 1} \right) - c_i
+\pi^{\D}_i(\D, \abf_{-i})&= \displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N \cdot \mathcal{C}(\D,\abf_{-i})} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\D,\abf_{-i}) - 1} \right)\\[15pt]
+\pi^{\C}_i(\C, \abf_{-i}) &= \displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N \cdot \mathcal{C}(\C,\abf_{-i})} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\C,\abf_{-i}) - 1} \right) - c_i
 \label{Eq:payoff-synergistic-asymmetric}
@@
 \ref{}b).
-It is fixed to a value such that there is full cooperation in the long run in a group of arbitrary size when $w > 1$.
+It is fixed to a value such that in a synergistic PG ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size.
 In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run.
-For a fixed value of $w (< 1)$, cooperation rates fall with larger group sizes.
+When the public good is discounted ($w < 1$), cooperation rates fall with larger group sizes.
+
+\section*{Application: Introspection learning in a game with cooperation and rewards}
+
+In all the examples that we have studied so far, players can only play two actions (or strategies).
+Introspection dynamics can also be used to study games in which players have larger strategy sets.
+In this section, we study the stationary behaviour of players in a game where each player has 16 possible strategies.
+To this end, we adopt the multiplayer cooperation and rewarding game from Pal et al.
+\cite{Pal:NatCom:2022}.
+In this game, there are two stages: in stage 1, players decide whether or not they contribute to a linear public good and in stage 2, they decide whether or not they reward their peers.
+When a player contributes to the public good, they pay a cost $c_i$ but generate a benefit worth $r_i c_i$ that is equally shared by everyone.
+When a player rewards a peer, they provide a reward benefit of $\rho$ to the peer and incur a cost of $\gamma_i$ to self.
+In between the stages, players get full information about the contribution of their peers.
+In the rewarding stage, players have four possible strategies: they can either reward all the peers who contributed (social rewarding), reward all the peers who defected (antisocial rewarding), reward all peers irrespective of contribution (always rewarding) or reward none of the peers (never rewarding).
+Before stage 1 commences, player $i$ knows, with some probability $\lambda_i$, the rewarding strategy of all his peers.
+In stage 1, players can have four possible strategies: they can either contribute or defect unconditionally or they can be conditional cooperators or conditional defectors.
+Conditional cooperators (or defectors) contribute (or do not contribute) when they have no information about their peers.
+When a conditional player, $i$, knows the rewarding strategy of all their peers (which happens with probability $\lambda_i$) and finds that there are $n_{\mathrm{SR}}$ social rewarders and $n_{\mathrm{AR}}$ antisocial rewarders in their group, they cooperate if and only if:
+
+\begin{equation}
+\rho(n_{\mathrm{SR}} - n_{\mathrm{AR}}) \geq c_i \left( 1 - \frac{r_i}{N} \right)
+\label{Eq:palrewardsequation}
+\end{equation}
+\\
+\noindent Combining the two stages, players can use one of 16 possible strategies.
+In the simple case where players are identical, one can characterize the Nash equilibria of the game and identify the conditions which allow an equilibrium in which all players to contribute in the first stage and reward peers in second stage \cite{Pal:NatCom:2022}.
+In the symmetric case, full cooperation and rewarding is feasible in equilibrium when all players have sufficient information about each other and the reward benefit $\rho$ is neither too high, nor too low.
+In this section, we study three simple cases of asymmetry between players to demonstrate how these asymmetric players take up different roles in the long run to produce the public good.
+To this end, we consider a 3-player game in which player 1 and 2 are identical but player 3 is asymmetric to them in some aspect.
+We consider three cases in which the asymmetric player either has \textbf{a}) very high cost of rewarding $\gamma_3 > \gamma_1$  or, \textbf{b}) low productivitiy  $r_3 < r_1$ or, \textbf{c}) less information about peers $\lambda_3 < \lambda_1$.
+We simulate the introspection dynamics with a strong selection strength $\beta = 10$ for many iterations ($10^5$ time-steps) to estimate the average abundances of the 16 strategies.
+\\ \\
+\noindent In the case where player 3 is asymmetric with respect to their cost of rewarding, the long-run outcome of introspection reflects a division in labour between the players in producing the public good (Fig \ref{}a).
+The players, to whom rewarding is less costly (player 1 and player 2), reward cooperation with a higher probability than to whom rewarding is very costly (player 3).
+In return, player 3 cooperates with more probability than their co-players in the long run.
+With these specific parameters, one player takes up the role of providing the highest per-capita contribution while the others compensate by rewarding more.
+When the asymmetric player differs only in their productivity, a different effect may appear in the long run (Fig \ref{}b).
+In this case, the less productive player free rides on the cooperation of their higher productive peers, but they rewards their cooperation nonetheless.
+The probability with which the less productive player rewards others in the long run is slightly higher than the probability with which the goods producing individuals reward each other.
+Finally, we consider the case where the asymmetric individual differs from others in terms of the information players have about others' rewarding strategy.
+In this case, the asymmetric player knows others' strategy with a considerably less chance than his peers.
+In the long run, the asymmetric player cooperates less on average than the peers with more information because they cannot cooperate opportunistically enough.
+However, both types of player reward cooperation almost equally and just enough to sustain cooperaiton.
 

### 2023-02-21 latex/supp.tex
all changes untill Tuesday, merged new Marta Intro and Discussion. Changed Fig captions. Waiting for Supp Figures and their parameters.

--- 2023-01-30 latex/supplementary.tex
@@
 \onehalfspacing
-\section*{The general model for introspection dynamics}
-We consider a normal form game with $N (>2)$ players.
-Each player, $i$, has access to their action set, $\A^i$, in which there are $m^i$ possible actions that they can play, $\A^i = \{a^i_1, a^i_2, ..., a^i_{m^i}\}$.
-The payoff for an individual $i$ depends on what everyone plays and is represented by $\pi^i(\abf^1, \abf^2, ..., \abf^N)$, where $\abf := (\abf^1, \abf^2,...,\abf^N) \in \A^1 \times \A^2 \times ...
-\times \A^N =: \A$ represents a state of the game.
-In this model we only consider pure strategies for players.
-So, player $i$ has only $m^i$ possible strategies.
-Therefore, the total number of states possible for the game is the product of all $m^i$.
-\\ \\
-\noindent We represent a state of the game, $\abf$, from the perspective of player $j$ as $\abf =: (\abf^j, \abf^{-j})$.
-In the state $(\abf^j, \abf^{-j})$, player $j$ plays the action $\abf^j \in \A^j$ and all the other co-players of $j$ play $\abf^{-j} \in \Pi_{k \neq j} \A^k$.
-The payoff of player $j$ in this state is also represented as $\pi^j(\abf^j, \abf^{-j})$.
-\\ \\
-\noindent The players update their strategies over time using the introspection dynamics \cite{couto2022introspection}.
-At every time step, one randomly chosen player can update their strategy.
-The randomly chosen player, say $j$, currently playing strategy $a^j_k$, compares their current payoff to the payoff that they would obtain if they played a randomly selected strategy,  $a^j_l \neq a^j_k$, from their action set $\A^j$.
-This comparison is done while assuming that the co-players do not change from $\abf^{-j}$.
-Then, they adopt this new strategy  with the probability:
+\section*{Supplementary Figures}
+\begin{figure}[h!]
+\centering
+\includegraphics[width =  \textwidth]{figures/figure1.eps}~\\[0.4cm]
+\caption{\onehalfspacing
+\textbf{Symmetric linear public goods game.}
+a) Frequency of each state in the stationary distribution of introspection dynamics.
+As players are indistinguishable here, each state can be fully defined by the number of cooperators.
+Parameters: $N = 4$, $b = 2$, $c = 1$ and $\beta = 5$.
+b) For the same game parameters ($N = 4$, $b = 2$ and $c = 1$), we now show the frequency of each state (same color code as in panel a) for varying selection strength $\beta$.
+Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators.
+Indeed, up to $\beta \approx 3$, state $0$ is not even the most frequent.
+c) Average cooperation frequency for varying dilemma strength.
+We use as a measure of the dilemma strength the marginal gain by choosing to cooperate over choosing to defect, $b/N - c$.
+When this quantity is low, we say there is a ``strong dilemma”, where there is no individual advantage to cooperate, whereas when the marginal gain is high, we say there is a ``weak dilemma” (or no dilemma), where to cooperate becomes advantageous.
+Typically, a linear public goods dilemma is defined as having a negative marginal gain (see conditions above).
+Here, we show the whole parameter range for completeness and a full grasp of this game.
+We also show the result for different values of selection strength, $\beta = 1, 5$ and $100$.
+For high $\beta$, we confirm the classical prediction that, assuming a negative marginal gain, defection is dominant.
+For low $\beta$, however, we see again that some cooperation is possible.
+}
+\label{Fig:LPGG-symmetric}
+\end{figure}
+\clearpage
 
-\begin{equation}
- p^j_{a^j_k \to a^j_l} (\abf^{-j})= \frac{1}{1 + e^{\displaystyle -\beta(\pi^j(a^j_l, \abf^{-j}) - \pi^j(a^j_k, \abf^{-j}))}}
- \label{Eq:introspection-update}
-\end{equation}
-\\
-\noindent Where $\beta$ is the selection parameter. The probability that no update is made by the randomly chosen player is given by the normalization condition:
-
-\begin{equation}
- p^j_{a^j_k \to a^j_k} (\abf^{-j}) = 1 - \sum_{k \neq l} p^j_{a^j_k \to a^j_l} (\abf^{-j})
- \label{Eq:introspection-normalization}
-\end{equation}
-\\ 
-\noindent Now, with the help of Eq.
-\ref{Eq:introspection-update} and \ref{Eq:introspection-normalization}, we can define the transition matrix $\T$ of the process.
-The transition matrix is a square matrix of size $M = m^1 \times m^2 \times ...
-\times m^N$.
-The element $\T_{\abf_p, \abf_q}$ of the matrix represents the probability that the game will go to state $\abf_q$ from state $\abf_p$ in a time step.
-Before defining the transition matrix, we define the notion of neighbouring states.
-
-\begin{definition}
-\textbf{Neighbouring states}: \\ The state $\abf_q \in \mathit{Neb}(\abf_p)$, the neighbourhood of state $\abf_p$, if and only if $\exists j$ such that $\abf_p^{-j} = \abf_q^{-j}$ and $\abf_p^{j} \neq \abf_q^{j}$.
-\label{Def:neighbourhood-states}
-\end{definition}
-\noindent Note that if $\abf_q \in \mathit{Neb}(\abf_p)$ then by definition $\abf_p \in \mathit{Neb}(\abf_q)$.
-We give an example to explain the notion of neighbourhood.
-Consider three players, player $1,2$ and $3$.
-Each of these players choose actions from an identical binary action set $\{\mathit{0},\mathit{1}\}$.
-In this example, the state $(\mathit{0}, \mathit{0}, \mathit{0})$ is a neighbour of $(\mathit{0}, \mathit{0}, \mathit{1})$ and vice versa.
-The index of difference between the two states is player $3$.
-The states  $(\mathit{0}, \mathit{0}, \mathit{0})$ and $(\mathit{0}, \mathit{1}, \mathit{1})$ are not neighbouring states because more than one player's action are changed.
-
-\begin{definition}
-\textbf{Index of difference for neighbouring states}: \\ \\ If the states $\abf_p$ and $\abf_q$ are neighbours then, the unique $j$ for which $\abf_p^{j} \neq \abf_q^{j}$, is called the index of difference.
-Or $I(\abf_p,\abf_q) := j$
-\label{Def:index-of-difference}
-\end{definition}
-\noindent For the earlier example, let $\abf_p = (\mathit{0}, \mathit{0}, \mathit{0})$ and $\abf_q = (\mathit{0}, \mathit{0}, \mathit{1})$. Then, $I(\abf_p,\abf_q) = 3$. 
-\\ \\ 
-Using the above definitions of neighbourhood and index of difference, we can define the transition matrix $\T$ for the process as the follows: 
-\begin{align}
-\T_{\abf_p,\abf_q} = 
-\begin{cases}
-\frac{1}{N(m_j-1)}  \cdot p^j_{\abf^j_p \to \abf^j_q} (\abf_p^{-j}) \quad  \quad &\abf_p \in \mathit{Neb}(\abf_q) \quad \text{and,} \quad j = I(\abf_p,\abf_q)\\ \\ 
-0 \quad & \abf_{p} \notin \mathit{Neb}(\abf_q) \\ \\
-1 - \sum_{\forall \abf_k \neq \abf_p} \T_{\abf_p,\abf_k} \quad &\abf_p = \abf_q
-\end{cases}
-\label{Eq:transition-matrix}
-\end{align}
-\noindent The stochastic transition matrix $\T$ is row-stochastic.
-This implies that its stationary distribution is a left eigenvector of $\T$ corresponding to eigenvalue $1$.
-We denote the stationary distribution of $\T$ as $\ubf := (\ubf_{\abf})_{\abf \in \A}$.
-Furthermore, since no state of the process is isolated (i.e., every state has atleast one neighbour), a finite $\beta$ assures that a state is reachable from any other state with positive probability in a finite number of steps.
-Therefore, $\T$ is also primitive.
-The stationary distribution $\ubf$ is unique and strictly positive (from the Perron-Frobenius Theorem).
-The following conditions are satisfied by the stationary distribution $\ubf$ when it is additionally also a probability distribution.
-
-\begin{eqnarray}
-\label{Eq:lefteigenvector}
-\ubf \T = \ubf \\ 
-\label{Eq:normalizationcondition}
-\ubf \cdot \mathbf{1} = 1
-\end{eqnarray}
-
-\noindent The marginal distribution over the strategies of a player $j$ at the stationary distribution is given by $\mathbf{\xi}^j := (\mathbf{\xi}^j_{a^j_1}, \mathbf{\xi}^j_{a^j_2}, ..., \mathbf{\xi}^j_{a^j_{m_j}})$.
-This distribution indicates the probability with which player $j$ plays strategies from their action set $\A^j$ at the stationary distribution.
-The relationship between the marginal distribution and the stationary distribution is given by:
-
-\begin{equation}
-\mathbf{\xi}^j_{a^j_k} := \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(a^j_k, \mathbf{b})}
-\label{Eq:marginal-definition}
-\end{equation}
-
-\noindent Where, $\A^{-j} = \prod_{l \neq j} \A^l$. One can note that the marginal distribution is also a probability distribution. That is, for all $j$:
-
-\begin{equation}
-\sum_{a' \in \A^j} \xi^j_{a'}= 1
-\label{Eq:marginal-prob-dist}
-\end{equation}
-
-\subsection*{Additive games and their properties under introspection dynamics}
-
-In this subsection we discuss a special class of general multiplayer games: additive games \cite{mcavoy2015asymmetric} and some of their properties under the introspection dynamics.
-Additive games are games where the payoff earned by a player $j$ in the state $\abf$ can be broken down into two-components - one which is only dependent on what player $j$ played in the state: $\abf^j$ and the other which only depends on what their co-players $-j$ played in the state: $\abf^{-j}$ .
-That is, for all players $j$,
-
-\begin{equation}
-\pi^j(\abf) = \pi^j_{\abf^j} + \pi^j_{\abf^{-j}}
-\label{Eq:additive games}
-\end{equation}
-
-\noindent holds.
-In additive games, the payoff difference earned by a player when they switch between two strategies in their action set is independent of what other co-players are playing (given all other co-players do not change their strategies).
-That is, for all $j$ and any pair of strategies $a^j_p, a^j_q\in \A^j$,
-
-\begin{equation}
-\pi^j(a^j_p, \mathbf{b}) - \pi^j(a^j_q, \mathbf{b}) = \pi^j_{a^j_p} - \pi^j_{a^j_q}
-\label{Eq:additive games property}
-\end{equation}
-
-\noindent holds for any $\mathbf{b} \in \prod_{l \neq j} \A^l$. 
-\\ \\
-We see an example of additive game in the next section.
-Under introspection dynamics, stationary distribution and marginal distributions from additive games show interesting properties.
-They are discussed in the theorems below:
-
-\begin{Prop}
-When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
-\begin{equation}
-\ubf_a = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
-\label{Eq:additive-game-stationary-distribution}
-\end{equation}
-where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$.
-\label{Th:additive-games-stationary-dist}
-\end{Prop}
-\noindent The above theorem gives a closed form expression of the stationary distribution of the introspection dynamics for additive multiplayer games.
-For any finite value of the selection parameter, $\beta$, the stationary distribution can be analytically calculated using the expression in Eq.
-(\ref{Eq:additive-game-stationary-distribution}).
-The expression is derived by assuming that the update process of the introspection dynamics is governed by Eq.
-(\ref{Eq:introspection-update}) and (\ref{Eq:introspection-normalization}).
-For proof, see Appendix \ref{Section:Appendix}.
-
-\begin{Prop}
-Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game.
-Then, $\ubf_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$.
-That is,
-
-\begin{equation}
-\ubf_\abf = \prod_{j = 1}^N \xi^j_{\abf^j}
-\label{Eq:additive-game-products}
-\end{equation}
-
-\noindent where the marginal probability, $\xi^j_{\abf^j}$, is the cumulative probability that player $j$ plays $\abf^j$ at the stationary distribution. The marginal probability is given by:
-
-\begin{equation}
-\xi^j_{\abf_j} = \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
-\label{Eq:marginal-at-additive-game}
-\end{equation}
-\noindent where, $\pi^j_{a'} - \pi^j_{\abf^j}$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play to $a'$ from $\abf^j$ in an additive game.
-\label{Th:additive-game-product-of-marginals}
-\end{Prop}
-
-\noindent In other words, the above theorem states for additive games, the probability that the game will be in state $\abf = (\abf^1, \abf^2, ...,\abf^N)$ in the long run (considering a finite selection strength introspection dynamics) is the product of the cumulative probabilities that each player $j$ respectively adopts the action $\abf^j$ in the stationary distribution.
-\\ \\
-\noindent To elucidate this result further, we use an example of a 2-player additive game where each player has three possible actions from the action set $\{\mathit{0},\mathit{1},\mathit{2}\}$.
-The result says that the expected frequency of the state $(\mathit{0,2})$, say, where player 1 and player 2 simultaneously play $\mathit{0}$ and $\mathit{2}$ respectively: $\ubf_{(\mathit{0,2})}$, is the product of the marginal probabilities that the first player plays $\mathit{0}$ and the second player plays $\mathit{2}$ in the game.
-That is,
-
-\begin{equation}
-\ubf_{(\mathit{0,2})} = \xi^1_{\mathit{0}}  \xi^2_{\mathit{2}} = (\ubf_{(\mathit{0,0})} + \ubf_{(\mathit{0,1})} + \ubf_{(\mathit{0,2})})(\ubf_{(\mathit{0,2})} + \ubf_{(\mathit{1,2})} + \ubf_{(\mathit{2,2})})
-\label{Eq:additive-stationary-dist-example}
-\end{equation}
-\\
-\noindent As stated in the theorem above, this result holds for any additive game with arbitrary number of players and each player having arbitrary action sets.
-
-\subsection*{Example of multiplayer additive game: linear public goods game}
-We consider the linear public goods game with $N$ asymmetric players.
-Each player has two possible actions, to contribute (action, $\C$), or to not contribute (action, $\D$).
-The players differ in their cost of cooperation and their productivities.
-The cost of cooperation and the productivity of a player $i$ are denoted by $c^i$ and $r^i$.
-The payoff for player $i$ when the state of the game is $\abf$ is given by:
-
-\begin{equation}
-\pi^i(\abf) = \sum_{j=1}^N \frac{\displaystyle r^j a^j c^j}{N} - a^i c^i
-\label{Eq:linear-pgg-payoff}
-\end{equation}
-\\
-\noindent The difference in payoffs between playing the two actions in a linear public goods game is independent of what the other co-players play in the game. That is,
-
-\begin{equation}
-\pi^i(\abf^i = \D, \abf^{-i}) - \pi^i(\abf^i = \C, \abf^{-i}) = c^i \left(1 - \frac{r^i}{N} \right) =: f(c^i, r^i) 
-\label{Eq:difference-payoffs-lpgg}
-\end{equation}
-\\
-\noindent is independent of $\abf^{-i}$.
-The linear public goods game is therefore an example of an additive game.
-This property of the game results in dominated strategies for player $i$ depending on the relationship between their productivity $r^i$ and number of players $N$.
-When $r^i < N$, the action of not contributing ($\D$) dominates the action of contributing ($\C$) and vice-versa.
-\\
-\begin{Prop}
-\label{prop:stationary-dist-lpgg}
-When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for an asymmetric linear public goods game under introspection dynamics is given by: 
-\\
-\begin{equation}
-\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^j)\beta f(c^j, r^j )}} \quad ,\forall \abf \in \{\C, \D\}^N
-\label{Eq:stationary_dist_lpgg}
-\end{equation}
-where, 
-\begin{equation}
-\label{Eq:sign-function}
-\mathit{sign}(a) =
-\begin{cases}
-1& \quad \text{if} \quad a = \C \\
--1& \quad \text{if} \quad a = \D
-\end{cases}
-\end{equation}
-\end{Prop}
-
-\section*{Symmetric multiplayer games with two strategies}
-
-In the previous section we looked at properties of the stationary distribution of the introspection dynamics for additive games.
-In this section we look at properties of the stationary distribution for any multiplayer game where players are symmetric and have two actions in their action set.
-A $N-$player symmetric normal form game satisfies the following properties:
-
-\begin{enumerate}
-\item $\A^1 = \A^2 = ... = \A^N = \mathcal{A}$, and
-\item For any $i, j \in \{1,2,...,N\}, a \in \mathcal{A}$ and $\mathbf{b} \in \displaystyle \prod_{k=1}^{N-1} \mathcal{A}$: 
-\begin{equation}
-\pi^i(a, \mathbf{b}) = \pi^j(a, \mathbf{b})
-\end{equation}
-\end{enumerate}
-
-\noindent In addition, when there are only two actions in the action set of players we define the action set in the same way as we did in the section of linear public goods game: $\mathcal{A} := \{\C, \D\}$.
-\subsection*{Notations}
-We introduce some notations before presenting the results
-\begin{enumerate}
-
-\item We denote the payoffs of a $\C$ and $\D$ player when they have $j$ co-players playing $\C$, as $\pi^{\C}(j)$ and $\pi^{\D}(j)$ respectively. 
-\item We define a simple mapping function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to $0$. That is, 
-\begin{equation}
-\alpha(a):= 
-\begin{cases}
-1 \quad \text{if} \quad a = \C \\
-0 \quad \text{if} \quad a = \D  
-\end{cases}
-\end{equation}
-\item For every state $\abf \in \mathcal{A}^N$, we count the number of $\C$ players in the state and denote it with $\mathcal{C}(\abf)$. That is, 
-\begin{equation}
-\mathcal{C}(\abf) := \sum_{j=1}^N \alpha(\abf^j)
-\end{equation}
-\end{enumerate}
-\newpage
-\begin{Prop}
-\label{Prop:Symmetric-2-strategies-state}
-When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\ubf_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
-\begin{equation}
-\label{Eq:stationary-dist-symm-2-stgs-state}
-\ubf_\abf = \frac{1}{\Gamma} \displaystyle \prod_{j=1}^{\mathcal{C}(\abf)} \displaystyle e^{-\beta f(j-1)}
-\end{equation}
-where $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$. The term $\Gamma$ is the normalization factor given by:
-\begin{equation}
-\label{Eq:stationary-dist-normalization-symm-2-stgs-state}
-\Gamma = \displaystyle \sum_{\forall \abf' \in \mathcal{A}^N} \prod_{j = 1}^{\mathcal{C}(\abf')} \displaystyle e^{-\beta f(j-1)}
-\end{equation}
-\end{Prop}
-
-\noindent The above proposition gives an exact closed form expression for the steady state distribution of the introspection dynamics for symmetric games with two strategies.
-Since all players are symmetric in this two strategy game, the number of unique states of the game can be reduced to $N+1$ from $2^N$.
-Now, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
-Then, Proposition \ref{Prop:Symmetric-2-strategies-state} can be simplified by accounting for states with number of $\C$ players as follows:
-
-\begin{Corollary}
-\label{Lemma: Symmetric-2-stg}
-When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
-\begin{equation}
-\label{Eq:stationary-dist-symm-2-stgs}
-\ubf_k = \frac{1}{\Gamma} \cdot {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
-\end{equation} \\ 
-where, $k$ represents the number of $\C$ players in the state and $f(j) := \pi^\D(j) - \pi^\C(j)$ is the difference in payoffs of playing $\D$ and $\C$ when there are $j$ co-players playing $\C$.
-The term $\Gamma$ is the normalization factor, given by, \\
-\begin{equation}
-\label{Eq:normalization-Tk}
-\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k+1  } \displaystyle e^{-\beta f(j-1)}
-\end{equation}
-\end{Corollary}
-\noindent The above lemma follows directly from Proposition \ref{Prop:Symmetric-2-strategies-state}.
-The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$, $\C$ players and $N-k$, $\D$ players.
-This count is simply the binomal coefficient $N \choose k$.
-For details see the proof in the Appendix.
-\newpage 
-\section*{Appendix: Proofs}
-\label{Section:Appendix}
-\begin{proof}
-\textbf{Proof of Proposition} \ref{Th:additive-games-stationary-dist} \\ \\ 
-Since $\beta$ is finite, the transition matrix of the process $\T$ given by Eq.
-\ref{Eq:transition-matrix} is primitive and therefore, the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the row-stochastic transition matrix is unique and satisfies the conditions laid out in Eq.
-\ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}.
-To continue for the rest of the proof, we introduce some short-cut notation that will be of use later in the proof:\\
-\begin{align}
-I_{q} &:= I(\abf_q,\abf), \quad \mathit{iff} \quad \abf_q \in \mathit{Neb}(\abf) \\ \notag \\ 
-\label{Eq:shortcut-tau}
-\tau^j_{\abf^j} &:= \frac{1}{\displaystyle \sum_{a' \in \A^j} e^{\beta \left( \pi^j_{a'} -  \pi^j_{\abf^j} \right) }} 
-\end{align}
-\noindent In order to show that the candidate stationary distribution, as proposed in Eq.
-\ref{Eq:additive-game-stationary-distribution} is the stationary distribution of the process, we need to show that the following are true:
-\begin{eqnarray}
-\label{step-one}
-\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \ubf_a \quad \forall \abf \in \A \\ 
-\label{step-two}
-\sum_{\abf \in \A} \ubf_\abf  = 1
-\end{eqnarray}
-The Eq \ref{step-one} can be simplified further with the steps: 
-\begin{align}
-&\T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}= \\
-& \left( 1 - \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \ubf_{\abf} \right) + \sum_{\abf_q \in \mathit{Neb}(\abf)}  \frac{1}{m^{I_q}-1} \cdot p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \ubf_{\abf_q} = \\ \notag \\
-\label{eq:important-step}
-& \ubf_\abf +  \frac{1}{N} \sum_{\abf_q \in \mathit{Neb}(\abf)} \left( \prod_{k \neq I_q} \tau^k_{\abf^k} \right) \left( p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} \right) \cdot \left(  \frac{1}{m^{I_q}-1} \right)
-\end{align}
-\\ Using the definition of probability of update of the introspection dynamics, as given by Eq. \ref{Eq:introspection-update} and Eq. \ref{Eq:shortcut-tau}, it can be shown that: 
-\begin{equation}
-p^{I_q}_{\abf^{I_q}_q \to \abf^{I_q}} \cdot \tau^{I_q}_{\abf^{I_q}} -  p^{I_q}_{\abf^{I_q} \to \abf^{I_q}_q} \cdot \tau^{I_q}_{\abf^{I_q}_q} = 0
-\label{important-step-is-zero}
-\end{equation}
-\\ \noindent Plugging the equality in Eq.
-\ref{important-step-is-zero} into Eq.
-\ref{eq:important-step}, we can see that the left hand side of Eq.
-\ref{step-one} indeed simplifies to $\ubf_{\abf}$.
-Now, to confirm that the candidate $\ubf$ is the unique stationary distribution we need to check if Eq.
-\ref{step-two} holds.
-Simplifying the left hand side of this equation shows that:
-\begin{align}
-\sum_{\abf \in \A} \ubf_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau^k_{\abf^k} \\ \notag \\
-\label{step-prod-sum-sum-prod}
-&= \left( \prod_{k=1}^N \sum_{\abf' \in \A} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\abf \in \A} \prod_{k=1}^N \displaystyle e^{\beta \pi^k_{\abf^k}} \right) \\ \notag \\
-\label{step-prod-is-one}
-&= 1
-\end{align}
-\noindent The step from Eq.
-\ref{step-prod-sum-sum-prod} to Eq.
-\ref{step-prod-is-one} is possible because the sum and product in Eq.
-\ref{step-prod-sum-sum-prod} are interchangeable for both the terms.
-Therefore, condition Eq.
-\ref{step-two} is satisfied too.
-\end{proof}
-
-\begin{proof}
-\textbf{Proof of Proposition} \ref{Th:additive-game-product-of-marginals} \\ \\ 
-If $\ubf$ is the unique stationary distribution of the $N-$player additive game with under the finite selection introspection dynamics, it is given by the expression in Eq.
-\ref{Eq:additive-game-stationary-distribution}.
-We calculate the marginal distribution of any arbitrary state $\abf$, $\xi_{\abf} = (\xi^j_{\abf^j})_{j = 1,2,...,N}$ by using the definition of marginal distribution in Eq.
-\ref{Eq:marginal-definition}.
-It follows that:
-\begin{align}
-\xi^j_{\abf^j} &= \sum_{\mathbf{b} \in \A^{-j}} \ubf_{(\abf^j,\mathbf{b})} \\ \notag \\
-&= \left( \prod_{k=1}^N \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
-&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \prod_{k\neq j} \sum_{\abf' \in \A^k} \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
-&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \pi^j_{\abf'}}\right)^{-1} \cdot \displaystyle e^{\beta \pi^j_{\abf^j}} \cdot \left( \sum_{\abf' \in \A^{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi^k_{\abf'}}\right)^{-1} \cdot \left( \sum_{\mathbf{b} \in \A^{-j}} \prod_{k \neq j} e^{\beta \pi^k_{\mathbf{b}^k}} \right) \\ \notag \\
-&= \left( \sum_{\abf' \in \A^j} \displaystyle e^{\beta \left( \pi^j_{\abf'} - \pi^j_{\abf^j}\right)}\right)^{-1}
-\end{align}
-\noindent Therefore, the marginal distribution follows Eq.
-\ref{Eq:marginal-at-additive-game}.
-Now since we also additionally know that the stationary distribution follows the form Eq.
-\ref{Eq:additive-game-stationary-distribution}, we can conclude that for additive games, under introspection dynamics with finite selection, Eq.
-\ref{Eq:additive-game-products} holds.
-\end{proof}
-
-\begin{proof}
-\textbf{Proof of Proposition} \ref{prop:stationary-dist-lpgg} \\ \\
-Since we have demonstrated that the linear public goods game is an additive game, the proof of this theorem can be performed by directly using Theorem \ref{Th:additive-games-stationary-dist}.
-Here, we provide an independent proof.
-The idea behind this proof is identical to the proof of Theorem \ref{Th:additive-games-stationary-dist}.
-\\ \\
-\noindent The stationary transition matrix $\T$ for the linear public goods game is primitive when $\beta$ is finite (i.e., there is a positive power $k$ such that $\T^k$ is a strictly positive matrix).
-Therefore, the stationary distribution of $\T$ will always be unique.
-We define the following short cut notations for the ease of the proof:
-\begin{eqnarray}
-\bar{\abf}^j &:= \{\D,\C\} \setminus \abf^j  \\ 
-p^j &:= \frac{1}{1 + \displaystyle e^{\beta f(c^j, r^j)}} 
-\end{eqnarray}
-In addition we introduce a mapping function $\alpha(.)$ which maps the action $\C$ to 1 and the action $\D$ to 0.
-That is $\alpha(\C) := 1$ and $\alpha(\D) := 0$.
-Using these notations and Eq.
-\ref{Eq:introspection-update} and \ref{Eq:difference-payoffs-lpgg} we can write the probability that a player $j$ updates from $\abf^j$ to $\bar{\abf}^j$ while their co-players play $\abf^{-j}$ as: \\
-\begin{equation}
-p^j_{\displaystyle \bar{\abf}^j  \to \abf^j} (\abf^{-j}) = p^j \mathit{sign}(\abf^j) + \alpha(\bar{\abf}^j) \\ \\
-\end{equation}
-The candidate stationary distribution $\ubf$ given in Eq \ref{Eq:stationary_dist_lpgg} can be written down using our shortcut notation as: 
-\begin{equation}
-\label{Eq:stationary-dist-shortcut}
-\ubf_\abf = \prod_{k = 1}^{N}  p^k \mathit{sign}(\abf^k) + \alpha(\bar{\abf}^k) \quad ,\forall \abf \in \{0,1\}^N
-\end{equation}
-This stationary distribution must satisfy the following properties, which are also given in Eq  \ref{Eq:lefteigenvector} and \ref{Eq:normalizationcondition}:
-\begin{align}
-\label{Eq:transition-in-proof}
-&\ubf_\abf = \T_{\abf,\abf} \ubf_\abf  + \sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q}  \\[10pt] 
-\label{Eq:normalization-in-proof}
-&\sum_{\forall \abf_q} \ubf_{\abf_q}= 1
-\end{align}
-Where, the terms in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified using Eq \ref{Eq:introspection-update} and \ref{Eq:transition-matrix} as follows:
-\begin{eqnarray}
-\T_{\abf,\abf} = 1 - \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}), (\bar{\abf}^k,\abf^{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \alpha(\abf^k)
-\label{Eq:first-term-rhs-proof}
-\end{eqnarray} 
-and additionally, also using Eq. \ref{Eq:stationary-dist-shortcut} the second term can be simplified too:
-\begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k = 1}^N \T_{(\bar{\abf}^k,\abf^{-k}), (\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k,\abf^{-k})} \\[10pt]
-&= \frac{1}{N} \sum_{k = 1}^N \left(p^k \textit{sign}(\abf^k) +\alpha(\bar{\abf}^k) \right) \ubf_{(\bar{\abf}^k,\abf^{-k})} \\[10pt] 
-\label{Eq:second-term-rhs-proof}
-&= \frac{\ubf_\abf}{N} \sum_{k=1}^{N} p^k \textit{sign}(\bar{\abf}^k) + \alpha(\abf^k) 
-\end{align}
-Now, using Eq.
-\ref{Eq:first-term-rhs-proof}, \ref{Eq:second-term-rhs-proof} one can show that the right hand side of Eq.
-\ref{Eq:transition-in-proof} is the element of the stationary distribution, corresponding to the state $\abf$, $\ubf_a$.
-Now, to complete the proof, we must show that Eq.
-\ref{Eq:normalization-in-proof} is also true for our candidate stationary distribution.
-This can be done by decomposing the sum of the elements of the stationary distribution as follows:
-\begin{align}
-\sum_{\forall \abf_q} u_{\abf_q} =& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^N p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k) \\[10pt]
-=& \displaystyle \displaystyle \sum_{\forall \abf_q} (1-p^N)  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k)  + p^N  \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k) \\[10pt]
-=& \displaystyle \sum_{\forall \abf_q} \prod_{k=1}^{N-1} p^k \mathit{sign}(\abf_q^k) + \alpha(\bar{\abf}_q^k)
-\end{align}
-When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also a probability distribution.
-\end{proof}
-
-\begin{proof}
-\textbf{Proof of Proposition} \ref{Prop:Symmetric-2-strategies-state} \\ \\
-By construction, the candidate stationary distribution given by Eq.
-\ref{Eq:stationary-dist-symm-2-stgs-state} and Eq.
-\ref{Eq:stationary-dist-normalization-symm-2-stgs-state} is a probability distribution since it satisfies the condition in Eq.
-\ref{Eq:normalizationcondition} and for any state $\abf'$, $\ubf_{\abf'}$ is between 0 and 1.
-Moreover, since $\beta$ is finite, the transition matrix of the process $\T$ is primitive and therefore, it will have a unique stationary distribution.
-To show that the candidate stationary distribution is the unique stationary distribution, we need to check if for this process, $\ubf \T= \ubf$.
-That is, the Eq.
-\ref{Eq:transition-in-proof} must hold.
-We re-introduce some notations that we will use in this proof:
-\begin{align}
-\bar{\abf}^j &:= \{\D,\C\} \setminus \abf^j \\[10pt]
-\alpha(a)&:= 
-\begin{cases}
-1 \quad \text{if} \quad a = \C \\[10pt]
-0 \quad \text{if} \quad a = \D 
-\end{cases}\\[10pt]
-\mathcal{C}(\abf) &= \sum_{j=1}^N \alpha(\abf^j)
-\end{align}
-For this process, the first term in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified as: 
-\begin{align}
-\ubf_{\abf} \T_{\abf,\abf}  &= \ubf_\abf - \ubf_{\abf} \sum_{k=1}^{N} \T_{(\abf^k, \abf^{-k}),(\bar{\abf}^{k}, \abf^{-k})} \\[10pt]
-&= \ubf_{\abf} - \frac{\ubf_{\abf}}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}^{k}) \beta f(N_k)}}
-\label{Eq:T_aa_u_a term}
-\end{align}
-\\ \noindent Where, the function $\mathit{sign}(.)$ is  defined in Eq.
-\ref{Eq:sign-function} and$f(j)$ is the difference in payoffs between playing $\D$ and $\C$ when there are $j$ co-players playing $\C$.
-The term $N_k$ is the number of co-players of $k$ that play $\C$ in state $\abf_\C$.
-That is,
-\begin{equation}
-N_k := \sum_{j \neq k} \alpha(\abf^l)
-\end{equation}
-The second term in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified as, 
-\begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \ubf_{(\bar{\abf}^k, \abf^{-k})} \\[10pt]
-\label{Eq:step-single-product}
-&= \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \prod_{j=1}^{\mathcal{C}((\bar{\abf}^k, \abf^{-k}))} e^{-\beta f(j-1)}\\[10pt]
-&=  \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \displaystyle \left( \prod_{j=1}^{\sum_{j \neq k} \alpha(\abf^l)}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ \sum_{j \neq k} \abf^l)}
-\label{Eq:step-product-broken}
-\end{align}
-Between the steps, Eq.
-\ref{Eq:step-single-product} and \ref{Eq:step-product-broken}, we took out one term from the product that is present in our candidate distribution.
-This term accounts for the $k^{th}$ players action in the state $(\bar{\abf}^k, \abf^{-k})$.
-For simplicity, we replace $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ with just $\T$ in the next steps and also denote the number of co-players of $k$ that play $\C$ in the state $\abf$ as $N_k$.
-\noindent We continue the simplification of Eq. \ref{Eq:step-product-broken} in the later steps by introducing terms that cancel each other. \\[10pt]
-\begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \cdot e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) + N_k)}
-\label{Eq:new-cancelable-term-introduced}
-\end{align}
-\\ \noindent The newly introduced term in Eq.
-\ref{Eq:new-cancelable-term-introduced} can be taken inside the product.
-Note that this term is 0 if the $k^{th}$ player plays $\D$ in the state $\abf$.
-When this term is taken inside the product bracket, products of exponent $e^{-\beta f(j-1)}$ can be performed where $j$ ranges from $1$ to the number of cooperators in state $\abf$, $\mathcal{C}(\abf)$.
-This product is then the stationary distribution probability $\ubf_\abf$.
-That is,
-\begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \cdot e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) + N_k)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \\[10pt]
-&= \frac{1}{N} \sum_{k=1}^N  \T \cdot \left( \frac{1}{\Gamma} \prod_{j=1}^{\mathcal{C}(\abf)} e^{-\beta f(j-1)}\right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \\[10pt]
-&= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \cdot \ubf_\abf \cdot \frac{e^{-\beta \alpha(\bar{\abf}^k)f(-\alpha(\abf^k)+ N_k)}}{e^{-\beta \alpha(\abf^k)f(-\alpha(\bar{\abf}^k) +N_k)}} \label{Eq: last-step-w-fraction}
-\end{align}
-\\ \noindent The fraction inside the sum in  Eq. \ref{Eq: last-step-w-fraction} can be simplified as follows leading to further simplification of Eq. \ref{Eq: last-step-w-fraction}:
-\begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} \cdot \ubf_\abf \cdot e^{sign(\abf^k) \beta f(N_k)} 
-\label{Eq:only-need-to-replace-T-now}
-\end{align}
-\\ \noindent In Eq. \ref{Eq:only-need-to-replace-T-now} we can replace the element of the transition matrix $\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})}$ by using the following: 
-\begin{equation}
-\T_{(\bar{\abf}^k, \abf^{-k}),(\abf^k, \abf^{-k})} = \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^k) \beta f(N_k)}} 
-\label{Eq:transition-matrix-T-symm-2-stgs}
-\end{equation}
-\\ \noindent Using the expression for the transition matrix element from Eq.
-\ref{Eq:transition-matrix-T-symm-2-stgs} into Eq.
-\ref{Eq:only-need-to-replace-T-now} and by using Eq.
-\ref{Eq:T_aa_u_a term}, we can simplify further:
-\begin{align}
-\sum_{\abf_q \neq \abf} \T_{\abf_q, \abf} \ubf_{\abf_q} &= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf^k) \beta f(N_k)}} \cdot  e^{sign(\abf^k) \beta f(N_k)} \\[10pt]
-&= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}^k) \beta f(N_k)}}  \\[10pt]
-&= \ubf_\abf - \ubf_\abf \T_{\abf,\abf}
-\end{align}
-\\ \noindent The final step in the previous simplification shows that Eq.
-\ref{Eq:transition-in-proof} holds for any $\abf \in \{\C,\D\}^N$.
-Therefore, the candidate distribution we propose in Eq.
-\ref{Eq:stationary-dist-symm-2-stgs-state} is the unique stationary distribution of the symmetric $N$-player game with two strategies.
-\end{proof}
-
-\begin{proof}
-\textbf{Proof of Corollary} \ref{Lemma: Symmetric-2-stg} \\ \\
-
-\end{proof}
-\newpage
-\section*{Supplementary References}
-\bibliographystyle{unsrt}
-\bibliography{bibliography.bib }
+\begin{figure}
+\centering
+\includegraphics[width =  \textwidth]{figures/figure2.eps}~\\[0.4cm]
+\caption{\onehalfspacing
+\textbf{Asymmetric linear public goods game.} In the upper panels a) and b), we show the parameter values of the cost and benefit on the left and the average cooperation frequency on the right, of each player.
+Parameters: $N=3$, $\bar{c} = 1$, $\bar{b} = 2$, $\beta = 2$, where $\bar{c}$ and $\bar{b}$ are the mean values and are represented by black, dashed lines.
+In a) the cost varies among the 3 players by $\delta_c = 0.5$, such that players have costs of $\bar{c} + \delta_c $, $\bar{c}$, and $\bar{c} - \delta_c$ (in this case, $1.5$, $1$, and $0.5$), while the benefit is the same.
+Conversely, in b) the benefit varies among the 3 players, by $\delta_b = 1$, such that players have benefits of $\bar{b} + \delta_b $, $\bar{b}$, and $\bar{b} - \delta_b$ (in this case, $3$, $2$, and $1$), while the cost is the same.
+In c), we vary the asymmetry strengths $\delta_c $ and $\delta_b$ at the same time and show both each player’s average cooperation frequency and the overall average cooperation frequency.
+The area within the white dashed lines represents the parameter range for which the marginal gain by cooperating is negative, for each single player and, in the right-most panel, for all players.
+Parameters: $N=3$, $\bar{c} = 1$, $\bar{b} = 2$, $\beta = 5$.
+}
+\label{Fig:LPGG-asymmetric}
+\end{figure}
 \end{document}

### 2023-02-21 latex/article.tex

--- 2023-02-16 latex/article.tex
@@
 
-\renewcommand{\figurename}{Supplementary Figure}
+\renewcommand{\figurename}{Figure}
 
@@
 
-\title{\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}}
+%\title{\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}}
+\title{\sffamily \Large {\bfseries Introspection dynamics in asymmetric multiplayers games}}
 \date{\empty}
-\author{\parbox[c]{16cm}{\centering \onehalfspacing \fontsize{11}{12}\selectfont Marta Couto$^1$ and Saptarshi Pal$^1$\\[0.2cm]
-$^1$Max Planck Research Group Dynamics of Social Behavior, Max Planck Institute for Evolutionary Biology, 24306~Ploen, Germany}}
+\author{\parbox[c]{16cm}{\centering \onehalfspacing \fontsize{11}{12}\selectfont Marta Couto$^{1*}$ and Saptarshi Pal$^{1*}$\\[0.2cm]
+$^1$Max Planck Research Group Dynamics of Social Behavior, Max Planck Institute for Evolutionary Biology, 24306~Ploen, Germany}\\ \\
+$^*$ \fontsize{11}{12}\selectfont co-first authors}
 
@@
 Introspection dynamics has proven to be a useful learning model to tackle complex games.
-%To analyse more complex games, reserachers typically use approximations, e.g. weak selection, small mutation. 
+%To analyse more complex games, researchers typically use approximations, e.g. weak selection, small mutation. 
 Here, our aim is to analyse multiplayer and (a)symmetric games. We extend previous analytical results of pairwise games under introspection dynamics to multiplayer games. 
-We divide games in two main categories: additive and non-additive (or general) games.
+We divide games into two main categories: additive and non-additive (or general) games.
 In additive games, for any player, the difference between the payoffs provided by any two actions (or strategies) is constant, regardless of the co-players' actions. 
 Non-additive are all games that do not hold this property; hence, general games.
-For additive games, we derive the stationary distribution of strategies analitically, for any number of players and strategies. 
+For additive games, we derive the stationary distribution of strategies analytically, for any number of players and strategies. 
 %Additionally, we find that the joint distribution of strategies factorizes over the marginal distribution of strategies.
@@
 \newpage
+
 \section*{Introduction}
@@
 The simplest form of social interaction occurs between two individuals.
-These pairwise interactions have been studied extensively \cite{bibid}.
-Despite their simplicity, they provide important insights, e.g., on how social species can maintain cooperation \cite{bibid}.
+These pairwise interactions have been studied extensively \cite{Hofbauer:book:1998}.
+Despite their simplicity, they provide important insights, e.g., on how social species can maintain cooperation \cite{Axelrod:book:1984, Nowak:book:2011}.
 An ubiquitous example of a model game for two players is the prisoner's dilemma.
 There, the two individuals have a temptation to cheat on each other, while both would be better off by offering mutual help.
-Solving this apparent paradox has been the focus of many studies, where various explanations were proposed \cite{bibid}.
+Solving this apparent paradox has been the focus of many studies, where various explanations were proposed \cite{Nowak:Science:2006}.
 %some references
@@
 % non-linearity
-\noindent Yet, many interesting collective behavior occur when multiple individuals interact simultaneously \cite{Palm:JMB:1984, Skyrms:book:2003, Pacheco:PRSB:2009, Archetti:EL:2011, Archetti:JTB:2012, Gokhale:DGAA:2014, Hilbe:JTB:2015, Venkateswaran:PRSB:2019}.
-% + refs!
-Notably, most of these situations cannot be captured by the sum of several pairwise interactions.
-Thus, to account for such non-linearities we need to consider multiplayer games \cite{Gokhale:DGAA:2014}.
-One well-known effect that only emerges when more than two players are present is the second-order free riding problem \cite{Pal:NatCom:2022}.
+\noindent Yet, many interesting collective behaviors occur when multiple individuals interact simultaneously \cite{Palm:JMB:1984, Skyrms:book:2003, Pacheco:PRSB:2009, Archetti:EL:2011, Archetti:JTB:2012, Gokhale:DGAA:2014, Hilbe:JTB:2015, Venkateswaran:PRSB:2019}.
+Importantly, most of these situations cannot be captured by the sum of several pairwise interactions.
+Thus, to account for such non-linearities, we need to consider multiplayer games \cite{Gokhale:DGAA:2014}.
+One well-known effect that only emerges when more than two players are present is the ``second-order free-riding problem" \cite{Fowler:PNAS:2005}.
 A natural solution to maintain pro-social behavior in a community is to monitor and punish defectors (and/or reward cooperators).
-However, most forms of sanctioning are considerably costly \cite{bibid}.
+However, most forms of sanctioning are considerably costly \cite{Henrich:Science:2006}.
 Therefore, an additional (second-order) dilemma is at stake: deterring defection is beneficial for all, but an individual that does not pay the associated cost has an advantage over the ones that do.
-As such, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms or a suitable design \cite{Couto:JTB:2020}.
-%refs
+As such, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms or a suitable design \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.
 \\ \\
@@
 % size
-Another interesting aspect of multiplayer games is the scale or size of the interaction itself.
-Are many-player social dilemmas harder to solve than small-groups'?
-\cite{Skyrms:book:2003}.
-Indeed, in situations that require some sort of coordination and expectations on others play an important role in one's decisions (like in stag-hunt games), it is easy to see how a growing group size might hinder the optimal outcome -- it is hard to cooperate in large groups \cite{bibid}.
-% need ref here!
-\cite{Hilbe:JTB:2015}
+Another interesting effect that multiplayer games allow exploring is that of the scale or size of the interaction itself.
+In situations that require some sort of coordination and where expectations on others play an important role in one's decisions (like in stag-hunt games), a growing group size might hinder the optimal outcome \cite{Skyrms:book:2003}.
+Likewise, it has been shown that it is hard to cooperate in large groups for some conditions \cite{Santos:PNAS:2011, Hilbe:JTB:2015}.
 This is not a general effect, though.
 It can happen that adding more players actually promotes cooperation.
-As a biological example, consider a task allocation problem in a bacterial system.
+Gokhale et al.
+\cite{gokhale:JTB:2011} investigate the 2-player and 3-player cases of a task allocation problem.
+Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, resulting in a decrease in freeloading.
+%As a biological example, consider a task allocation problem in a bacterial system.
 A strain of bacteria can do any of three actions: to specialize in producing one of two kinds of enzymes (at some personal cost) or not to produce any enzyme.
-The bacteria need the two different types of enzymes at the same time to obtain resources from the environment.
+The bacteria need two different types of enzymes at the same time to obtain resources from the environment.
 In \cite{gokhale:JTB:2011}, authors investigate both the 2-player and 3-player cases of this scenario.
 Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, and hence the outcomes.
-With three players, the production of one of the enzymes increases while freeloading decreases, comparing to the 2-player case.
+With three players, the production of one of the enzymes increases while freeloading decreases, compared to the 2-player case.
 Additionally, not only the average group size can have an important effect, but also the variance of the group size distribution \cite{Pena:Evolution:2011, Broom:BMB:2019}.
@@
 In symmetric games, all players are indistinguishable.
-Thus, to fully characterise a state of the game, we only require to know the number of players playing each strategy.
+Thus, to fully characterise the state of the game, we only require to know the number of players playing each strategy.
 Conversely, in asymmetric games, players can be different in several ways.
@@
 Therefore, they can have uneven effects on others' payoffs too.
-For example, in a public goods game, even if every player chooses to cooperate, their contributions to the common good or, alternatively, the cost they pay might be diverse \cite{Hauser:Nature:2019}.
-Hence, to fully describe a state of the game, we need to know which of the players is doing what.
+For example, in public goods games and collective-risk dilemmas, players can have different initial endowments (or wealth), productivitites, costs, risk perceptions, or risk exposures \cite{Milinski:CC:2011, Vasconcelos:PNAS:2014, Abouchakra:JTB:2014, Hauser:Nature:2019, Merhej:JAIR:2022}.
+Hence, to fully describe the state of the game, we need to know which of the players is doing what.
 This greatly increases the size of the game's state space; even more so, for more than two players.
@@
 \noindent From this, we see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
-Perhaps for that reason, there are not many studies on multiplayer asymmetric games, compared to their simpler counterparts.
-Some exceptions are \cite{Hauser:Nature:2019}.
-%refs
-Still, we believe a general approach is lacking.
-As such, our aim here is to narrow that gap, by studying multiplayer, (a)symmetric games.
-In the following, we discuss several canonical frameworks from the literature that have been used to study both multiplayer and asymmetric games.%, pointing out the gaps.
+Perhaps for that reason, there are not many studies on a general approach to multiplayer asymmetric games.
+As such, our aim here is to narrow that gap using introspection dynamics \cite{Couto:NJP:2022}.
+In the following section, we discuss several canonical frameworks from the literature that have been used to study both multiplayer and asymmetric games.%, pointing out the gaps.
 
@@
 % deterministic EGT
-From evolutionary game theory \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior.
+From evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior.
 In evolutionary game theory, we assume a population of players and a mechanism by which strategies evolve over time.
-More successfull strategies tend to persist in the population, either by genetic or cultural inheritance.
+More successful strategies tend to persist in the population, either by genetic or cultural inheritance.
 The first key concept in evolutionary game theory is ``evolutionary stable strategy" (ESS),  introduced in 1973, in the seminal paper of John Maynard Smith and George Price \cite{Maynard-Smith:Nature:1973}.
-A monomorphic population playing an ESS cannot be invaded by mutants.
-The concept of ESS, originally proposed for parwise encounters, was already extended for multiplayer games in \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}.
+A (monomorphic) population playing an ESS cannot be invaded by mutants.
+The concept of ESS, originally proposed for parwise encounters, was already extended for multiplayer games \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}.
 Although suggestive of an evolutionary process, ESS does not really describe a dynamical system.
-In the more classical infinite population models, ordinary differential equations are the central mathematical tools \cite{Hofbauer:book:1998}.
+In the more classical infinite population models (deterministic EGT), ordinary differential equations are the central mathematical tools \cite{Hofbauer:book:1998}.
 One of the most famous of these dynamics is the replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998}.
@@
 As for asymmetric games, a few additional assumptions are needed.
-For example, if there are two different types of players, typically, either there are two populations co-evolving (``bimatrix games" \cite{Hofbauer:book:1998, Tuyls:SciRep:2018}) or there is a single population of players where each can play the two types or roles (``role games") \cite{Hofbauer:book:1998}.
-In the latter kind of model, a strategy must include the action played in each of the two roles.
-% asymmetric multiplayer replicator dynamics?
-% 1+ paper for role games
+For example, if there are two different types of players, typically, either there are two populations co-evolving (``bimatrix games" \cite{Hofbauer:book:1998, Gokhale:PRSB:2012, Tuyls:SciRep:2018}) or there is a single population of players where each can play the two types or roles (``role games") \cite{Hofbauer:book:1998}.
+For role games, a strategy must include the action played in each of the two roles.
+The case of asymmetric games with more than two players is substantially less studied within deterministic EGT.
+Exceptions are  \cite{Gokhale:PRSB:2012, Zhang:arxiv:2022}.
+Notably, although these works study multiplayer games, they consider, at most, two different types (drawn from two populations), which leaves out the exploration of full asymmetry.
+% models of multiple populations seem unnatural
 \\ \\
@@
 Besides the finiteness of population sizes, it also considers random mutations.
-Here, the quantitites of interest are fixation probabilities and fixation times (i.e., the probability and average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{bibid}, or average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}.
+Here, the quantities of interest are fixation probabilities and fixation times (i.e., the probability and the average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{Fudenberg:TPB:2006}, or average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}.
 \\ \\
@@
 These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types.
-Fixation probabilities for asymmetric 2-player \cite{Sekiguchi:DGA:2017} and 3-player games \cite{Sekiguchi:DGA:2022} were recently derived.
-Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:PNAS:2010, gokhale:JTB:2011, Wu:Games:2013}.
+Fixation probabilities for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived.
+Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013}.
 For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to \cite{Gokhale:DGAA:2014}.\\
-%comment on pervasiveness of weak selection
+%comment on the pervasiveness of weak selection
 %strategy abundance papers (intermediate mutation or mutation-selection equilibrium)
@@
 
-%[Learning models]
+%[Learning models] IM NOT VERY HAPPY WITH HOW THIS SECTION READS YET
 %learning models in general
@@
 There is no evolution of strategies in a population necessarily, but a process by which individuals learn strategies dynamically.
-Despite of the conceptual disparities, there have been some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005}.
-\\ \\
-\noindent Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from classical game theory itself \cite{fudenberg:book:1998b}.
+Despite the conceptual disparities, there have been already some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005, Bloembergen:JAIR:2015, Zhang:arxiv:2022}.
+\noindent Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from the classical game theory itself \cite{Fudenberg:book:1998b}.
 The ``theory of learning in games" was proposed as a refinement of classical equilibrium concepts, like Nash equilibrium, where strict assumptions of common knowledge of rationality are made.
-Instead, learning consists of ``\textit{an alternative explanation that equilibrium arises as the long-run outcome of a process in which less than fully rational players grope for optimality over time}" \cite{fudenberg:book:1998b}.
-In this context, several learning models were introduced, such as fictitious play \cite{bibid}.
+Instead, learning consists of ``\textit{an alternative explanation that equilibrium arises as the long-run outcome of a process in which less than fully rational players grope for optimality over time}" \cite{Fudenberg:book:1998b}.
+In this context, several learning models were introduced, such as fictitious play \cite{Gaunersdorfer:GEB:1995} or perturbed best response dynamics \cite{Hofbauer:GEB:2005}.
 \\  \\
@@
 %introspection dynamics
-\noindent Introspection dynamics has proven to be a useful learning model for tackling 2-player, asymmetric games \cite{Couto:NJP:2022}.
-This feature comes from the fact that players update their strategies by exploring their own set of strategies in the following simple way: at each time, after a round of the game, a player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, the player more likely adopts it on the next round.
-While in \cite{Couto:NJP:2022} only 2-player games were considered, this framework is general enough to account for multiple players.
+\noindent Introspection dynamics has proven to be a useful learning model for tackling asymmetric games \cite{Couto:NJP:2022, Hauser:Nature:2019, McAvoy:PNASnexus:2022, Schmid:PlosCB:2022}. 
+This feature comes from the fact that players update their strategies by exploring their own set of strategies in the following simple way: each time, after a round of the game, a player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, it is more likely adopted on the next round.
+While in Couto et al.
+\cite{Couto:NJP:2022} only 2-player games were considered, this framework is general enough to account for multiple players.
 Indeed, as each player assumes that all others remain the same when doing the counterfactual comparison, introspection dynamics is an appropriate model to deal with the complexity introduced by multiple players.
+Particularly, it allows a natural exploration of full asymmetry in many-player games, compared to population models.
 \\ \\
@@
 \noindent Here, we extend previous analytical results of pairwise games under introspection dynamics to multiplayer games. 
-For general games, we obtain the analytical stationary distribution for 2-strategies symmetric games.
+For general games, we obtain the analytical stationary distribution for 2-strategy symmetric games.
 For a particularly simple class of games -- additive games -- we derive the stationary distribution of strategies analytically, for any number of players and strategies, and with no restriction to symmetric games.
 To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas, extending the framework in \cite{Hauert:JTB:2006a} to asymmetric games.
+Finally, we also study the asymmetric version of a public good game with a rewarding stage \cite{Pal:NatCom:2022}.
 
 \section*{Model}
-We consider the normal form game with $N$ players where $N > 2$.
+We consider a normal form game with $N$ players where $N > 2$.
 In the game, a player, say player $i$, can play actions from their action set, $\A_i := \{a_{i,1}, a_{i,2}, ..., a_{i,m_i} \}$.
 The action set of player $i$ has $m_i$ actions.
-There are, therefore, $m_i \times m_2 \times ...
-\times m_N$ distinct states of the game.
+In this model, we consider that players do not randomize their actions in a play (i.e., they only use pure strategies).
+Therefore, there are only finitely many states of the game.
+More precisely, there are exactly $m_1 \times m_2 \times ...
+\times m_N$ states.
 We denote a state of the game by collecting the actions of all the players in the game in a vector, $\abf := (\abf_1, \abf_2, ..., \abf_N)$ where $\abf \in \A := \A_1 \times \A_2 \times ...
@@
 We also use the notation, $\abf := (\abf_i, \abf_{-i})$ to denote the state from the perspective of player $i$.
-In the state $(\abf_i, \abf_{-i})$, player $i$ plays the action $\abf_i \in \A_i$ and their co-players play the action $\abf_{-i} \in \A_{-i} := \prod_{j \neq i} \A_j$.
+In the state $(\abf_i, \abf_{-i})$, player $i$ plays the action $\abf_i \in \A_i$ and their co-players play the action $\abf_{-i} \in \A_{-i}$ where $\A_{-i}$ is defined as $\A_{-i}:= \prod_{j \neq i} \A_j$.
 The payoff of a player depends on the state of the game.
@@
 \\ \\
-\noindent The players update their strategies over time using the introspection dynamics \cite{couto2022introspection}.
+\noindent Since players only use pure strategies in this model, we use the terms strategies and actions interchangebly throughout the whole paper.
+In this model, players update their strategies over time using the introspection dynamics \cite{Couto:NJP:2022}.
 At every time step, one randomly chosen player can update their strategy.
-The randomly chosen player, say $i$, currently playing strategy $a_{i,k}$, compares their current payoff to the payoff that they would obtain if they played a randomly selected strategy,  $a_{i,l} \neq a_{i,k}$, from their action set $\A_i$.
-This comparison is done while assuming that the co-players do not change their respective plays.
-When the co-players of player $i$ play $\abf_{-i}$, player $i$ changes to the new strategy $a_{i,l}$ from $a_{i,k}$ with the probability, \\
+The randomly chosen player, say $i$, currently playing  action $a_{i,k}$, compares their current payoff to the payoff that they would obtain if they played a randomly selected action,  $a_{i,l} \neq a_{i,k}$, from their action set $\A_i$.
+This comparison is done while assuming that the co-players do not change their respective actions.
+When the co-players of player $i$ play $\abf_{-i}$, player $i$ changes from action $a_{i,k}$ to the new action $a_{i,l}$ with the probability, \\
 \begin{equation}
@@
 \\ \\ \noindent in the next round.
-Here $\beta \in [0,\infty)$ is the selection strength parameter that represents the importance that players give to payoff differences while updating their strategies.
+Here $\beta \in [0,\infty)$ is the selection strength parameter that represents the importance that players give to payoff differences while updating their actions.
 At $\beta = 0$, players update to a randomly chosen strategy with probablity $0.5$.
 For $\beta > 0$, players update to new strategy with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
-The probability that the chosen player makes no-update is then, \\
+The probability that the chosen player does not update the action to a new action is then, \\
 \begin{equation}
@@
 \\ 
-Introspection dynamics can be studied by analyzing properties of the resulting transition matrix, $\T$.
+Introspection dynamics can be studied by analyzing properties of the transition matrix, $\T$ of the resulting dynamical process.
 The transition matrix element $\T_{\abf,\bbf}$ denotes the conditional probability that the game goes to the state $\bbf$ in the next round if it is in state $\abf$ in the current round.
+In order to formally define the transition matrix, we first need to introduce some notations and definitions.
 We define the neighbourhood set of $\abf$ as the following:
-\newpage
+
 \begin{definition}[Neighbourhood set of a state] The neighbourhood set of state $\abf$, $\mathrm{Neb}(\abf)$, is defined as the following:
@@
 Consider the game where there are  three players and each player has the identical action set $\{\C, \D \}$.
-The state $(\C,\C,\C)$ is in the neighbouring set of $(\C,\C,\D)$ whereas the state $(\C,\D,\D)$ is not in the neighbourhood set of $(\C,\C, \C)$.
-Two states that belong in each other's neighbourhood set only differ in exactly a single player's (that we call as the index of difference) action.
+The state $(\C,\C,\C)$ is in the neighbourhood set of $(\C,\C,\D)$ whereas the state $(\C,\D,\D)$ is not in the neighbourhood set of $(\C,\C, \C)$.
+In our definition, states are not included in their own neighbourhood.
+In addition, if a state $\bbf$ belongs in the neighbourhood of state $\abf$, by definition state $\abf$ belongs in the neighbourhood of state $\bbf$.
+That is, $\bbf \in \mathrm{Neb}(\abf) \implies \abf \in \mathrm{Neb}(\bbf)$.
+Two states that belong in each other's neighbourhood set only differ in exactly a single player's action (and, we call this player as the index of difference between the neighbouring states),
 
@@
 This implies that the stationary distribution of $\T$: a left eigenvector of $\T$ corresponding to eigenvalue $1$, always exists.
-The following proposition introduces a sufficient condition for this stationary distribution to be unique.
+The following proposition introduces a sufficient condition for the stationary distribution of $\T$ to be unique.
 \begin{Prop} When $\beta$ is finite, the transition matrix of the introspection dynamics has a unique stationary distribution. 
@@
 \end{Prop}
-\noindent \textbf{Proof:} A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
-Since no state is isolated (i.e., every state belongs in the neighbourhood set of another state), every state is reachable in a finite number of steps from a starting point with non-zero probability.
+\begin{proof}
+A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
+Since no state is isolated (i.e., every state belongs in the neighbourhood set of another state) and there are only finitely many states of the game, every state is reachable in a finite number of steps from a starting point with non-zero probability.
 The transition matrix $\T$ is therefore primitive for a finite $\beta$.
@@
 \noindent where $\mathbf{1}$ is the column vector with size same as $\ubf$ and has all elements as $1$. 
-The above equations only present an explicit representation of the stationary distribution $\ubf$.
+\end{proof}
+\noindent The above equations only present an explicit representation of the stationary distribution $\ubf$.
 The stationary distribution can be explictly calculated by the following expression (which is derived using Eq.
@@
 \label{Eq:explicit-stationary-dist-representation}
-\end{equation}
+\end{equation} \\
 where $\mathbf{U}$ is a square matrix of size same as $\T$ with all elements 1 and $\mathbb{1}$ is the identity matrix.
 For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distribution of the processes are unique.
-The stationary distribution element $\ubf_\abf$ is the probability that state $\abf$ will be played by the players in the long run.
+\\
+
+\noindent The stationary distribution element $\ubf_\abf$ is the probability that state $\abf$ will be played by the players in the long run.
 Using the stationary distribution, one can calculate the marginal probabilities corresponding to each player's actions.
@@
 \section*{Additive games and their properties under introspection dynamics}
-In this section we discuss the stationary properties of the introspection dynamics when players learn to play strategies in a special class of games: the additive games \cite{pena2014gains, mcavoy2015asymmetric}.
+In this section we discuss the stationary properties of the introspection dynamics when players learn to play strategies in a special class of games: the additive games \cite{McAvoy:PlosCB:2015, Pena:JTB:2014}.
 In an additive game, the payoff difference that a player earns by making a unilateral switch in their actions is independent of what their co-players play.
@@
 \noindent is independent of $\qbf$ and only dependent on $x$ and $y$.
-In the literature, this property is sometimes called the property of \emph{equal gains from switching} \cite{pena2014gains}.
+In the literature, this property is sometimes called the property of \emph{equal gains from switching} \cite{Pena:JTB:2014}.
 For games with this property, the stationary distribution of introspection dynamics takes a simple form;
@@
 (\ref{Eq:additive-game-stationary-distribution}).
-For a proof, see Appendix.
+For a proof, please see Appendix.
 Using the stationary distribution, one can also exactly compute the cumulative probabilities with which players play their actions in the long run (i.e., the marginal distribution) using Eq.
@@
 \noindent The above proposition states that for additive games, the stationary distribution of the introspection dynamics can be factorized into its corresponding marginals.
-In the long run, the probability that players simultaneously play the state ($\abf_1, \abf_2, ...,\abf_N$) is the product of the cumulative probabilities that player 1 plays $\abf_1$, player 2 plays $\abf_2$ and so on.
+In the long run, the probability that players play the state ($\abf_1, \abf_2, ...,\abf_N$) is the product of the cumulative probabilities that player 1 plays $\abf_1$, player 2 plays $\abf_2$ and so on.
+For a proof, please see Appendix.
+This property of the additive game was aleady shown for the simple two-player, two-action donation game in Couto et al.
+\cite{Couto:NJP:2022}.
+Here we extend that result for any number of players, each having an arbitrary number of strategies.
 While this factorizing property of the stationary distribution appears for additive games, we do not show that this property is unique to additive games.
-We use the well-studied example of the linear public goods game to demonstrate the stationary properties of the introspection dynamics in additive games.
+In the next section we use the well-studied example of the linear public goods game to demonstrate the stationary properties of the introspection dynamics in additive games.
 
 \subsection*{Example of an additive game: linear public goods game with 2 actions}
-In the simplest version of the linear public goods game with $N-$players, each player has two possible actions, to contribute (action, $\C$, to cooperate), or to not contribute (action, $\D$, to defect) to the public good.
+In the simplest version of the linear public goods game with $N-$players, each player has two possible actions, to contribute (action $\C$, to cooperate), or to not contribute (action $\D$, to defect) to the public good.
 The players differ in their cost of cooperation and the benefit they provide by contributing to the public good.
-We denote the cost of cooperation for player $i$ and the benefit that they provide to the public good with $c_i$ and $b_i$ respectively.
-In addition, we define a mapping function $\alpha(.)$ to map the action of cooperation to 1 and the action of defection to 0.
+We denote the cost of cooperation for player $i$ and the benefit that they provide to the public good by $c_i$ and $b_i$ respectively.
+We define a mapping function $\alpha(.)$ to map the action of cooperation to 1 and the action of defection to 0.
 That is $\alpha(\C) = 1$ and $\alpha(\D) = 0$.
@@
 \begin{equation}
-\pi_i(\abf) = \sum_{j=1}^N \frac{\displaystyle \alpha(\abf_j) b_j}{N} - \alpha(\abf_i) c_i
+\pi_i(\abf) = \frac{1}{N}\sum_{j=1}^N \displaystyle \alpha(\abf_j) b_j - \alpha(\abf_i) c_i
 \label{Eq:linear-pgg-payoff}
@@
 The linear public goods game is therefore an example of an additive game.
-This property of the game results in dominated strategies for players.
+This property of the game results in easily identifiable dominated strategies.
 Defection dominates cooperation when $c_i > b_i/N$ while cooperation dominates defection when $c_i < b_i/N$.
-Using proposition \ref{Th:additive-games-stationary-dist}, one can derive the closed form expression for the stationary distribution of a $N-$player linear public goods game with two strategies.
+Using Proposition \ref{Th:additive-games-stationary-dist}, one can derive the closed form expression for the stationary distribution of a $N-$player linear public goods game with two strategies.
+\newpage
 \begin{Prop}
@@
 \end{cases}
-\end{equation}
+\end{equation} \\
 \end{Prop}
-\noindent We use a simple example to demonstrate the above result.
+\noindent This result directly follows from Proposition \ref{Th:additive-games-stationary-dist}.
+For an independent proof, please see Appendix.
+We use a simple example to demonstrate the above result.
 Consider a 3-player linear public goods game.
 All players provide a benefit of 2 units when they contribute to the public good ($b_1 = b_2 = b_3 = 2$).
-They differ however in their cost of cooperation.
+They differ, however, in their cost of cooperation.
 For player 1 and 2, the cost of cooperation is 1 unit ($c_1 = c_2 = 1$) while for the third player, the cost is slightly higher at 1.5 units ($c_3 = 1.5$).
-In the stationary distribution of the process with selection strength $\beta = 1$, the state where player 1 and 2 play $\C$ and player 3 plays $\D$, $\ubf_{\C\C\D}$, occurs with probability $\approx 0.112$ (rounded up to three decimal places).
+In the stationary distribution of the process with selection strength $\beta = 1$, the state where player 1 and 2 play $\C$ and player 3 plays $\D$, $\ubf_{\C\C\D}$, occurs with probability $\approx 0.121$ (rounded up to three decimal places).
 We calculate this probability exactly with Eq.
 (\ref{Eq:stationary_dist_lpgg}).
-The marginal probabilities that in the long run player 1 (or player 2) plays cooperation and player 3 plays defection are 0.4 and 0.7 respectively.
-That is, $\xi_{1:\C} = \xi_{2:\C} \approx 0.4$ and $\xi_{3:\D} \approx 0.7$ (rounded upto a single decimal place).
-With the exact values (and also with the approximations here), one can confirm the factorizing property of the stationary distribution for additive games in this example (i.e., proposition \ref{Th:additive-game-product-of-marginals}).
+The marginal probabilities that in the long run player 1 (or player 2) plays cooperation and player 3 plays defection are 0.417 and 0.697 respectively.
+That is, $\xi_{1:\C} = \xi_{2:\C} \approx 0.417$ and $\xi_{3:\D} \approx 0.697$ (rounded up to a three decimal places).
+With the exact values (and also with the approximations here), one can confirm the factorizing property of the stationary distribution for additive games in this example (i.e., Proposition \ref{Th:additive-game-product-of-marginals}).
 That is, $\ubf_{\C\C\D} = \xi_{1:\C} \cdot \xi_{2:\C} \cdot \xi_{3:\D}$.
 \\ \\
-\noindent First, we systematically the linear public goods game in which all players are symmetric.
+\noindent First, we analyze the simplest case of the linear public goods game in which all players are symmetric to each other.
 We consider a game with 4 players.
-All players have the same cost of cooperation ($c_i = c$) and they all provide the same benefit to the public goods ($b_i = b$).
+All players have the same cost of cooperation ($c_i = c$) and they all provide the same benefit to the public good ($b_i = b$).
 Since all players are identical, the states of the game can be enumerated by counting the number of cooperators in the state.
-There can only be 5 distinct states of the game (from 0 to 4 contributors).
+There can only be 5 distinct states of the game (from 0 to 4 cooperators).
+In this case, one can show with Eq.
+(\ref{Eq:stationary_dist_lpgg}) that, between the states with $k$ and $k+1$ cooperators, the stationary distribution changes by a factor of $(k+1)/(4-k) \cdot \mathrm{exp}(\beta f_j(\D,\C))$.
 When the parameters of the game are such that defection dominates cooperation ($b = 2, c = 1$, Fig.
-\ref{}a), the stationary distribution of the process at high $\beta$ ($\beta = 5$), indicates an exponential decrease in the probability of a state with increase in the number of cooperators in the state.
-However, for intermediate and low $\beta$, the long-run outcomes of the introspection dynamics are qualitatively different to the outcomes at high $\beta$.
+\ref{Fig:LPGG-symmetric}a), the stationary distribution of the process at high $\beta$ indicates that in the long-run, states with higher number of cooperators are less likely than states with lower number of cooperators.
+However, for intermediate and low $\beta$, stationary results are qualitatively different.
 Here, the state with $1$ cooperator (or even $2$ cooperators, depending on how small $\beta$ is) is the most probable state in the long-run (Fig.
-\ref{}b).
-Naturally, $\beta$ plays an important role determining the overall cooperation frequncy in the public goods game.
+\ref{Fig:LPGG-symmetric}b).
+Naturally, $\beta$ plays an important role in determining the overall cooperation frequncy in the game.
 When $\beta$ is low, the average cooperation frequency varies weakly with the strength of the dilemma, $b/N - c$ (Fig.
-\ref{}c).
+\ref{Fig:LPGG-symmetric}c).
 Even when the temptation to defect is high ($b/N - c \approx -2$), players cooperate with a non-zero probability in the long run ($\approx 0.1$).
-Similarly, when cooperation is highly beneficial ($b/N - c \approx 2$), players defect with some probability ($\approx 0.2$).
-At higher values of $\beta$, the stationary behaviour of the players is more responsive to the payoffs of the game and thus reflect an abrupt change around the parameter region where the game transitions from defection-dominating to cooperation-dominating ($b/N - c = 0$).
+Similarly, when cooperation is highly beneficial and strictly dominates defection ($b/N - c \approx 2$), players defect with a non-zero probability ($\approx 0.1$).
+At higher values of $\beta$, the stationary behaviour of players is more responsive to the payoffs and thus reflects an abrupt change around the parameter region where the game transitions from defection-dominating to cooperation-dominating ($b/N - c = 0$).
 \\ \\
 \noindent 
-For studying the linear public goods game with asymmetric players, we consider a setup with 3 players.
-All the players differ in their cost of cooperation and the benefit they provide to the public goods.
+For studying the asymmetric linear public goods game, we consider a setup with 3 players.
+All the players can differ in their cost of cooperation and the benefit they provide to the public goods.
 In this setup, the reference player's (player 2) cost and benefit values are $1$ and $2$ units respectively.
@@
 For player 1, the cost and benefit are $1 + \delta_c$ and $2 + \delta_b$ respectively while for player 3, the cost and benefit are $1 - \delta_c$ and $2 - \delta_b$, respectively.
-First, we study a simple case in which players only vary in their cost of cooperation ($\delta_b = 0$ and $\delta_c = 0.5$, Fig \ref{}a).
+First, we study a simple case in which players only differ in their cost of cooperation ($\delta_b = 0$ and $\delta_c = 0.5$, Fig \ref{Fig:LPGG-asymmetric}a, left).
 In the long run, the relative cooperation frequency of players reflect their relative ability to cooperate.
-The player with the lowest cooperation cost (player 3), cooperates with the highest probability (and \emph{vice-versa}).
-Similarly, when players only differ in their ability to produce the public good ($\delta_b = 1$ and $\delta_c = 0$, Fig \ref{}b), their relative cooperation in the long run reflects the relative benefits they provide with their cooperation.
-The player with the highest benefit value (player 1) cooperates with the highest probability.
+The player with the lowest cooperation cost (player 3), cooperates with the highest probability (and \emph{vice-versa},  Fig \ref{Fig:LPGG-asymmetric}a, right).
+Similarly, when players only differ in their ability to produce the public good ($\delta_b = 1$ and $\delta_c = 0$, Fig \ref{Fig:LPGG-asymmetric}b left), their relative cooperation in the long run reflects the relative benefits they provide with their cooperation.
+The player with the highest benefit value (player 1) cooperates with the highest probability (Fig \ref{Fig:LPGG-asymmetric}b, right).
 For this particular setup with three asymmetric players, defection dominates cooperation for player 1 if and only if $\delta_b < 1 + 3\delta_c$ .
@@
 These regions in the $\delta_b-\delta_c$ parameter plane that correspond to defection dominating cooperation are circumscribed by white dashed lines in Fig.
-\ref{}c.
+\ref{Fig:LPGG-asymmetric}c.
 When players learn to play at high selection strength, $\beta$, their cooperation frequency in the long-run reflect the rational play (Fig.
-\ref{}c).
+\ref{Fig:LPGG-asymmetric}c).
 In the long run, the average cooperation frequency of the group is low if the asymmetry in the benefit value is bounded, $3\delta_c - 1 < \delta_b < 3\delta_c + 1$.
@@
 A relatively high cooperation frequency is only assured if players are aligned in their asymmetries (i.e., either $\delta_b < 3\delta_c +1$ or $\delta_b > 3\delta_c - 1$).
+Or, in other words, if the player that has low cost of cooperation also provides a high benefit upon contribution, then cooperation frequencies are high in the long-run.
 
@@
 
-In this section, we study the stationary properties of games with two actions.
-These games are not necessarily additive.
-First, we study the simplest case in which all players are symmetric.
+In the previous section we studied the properties of additive games under introspection dynamics.
+In this section, we study the stationary properties of games that are a) not necessarily additive and b) have only two actions for each player.
+First, we study the symmetric version of such a game.
 A $N$-player symmetric normal form game with two actions has the following properties:
@@
 \begin{enumerate}
-\item  $\A_1 = \A_2 = ... = \A_N := \mathcal{A} := \{\C,\D\}$
-\item For any $i,j \in \{1,2,...,N\}$, $a \in \mathcal{A}$ and $\bbf \in \displaystyle \prod_{j=1}^{N} \mathcal{A}$:
+\item  All players have the same action set $\mathcal{A}$. That is, $\A_1 = \A_2 = ... = \A_N := \mathcal{A}$. We denote this set by, $\mathcal{A} := \{\C,\D\}$.
+\item Players have the same payoff when they play against the same composition of co-players. That is, for any $i,j \in \{1,2,...,N\}$, $a \in \mathcal{A}$ and $\bbf \in \mathcal{A}^{N-1}$,
 \begin{equation}
@@
 \noindent Since players are symmetric, states can again be enumerated by counting the number of $\C$ players in the state.
-We denote the payoff of a $\C$ and $\D$ player in a state where there are $j$ $\C$ players with $\pi_\C(j)$ and $\pi_\D(j)$ respectively.
-From the previous section, we adopt the mapping function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to 0.
-We use the notation $\mathcal{C}(\abf)$ to denote the number of cooperators in the state $\abf$.
+We denote the payoff of a $\C$ and $\D$ player in a state where there are $j$ co-players playing $\C$ by $\pi_\C(j)$ and $\pi_\D(j)$ respectively.
+From the previous section, we adopt the mapping function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to 0, and the notation $\mathcal{C}(\abf)$ to denote the number of cooperators in the state $\abf$.
 That is,
@@
 
-\noindent The number of unique states of the game can be reduced to $N+1$ from $2^N$ due to symmetry.
-In the reduced state space, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
-Then, Proposition \ref{Prop:Symmetric-2-strategies-state} can be reformulated by relabelling the states as follows,
+\noindent For a proof of this proposition, please see Appendix.
+The number of unique states of the game can be reduced to $N+1$ from $2^N$ due to symmetry.
+In the reduced state space, the state, $k$, corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
+Then, Proposition \ref{Prop:Symmetric-2-strategies-state} can be simply reformulated by relabelling the states as follows,
 
@@
 (\ref{Eq:explicit-stationary-dist-representation}).
-In the next section, we study the stationary behaviour of the introspection dynamics in the general public goods game (symmetric and asymmetric).
+In the next section, we study the stationary behaviour of the introspection dynamics in a two-action general game with an example.
+To this end, we use the example of a non-linear public goods game to demonstrate the results.
 
@@
 
-To study general public goods game we adopt the framework of general social dilemmas from Hauert et al.
+To study general public goods game, we adopt the framework of general social dilemmas from Hauert et al.
 \cite{Hauert:JTB:2006a}.
-This framework introduces a parametric normal form game with symmetric players.
+This framework introduces a normal form game with symmetric players.
+The game's properties are determined by a parameter $w$ that determines the nature of the public good.
 The players have two actions: cooperation, $\C$ and defection, $\D$.
+In Hauert et al., authors introduce a symmetric public goods game.
 Here, we extend their framework to account for players with asymmetric payoffs.
-For player $i$, the cost of cooperation is $c_i$.
+Before we explain the asymmetric setup, we describe the original model briefly.
+In the symmetric case, all $N$ players have the same cost of cooperation, $c$ and they all generate the same benefit $b$ for the public good.
+Unlike the linear public goods game, contributions to the public good are scaled by a factor that is determined by $w$ and the number of cooperators in the group.
+The payoff of a defector and a cooperator in a group with $k$ cooperators and $N-k$ defectors is given by,
+
+\begin{align}
+\pi^{\D}_i(k) &= \frac{b}{N}(1 + w + w^2 + ... + w^{k-1}) \\[15pt]
+\pi^{\C}_i(k) &= \pi^{\D}_i(k) - c
+\label{Eq:payoff-synergistic-symmetric}
+\end{align}
+
+\noindent The parameter $w$ represents the non-linearity of the public good.
+The nature is linear when $w = 1$.
+Every additional cooperator's contribution is as valuable as the benefit that they can generate.
+When $w < 1$, the effective contribution of every new cooperator goes down by a factor of $w$ (compared to the last cooperator).
+The public goods is said to be discounting in this case.
+On the other hand when $w > 1$, every new contributor is more valuable than the previous one.
+These public goods are called synergistic.
+For the symmetric case, the relationship between the cost to benefit ratio, $cN/b$, and the discount/synergy factor, $w$, determines the type of social dilemma arising from this general public goods game.
+In principle, this framework can produce generalizations of the prisoner's dilemma (defection dominating cooperation), the snowdrift game (no dominance but coexistence under the replicator dynamics), the stag-hunt game (no dominance but existence of an internal equilibrium that is unstable under the replicator dynamics) and the harmony game (cooperation dominating defection) with respect to its evolutionary trajectories.
+For more details see Hauert et al.
+\cite{Hauert:JTB:2006a}.
+We study the long term stationary behaviour of players in this game when they learn through introspection dynamics.
+\\
+
+\noindent Now, we describe our extension of the original model to account for asymmetric players.
+Here, for player $i$, the cost of cooperation is $c_i$.
 The benefit that they can generate for the public good is $b_i$.
-However, in the general public goods game, the benefit of cooperation generated by a player is either synergized (or discounted) by a factor depending on the number of cooperators already in the group and the synergy/discount factor, $w$.
-If there are already $k-1$ cooperators in the group, the effective benefit provided to the public good by the $k^{th}$ cooperating player (say $i$), is $w^{k-1} b_i$.
-In this setup, we assume that all the orders in which cooperators' benefits can be synergized (or discounted) are equally likely.
-We clarify with an example.
-Consider that there are three cooperators in the group: player $i, j$ and $k$.
-The total benefit that they provide to the public good can be one of the six possibilities from $x + y w + z w^2$, where $x,y$ and $z$ are permutations  of $b_i, b_j$ and $b_k$.
-We assume that all the six possibilities are equally likely, and therefore, the expected benefit is given by $\bar{b}(1 + w + w^2)$ where $\bar{b} = (b_i + b_j + b_k)/3$.
+However, the benefit of cooperation generated by a player is either synergized (or discounted) by a factor depending on the number of cooperators already in the group and the synergy/discount factor, $w$ (just like the original model).
+However, now, since players are asymmetric it is not entirely clear in which order the contributions of cooperators should be discounted (or synergized).
+For example, consider that there are three cooperators in the group: player $p, q$ and $r$.
+The total benefit that they provide to the public good can be one of the six possibilities from $x + y w + z w^2$, where $x,y$ and $z$ are permutations  of $b_p, b_q$ and $b_r$.
+In this model, we assume that all such permutations are equally likely, and therefore, the expected benefit provided by all three of them is given by $\bar{b}(1 + w + w^2)$ where $\bar{b} = (b_p + b_q + b_r)/3$.
 \\
 
-\noindent The complete state space of the game is $\A = \{\C,\D\}^N$.
+\noindent The complete state space of the game with asymmetric players is $\A = \{\C,\D\}^N$.
 The payoff of a defector in a state $(\D, \abf_{-i})$ and that of a cooperator in state $(\C,\abf_{-i})$ where $\abf_{-i} \in \{\C,\D\}^{N-1}$ are respectively given by:
@@
 Note that the number of cooperators in the two states are related as: $\mathcal{C}(\D,\abf_{-i}) = \mathcal{C}(\C,\abf_{-i}) - 1$.
-In the symmetric case, were every player has the same cost and benefit values, the payoffs of a defector and a cooperator in a group with $k$ cooperators can be simply written as:
-
-\begin{align}
-\pi^{\D}_i(k) &= \frac{b}{N}(1 + w + w^2 + ... + w^{k-1}) \\[15pt]
-\pi^{\C}_i(k) &= \pi^{\D}_i(k) - c
-\label{Eq:payoff-synergistic-symmetric}
-\end{align}
-
-\noindent The parameter $w$ represents the nature of the public goods.
-The nature is linear when $w = 1$.
-Every additional cooperator's contribution is as valuable as the benefit that they can generate.
-When $w < 1$, the effective value of every new cooperator goes down by a factor of $w$ (compared to the last cooperator).
-The public goods is said to be discounting in that case.
-On the other hand when $w > 1$, every new contributor is more valuable than the previous one.
-These public goods are called synergistic.
-For the symmetric case, the relationship between the cost to benefit ration $cN/b$ and the discount/synergy factor determines the type of social dilemma arising from this general public goods game.
-In principle, this framework can produce generalizations of the prisoner's dilemma (defection dominating cooperation), the snowdrift game (no dominance but coexistence under the replicator dynamics), the stag-hunt game (no dominance but existence of an internal equilibrium that is unstable under the replicator dynamics) and the harmony game (cooperation dominating defection) with respect to its evolutionary trajectories.
-For more details see Hauert et al.
-\cite{Hauert:JTB:2006a}.
-We study the long term stationary behaviour of players when they learn through introspection dynamics.
-First we focus on only the symmetric version of this game.
-\\ \\ 
-\noindent To compute the stationary distribution of the symmetric general public goods game (PG), we use the closed for expression in Eq.
+In the following, we discuss results from the symmetric public goods game and then discuss results for the game with asymmetric players.\\
+
+\noindent To compute the stationary distribution of introspection dynamics in a symmetric (general) public goods game (PG), we use the closed for expression in Eq.
 (\ref{Eq:stationary-dist-symm-2-stgs}).
 We consider that every player in a 4-player game can generate a benefit $b$ of value $2$.
-We study an introspection process with selection strength $\beta = 5$.
 Before exploring the $c-w-N$ parameter space, we study four specific cases.
-In two of these cases, the public goods is discounted ($w = 0.5$) and in two other cases, the public goods is synergistic ($w = 1.5$).
-For each case we consider two sub-cases: one, in which cost is high ($c = 1$) and two, when cost is low ($c = 0.2$).
+In two of these cases, the public goods is discounted ($w = 0.5$, Fig.
+\ref{Fig:GPGG-symmetric}a left panels) and in two other cases, the public goods is synergistic ($w = 1.5$, Fig.
+\ref{Fig:GPGG-symmetric}a right panels).
+For each case, we consider two sub-cases: one, in which cost is high ($c = 1$,  Fig.
+\ref{Fig:GPGG-symmetric}a top panels) and two, when cost is low ($c = 0.2$, Fig.
+\ref{Fig:GPGG-symmetric}a bottom panels).
 The four parameter combinations are chosen such that each of them represents a unique social dilemma under the replicator dynamics.
@@
 When the PG is synergistic ($w = 1.5$) and costs are high ($c = 1$), both cooperation and defection are locally stable equilibria.
-In addition there is also an internal equilibrium which is unstable.
+In addition, there is also an internal equilibrium which is unstable.
 This represents the stag-hunt game.
@@
 This situation represents the harmony game.
-The stationary behaviour of the players from the introspection dynamics in these games reflect the outcomes from the replicator dynamics (Fig.
-\ref{}a).
-Since selection strength is chosen to be intermediate, in some of these cases, players play actions that are not optimal for the dilemma with positive probability in the long run.
+The stationary behaviour of players in these games reflect the outcomes from the replicator dynamics (Fig.
+\ref{Fig:GPGG-symmetric}a).
+As selection strength is intermediate ($\beta = 5$), in some cases, players learn to play actions that are not optimal for the dilemma with non-zero probability.
 For example, even when the parameters of the game make cooperation to be the dominated strategy, there is a single cooperator in the group with a sizeable chance ($\approx 20\%$) in the long run.
 When the parameters of the game reflect the stag-hunt dilemma, players are more likely to coordinate their actions in the long run.
-The probabilities that the whole group plays $\C$ or $\D$ is higher than the probability that there is a group with mixed play.
+In the long-run, the probabilities that the whole group plays $\C$ or $\D$ is higher than the probabilities that there is a group with a mixture of $\C$ and $\D$ players.
 In contrast, when the parameters reflect the snowdrift game, we get the opposite effect.
@@
 In fact, the group with exactly 2 cooperators and 2 defectors is the most likely outcome in the long run.
-Finally, when the parameters of the game make defection the dominated action, all players in the group learn to play cooperation in the long run.
+Finally, when the parameters of the game make defection the dominated action, all players in the group learn to cooperate in the long run.
 \\ \\
@@
 \ref{}b).
-It is fixed to a value such that there is full cooperation in the long run in a group of arbitrary size when $w > 1$.
+It is fixed to a value such that in a synergistic PG ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size.
 In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run.
-For a fixed value of $w (< 1)$, cooperation rates fall with larger group sizes.
+When the public good is discounted ($w < 1$), cooperation rates fall with larger group sizes.
+\\
+
+\noindent
+
+\section*{Application: Introspection learning in a game with cooperation and rewards}
+
+In all the examples that we have studied so far, players can only play can only choose between two actions (pure strategies).
+Introspection dynamics is particularly useful when players have larger strategy sets available to them.
+In this section, we study the stationary behaviour of players in a game where each player has 16 possible actions (pure strategies).
+To this end, we adopt the multiplayer cooperation and rewarding game from Pal et al.
+\cite{Pal:NatCom:2022}.
+In this game, there are two stages: in stage 1, players decide whether or not they contribute to a linear public good and in stage 2, they decide whether or not they reward their peers.
+When a player contributes to the public good, they pay a cost $c_i$ but generate a benefit worth $r_i c_i$ that is equally shared by everyone.
+When a player rewards a peer, they provide them a benefit of $\rho$ while incurring the cost of rewarding, $\gamma_i$ to self.
+In between the stages, players get full information about the contribution of their peers.
+In the rewarding stage, players have four possible strategies: they can either reward all the peers who contributed (social rewarding), reward all the peers who defected (antisocial rewarding), reward all peers irrespective of contribution (always rewarding) or reward none of the peers (never rewarding).
+Before stage 1 commences, player $i$ knows with some probability, $\lambda_i$, the rewarding strategy of all their peers.
+In stage 1, players can have four possible strategies: they can either contribute or defect unconditionally or they can be conditional cooperators or conditional defectors.
+Conditional cooperators (or defectors) contribute (or do not contribute) when they have no information about their peers (which happens with probability $1 - \lambda_i$).
+When a conditional player, $i$, knows the rewarding strategy of all their peers (which happens with probability $\lambda_i$) and finds that there are $n_{\mathrm{SR}}$ social rewarders and $n_{\mathrm{AR}}$ antisocial rewarders among his peers, they cooperate if and only if the marginal gain from rewards for choosing cooperation over defection outweighs the effective cost of cooperation.
+That is,
+
+\begin{equation}
+\rho(n_{\mathrm{SR}} - n_{\mathrm{AR}}) \geq c_i \left( 1 - \frac{r_i}{N} \right)
+\label{Eq:palrewardsequation}
+\end{equation}
+\\
+\noindent Combining the two stages, players can use one of 16 possible strategies.
+In the simple case where players are identical, one can characterize the Nash equilibria of the game and identify the conditions which allow an equilibrium where all players contribute in the first stage and reward peers in second stage \cite{Pal:NatCom:2022}.
+In the symmetric case, full cooperation and rewarding is feasible in equilibrium when all players have sufficient information about each other and the reward benefit $\rho$ is neither too high, nor too low.
+In this section, we study three simple cases of asymmetry between players to demonstrate how these asymmetric players may learn to play the game through introspection dynamics.
+The three specific examples that we show demonstrate that with introspection dynamics, asymmetric players can end up taking different roles in the long run to produce the public good.
+To this end, we consider a 3-player game in which player 1 and 2 are identical but player 3 is asymmetric to them in some aspect.
+We consider three cases.
+In each case the asymmetric player either has \textbf{a}) a higher cost of rewarding $\gamma_3 > \gamma_1$  or, \textbf{b}) low productivitiy  $r_3 < r_1$ or, \textbf{c}) or, less information about peers $\lambda_3 < \lambda_1$ than his peers.
+We simulate the introspection dynamics (with a strong selection strength, $\beta = 10$) for many iterations ($10^5$ time-steps) to estimate the average abundances of the 16 strategies.
+\\ \\
+\noindent In the case where player 3 is asymmetric with respect to their cost of rewarding, the long-run outcome of introspection reflects a division in labour between the players in producing the public good (Fig.
+\ref{Fig:SocialRewarding}a).
+The players, to whom rewarding is less costly (player 1 and player 2), reward cooperation with a higher probability than to whom rewarding is very costly (player 3).
+In return, player 3 learns to respond by contributing with more probability than their co-players.
+With these specific parameters, one player takes up the role of providing the highest per-capita contribution while the others compensate with costly rewarding.
+When the asymmetric player differs only in their productivity, a different effect may appear in the long run (Fig \ref{Fig:SocialRewarding}b).
+We choose a very specific set of parameters to display this effect.
+In this case, the less productive player free rides on the cooperation of their higher productive peers, but eventually reward the cooperation of their peers nonetheless.
+The asymmetric player free-rides but does not second-order free ride.
+The probability with which the less productive player rewards others in the long run is slightly higher than the probability with which the contributing individuals reward each other.
+Finally, we consider the case where the asymmetric individual differs from others in terms of the information players have about others' rewarding strategy (Fig \ref{Fig:SocialRewarding}c).
+In this case, the asymmetric player knows others' strategy with a considerably less chance than his peers.
+In the long run, the asymmetric player cooperates less on average than their peers.
+This is because they cannot cooperate opportunistically enough, unlike their peers with higher information.
+However, both types of player reward cooperation almost equally and just enough to sustain cooperation.
 
@@
 %[Short summary]
+Most previous evolutionary models focus on limiting regimes, namely low mutation rate and selection strength approximations, as they allow for analytical results. 
+Here, we show that it is possible to obtain analytical expressions for the long-run average strategy abundances for multiplayer games resorting to introspection dynamics, even for intermediate values of selection strength.
+We start by analysing the set of additive games, for which the gain from switching between any two actions is constant, regardless of what co-players do. 
+Due to this simple feature, additive games allow for the most general close-form expression for the stationary distribution, regarding the number of players, strategies, and asymmetry of the game. 
+Additionally, we find that for any additive game, the joint distribution of strategies factorizes over the marginal distribution of strategies. 
+For general games (for which additivity does not hold in general), we provide the stationary distribution formula for 2-strategy, symmetric games.
+By studying several examples of social dilemmas, we conclude that, generally, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently. \\ \\ 
+\noindent Introspection dynamics is a rather broad model.
+Here, we mainly focused on introducing a general framework to the detriment of exploring more realistic, complex examples.
+Nevertheless, in the last section, we give one step forward in that direction, by studying a 2-stage game, where players can choose among $16$ strategies.
+There, individuals can reward their co-players condition on their previous cooperative (or not) behavior.
+%[What we didn't do, limitations, further work]
+\noindent Clearly, there are a number of ways in which we can further employ our model.
+For example, other researchers recently studied multiplayer games considering multiple games played concurrently \cite{Venkateswaran:PRSB:2019}, fluctuating environments \cite{Baron:JRSOP:2018}, continuous strategies \cite{Molina:JMB:2017}, or repeated interactions \cite{Hilbe:JTB:2015}.
+Finally, for the sake of mathematical tractability, introspection dynamics, as we present it here, does not consider a population, not to mention complex population structures \cite{Broom:JTB:2012, Wu:Games:2013, Perc:JRSI:2013, Pena:JTB:2015, Pena:JRSI:2016, Pattni:JTB:2017, Su:PNAS:2022}.
+However, it can be equally applicable to population models.
+In that case, players obtain average payoffs either from well-mixed or network-bounded interactions, as usual, but update their strategies introspectively.
 
 %[Comparison to other models]
-
-%[What we didn't do, limitations, further work]
-Introspection dynamics is a rather broad model.
-Here, we mainly focused on general cases to the detriment of more realistic, complex examples.
-Nevertheless, in the last section, we give one step forward in that direction, by studying a 2-stage game, where individuals are allowed to reward their co-players condition on previous actions.
-Clearly, there are a number of ways in which we can further employ our model.
-For example, other researchers recently studied multiplayer games considering multiple games played concurrentlyin \cite{Venkateswaran:PRSB:2019}, fluctuating environments \cite{Baron:JRSOP:2018}, continuous strategies \cite{Molina:JMB:2017}, or repeated interactions \cite{Hilbe:JTB:2015}.
-\\ \\
-\noindent
-Finally, for the sake of mathematical tractability, introspection dynamics, as we present it here, does not consider a population, not to mention complex population structures \cite{Broom:JTB:2012, Wu:Games:2013, Pena:JTB:2015, Pena:JRSI:2016, Pattni:JTB:2017, Su:PNAS:2022}.
-However, it can be equally applicable to population models.
-In that case, players obtain payoffs either from well-mixed or network-bounded interactions, as usual, but update their strategies introspectively.
+%see e.g Hofbauer:GEB:2005
 
@@
 
-%\newpage
-%\begin{figure}[t!]
-%\centering
-%\includegraphics[width =  0.95\textwidth]{figures/figure1.eps}~\\[-0.4cm]
-%\caption{\onehalfspacing
-%\textbf{Symmetric linear public goods game,}
-%a) Frequency of each state in the stationary distribution of introspection dynamics.
-As players are indistinguishable here, each state can be fully defined by the number of cooperators.
-Parameters: $N = 4$, $b = 2$, $c = 1$ and $\beta = 5$.
-b) For the same game parameters ($N = 4$, $b = 2$ and $c = 1$), we now show the frequency of each state (same color code as in panel a) for varying selection strength $\beta$.
-Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators.
-Indeed, up to $\beta \approx 3$, state $0$ is not even the most frequent.
-c) Average cooperation frequency for varying dilemma strength.
-We use as a measure of the dilemma strength the marginal gain by choosing to cooperate over choosing to defect, $b/N - c$.
-When this quantity is low, we say there is a ``strong dilemma”, where there is no individual advantage to cooperate, whereas when the marginal gain is high, we say there is a ``weak dilemma” (or no dilemma), where to cooperate becomes advantageous.
-Typically, a linear public goods dilemma is defined as having a negative marginal gain (see conditions above).
-Here, we show the whole parameter range for completeness and a full grasp of this game.
-We also show the result for different values of selection strength, $\beta = 1, 5$ and $100$.
-For high $\beta$, we confirm the classical prediction that, assuming a negative marginal gain, defection is dominant.
-For low $\beta$, however, we see again that some cooperation is possible.
-}
-%\end{figure}
+%ACKNOWLEDGEMENTS: CH, DSBRG, ERC
+
+%Rev: broom, archetti, pena, schmidt, mcavoy, wu
 
@@
 \textbf{Proof of Proposition} \ref{prop:stationary-dist-lpgg} \\ \\
-Since we have demonstrated that the linear public goods game is an additive game, the proof of this theorem can be performed by directly using proposition \ref{Th:additive-games-stationary-dist}.
+Since we have demonstrated that the linear public goods game is an additive game, the proof of this theorem can be performed by directly using Proposition \ref{Th:additive-games-stationary-dist}.
 Here, we provide an independent proof.
@@
 \\ \\
-\noindent Using proposition \ref{Prop:unique-stationary-dist}, we can confirm that since $\beta$ is finite, the process will have a unique stationary distribution.
+\noindent Using Proposition \ref{Prop:unique-stationary-dist}, we can confirm that since $\beta$ is finite, the process will have a unique stationary distribution.
 Before continuing with the rest of the proof where we show that our candidate stationary distribution is \emph{the} unique stationary distribution, we define the following short-cut notations for the ease of the proof:
@@
 (\ref{Eq:normalizationcondition}) and for any state $\abf$, $\ubf_{\abf}$ is between 0 and 1.
-Moreover, since $\beta$ is finite, by proposition \ref{Prop:unique-stationary-dist}, the process will have a unique stationary distribution.
+Moreover, since $\beta$ is finite, by Proposition \ref{Prop:unique-stationary-dist}, the process will have a unique stationary distribution.
 To show that the candidate stationary distribution is the unique stationary distribution, we need to check if for this process, $\ubf \T= \ubf$.
@@
 \begin{equation}
-\ubf_{k} = \sum_{\forall \abf,  \mathcal{C(\abf)} = k} \ubf_\abf = \frac{1}{\Gamma} {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)} \\[10pt]
+\ubf_{k} = \sum_{\mathcal{C(\abf)} = k} \ubf_\abf = \frac{1}{\Gamma} {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)} \\[10pt]
 \end{equation} 
@@
 \newpage
-\section*{Supplementary References}
+
+%--------FIGURE WITH LINEAR PGG-----
+\begin{figure}
+\centering
+\includegraphics[width =  \textwidth]{figures/figure1.eps}~\\[0.4cm]
+\caption{\onehalfspacing
+\textbf{Symmetric linear public goods game.}
+We use the following parameters for all the panels in this figure: $N = 4$ (group size), $b = 2$ (benefit provided to the public good on cooperation), $c = 1$ (cost of cooperation) a) Here we show the frequency of each state in the stationary distribution of introspection dynamics.
+As players are identical here, each state can be defined by the number of cooperators.
+We use a selection strength of $\beta = 5$ for the introspection dynamics.
+For this strength of selection, states with more cooperators are less likely than states with less cooperators in the stationary distribution b) The frequency of each state for varying selection strength, $\beta$.
+We use the same color code as the previous panel.
+Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators.
+Indeed, up to $\beta \approx 3$, state $0$ is not the most frequent state in the long run c) Average cooperation frequency for varying dilemma strength depends on the selection strength $\beta$ and the parameters of the linear public goods game: $b,c, N$.
+We use the marginal gain of choosing cooperation over defection, $b/N - c$, as a measure of the dilemma strength.
+When this quantity is negative and low, we say that the dilemma is strong.
+In this case, there is no individual advantage to cooperate.
+When this quantity is positive and high, we say that the dilemma is weak.
+In this case, cooperation dominates defection.
+Typically, a linear public goods dilemma is defined to have a negative marginal gain (see conditions above).
+Here, we show the dilemma strength varying from $-2$ to $2$.
+The results are shown for different values of selection strength, $\beta = 1, 5$ and $100$.
+For high $\beta$, stationary distribution of the introspection dynamics reflects the rational play.
+In the long run player play the Nash equilibrium.
+When marginal gain is negative, defection is played with almost certainty (and \emph{vice-versa}).
+For low $\beta$, however, we see that some cooperation is possible even when the dilemma is strong.
+}
+\label{Fig:LPGG-symmetric}
+\end{figure}
+\clearpage
+\begin{figure}
+\centering
+\includegraphics[width =  \textwidth]{figures/figure2.eps}~\\[0.4cm]
+\caption{\onehalfspacing
+\textbf{Asymmetric linear public goods game.} In the upper panels (a and b) we show the cost of cooperation and the benefit of provided due to cooperation for the three players on the left and the average cooperation frequency on the right.
+In this example, the cost of cooperation for players 1, 2 and 3 are $1 + \delta_c, 1$ and $1 - \delta_c$ respectively.
+The benefits that player 1, 2 and 3 provide upon cooperation are $2 + \delta_b, 2$ and $2 - \delta_b$ respectively.
+The cost and benefit for the reference player (player 2) are shown with black dashed lines in the left panels of a and b.
+In a) player 1 and 3 differ by 0.5 units in their cost of cooperation from the reference player.
+All the players provide the same benefit when they contribute (i.e., $\delta_b = 0$).
+Conversely, in b) benefit by player 1 and 3 differ from the reference player by 1 unit.
+The cost of cooperation is the same for all players ($c = 1$).
+In c), we vary the asymmetry strengths $\delta_c $ and $\delta_b$ simultaneously and show both average individual cooperation frequency and the overall average cooperation frequency in the long-run.
+The reference player's cost and benefit are 1 and 2 units respectively.
+The area within the white dashed lines represents the parameter values for which the marginal gain of choosing cooperation over defection is negative, for each single player and, in the right-most panel, for all players simultaneously.
+For panels a and b we use a selection strength of $\beta = 2$ while for panel c, we use a selection strength of $\beta = 5$.
+}
+\label{Fig:LPGG-asymmetric}
+\end{figure}
+\clearpage
+\begin{figure}
+\centering
+\includegraphics[width =  0.65\textwidth, keepaspectratio]{figures/figure3}~\\[0.4cm]
+\caption{\onehalfspacing
+\textbf{Symmetric general public goods game}.
+We study introspection dynamics in the general public goods game with 4 symmetric players, each having two possible actions - cooperation and defection.
+For a detailed description of the game, please see the main text.
+a) The frequency of each state in the stationary distribution of introspection dynamics in four types of multiplayer social dilemmas display qualitatively different results.
+The upper panels refer to a high cost of cooperation ($c=1$) while the bottom panels to a low cost of cooperation ($c = 0.2$); left panels refer to a discounted public good ($w = 0.5$), and the right panels refer to a synergistic public good ($w = 1.5$).
+Each case is tagged with a symbol that places the particular case in the contour plot in panel b, b) Average cooperation frequency for varying discount/synergy factor, $w$, and varying cost of cooperation, $c$.
+Cooperation is feasible when costs are not restrictively high and the public good is not too discounted.
+c) Average cooperation frequency for varying discount/synergy factor, $w$, and group size $N$.
+For this plot,the cost of cooperation for each player is $c = 0.4$.
+The feasibility of cooperation drops with larger group sizes when the public good is discounted.
+For all panels, the benefit of cooperation generated by each player is worth 2 units.
+The selection strength of the process is $\beta = 5$ for all panels.}
+\label{Fig:GPGG-symmetric}
+\end{figure}
+\clearpage
+\begin{figure}
+\centering
+\includegraphics[width =  \textwidth]{figures/figure4.eps}~\\[0.4cm]
+\caption{\onehalfspacing
+\textbf{Cooperation and social rewarding in the stationary distribution of introspection dynamics in the linear public goods game with peer rewarding} Here we study a game with three asymmetric players, each having 16 possible strategies.
+Players cooperate in a linear public goods and then reward each other in the next stage after everyone's contribution is revealed.
+Players can condition their cooperation on the information they have about their co-players' rewarding strategies.
+For a full description of the model, please see the section on rewarding above.
+In this example, players 1 and 2 are identical in all aspects while player 3 is asymmetric to them in only a single aspect.
+In here, we plot the average frequency with which players cooperate and reward cooperation after a long time (after $10^5$ time steps of a computer simulation).
+We consider three types of asymmetry for player 3.
+a) First, we consider the case where player 3 has a high cost of rewarding compared to player 1 and 2, $0.7 = \gamma_3 > \gamma_1 = 0.1$.
+b) Then, we consider the case where player 3 is less productive than their co-players, $1.2 = r_3 < r_1 = 2$.
+c) Finally, we consider the case where player 3 has less information about co-players' rewarding strategies than their peers, that is, $0.1 = \lambda_3 < \lambda_1 = 0.9$.
+For all plots, we consider the selection strength of players are high, $\beta = 10$.
+Unless otherwise mentioned, the following parameters are maintained for all panels: $c_i = 1$ (individual cost of cooperation), $r_i = 2$ (individual productivity), $\gamma_i = 0.1$ (individual cost of cooperation), $\lambda_i = 0.9$ (individual information about co-players' strategies).
+In panels a and b, the reward value $\rho$ is 0.3 while for the last panel, c, the reward value $\rho = 1$.}
+\label{Fig:SocialRewarding}
+\end{figure}
 \bibliographystyle{unsrt}
-\bibliography{bibtex.bib}
+\clearpage
+
+\newpage
+\bibliography{bibtex}
 \end{document}

### 2023-02-22 latex/article.tex
all figs done

@@
 \usepackage{amsmath,amsthm,amssymb,bbold, mathtools,setspace,enumitem,epsfig,titlesec,verbatim,color,array,multirow,comment,graphicx,hyperref,blkarray}
-%\usepackage[sort&compress]{natbib} % ProcB
-\usepackage[super,sort&compress,comma]{natbib} % NComms
+\usepackage[sort&compress]{natbib} % ProcB
+%\usepackage[super,sort&compress,comma]{natbib} % NComms
 \usepackage[bf,small]{caption}
@@
 Fixation probabilities for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived.
-Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013}.
+Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:Jmb:2022}.
 For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to \cite{Gokhale:DGAA:2014}.\\
@@
 Using Proposition \ref{Th:additive-games-stationary-dist}, one can derive the closed form expression for the stationary distribution of a $N-$player linear public goods game with two strategies.
-\newpage
 \begin{Prop}
@@
 \\ \\
-\noindent The average cooperation frequency of the group in the long run are shown in the $c-w$ and $N-w$ parameter planes in Fig \ref{}b.
-First, let us consider the case when the group size is fixed at 4 players (the $c-w$ plane in Fig\ref{}b).
+\noindent The average cooperation frequency of the group in the long run are shown in the $c-w$ and $N-w$ parameter planes in Fig \ref{Fig:GPGG-symmetric}b.
+First, let us consider the case when the group size is fixed at 4 players (the $c-w$ plane in Fig\ref{Fig:GPGG-symmetric}b).
 In that case if the cost of cooperation is too high, the average cooperation rate is negligible and does not change with the change in the nature of the public good.
@@
 In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run.
-When the public good is discounted ($w < 1$), cooperation rates fall with larger group sizes.
-\\
-
+When the public good is discounted ($w < 1$), cooperation rates fall with larger group sizes.\\
 \noindent 
-
+We also study the introspection dynamics in general public goods game with asymmetric players.
+We use the same setup that we used for studying the linear public goods with three asymmetric players.
+The average frequency of cooperation per player is summarized in Supplementary Figures 1 and 2.
+First, we study two cases, one in which the public good is synergized (and players have a high average cost) and two in which public good is discounted (and players have a lower average cost).
+In the first case, the player with the highest benefit cooperates only when they have a low cost of cooperation.
 \section*{Application: Introspection learning in a game with cooperation and rewards}
@@
 \end{align} \\ 
-\noindent Therefore, the stationary distribution sums up to 1. The candidate distribution we propose for the additive game is the unique stationary distribution of the process.
+\noindent Therefore, the stationary distribution sums up to 1. The candidate distribution we propose for the additive game is the unique stationary distribution of the process.\\
 \end{proof}
@@
 \end{align}
-When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also a probability distribution.
+When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also a probability distribution.\\
 \end{proof}
@@
 (\ref{Eq:stationary-dist-symm-2-stgs-state}) is the unique stationary distribution of the symmetric $N$-player game with two strategies.
+\\
 \end{proof}
@@
 \caption{\onehalfspacing
-\textbf{Symmetric linear public goods game.}
-We use the following parameters for all the panels in this figure: $N = 4$ (group size), $b = 2$ (benefit provided to the public good on cooperation), $c = 1$ (cost of cooperation) a) Here we show the frequency of each state in the stationary distribution of introspection dynamics.
-As players are identical here, each state can be defined by the number of cooperators.
+\textbf{Introspection dynamics in a symmetric linear public goods game.}
+The stationary distribution of the introspection dynamics for a linear public goods game with all identical players is shown in this figure.
+For all the panels in this figure, we use the following parameters: $N = 4$ (group size), $b = 2$ (benefit provided to the public good upon cooperation), $c = 1$ (cost of cooperation) a) Here we show the frequency of each state in the stationary distribution of introspection dynamics.
+As players are identical, each state can be defined by the number of cooperators.
 We use a selection strength of $\beta = 5$ for the introspection dynamics.
-For this strength of selection, states with more cooperators are less likely than states with less cooperators in the stationary distribution b) The frequency of each state for varying selection strength, $\beta$.
+For this strength of selection, states with more cooperators are less likely than states with less cooperators in the stationary distribution b) Here we show the frequency of each state for varying selection strength, $\beta$.
 We use the same color code as the previous panel.
 Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators.
-Indeed, up to $\beta \approx 3$, state $0$ is not the most frequent state in the long run c) Average cooperation frequency for varying dilemma strength depends on the selection strength $\beta$ and the parameters of the linear public goods game: $b,c, N$.
+Indeed, up to $\beta \approx 3$, state $0$ is not the most frequent state in the long run.
+c) Average cooperation frequency for varying dilemma strength depends on the selection strength, $\beta$, and the parameters of the linear public goods game: $b,c, N$.
 We use the marginal gain of choosing cooperation over defection, $b/N - c$, as a measure of the dilemma strength.
 When this quantity is negative and low, we say that the dilemma is strong.
-In this case, there is no individual advantage to cooperate.
+In this case, chosing cooperation is strictly disadvantageous.
 When this quantity is positive and high, we say that the dilemma is weak.
 In this case, cooperation dominates defection.
-Typically, a linear public goods dilemma is defined to have a negative marginal gain (see conditions above).
+Typically, a linear public goods dilemma is defined to have a negative marginal gain.
 Here, we show the dilemma strength varying from $-2$ to $2$.
@@
 For high $\beta$, stationary distribution of the introspection dynamics reflects the rational play.
-In the long run player play the Nash equilibrium.
+In the long-run player play the Nash equilibrium.
 When marginal gain is negative, defection is played with almost certainty (and \emph{vice-versa}).
@@
 \caption{\onehalfspacing
-\textbf{Asymmetric linear public goods game.} In the upper panels (a and b) we show the cost of cooperation and the benefit of provided due to cooperation for the three players on the left and the average cooperation frequency on the right.
+\textbf{Introspection dynamics in an asymmetric linear public goods game.} Three asymmetric players learn to play the linear public goods game through introspection dynamics.
+The cooperation probabilities in the stationary distribution are displayed here.
+For each of the upper panels (a and b), we show the cost of cooperation and the benefit provided upon cooperation for the players on the left and the average cooperation frequency in the long-run on the right.
 In this example, the cost of cooperation for players 1, 2 and 3 are $1 + \delta_c, 1$ and $1 - \delta_c$ respectively.
@@
 The cost and benefit for the reference player (player 2) are shown with black dashed lines in the left panels of a and b.
-In a) player 1 and 3 differ by 0.5 units in their cost of cooperation from the reference player.
+In panel a, player 1 and 3 differ by 0.5 units in their cost of cooperation from the reference player.
 All the players provide the same benefit when they contribute (i.e., $\delta_b = 0$).
-Conversely, in b) benefit by player 1 and 3 differ from the reference player by 1 unit.
+Conversely, in panel b, benefit by player 1 and 3 differ from the reference player by 1 unit.
 The cost of cooperation is the same for all players ($c = 1$).
-In c), we vary the asymmetry strengths $\delta_c $ and $\delta_b$ simultaneously and show both average individual cooperation frequency and the overall average cooperation frequency in the long-run.
-The reference player's cost and benefit are 1 and 2 units respectively.
+In c), we vary the asymmetry strengths between the players, $\delta_c $ and $\delta_b$, simultaneously and show both average individual cooperation frequency and the overall average cooperation frequency in the long-run.
+The reference player's cost and benefit are again 1 and 2 units respectively.
 The area within the white dashed lines represents the parameter values for which the marginal gain of choosing cooperation over defection is negative, for each single player and, in the right-most panel, for all players simultaneously.
+In this example, with this specific asymmetrical players, cooperation is only feasible in the long run if the asymmetries of players are aligned.
+That is, overall cooperation is high only when the individual with a low cost of cooperation has a high benefit value.
 For panels a and b we use a selection strength of $\beta = 2$ while for panel c, we use a selection strength of $\beta = 5$.
@@
 \centering
-\includegraphics[width =  0.65\textwidth, keepaspectratio]{figures/figure3}~\\[0.4cm]
+\includegraphics[width =  0.65\textwidth, keepaspectratio]{figures/figure3.eps}~\\[0.4cm]
 \caption{\onehalfspacing
-\textbf{Symmetric general public goods game}.
+\textbf{Introspection dynamics in a symmetric general public goods game}.
 We study introspection dynamics in the general public goods game with 4 symmetric players, each having two possible actions - cooperation and defection.
@@
 Cooperation is feasible when costs are not restrictively high and the public good is not too discounted.
-c) Average cooperation frequency for varying discount/synergy factor, $w$, and group size $N$.
-For this plot,the cost of cooperation for each player is $c = 0.4$.
+c) Here we show the average cooperation frequency for varying discount/synergy factor, $w$, and group size $N$.
+For this plot, the cost of cooperation for each player is $c = 0.4$.
 The feasibility of cooperation drops with larger group sizes when the public good is discounted.
 For all panels, the benefit of cooperation generated by each player is worth 2 units.
-The selection strength of the process is $\beta = 5$ for all panels.}
+The selection strength of the introspection dynamics is $\beta = 5$ for all panels.}
 \label{Fig:GPGG-symmetric}
@@
 \caption{\onehalfspacing
-\textbf{Cooperation and social rewarding in the stationary distribution of introspection dynamics in the linear public goods game with peer rewarding} Here we study a game with three asymmetric players, each having 16 possible strategies.
+\textbf{Intropection dynamics in a game with linear public goods game with peer rewarding.} Here we study a game with three asymmetric players, each having 16 possible strategies.
 Players cooperate in a linear public goods and then reward each other in the next stage after everyone's contribution is revealed.
-Players can condition their cooperation on the information they have about their co-players' rewarding strategies.
-For a full description of the model, please see the section on rewarding above.
+In the first stage, players can condition their cooperation on the information they have about their co-players' rewarding strategies.
+For a full description of the model, please see the section on rewarding.
 In this example, players 1 and 2 are identical in all aspects while player 3 is asymmetric to them in only a single aspect.
@@
 c) Finally, we consider the case where player 3 has less information about co-players' rewarding strategies than their peers, that is, $0.1 = \lambda_3 < \lambda_1 = 0.9$.
-For all plots, we consider the selection strength of players are high, $\beta = 10$.
-Unless otherwise mentioned, the following parameters are maintained for all panels: $c_i = 1$ (individual cost of cooperation), $r_i = 2$ (individual productivity), $\gamma_i = 0.1$ (individual cost of cooperation), $\lambda_i = 0.9$ (individual information about co-players' strategies).
+For all plots, we consider a high value for the selection strenght, $\beta = 10$.
+Unless otherwise mentioned, the following parameters are maintained for all panels: $c_i = 1$ (individual cost of cooperation), $r_i = 2$ (individual productivity), $\gamma_i = 0.1$ (individual cost of rewarding), $\lambda_i = 0.9$ (individual information about co-players' strategies).
 In panels a and b, the reward value $\rho$ is 0.3 while for the last panel, c, the reward value $\rho = 1$.}

### 2023-02-22 latex/supp.tex
all figs done

@@
 \onehalfspacing
-\section*{Supplementary Figures}
+\section*{Supplementary Figures: Asymmetric general public goods game}
+
 \begin{figure}[h!]
 \centering
-\includegraphics[width =  \textwidth]{figures/figure1.eps}~\\[0.4cm]
+\includegraphics[width =  \textwidth]{figures/Supfigure1.eps}~\\[0.4cm]
 \caption{\onehalfspacing
-\textbf{Symmetric linear public goods game.}
-a) Frequency of each state in the stationary distribution of introspection dynamics.
-As players are indistinguishable here, each state can be fully defined by the number of cooperators.
-Parameters: $N = 4$, $b = 2$, $c = 1$ and $\beta = 5$.
-b) For the same game parameters ($N = 4$, $b = 2$ and $c = 1$), we now show the frequency of each state (same color code as in panel a) for varying selection strength $\beta$.
-Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators.
-Indeed, up to $\beta \approx 3$, state $0$ is not even the most frequent.
-c) Average cooperation frequency for varying dilemma strength.
-We use as a measure of the dilemma strength the marginal gain by choosing to cooperate over choosing to defect, $b/N - c$.
-When this quantity is low, we say there is a ``strong dilemma”, where there is no individual advantage to cooperate, whereas when the marginal gain is high, we say there is a ``weak dilemma” (or no dilemma), where to cooperate becomes advantageous.
-Typically, a linear public goods dilemma is defined as having a negative marginal gain (see conditions above).
-Here, we show the whole parameter range for completeness and a full grasp of this game.
-We also show the result for different values of selection strength, $\beta = 1, 5$ and $100$.
-For high $\beta$, we confirm the classical prediction that, assuming a negative marginal gain, defection is dominant.
-For low $\beta$, however, we see again that some cooperation is possible.
+\textbf{Introspection dynamics in general public goods game with asymmetric players.
+We show stationary properties of the dynamics in a game with particular values of synergy/discount parameter and reference cost.} For a detailed description of the game, please see the section on general public goods game the main text.
+The setup is the same as Figure 3 of main text.
+There are three players with asymmetric costs and benefits.
+The respective costs for player 1, 2 and 3 are $c + \delta_c, c$, and $c - \delta_c$ respectively.
+The respective benefits they provide upon cooperation are $b + \delta_b, b$ and $b - \delta_b$ respectively.
+The parameters $c$ and $b$ respectively are the cost and benefits of the reference player (player 2).
+In here, we look at the cooperation probability for each player (and also overall cooperation) in stationary distribution of the introspection process.
+Players use a selection strength of $\beta = 5$.
+In the top row, we i) set the public good to be synergistic $w = 1.5$ and ii) allow a high reference cost, $c = 1$.
+In the bottom row, we i) set the public good to be discounted $w = 0.5$ and ii) allow a low reference cost $c = 0.2$.
 }
-\label{Fig:LPGG-symmetric}
+
+\label{Fig:Supp-Fig1}
 \end{figure}
@@
 \centering
-\includegraphics[width =  \textwidth]{figures/figure2.eps}~\\[0.4cm]
+\includegraphics[width =  \textwidth]{figures/Supfigure2.eps}~\\[0.4cm]
 \caption{\onehalfspacing
-\textbf{Asymmetric linear public goods game.} In the upper panels a) and b), we show the parameter values of the cost and benefit on the left and the average cooperation frequency on the right, of each player.
-Parameters: $N=3$, $\bar{c} = 1$, $\bar{b} = 2$, $\beta = 2$, where $\bar{c}$ and $\bar{b}$ are the mean values and are represented by black, dashed lines.
-In a) the cost varies among the 3 players by $\delta_c = 0.5$, such that players have costs of $\bar{c} + \delta_c $, $\bar{c}$, and $\bar{c} - \delta_c$ (in this case, $1.5$, $1$, and $0.5$), while the benefit is the same.
-Conversely, in b) the benefit varies among the 3 players, by $\delta_b = 1$, such that players have benefits of $\bar{b} + \delta_b $, $\bar{b}$, and $\bar{b} - \delta_b$ (in this case, $3$, $2$, and $1$), while the cost is the same.
-In c), we vary the asymmetry strengths $\delta_c $ and $\delta_b$ at the same time and show both each player’s average cooperation frequency and the overall average cooperation frequency.
-The area within the white dashed lines represents the parameter range for which the marginal gain by cooperating is negative, for each single player and, in the right-most panel, for all players.
-Parameters: $N=3$, $\bar{c} = 1$, $\bar{b} = 2$, $\beta = 5$.
+\textbf{Introspection dynamics in general public goods game with asymmetric players.
+We show stationary properties of the dynamics in a game with fixed asymmetry strengths.} For a detailed description of the game, please see the section on general public goods game in the main text.
+The setup is the same as Supplementary Figure \ref{Fig:Supp-Fig1}.
+In here, we show the cooperation probability of each player (and also the overall cooperation) in the stationary distribution of the introspection process versus the reference cost $c$ (cost of player 2) and tthe synergy/discount factor of the public good, $w$.
+For each row, the strength of asymmetry between the players is fixed.
+In the top row, the players do not differ in their benefits (they all have a benefit of value 2) but player 1 and player 3 have their cost of cooperation 0.5 units higher and lower respectively than player 2 (cost of cooperation for player 2 is varied in the y-axis).
+In the bottom row, all the players have the same cost of cooperation, $c$ (which is varied in the y-axis).
+In this case, player 1, 2 and 3 generate asymmetric benefits.
+Player 1,2 and 3 generate, 3, 2 and 1 units of benefits.
 }
-\label{Fig:LPGG-asymmetric}
+\label{Fig:Supp-Fig2}
 \end{figure}

### 2023-02-23 latex/article.tex
changes before sending to CH

@@
 
-The simplest form of social interaction occurs between two nearly similar individuals. This scenario can be stylized in a pairwise symmetric game. 
-More complex behavior emerges when instead we consider multiple interacting individuals, and they may differ significantly among themselves.
+%-----SP ABSTRACT-----%
+Social interactions are often modelled using simultaneous games.
+The simplest model involves two identical players.
+However, interactions in everyday life are complex and often involve more than two individuals that differ between themselves.
+Such interactions can be captured more realistically using asymmetric multiplayer games.
+Over the years, learning models and models from evolutionary game theory have studied how players may learn to play strategically in these games.
+Recently, introspection dynamics has proven to be a useful learning model for tackling complex games.
+In this dynamics, players compare their current strategy to an alternate strategy.
+If the update results in a payoff advantage, it is more likely adopted.
+This dynamics provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (the stationary distribution).
+In this paper, we extend some of the previous analytical results of introspection dynamics on games with two-players to games with more players.
+We obtain analytical expressions of the stationary distribution for multiplayer games that have the special property of being additive in the payoffs.
+In such games, the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions that their co-players play.
+In addition, we derive the stationary distribution for symmetric multiplayer games with two strategies.
+We discuss several classical games like the general public goods game to illustrate our results.
+
+%------MC ABSTRACT------%
+%The simplest form of social interaction occurs between two nearly similar individuals. This scenario can be stylized in a pairwise symmetric game. 
+%More complex behavior emerges when instead we consider multiple interacting individuals, and they may differ significantly among themselves.
 This case can be captured by a multiplayer asymmetric game.
 The complexity of these games increases both with the number and diversity of players.
-From evolutionary dynamics to learning models, game theoretic frameworks have been widely used to study strategic behavior. 
-Introspection dynamics has proven to be a useful learning model for tackling complex games. 
-It provides a simple way to compute the average abundance of each combination of strategies (or actions), that is, the stationary distribution of strategies.
-Here, our aim is to analyse multiplayer and (a)symmetric games.
-We extend previous analytical results on pairwise games under introspection dynamics to multiplayer games. 
-For general games, we obtain the analytical stationary distribution for 2 strategies, symmetric games.
-Moreover, we consider a particular class of games -- additive games. 
-In additive games, for any player, the difference between the payoffs provided by any two actions is constant, regardless of the co-players' actions. 
-For these games, we derive the stationary distribution analytically, for any number of players and strategies, with no restriction to symmetric games. 
-To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas. 
-In general, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
+%From evolutionary dynamics to learning models, game theoretic frameworks have been widely used to study strategic behavior. 
+%Introspection dynamics has proven to be a useful learning model for tackling complex games. 
+%It provides a simple way to compute the average abundance of each combination of strategies (or actions), that is, the stationary distribution of strategies.
+%Here, our aim is to analyse multiplayer and (a)symmetric games.
+%We extend previous analytical results on pairwise games under introspection dynamics to multiplayer games. 
+%For general games, we obtain the analytical stationary distribution for 2 strategies, symmetric games.
+%Moreover, we consider a particular class of games -- additive games. 
+%In additive games, for any player, the difference between the payoffs provided by any two actions is constant, regardless of the co-players' actions. 
+%For these games, we derive the stationary distribution analytically, for any number of players and strategies, with no restriction to symmetric games. 
+%To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas. 
+%In general, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
 % 244 words
@@
 An ubiquitous example of a model game for two players is the prisoner's dilemma.
-There, the two individuals have a temptation to cheat on each other, while both would be better off by offering mutual help.
-Solving this apparent paradox has been the focus of many studies, where various explanations were proposed \cite{Nowak:Science:2006}.
+Here, the two individuals have a temptation to cheat, but at the same time, players are better off if they help each other.
+Solving this paradox has been the focus of many studies.
+These studies provide several explanations for why one can expect cooperation in such interactions \cite{Nowak:Science:2006}.
 %some references
@@
 Therefore, an additional (second-order) dilemma is at stake: deterring defection is beneficial for all, but an individual that does not pay the associated cost has an advantage over the ones that do.
-As such, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms or a suitable design \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.
+As long as cooperation is incentivized by punishment (or rewards) of others, individuals can take advantage by defecting in this second-order dilemma.
+However, this tempts everyone to not pay the costs of punishment (or rewards).
+Cooperation can break down when everyone refuses to provide the incentives.
+For this reason, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms or a suitable design \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.
 \\ \\
@@
 % size
-Another interesting effect that multiplayer games allow exploring is that of the scale or size of the interaction itself.
-In situations that require some sort of coordination and where expectations on others play an important role in one's decisions (like in stag-hunt games), a growing group size might hinder the optimal outcome \cite{Skyrms:book:2003}.
+Another interesting effect that can be explored with multiplayer games is the scale or size of the interaction itself.
+In situations that require some sort of coordination and where expectations on others play an important role in one's decisions, a growing group size might hinder the optimal outcome \cite{Skyrms:book:2003}.
 Likewise, it has been shown that it is hard to cooperate in large groups for some conditions \cite{Santos:PNAS:2011, Hilbe:JTB:2015}.
@@
 It can happen that adding more players actually promotes cooperation.
-Gokhale et al.
-\cite{gokhale:JTB:2011} investigate the 2-player and 3-player cases of a task allocation problem.
+In \cite{gokhale:JTB:2011}, authors investigate the 2-player and 3-player cases of a task allocation problem.
 Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, resulting in a decrease in freeloading.
@@
 Conversely, in asymmetric games, players can be different in several ways.
-We say they are of different types or roles, which can differ in payoffs and strategies.
+For example, player can have different types or roles, which can have consequences in the payoffs and strategies.
 Therefore, they can have uneven effects on others' payoffs too.
@@
 %meta communication; lit gap; our aim
-\noindent From this, we see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
+\noindent Dur to these reasons one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
 Perhaps for that reason, there are not many studies on a general approach to multiplayer asymmetric games.
 As such, our aim here is to narrow that gap using introspection dynamics \cite{Couto:NJP:2022}.
-In the following section, we discuss several canonical frameworks from the literature that have been used to study both multiplayer and asymmetric games.%, pointing out the gaps.
+In the following section, we discuss several canonical frameworks from the literature that have been used to study both multiplayer games and asymmetric games.%, pointing out the gaps.
 
@@
 In the more classical infinite population models (deterministic EGT), ordinary differential equations are the central mathematical tools \cite{Hofbauer:book:1998}.
-One of the most famous of these dynamics is the replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998}.
+Among these the replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998} is the most popular model.
 Replicator equation has been widely used and easily comprises multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Pena:Evolution:2011, Cressman:PNAS:2014, Pena:JTB:2014}.
@@
 % stochastic EGT
-\noindent To account for stochastic effects naturally present in finite populations, another set of tools was developed, known as stochastic evolutionary game dynamics.
+\noindent To account for stochastic effects that are naturally present in finite populations, another set of tools was developed, known as stochastic evolutionary game dynamics.
 \cite{Nowak:Nature:2004, Traulsen:bookchapter:2009}.
 Besides the finiteness of population sizes, it also considers random mutations.
-Here, the quantities of interest are fixation probabilities and fixation times (i.e., the probability and the average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{Fudenberg:TPB:2006}, or average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}.
+Here, the quantities of interest are fixation probabilities and fixation times (i.e., the probability and the average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{Fudenberg:TPB:2006}, or the average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}.
 \\ \\
@@
 Fixation probabilities for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived.
-Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:Jmb:2022}.
+Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:JMB:2022}.
 For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to \cite{Gokhale:DGAA:2014}.\\
@@
 This feature comes from the fact that players update their strategies by exploring their own set of strategies in the following simple way: each time, after a round of the game, a player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, it is more likely adopted on the next round.
+We discuss the model formally in the next section.
 While in Couto et al.
@@
 
-\section*{Model}
+\section*{Model of introspection dynamics in multiplayer games}
 We consider a normal form game with $N$ players where $N > 2$.
@@
 That is, $\bbf \in \mathrm{Neb}(\abf) \implies \abf \in \mathrm{Neb}(\bbf)$.
-Two states that belong in each other's neighbourhood set only differ in exactly a single player's action (and, we call this player as the index of difference between the neighbouring states),
+Two states that belong in each other's neighbourhood set only differ in exactly a single player's action (and, we call this player as the index of difference between the neighbouring states).
 
@@
 A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
-Since no state is isolated (i.e., every state belongs in the neighbourhood set of another state) and there are only finitely many states of the game, every state is reachable in a finite number of steps from a starting point with non-zero probability.
-The transition matrix $\T$ is therefore primitive for a finite $\beta$.
-By the Perron-Frobenius theorem, a primite matrix, $\T$ will have a unique and strictly positive stationary distribution $\ubf := (\ubf_\abf)_{\abf \in \A}$ which satisfies the conditions:
+Since no state is isolated (i.e., every state belongs in the neighbourhood set of another state) and there are only finitely many states of the game, every state is reachable in a finite number of steps from any starting point with non-zero probability.
+The transition matrix, $\T$, is therefore primitive for a finite $\beta$.
+By the Perron-Frobenius theorem, a primitive matrix, $\T$ will have a unique and strictly positive stationary distribution $\ubf := (\ubf_\abf)_{\abf \in \A}$ which satisfies the conditions:
 \begin{eqnarray}
@@
 Next we consider the case where the cost of cooperation is fixed (the $N-w$ plane in Fig.
-\ref{}b).
+\ref{Fig:GPGG-symmetric}b).
 It is fixed to a value such that in a synergistic PG ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size.
 In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run.
-When the public good is discounted ($w < 1$), cooperation rates fall with larger group sizes.\\
+When the public good is discounted ($w < 1$), cooperation rates fall with larger group sizes.\\ \\
 \noindent 
@@
 First, we study two cases, one in which the public good is synergized (and players have a high average cost) and two in which public good is discounted (and players have a lower average cost).
-In the first case, the player with the highest benefit cooperates only when they have a low cost of cooperation.
+In both of these cases, players cooperate highly when they simultaneously have low cost and high benefit.
+The only noticebale difference between the two cases is the minimum relationship between the asymmetries $\delta_b$ and $\delta_c$ that results in high cooperation for the player with low cost and high benefit.
+When we observe individual cooperation frequency versus the synergy/discount factor, $w$ (Supplementary Figure 2), we find that when players are symmetric with respect to just benefits (or just costs), the one with the lowest cost (or highest benefit) cooperates with a high probability across all types of public goods, even for a high value of average cost.
+
 \section*{Application: Introspection learning in a game with cooperation and rewards}
@@
 
-%ACKNOWLEDGEMENTS: CH, DSBRG, ERC
-
-%Rev: broom, archetti, pena, schmidt, mcavoy, wu
-
+\section*{Acknowledgements}
+This work was supported by the European Research Council Starting Grant 850529 (E-DIRECT) and by the Max Planck Society.
+We would like to thank Christian Hilbe and the members of the Research Group Dynamics of Social Behavior for valuable feedback.
+\newpage
 \section*{Appendix: Proofs}
@@
 &\T_{\abf,\abf} \ubf_\abf  + \sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf}\\
-&= \left( 1 - \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} \cdot \ubf_{\abf} \right) + \sum_{\bbf \in \mathrm{Neb}(\abf)}  \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{\bbf_{\mathrm{I}_\bbf} \to \abf_{\mathrm{I}_\bbf}} \cdot \ubf_{\bbf}\\ \notag \\
+&= \left( 1 - \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} \right) \ubf_{\abf}+ \frac{1}{}\sum_{\bbf \in \mathrm{Neb}(\abf)}  \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{\bbf_{\mathrm{I}_\bbf} \to \abf_{\mathrm{I}_\bbf}} \cdot \ubf_{\bbf}\\ \notag \\
 \label{eq:important-step}
@@
 %&= 1
-\noindent \\ \\ where $\qbf_{-1}, \qbf_{-2},...,\qbf_{-N}$ are fixed tuples from $\A_{-1}, \A_{-2},...,\A_{-N}$ respectively.
+\noindent \\ \\ where $\qbf_{-1}, \qbf_{-2},...,\qbf_{-N}$ are any arbitrary tuples from $\A_{-1}, \A_{-2},...,\A_{-N}$ respectively.
 The denominator in the above expression can be taken out completely from the first sum.
@@
 \textbf{Proof of Proposition} \ref{Th:additive-game-product-of-marginals} \\ \\ 
-Just like the previous proof, we will denote $\pbf_{-1}, \pbf_{-2},...,\pbf_{-N} $ as fixed tuples from $\A_{-1}, \A_{-2},...,\A_{-N}$ respectively.
+Just like the previous proof, $\pbf_{-1}, \pbf_{-2},...,\pbf_{-N} $ are arbitrary tuples from $\A_{-1}, \A_{-2},...,\A_{-N}$ respectively.
 In the steps below, we always decompose the expression $f_j(a,b)$ to $\pi_j(a,\pbf_{-j}) - \pi_j(b,\pbf_{-j})$.
@@
 We use this expression to calculate the marginal distribution of actions played at a particular state $\abf$, $(\xi_{j:\abf_j})_{j \in \{1,2,...,N\}}$.
-\newpage
 \begin{align}
@@
 \end{align}
-For this process, the first term in the right hand side of Eq. (\ref{Eq:transition-in-proof}) can be simplified as: 
+For this process, since there are only two actions, the first term in the right hand side of Eq. (\ref{Eq:transition-in-proof}) can be simplified as: 
 \begin{align}
@@
 We continue the simplification of Eq.
-(\ref{Eq:step-product-broken})in the later steps by introducing terms that cancel each other.
+(\ref{Eq:step-product-broken}) in the next steps by introducing terms that cancel each other.
 \\[10pt]
@@
 (\ref{Eq:new-cancelable-term-introduced}) can be taken inside the product.
-Note that this term is 0 if the $k^{th}$ player plays $\D$ in the state $\abf$.
+Note that this term is 1 if the $k^{th}$ player plays $\D$ in the state $\abf$.
 When this term is taken inside the product bracket, products of exponent $e^{-\beta f(j-1)}$ can be performed for $j$ ranging from $1$ to the number of cooperators in state $\abf$, $\mathcal{C}(\abf)$.
@@
 \newpage
-\bibliography{bibtex}
+\bibliography{bibtex.bib}
 \end{document}

### 2023-02-27 latex/article.tex

@@
 Recently, introspection dynamics has proven to be a useful learning model for tackling complex games.
-In this dynamics, players compare their current strategy to an alternate strategy.
+In this dynamics, players compare their current strategy to an alternative strategy.
 If the update results in a payoff advantage, it is more likely adopted.
@@
 In this paper, we extend some of the previous analytical results of introspection dynamics on games with two-players to games with more players.
-We obtain analytical expressions of the stationary distribution for multiplayer games that have the special property of being additive in the payoffs.
+We obtain analytical expressions of the stationary distribution for multiplayer asymmetric games that have the special property of being additive in the payoffs.
 In such games, the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions that their co-players play.
@@
 As long as cooperation is incentivized by punishment (or rewards) of others, individuals can take advantage by defecting in this second-order dilemma.
-However, this tempts everyone to not pay the costs of punishment (or rewards).
-Cooperation can break down when everyone refuses to provide the incentives.
+However, this tempts everyone to not engage in costly punishment (or rewarding).
+Cooperation can break down when there are not enough individuals punishing (or giving rewards).
 For this reason, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms or a suitable design \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.
@@
 Conversely, in asymmetric games, players can be different in several ways.
-For example, player can have different types or roles, which can have consequences in the payoffs and strategies.
+For example, players can have different types or roles, which can have consequences in the payoffs and strategies.
 Therefore, they can have uneven effects on others' payoffs too.
@@
 %meta communication; lit gap; our aim
-\noindent Dur to these reasons one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
+\noindent Due to these reasons, one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
 Perhaps for that reason, there are not many studies on a general approach to multiplayer asymmetric games.
@@
 To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas, extending the framework in \cite{Hauert:JTB:2006a} to asymmetric games.
-Finally, we also study the asymmetric version of a public good game with a rewarding stage \cite{Pal:NatCom:2022}.
+Finally, we also study the asymmetric version of a public goods game with a rewarding stage \cite{Pal:NatCom:2022}.
 
 \section*{Model of introspection dynamics in multiplayer games}
-We consider a normal form game with $N$ players where $N > 2$.
+We consider a normal form game with $N$ players where $N \geq 2$.
 In the game, a player, say player $i$, can play actions from their action set, $\A_i := \{a_{i,1}, a_{i,2}, ..., a_{i,m_i} \}$.
 The action set of player $i$ has $m_i$ actions.
-In this model, we consider that players do not randomize their actions in a play (i.e., they only use pure strategies).
+In this model, players only use pure strategies.
 Therefore, there are only finitely many states of the game.
@@
 At $\beta = 0$, players update to a randomly chosen strategy with probablity $0.5$.
-For $\beta > 0$, players update to new strategy with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
-The probability that the chosen player does not update the action to a new action is then, \\
-\begin{equation}
- p_{a_{i,k} \to a_{i,k}} (\abf_{-i}) = 1 - \sum_{k \neq l} p_{a_{i,k} \to a_{i,l}} (\abf_{-i})
- \label{Eq:introspection-normalization}
-\end{equation}
-\\ 
-Introspection dynamics can be studied by analyzing properties of the transition matrix, $\T$ of the resulting dynamical process.
+For $\beta > 0$, players update to the alternate strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
+The probability that the chosen player does not update the action to a new action is then, \\ \\
+\noindent Introspection dynamics can be studied by analyzing properties of the transition matrix, $\T$ of the resulting dynamical process.
 The transition matrix element $\T_{\abf,\bbf}$ denotes the conditional probability that the game goes to the state $\bbf$ in the next round if it is in state $\abf$ in the current round.
@@
 
-\begin{definition}[Neighbourhood set of a state] The neighbourhood set of state $\abf$, $\mathrm{Neb}(\abf)$, is defined as the following:
-\begin{equation}
-\mathrm{Neb}(\abf) := \{\bbf \in \A \setminus \{ \abf \}  : (\exists j) [ \bbf_{-j} = \abf_{-j} \land  \bbf_{j} \neq \abf_{j}] \}
+\begin{definition}[Neighbourhood set of a state] The neighbourhood set of state $\abf$, $\mathrm{Neb}(\abf)$, is defined as:
+\begin{equation}
+\mathrm{Neb}(\abf) := \{\bbf \in \A  \big| \quad \exists j:  \bbf_{j} \neq \abf_{j} \land \bbf_{-j} = \abf_{-j}  \}
 \label{Eq:neighbourhood-states}
@@
 The state $(\C,\C,\C)$ is in the neighbourhood set of $(\C,\C,\D)$ whereas the state $(\C,\D,\D)$ is not in the neighbourhood set of $(\C,\C, \C)$.
-In our definition, states are not included in their own neighbourhood.
-In addition, if a state $\bbf$ belongs in the neighbourhood of state $\abf$, by definition state $\abf$ belongs in the neighbourhood of state $\bbf$.
-That is, $\bbf \in \mathrm{Neb}(\abf) \implies \abf \in \mathrm{Neb}(\bbf)$.
 Two states that belong in each other's neighbourhood set only differ in exactly a single player's action (and, we call this player as the index of difference between the neighbouring states).
@@
 \noindent In the previous example, the index of difference between the neighbouring states $(\C,\C,\C)$ and $(\C,\C,\D)$ is $3$.
-The third player's action is the difference between the two neighbouring states.
 Using the above definitions, one can formally define the transition matrix of the introspection dynamics with:
@@
 \label{Eq:lefteigenvector}
-\ubf \T = \ubf \\ 
+\ubf \T &= \ubf \\ 
 \label{Eq:normalizationcondition}
-\ubf \mathbf{1} = 1
+\ubf \mathbf{1} &= 1
 \end{eqnarray}
@@
 \end{proof}
-\noindent The above equations only present an explicit representation of the stationary distribution $\ubf$.
+\noindent The above equations only present an implicit representation of the stationary distribution $\ubf$.
 The stationary distribution can be explictly calculated by the following expression (which is derived using Eq.
@@
 \end{equation} \\
-where $\mathbf{U}$ is a square matrix of size same as $\T$ with all elements 1 and $\mathbb{1}$ is the identity matrix.
+where $\mathbf{U}$ is a square matrix of the same size as $\T$ with all elements equal to 1 and $\mathbb{1}$ is the identity matrix.
 For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distribution of the processes are unique.
@@
 For a proof, please see Appendix.
-This property of the additive game was aleady shown for the simple two-player, two-action donation game in Couto et al.
+This property of the additive game was already shown for the simple two-player, two-action donation game in Couto et al.
 \cite{Couto:NJP:2022}.
@@
 We denote the cost of cooperation for player $i$ and the benefit that they provide to the public good by $c_i$ and $b_i$ respectively.
-We define a mapping function $\alpha(.)$ to map the action of cooperation to 1 and the action of defection to 0.
+We define an indicator function $\alpha(.)$ to map the action of cooperation to 1 and the action of defection to 0.
 That is $\alpha(\C) = 1$ and $\alpha(\D) = 0$.
@@
 \end{Prop}
-\noindent This result directly follows from Proposition \ref{Th:additive-games-stationary-dist}.
-For an independent proof, please see Appendix.
+\noindent For a proof, please see Appendix.
 We use a simple example to demonstrate the above result.
@@
 We denote the payoff of a $\C$ and $\D$ player in a state where there are $j$ co-players playing $\C$ by $\pi_\C(j)$ and $\pi_\D(j)$ respectively.
-From the previous section, we adopt the mapping function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to 0, and the notation $\mathcal{C}(\abf)$ to denote the number of cooperators in the state $\abf$.
+From the previous section, we adopt the indicator function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to 0, and the notation $\mathcal{C}(\abf)$ to denote the number of cooperators in the state $\abf$.
 That is,
@@
 \label{Eq:stationary-dist-normalization-symm-2-stgs-state}
-\Gamma = \displaystyle \sum_{\forall \abf' \in \mathcal{A}^N} \prod_{j = 1}^{\mathcal{C}(\abf')} \displaystyle e^{-\beta f(j-1)}
+\Gamma = \displaystyle \sum_{\abf' \in \mathcal{A}^N} \prod_{j = 1}^{\mathcal{C}(\abf')} \displaystyle e^{-\beta f(j-1)}
 \end{equation}
@@
 This count is simply the binomal coefficient $N \choose k$.
-For details, see the proof in the Appendix.
-In this paper, we do not derive a closed form expression for the stationary distribution of introspection dynamics in asymmetric games with two actions.
-Instead, we compute it numerically using the explicit formula in Eq.
-(\ref{Eq:explicit-stationary-dist-representation}).
+For a proof, please see Appendix.
 In the next section, we study the stationary behaviour of the introspection dynamics in a two-action general game with an example.
@@
 \begin{align}
-\pi^{\D}_i(\D, \abf_{-i})&= \displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N \cdot \mathcal{C}(\D,\abf_{-i})} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\D,\abf_{-i}) - 1} \right)\\[15pt]
+\pi^{\D}_i(\D, \abf_{-i})&= 
+\begin{cases}
+\displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N \cdot \mathcal{C}(\D,\abf_{-i})} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\D,\abf_{-i}) - 1} \right) &\quad  \text{if } \mathcal{C}(\D,\abf_{-i}) \neq 0 \\[15pt]
+0 &\quad  \text{if } \mathcal{C}(\D,\abf_{-i}) = 0
+\end{cases} \\[15pt]
 \pi^{\C}_i(\C, \abf_{-i}) &= \displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N \cdot \mathcal{C}(\C,\abf_{-i})} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\C,\abf_{-i}) - 1} \right) - c_i
@@
 \end{align} \\
-\noindent where $\mathcal{C}(a,\abf_{-i})$ is the number of cooperators in the state $(a,\abf_{-i})$ and $\alpha(.)$ is the mapping function that maps the actions $\C$ and $\D$ to 1 and 0 respectively.
+\noindent where $\mathcal{C}(a,\abf_{-i})$ is the number of cooperators in the state $(a,\abf_{-i})$ and $\alpha(.)$ is the indicator function that maps the actions $\C$ and $\D$ to 1 and 0 respectively.
 Note that the number of cooperators in the two states are related as: $\mathcal{C}(\D,\abf_{-i}) = \mathcal{C}(\C,\abf_{-i}) - 1$.
@@
 When the PG is discounted ($w = 0.5$) but costs are low ($c = 0.2$), the coexistence behaviour similar to the snowdrift game appears from the replicator equation.
-When the PG is synergistic ($w = 1.5$) and costs are high ($c = 1$), both cooperation and defection are locally stable equilibria.
+When the PG is synergistic ($w = 1.5$) and costs are high ($c = 1$), both cooperation and defection are locally stable equilibria under the replicator dynamics.
 In addition, there is also an internal equilibrium which is unstable.
@@
 
-In all the examples that we have studied so far, players can only play can only choose between two actions (pure strategies).
-Introspection dynamics is particularly useful when players have larger strategy sets available to them.
+In all the examples that we have studied so far, players can only choose between two actions (pure strategies).
+Introspection dynamics is particularly useful when players can use larger strategy sets.
 In this section, we study the stationary behaviour of players in a game where each player has 16 possible actions (pure strategies).
-To this end, we adopt the multiplayer cooperation and rewarding game from Pal et al.
-\cite{Pal:NatCom:2022}.
+To this end, we adopt the multiplayer cooperation and rewarding game from Pal and Hilbe \cite{Pal:NatCom:2022}.
 In this game, there are two stages: in stage 1, players decide whether or not they contribute to a linear public good and in stage 2, they decide whether or not they reward their peers.
@@
 When the asymmetric player differs only in their productivity, a different effect may appear in the long run (Fig \ref{Fig:SocialRewarding}b).
-We choose a very specific set of parameters to display this effect.
-In this case, the less productive player free rides on the cooperation of their higher productive peers, but eventually reward the cooperation of their peers nonetheless.
+In this case, the less productive player free-rides on the cooperation of their higher productive peers, but eventually reward the cooperation of their peers nonetheless.
 The asymmetric player free-rides but does not second-order free ride.
@@
 \begin{align}
+\label{Eq:OG_prod-of-sum}
 \sum_{\abf \in \A} \ubf_\abf =& \left( \displaystyle \prod_{k=1}^N \left( e^{\beta \pi_k(a_{k,1}, \qbf_{-k})}+...
 + e^{\beta \pi_k(a_{k,m_k}, \qbf_{-k})} \right) \right)^{-1} \cdot \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})} \right) \\[10pt]
+\label{Eq:OG_sum-of-prod}
 =& \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}  \right)^{-1} \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}  \right) = 1
 \end{align} \\ 
-\noindent Therefore, the stationary distribution sums up to 1. The candidate distribution we propose for the additive game is the unique stationary distribution of the process.\\
+\noindent The step from Eq.
+(\ref{Eq:OG_prod-of-sum}) to Eq.
+(\ref{Eq:OG_sum-of-prod}) involves multiplying out all the sums of exponents (where each term in the sum of exponents corresponds to payoff that player $k$ receives by playing their actions against co-player composition, $\qbf_{-k}$).
+Therefore, the stationary distribution sums up to 1.
+The candidate distribution we propose for the additive game is the unique stationary distribution of the process.\\
 \end{proof}
@@
 \textbf{Proof of Proposition} \ref{Th:additive-game-product-of-marginals} \\ \\ 
-Just like the previous proof, $\pbf_{-1}, \pbf_{-2},...,\pbf_{-N} $ are arbitrary tuples from $\A_{-1}, \A_{-2},...,\A_{-N}$ respectively.
+Just like the previous proof, $\pbf_{-1}, \pbf_{-2},...,\pbf_{-N} $ are any arbitrary tuples from $\A_{-1}, \A_{-2},...,\A_{-N}$ respectively.
 In the steps below, we always decompose the expression $f_j(a,b)$ to $\pi_j(a,\pbf_{-j}) - \pi_j(b,\pbf_{-j})$.
@@
 \label{step-prod-sum}
-&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})}\cdot \left( \prod_{k\neq j} \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k(a',\pbf_{-k})}\right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k,\pbf_{-k})} \right) \\ \notag \\
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})}\cdot \left( \prod_{k\neq j} \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k(a',\pbf_{-k})}\right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k,\pbf_{-k})} \right)
+\end{align}
+\newpage
+\begin{align}
 \label{step-sum-prod}
-&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})}\cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi_k(\qbf_k,\pbf_{-k})} \right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k,\pbf_{-k})}  \right) \\ \notag \\
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})}\cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi_k(\qbf_k,\pbf_{-k})} \right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k,\pbf_{-k})}  \right)
+\end{align}
+\noindent The interchange of the sum and the product between the expressions in Eq.
+(\ref{step-prod-sum}) and Eq.
+(\ref{step-sum-prod}) can be carried out by observing that when all the sums are multiplied out, one is left with sums of terms, each of which is a exponential with power equal to sum of payoffs that co-players of $j$ (here $k$) receive when they play their respective strategies from $\qbf$ (that is $\qbf_k$) against co-players that play $\pbf_{-k}$.
+This is the similar to the step between Eq.
+(\ref{Eq:OG_prod-of-sum}) and Eq.
+(\ref{Eq:OG_sum-of-prod}) in the proof of Proposition 2.
+\begin{align}
 &= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \left( \pi_j(a',\pbf_{-j}) - \pi_j(\abf_j,\pbf_{-j})\right)} \right)^{-1}\\ \notag \\
@@
 \end{align} \\
-\noindent The interchange of the sum and the product between the expressions in Eq.
-(\ref{step-prod-sum}) and Eq.
-(\ref{step-sum-prod}) can be carried out by observing that when all the sums are multiplied out, one is left with sums of terms, each of which is a exponential with power equal to sum of payoffs that co-players of $j$ (here $k$) receive when they play their respective strategies from $\qbf$ (that is $\qbf_k$) against co-players that play $\pbf_{-k}$.
-Using the expression in Eq.
-(\ref{final-expression}), we can confirm that for additive games, the product of the marginals is the stationary distribution,
+\noindent Using the expression in Eq. (\ref{final-expression}), we can confirm that for additive games, the product of the marginals is the stationary distribution,  
 \begin{equation}
@@
 \end{align} \\
-In addition we introduce a mapping function $\alpha(.)$ which maps the action $\C$ to 1 and the action $\D$ to 0.
+In addition we introduce an indicator function $\alpha(.)$ which maps the action $\C$ to 1 and the action $\D$ to 0.
 That is $\alpha(\C) := 1$ and $\alpha(\D) := 0$.
@@
 \end{eqnarray} 
-and additionally, also using Eq. (\ref{Eq:stationary-dist-shortcut}) the second term can be simplified too:
+and additionally, using Eq. (\ref{Eq:stationary-dist-shortcut}) the second term can be simplified too:
 \begin{align}
@@
 Moreover, since $\beta$ is finite, by Proposition \ref{Prop:unique-stationary-dist}, the process will have a unique stationary distribution.
-To show that the candidate stationary distribution is the unique stationary distribution, we need to check if for this process, $\ubf \T= \ubf$.
+Again, to show that the candidate stationary distribution is the unique stationary distribution, we need to check if Eq.
+(\ref{Eq:lefteigenvector}) holds.
 That is, the condition in Eq.
@@
 \end{align}
-Between the steps, Eq.
-\ref{Eq:step-single-product} and \ref{Eq:step-product-broken}, we took out one term from the product that is present in our candidate distribution.
+From Eq.
+(\ref{Eq:step-single-product}) to Eq.
+(\ref{Eq:step-product-broken}), we took out one term from the product that is present in our candidate distribution.
 This term accounts for the $k^{th}$ players action in the neighbouring state $(\bar{\abf}_k, \abf_{-k})$ of $\abf$.
@@
 \caption{\onehalfspacing
-\textbf{Intropection dynamics in a game with linear public goods game with peer rewarding.} Here we study a game with three asymmetric players, each having 16 possible strategies.
+\textbf{Intropection dynamics in the linear public goods game with peer rewarding.} Here we study a game with three asymmetric players, each having 16 possible strategies.
 Players cooperate in a linear public goods and then reward each other in the next stage after everyone's contribution is revealed.

### 2023-02-28 latex/article.tex
all changes to bold font made. revising my sections now. also changed fig caption of fig 4

@@
 \times m_N$ states.
-We denote a state of the game by collecting the actions of all the players in the game in a vector, $\abf := (\abf_1, \abf_2, ..., \abf_N)$ where $\abf \in \A := \A_1 \times \A_2 \times ...
-\times \A_N$.
-We also use the notation, $\abf := (\abf_i, \abf_{-i})$ to denote the state from the perspective of player $i$.
-In the state $(\abf_i, \abf_{-i})$, player $i$ plays the action $\abf_i \in \A_i$ and their co-players play the action $\abf_{-i} \in \A_{-i}$ where $\A_{-i}$ is defined as $\A_{-i}:= \prod_{j \neq i} \A_j$.
+We denote a state of the game by collecting the actions of all the players in the game in a vector, $\abf := (a_1, a_2, ..., a_N)$ where $\abf \in \A := \A_1 \times \A_2 \times ...
+\times \A_N$ and $a_i \in \A_i$.
+We also use the notation, $\abf := (a_i, \abf_{-i})$ to denote the state from the perspective of player $i$.
+In the state $(a_i, \abf_{-i})$, player $i$ plays the action $a_i \in \A_i$ and their co-players play the action $\abf_{-i} \in \A_{-i}$ where $\A_{-i}$ is defined as $\A_{-i}:= \prod_{j \neq i} \A_j$.
 The payoff of a player depends on the state of the game.
-We denote the payoff of player $i$ in the state $\abf$ with $\pi_i(\abf)$ or $\pi_i(\abf_i, \abf_{-i})$.
+In this paper, we use bold font letters to denote vectors and matrices.
+We use the corresponding normal font letters with subscripts to denote elements of the vectors (or matrices).
+We denote the payoff of player $i$ in the state $\abf$ with $\pi_i(\abf)$ or $\pi_i(a_i, \abf_{-i})$.
 \\ \\
@@
 At $\beta = 0$, players update to a randomly chosen strategy with probablity $0.5$.
-For $\beta > 0$, players update to the alternate strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
+For $\beta > 0$, players update to the alternative strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
 The probability that the chosen player does not update the action to a new action is then, \\ \\
 \noindent Introspection dynamics can be studied by analyzing properties of the transition matrix, $\T$ of the resulting dynamical process.
-The transition matrix element $\T_{\abf,\bbf}$ denotes the conditional probability that the game goes to the state $\bbf$ in the next round if it is in state $\abf$ in the current round.
+The transition matrix element $\mathrm{T}_{\abf,\bbf}$ denotes the conditional probability that the game goes to the state $\bbf$ in the next round if it is in state $\abf$ in the current round.
 In order to formally define the transition matrix, we first need to introduce some notations and definitions.
@@
 \begin{equation}
-\mathrm{Neb}(\abf) := \{\bbf \in \A  \big| \quad \exists j:  \bbf_{j} \neq \abf_{j} \land \bbf_{-j} = \abf_{-j}  \}
+\mathrm{Neb}(\abf) := \{\bbf \in \A  \big| \quad \exists j:  b_{j} \neq a_{j} \land \bbf_{-j} = \abf_{-j}  \}
 \label{Eq:neighbourhood-states}
@@
 \noindent In other words, a state in $\mathrm{Neb}(\abf)$ is a state that has exactly one player playing a different action than in state $\abf$.
-Consider the game where there are  three players and each player has the identical action set $\{\C, \D \}$.
-The state $(\C,\C,\C)$ is in the neighbourhood set of $(\C,\C,\D)$ whereas the state $(\C,\D,\D)$ is not in the neighbourhood set of $(\C,\C, \C)$.
+For example, consider the game where there are  three players and each player has the identical action set $\{\C, \D \}$.
+The state $(\C,\C,\D)$ is in the neighbourhood set of $(\C,\C,\C)$ whereas the state $(\C,\D,\D)$ is not.
 Two states that belong in each other's neighbourhood set only differ in exactly a single player's action (and, we call this player as the index of difference between the neighbouring states).
@@
 \begin{equation}
-\abf_{\mathrm{I}(\abf, \bbf)} \neq \bbf_{\mathrm{I}(\abf, \bbf)}
+a_{\mathrm{I}(\abf, \bbf)} \neq b_{\mathrm{I}(\abf, \bbf)}
 \end{equation} 
@@
 \noindent In the previous example, the index of difference between the neighbouring states $(\C,\C,\C)$ and $(\C,\C,\D)$ is $3$.
-Using the above definitions, one can formally define the transition matrix of the introspection dynamics with:
-
-\begin{align}
-\T_{\abf, \bbf} = 
+Using the above definitions, one can formally define the transition matrix of introspection dynamics with:
+
+\begin{align}
+\mathrm{T}_{\abf, \bbf} = 
 \begin{cases}
-\frac{1}{N(m_j-1)}  \cdot p_{\abf_{j} \to \bbf_{j}} (\abf_{-j}) \quad  \quad &\text{ if }\bbf \in \mathrm{Neb}(\abf) \quad \text{and,} \quad j = \mathrm{I}(\abf,\bbf)\\ \\ 
+\frac{1}{N(m_j-1)}  \cdot p_{a_{j} \to b_{j}} (\abf_{-j}) \quad  \quad &\text{ if }\bbf \in \mathrm{Neb}(\abf) \quad \text{and,} \quad j = \mathrm{I}(\abf,\bbf)\\ \\ 
 0 \quad &\text{ if } \bbf \notin \mathrm{Neb}(\abf) \\ \\
-1 - \sum_{\cbf \neq \bbf} \T_{\abf,\cbf} \quad &\text{ if } \abf = \bbf
+1 - \sum_{\cbf \neq \bbf} \mathrm{T}_{\abf,\cbf} \quad &\text{ if } \abf = \bbf
 \end{cases}
@@
 \noindent The transition matrix is a row stochastic matrix (the sums of the rows are 1).
-This implies that the stationary distribution of $\T$: a left eigenvector of $\T$ corresponding to eigenvalue $1$, always exists.
-The following proposition introduces a sufficient condition for the stationary distribution of $\T$ to be unique.
-\begin{Prop} When $\beta$ is finite, the transition matrix of the introspection dynamics has a unique stationary distribution. 
-\label{Prop:unique-stationary-dist}
-\end{Prop}
-\begin{proof}
+This implies that the stationary distribution of $\T$, a left eigenvector of $\T$ corresponding to eigenvalue $1$, always exists.
+We introduce a sufficient condition for the stationary distribution of $\T$ to be unique.
+\\ \\
+\noindent When the selection strength, $\beta$ is finite, the transition matrix of introspection dynamics has a unique stationary distribution.
 A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
@@
 The transition matrix, $\T$, is therefore primitive for a finite $\beta$.
-By the Perron-Frobenius theorem, a primitive matrix, $\T$ will have a unique and strictly positive stationary distribution $\ubf := (\ubf_\abf)_{\abf \in \A}$ which satisfies the conditions:
+By the Perron-Frobenius theorem, a primitive matrix, $\T$ will have a unique and strictly positive stationary distribution $\ubf := (\mathrm{u}_\abf)_{\abf \in \A}$ which satisfies the conditions:
 \begin{eqnarray}
@@
 \noindent where $\mathbf{1}$ is the column vector with size same as $\ubf$ and has all elements as $1$.
-\end{proof}
+For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distribution of the processes are unique.
+\\ \\
+%\begin{Prop} When $\beta$ is finite, the transition matrix of the introspection dynamics has a unique stationary distribution. 
+%\label{Prop:unique-stationary-dist}
+%\end{Prop}
+%\begin{proof}
+%A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
+Since no state is isolated (i.e., every state belongs in the neighbourhood set of another state) and there are only finitely many states of the game, every state is reachable in a finite number of steps from any starting point with non-zero probability.
+The transition matrix, $\T$, is therefore primitive for a finite $\beta$.
+By the Perron-Frobenius theorem, a primitive matrix, $\T$ will have a unique and strictly positive stationary distribution $\ubf := (\mathrm{u}_\abf)_{\abf \in \A}$ which satisfies the conditions:
+%\begin{eqnarray}
+%\label{Eq:lefteigenvector}
+%\ubf \T &= \ubf \\ 
+%\label{Eq:normalizationcondition}
+%\ubf \mathbf{1} &= 1
+%\end{eqnarray}
+%\noindent where $\mathbf{1}$ is the column vector with size same as $\ubf$ and has all elements as $1$. 
+%\end{proof}
 \noindent The above equations only present an implicit representation of the stationary distribution $\ubf$.
 The stationary distribution can be explictly calculated by the following expression (which is derived using Eq.
-(\ref{Eq:lefteigenvector}) and (\ref{Eq:normalizationcondition}) as:
+(\ref{Eq:lefteigenvector}) and (\ref{Eq:normalizationcondition})) as:
 \begin{equation}
@@
 where $\mathbf{U}$ is a square matrix of the same size as $\T$ with all elements equal to 1 and $\mathbb{1}$ is the identity matrix.
-For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distribution of the processes are unique.
-\\
-
-\noindent The stationary distribution element $\ubf_\abf$ is the probability that state $\abf$ will be played by the players in the long run.
+The matrix $\mathbb{1} + \mathbf{U} - \T$ is invertible when $\T$ is a primitive matrix \cite{Couto:NJP:2022}.
+Using Eq.
+(\ref{Eq:explicit-stationary-dist-representation}) one can compute the stationary distribution of introspection dynamics for any normal form game (with arbitrary number of asymmetric players).\\
+
+\noindent The stationary distribution element $\mathrm{u}_\abf$ is the probability that state $\abf$ will be played by the players in the long run.
 Using the stationary distribution, one can calculate the marginal probabilities corresponding to each player's actions.
-For example, the probability that player $i$ plays action $a_{i,k}$ in the long run, $\xi_{i:a_{i,k}}$, can be computed as,
-\begin{equation}
-\mathbf{\xi}_{i:a_{i,k}} := \sum_{\qbf \in \A_{-i}} \ubf_{(a_{i,k}, \qbf)}
+For example, the probability that player $i$ plays action $a \in \A_i$ in the long run, $\xi_{i,a}$, can be computed as,
+\begin{equation}
+\mathbf{\xi}_{i,a} := \sum_{\qbf \in \A_{-i}} \mathrm{u}_{(a, \qbf)}
 \label{Eq:marginal-definition}
 \end{equation}
-\noindent Since the stationary distribution is a probability distribution, marginal distributions also have the same property. That is, for a player $i$, 
-\begin{equation}
-\sum_{k = 1}^{m_i} \xi_{i:a_{i,k}}= 1
-\label{Eq:marginal-prob-dist}
-\end{equation}
+%\noindent Since the stationary distribution is a probability distribution, marginal distributions also have the same property. That is, for a player $i$, 
+%\begin{equation}
+%\sum_{k = 1}^{m_i} \xi_{a_{i,k}}= 1
+%\label{Eq:marginal-prob-dist}
+%\end{equation}
 \section*{Additive games and their properties under introspection dynamics}
-In this section we discuss the stationary properties of the introspection dynamics when players learn to play strategies in a special class of games: the additive games \cite{McAvoy:PlosCB:2015, Pena:JTB:2014}.
+In this section we discuss the stationary properties of introspection dynamics when players learn to play strategies in a special class of games: additive games \cite{McAvoy:PlosCB:2015, Pena:JTB:2014}.
 In an additive game, the payoff difference that a player earns by making a unilateral switch in their actions is independent of what their co-players play.
@@
 \pi_i(x, \qbf) - \pi_i(y, \qbf) =: f_i(x,y) 
+\label{Eq:coplayer-independent-payoffdiff}
 \end{equation}
@@
  \begin{Prop}
-When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
-\begin{equation}
-\ubf_\abf = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a', \abf_j)}} 
+When $\beta$ is finite, the unique stationary distribution, $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$, of introspection dynamics for the N-player additive game is given by: 
+\begin{equation}
+\mathrm{u}_\abf = \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a', a_j)}} 
 \label{Eq:additive-game-stationary-distribution}
 \end{equation}
-where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play from $\abf_j$  to $a'$.
+where, $f_j(a', a_j)$ is the co-player independent payoff difference given by Eq. (\ref{Eq:coplayer-independent-payoffdiff}).
+
 \label{Th:additive-games-stationary-dist}
@@
 (\ref{Eq:additive-game-stationary-distribution}).
-For a proof, please see Appendix.
+For a proof of the propositions and corollaries, please see Appendix.
 Using the stationary distribution, one can also exactly compute the cumulative probabilities with which players play their actions in the long run (i.e., the marginal distribution) using Eq.
@@
 \begin{Prop}
-Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game.
-Then, $\ubf_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$.
+Let $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$ be the unique stationary distribution of introspection dynamics with finite $\beta$ for the N-player additive game.
+Then, $\mathrm{u}_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$.
 That is,
@@
 \begin{equation}
-\ubf_\abf = \prod_{j = 1}^N \xi_{j:\abf_j}
+\mathrm{u}_\abf = \prod_{j = 1}^N \xi_{j,a_j}
 \label{Eq:additive-game-products}
@@
 
-\noindent where the marginal probability, $\xi_{j:\abf_j}$, is the cumulative probability that player $j$ plays $\abf_j$ at the stationary distribution.
+\noindent where the marginal probability, $\xi_{j,a_j}$, is the cumulative probability that player $j$ plays $a_j$ at the stationary distribution.
 The marginal probability for the $N$-player additive game is given by:
@@
 \begin{equation}
-\xi_{j:\abf_j} = \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a', \abf_j)}} 
+\xi_{j,a_j} = \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a',a_j)}} 
 \label{Eq:marginal-at-additive-game}
 \end{equation}
-\noindent where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play from $\abf_j$ to $a'$.
+\noindent where, $f_j(a', a_j)$ is the co-player independent payoff difference given by Eq. (\ref{Eq:coplayer-independent-payoffdiff}).
 \label{Th:additive-game-product-of-marginals}
 \end{Prop}
-\noindent The above proposition states that for additive games, the stationary distribution of the introspection dynamics can be factorized into its corresponding marginals.
-In the long run, the probability that players play the state ($\abf_1, \abf_2, ...,\abf_N$) is the product of the cumulative probabilities that player 1 plays $\abf_1$, player 2 plays $\abf_2$ and so on.
-For a proof, please see Appendix.
+\noindent The above proposition states that for additive games, the stationary distribution of introspection dynamics can be factorized into its corresponding marginals.
+In the long run, the probability that players play the state $\abf = (a_1, a_2, ...,a_N)$ is the product of the cumulative probabilities that player 1 plays $a_1$, player 2 plays $a_2$ and so on.
 This property of the additive game was already shown for the simple two-player, two-action donation game in Couto et al.
@@
 Here we extend that result for any number of players, each having an arbitrary number of strategies.
-While this factorizing property of the stationary distribution appears for additive games, we do not show that this property is unique to additive games.
-In the next section we use the well-studied example of the linear public goods game to demonstrate the stationary properties of the introspection dynamics in additive games.
+In the next section we use the well-studied example of the linear public goods game to demonstrate the stationary properties of introspection dynamics in additive games.
 
@@
 \begin{equation}
-\pi_i(\abf) = \frac{1}{N}\sum_{j=1}^N \displaystyle \alpha(\abf_j) b_j - \alpha(\abf_i) c_i
+\pi_i(\abf) = \frac{1}{N}\sum_{j=1}^N \displaystyle \alpha(a_j) b_j - \alpha(a_i) c_i
 \label{Eq:linear-pgg-payoff}
@@
 \label{prop:stationary-dist-lpgg}
-When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for a $N-$player linear public goods game is given by: 
+When $\beta$ is finite, the unique stationary distribution of introspection dynamics for a $N-$player linear public goods game is given by: 
 \\
 \begin{equation}
-\ubf_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf_j)\beta f_j(\D, \C )}} 
+\mathrm{u}_\abf = \prod_{j = 1}^{N} \frac{1}{1 + \displaystyle e^{\mathit{sign}(a_j)\beta f_j(\D, \C )}} 
 \label{Eq:stationary_dist_lpgg}
@@
 \end{Prop}
-\noindent For a proof, please see Appendix.
-We use a simple example to demonstrate the above result.
+\noindent We use a simple example to illustrate the above result.
 Consider a 3-player linear public goods game.
@@
 For player 1 and 2, the cost of cooperation is 1 unit ($c_1 = c_2 = 1$) while for the third player, the cost is slightly higher at 1.5 units ($c_3 = 1.5$).
-In the stationary distribution of the process with selection strength $\beta = 1$, the state where player 1 and 2 play $\C$ and player 3 plays $\D$, $\ubf_{\C\C\D}$, occurs with probability $\approx 0.121$ (rounded up to three decimal places).
+In the stationary distribution of the process with selection strength $\beta = 1$, the state where player 1 and 2 play $\C$ and player 3 plays $\D$, $\mathrm{u}_{\C\C\D}$, occurs with probability $\approx 0.121$ (rounded up to three decimal places).
 We calculate this probability exactly with Eq.
@@
 The marginal probabilities that in the long run player 1 (or player 2) plays cooperation and player 3 plays defection are 0.417 and 0.697 respectively.
-That is, $\xi_{1:\C} = \xi_{2:\C} \approx 0.417$ and $\xi_{3:\D} \approx 0.697$ (rounded up to a three decimal places).
+That is, $\xi_{1,\C} = \xi_{2,\C} \approx 0.417$ and $\xi_{3,\D} \approx 0.697$ (rounded up to a three decimal places).
 With the exact values (and also with the approximations here), one can confirm the factorizing property of the stationary distribution for additive games in this example (i.e., Proposition \ref{Th:additive-game-product-of-marginals}).
-That is, $\ubf_{\C\C\D} = \xi_{1:\C} \cdot \xi_{2:\C} \cdot \xi_{3:\D}$.
+That is, $\mathrm{u}_{\C\C\D} = \xi_{1,\C} \cdot \xi_{2,\C} \cdot \xi_{3,\D}$.
 \\ \\
@@
 \noindent Since players are symmetric, states can again be enumerated by counting the number of $\C$ players in the state.
-We denote the payoff of a $\C$ and $\D$ player in a state where there are $j$ co-players playing $\C$ by $\pi_\C(j)$ and $\pi_\D(j)$ respectively.
-From the previous section, we adopt the indicator function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to 0, and the notation $\mathcal{C}(\abf)$ to denote the number of cooperators in the state $\abf$.
+We denote the payoff of a $\C$ and $\D$ player in a state where there are $j$ co-players playing $\C$ by $\pi^\C(j)$ and $\pi^\D(j)$ respectively.
+We denote with $f(j)$ the payoff difference earned by switching from $\D$ to $\C$ when there are $j$ co-players playing $\C$,
+
+\begin{equation}
+f(j) := \pi^\D(j) - \pi^\C(j)
+\label{Eq:f-switching-CtoD}
+\end{equation}
+
+\noindent From the previous section, we adopt the indicator function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to 0, and the notation $\mathcal{C}(\abf)$ to denote the number of cooperators in the state $\abf$.
 That is,
@@
 \begin{equation}
-\mathcal{C}(\abf) := \sum_{j=1}^N \alpha(\abf_j)
-\end{equation}
-
-\noindent 
-The stationary distribution of a two-action symmetric game under introspection dynamics can be explictly computed using the following proposition,
+\mathcal{C}(\abf) := \sum_{j=1}^N \alpha(a_j)
+\end{equation}
+\\
+\noindent The stationary distribution of a two-action symmetric game under introspection dynamics can be explictly computed using the following proposition,
 
@@
 \label{Prop:Symmetric-2-strategies-state}
-When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\ubf_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
+When $\beta$ is finite, the unique stationary distribution of introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\mathrm{u}_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
 \begin{equation}
 \label{Eq:stationary-dist-symm-2-stgs-state}
-\ubf_\abf = \frac{1}{\Gamma} \displaystyle \prod_{j=1}^{\mathcal{C}(\abf)} \displaystyle e^{-\beta f(j-1)}
-\end{equation}
-where $f(j) := \pi^\D(j) - \pi^\C(j)$ is the payoff difference earned by switching the play from $\D$ and $\C$ when there are $j$ co-players playing $\C$.
-The term $\Gamma$ is the normalization factor given by:
+\mathrm{u}_\abf = \frac{1}{\Gamma} \displaystyle \prod_{j=1}^{\mathcal{C}(\abf)} \displaystyle e^{-\beta f(j-1)}
+\end{equation}
+where $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}). The term $\Gamma$ is the normalization factor given by:
 \begin{equation}
@@
 
-\noindent For a proof of this proposition, please see Appendix.
-The number of unique states of the game can be reduced to $N+1$ from $2^N$ due to symmetry.
+\noindent The number of unique states of the game can be reduced to $N+1$ from $2^N$ due to symmetry.
 In the reduced state space, the state, $k$, corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
@@
 \label{Lemma: Symmetric-2-stg}
-When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
+When $\beta$ is finite, the unique stationary distribution, $(\mathrm{u}_k)_{k \in \{0,1,...,N\}}$, of introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
 \begin{equation}
 \label{Eq:stationary-dist-symm-2-stgs}
-\ubf_k = \frac{1}{\Gamma} \cdot {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
+\mathrm{u}_k = \frac{1}{\Gamma} \cdot {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
 \end{equation} \\ 
-where, $k$ represents the number of $\C$ players in the state and $f(j) := \pi^\D(j) - \pi^\C(j)$ is the payoff difference earned by switching the play $\D$ and $\C$ when there are $j$ co-players playing $\C$.
-The term $\Gamma$ is the normalization factor, given by, \\
+where, $k$ represents the number of $\C$ players in the state and $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}). The term $\Gamma$ is the normalization factor, given by, \\
 \begin{equation}
@@
 This count is simply the binomal coefficient $N \choose k$.
-For a proof, please see Appendix.
-In the next section, we study the stationary behaviour of the introspection dynamics in a two-action general game with an example.
+In the next section, we study the stationary behaviour of introspection dynamics in a two-action general game with an example.
 To this end, we use the example of a non-linear public goods game to demonstrate the results.
@@
 \begin{align}
-\pi^{\D}_i(\D, \abf_{-i})&= 
+\pi_i(\D, \abf_{-i})&= 
 \begin{cases}
-\displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N \cdot \mathcal{C}(\D,\abf_{-i})} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\D,\abf_{-i}) - 1} \right) &\quad  \text{if } \mathcal{C}(\D,\abf_{-i}) \neq 0 \\[15pt]
+\displaystyle \sum_{i=1}^N b_i \alpha(a_i) \cdot \frac{1}{N \cdot \mathcal{C}(\D,\abf_{-i})} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\D,\abf_{-i}) - 1} \right) &\quad  \text{if } \mathcal{C}(\D,\abf_{-i}) \neq 0 \\[15pt]
 0 &\quad  \text{if } \mathcal{C}(\D,\abf_{-i}) = 0
 \end{cases} \\[15pt]
-\pi^{\C}_i(\C, \abf_{-i}) &= \displaystyle \sum_{i=1}^N b_i \alpha(\abf_i) \cdot \frac{1}{N \cdot \mathcal{C}(\C,\abf_{-i})} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\C,\abf_{-i}) - 1} \right) - c_i
+\pi_i(\C, \abf_{-i}) &= \displaystyle \sum_{i=1}^N b_i \alpha(a_i) \cdot \frac{1}{N \cdot \mathcal{C}(\C,\abf_{-i})} \cdot \left(1 + w + w^2 + ...w^{\mathcal{C}(\C,\abf_{-i}) - 1} \right) - c_i
 \label{Eq:payoff-synergistic-asymmetric}
@@
 The four parameter combinations are chosen such that each of them represents a unique social dilemma under the replicator dynamics.
-When the PG is discounted ($w = 0.5$) and costs are high ($c = 1$) defection dominates cooperation (the prisoner's dilemma).
-When the PG is discounted ($w = 0.5$) but costs are low ($c = 0.2$), the coexistence behaviour similar to the snowdrift game appears from the replicator equation.
+When the PG is discounted ($w = 0.5$) and costs are high ($c = 1$) defection dominates cooperation (like the prisoner's dilemma).
+When the PG is discounted ($w = 0.5$) but costs are low ($c = 0.2$), the there is stable coexistence between cooperators and defectors under the replicator dynamics just like the snowdrift game.
 When the PG is synergistic ($w = 1.5$) and costs are high ($c = 1$), both cooperation and defection are locally stable equilibria under the replicator dynamics.
 In addition, there is also an internal equilibrium which is unstable.
-This represents the stag-hunt game.
+This is alike the dilemma in the stag-hunt game.
 And finally when both the PG is synergistic and costs are low, cooperation dominates defection.
-This situation represents the harmony game.
+This situation is similar to the harmony game.
 The stationary behaviour of players in these games reflect the outcomes from the replicator dynamics (Fig.
@@
 \noindent 
-We also study the introspection dynamics in general public goods game with asymmetric players.
+We also study introspection dynamics in general public goods game with asymmetric players.
 We use the same setup that we used for studying the linear public goods with three asymmetric players.
 The average frequency of cooperation per player is summarized in Supplementary Figures 1 and 2.
-First, we study two cases, one in which the public good is synergized (and players have a high average cost) and two in which public good is discounted (and players have a lower average cost).
+First, we study two cases, one in which the public good is synergistic ($w > 1$, and players have a high average cost) and two in which public good is discounted (and players have a lower average cost).
 In both of these cases, players cooperate highly when they simultaneously have low cost and high benefit.
@@
 In each case the asymmetric player either has \textbf{a}) a higher cost of rewarding $\gamma_3 > \gamma_1$  or, \textbf{b}) low productivitiy  $r_3 < r_1$ or, \textbf{c}) or, less information about peers $\lambda_3 < \lambda_1$ than his peers.
-We simulate the introspection dynamics (with a strong selection strength, $\beta = 10$) for many iterations ($10^5$ time-steps) to estimate the average abundances of the 16 strategies.
+We use Eq.
+(\ref{Eq:explicit-stationary-dist-representation}) to exactly compute the expected abundances of the 16 strategies for each player.
 \\ \\
@@
 In the long run, the asymmetric player cooperates less on average than their peers.
-This is because they cannot cooperate opportunistically enough, unlike their peers with higher information.
+This is because the individual with less information has less instances of opportunistically cooperating with his co-players.
 However, both types of player reward cooperation almost equally and just enough to sustain cooperation.
@@
 \textbf{Proof of Proposition} \ref{Th:additive-games-stationary-dist} \\ \\ 
-Since $\beta$ is finite,the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the process is unique by Proposition \ref{Prop:unique-stationary-dist}.
+Since $\beta$ is finite,the stationary distribution $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$ of the process is unique.
 The stationary distribution also satisfies the equalities in Eq.
@@
 \label{Eq:shortcut-tau}
-\tau_{j:\abf_j} &:= \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a',  \abf_j)}} 
+\tau_{j,a_j} &:= \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a',  a_j)}} 
 \end{align}
@@
 \label{step-one}
-\T_{\abf,\abf} \ubf_\abf  + &\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} = \ubf_\abf \quad \forall \abf \in \A \\[10pt]
+\mathrm{T}_{\abf,\abf} \mathrm{u}_\abf  + &\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} = \mathrm{u}_\abf \quad \forall \abf \in \A \\[10pt]
 \label{step-two}
-&\sum_{\abf \in \A} \ubf_\abf  = 1
+&\sum_{\abf \in \A} \mathrm{u}_\abf  = 1
 \end{align} 
@@
 \begin{equation}
-\ubf_\abf = \prod_{j=1}^N \tau_{j:\abf_j}
+\mathrm{u}_\abf = \prod_{j=1}^N \tau_{j,a_j}
 \label{Eq:additive-stat-shortcut}
@@
 \begin{align}
-&\T_{\abf,\abf} \ubf_\abf  + \sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf}\\
-&= \left( 1 - \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} \right) \ubf_{\abf}+ \frac{1}{}\sum_{\bbf \in \mathrm{Neb}(\abf)}  \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{\bbf_{\mathrm{I}_\bbf} \to \abf_{\mathrm{I}_\bbf}} \cdot \ubf_{\bbf}\\ \notag \\
+&\mathrm{T}_{\abf,\abf} \mathrm{u}_\abf  + \sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf}\\
+&= \left( 1 - \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} \right) \mathrm{u}_{\abf}+ \frac{1}{N}\sum_{\bbf \in \mathrm{Neb}(\abf)}  \frac{1}{m_{\mathrm{I}_\bbf}-1} \cdot p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}} \cdot \mathrm{u}_{\bbf}\\ \notag \\
 \label{eq:important-step}
-&= \ubf_\abf +  \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \left( \prod_{k \neq I_\bbf} \tau_{k:\abf_k} \right) \left( p_{\bbf_{I_\bbf} \to \abf_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf: \abf_{\mathrm{I}_\bbf}} -  p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf: \bbf_{\mathrm{I}_\bbf}} \right) \cdot \left(  \frac{1}{m_{\mathrm{I}_\bbf}-1} \right)
-\end{align}
-\noindent For an additive game, the expressions for $p_{\bbf_{I_\bbf} \to \abf_{\mathrm{I}_\bbf}}$ and $p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}}$ can be simply written as: 
-\begin{align}
-p_{\bbf_{I_\bbf} \to \abf_{\mathrm{I}_\bbf}} &=\frac{1}{1 + \displaystyle e^{\beta f_{\mathrm{I}_\bbf}(\bbf_{\mathrm{I}_\bbf}, \abf_{\mathrm{I}_\bbf})}} \\[10pt] 
-p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} &= \frac{1}{1 + \displaystyle e^{\beta f_{\mathrm{I}_\bbf}(\abf_{\mathrm{I}_\bbf}, \bbf_{\mathrm{I}_\bbf})}} 
+&= \mathrm{u}_\abf +  \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \left( \prod_{k \neq I_\bbf} \tau_{k,a_k} \right) \left( p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, a_{\mathrm{I}_\bbf}} -  p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, b_{\mathrm{I}_\bbf}} \right) \cdot \left(  \frac{1}{m_{\mathrm{I}_\bbf}-1} \right)
+\end{align}
+\noindent For an additive game, the expressions for $p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}}$ and $p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}}$ can be simply written as: 
+\begin{align}
+p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}} &=\frac{1}{1 + \displaystyle e^{\beta f_{\mathrm{I}_\bbf}(b_{\mathrm{I}_\bbf}, a_{\mathrm{I}_\bbf})}} \\[10pt] 
+p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} &= \frac{1}{1 + \displaystyle e^{\beta f_{\mathrm{I}_\bbf}(a_{\mathrm{I}_\bbf}, b_{\mathrm{I}_\bbf})}} 
 \end{align} \\
@@
 \begin{equation}
-\left( p_{\bbf_{I_\bbf} \to \abf_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf: \abf_{\mathrm{I}_\bbf}} -  p_{\abf_{\mathrm{I}_\bbf} \to \bbf_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf: \bbf_{\mathrm{I}_\bbf}} \right) = 0
+ \left( p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, a_{\mathrm{I}_\bbf}} -  p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, b_{\mathrm{I}_\bbf}} \right) = 0
 \label{important-step-is-zero}
@@
 (\ref{eq:important-step}), we see that the left hand side of Eq.
-(\ref{step-one}) simplifies to $\ubf_{\abf}$.
+(\ref{step-one}) simplifies to $\mathrm{u}_{\abf}$.
 Now, to complete the proof we must check if Eq.
 (\ref{step-two}) holds for our candidate distribution.
-Summing up the elements of the stationary distribution $\ubf_\abf$ for all states $\abf \in \A$: \\
-\begin{align}
-\sum_{\abf \in \A} \ubf_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau_{k:\abf_k} = \sum_{\abf \in \A} \frac{\displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}}{\displaystyle \quad \prod_{k=1}^N \sum_{a' \in \A_k} e^{\beta \pi_k(a',\qbf_{-k})}}
+Summing up the elements of the stationary distribution $\mathrm{u}_\abf$ for all states $\abf \in \A$: \\
+\begin{align}
+\sum_{\abf \in \A} \mathrm{u}_\abf &= \sum_{\abf \in \A} \prod_{k=1}^N \tau_{k,a_k} = \sum_{\abf \in \A} \frac{\displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})}}{\displaystyle \quad \prod_{k=1}^N \sum_{a' \in \A_k} e^{\beta \pi_k(a',\qbf_{-k})}}
 \end{align}
@@
 \begin{align}
-\sum_{\abf \in \A} \ubf_\abf = &\sum_{\abf \in \A} \frac{\displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}}{\displaystyle \quad \prod_{k=1}^N \sum_{a' \in \A_k} e^{\beta \pi_k(a',\qbf_{-k})}} \\[15pt]
+\sum_{\abf \in \A} \mathrm{u}_\abf = &\sum_{\abf \in \A} \frac{\displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})}}{\displaystyle \quad \prod_{k=1}^N \sum_{a' \in \A_k} e^{\beta \pi_k(a',\qbf_{-k})}} \\[15pt]
 =& \left( \displaystyle \prod_{k=1}^N \left( e^{\beta \pi_k(a_{k,1}, \qbf_{-k})}+...
-+ e^{\beta \pi_k(a_{k,m_k}, \qbf_{-k})} \right) \right)^{-1} \cdot \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})} \right) \\
++ e^{\beta \pi_k(a_{k,m_k}, \qbf_{-k})} \right) \right)^{-1} \cdot \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})} \right) \\
 \end{align} \\
@@
 \label{Eq:OG_prod-of-sum}
-\sum_{\abf \in \A} \ubf_\abf =& \left( \displaystyle \prod_{k=1}^N \left( e^{\beta \pi_k(a_{k,1}, \qbf_{-k})}+...
-+ e^{\beta \pi_k(a_{k,m_k}, \qbf_{-k})} \right) \right)^{-1} \cdot \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})} \right) \\[10pt]
+\sum_{\abf \in \A} \mathrm{u}_\abf =& \left( \displaystyle \prod_{k=1}^N \left( e^{\beta \pi_k(a_{k,1}, \qbf_{-k})}+...
++ e^{\beta \pi_k(a_{k,m_k}, \qbf_{-k})} \right) \right)^{-1} \cdot \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})} \right) \\[10pt]
 \label{Eq:OG_sum-of-prod}
-=& \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}  \right)^{-1} \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(\abf_k, \qbf_{-k})}  \right) = 1
+=& \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})}  \right)^{-1} \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})}  \right) = 1
 \end{align} \\ 
@@
 In the steps below, we always decompose the expression $f_j(a,b)$ to $\pi_j(a,\pbf_{-j}) - \pi_j(b,\pbf_{-j})$.
-When $\ubf = (\ubf_\abf)_{\abf \in \A}$ is the unique stationary distribution of the $N-$player additive game under finite selection introspection dynamics, it is given by the closed form expression in Eq.
+When $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$ is the unique stationary distribution of the $N-$player additive game under finite selection introspection dynamics, it is given by the closed form expression in Eq.
 (\ref{Eq:additive-game-stationary-distribution}).
-We use this expression to calculate the marginal distribution of actions played at a particular state $\abf$, $(\xi_{j:\abf_j})_{j \in \{1,2,...,N\}}$.
-\begin{align}
-\xi_{j:\abf_j} &= \sum_{\qbf \in \A_{-j}} \ubf_{(\abf_j,\qbf)} \\ \notag \\
-&= \sum_{\qbf \in \A_{-j}} \left( \sum_{a' \in \A_j} \displaystyle e^{\beta f_j(a',\abf_j)}\right)^{-1} \prod_{k \neq j} \left( \sum_{a' \in \A_k} \displaystyle e^{\beta f_k(a',\qbf_k)}\right)^{-1} \\ \notag \\
-&= \left( \prod_{k=1}^N \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k (a', \pbf_{-k})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k, l_{-k})} \right) \\ \notag \\
+We use this expression to calculate the marginal distribution of actions played at a particular state $\abf$, $(\xi_{j,a_j})_{j \in \{1,2,...,N\}}$.
+\begin{align}
+\xi_{j,a_j} &= \sum_{\qbf \in \A_{-j}} \mathrm{u}_{(a_j,\qbf)} \\ \notag \\
+&= \sum_{\qbf \in \A_{-j}} \left( \sum_{a' \in \A_j} \displaystyle e^{\beta f_j(a',a_j)}\right)^{-1} \prod_{k \neq j} \left( \sum_{a' \in \A_k} \displaystyle e^{\beta f_k(a',q_k)}\right)^{-1} \\ \notag \\
+&= \left( \prod_{k=1}^N \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k (a', \pbf_{-k})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(a_j, \pbf_{-j})} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(q_k, l_{-k})} \right) \\ \notag \\
 \label{step-prod-sum}
-&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})}\cdot \left( \prod_{k\neq j} \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k(a',\pbf_{-k})}\right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k,\pbf_{-k})} \right)
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(a_j, \pbf_{-j})}\cdot \left( \prod_{k\neq j} \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k(a',\pbf_{-k})}\right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(q_k,\pbf_{-k})} \right)
 \end{align}
@@
 \label{step-sum-prod}
-&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(\abf_j, \pbf_{-j})}\cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi_k(\qbf_k,\pbf_{-k})} \right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(\qbf_k,\pbf_{-k})}  \right)
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(a_j, \pbf_{-j})}\cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi_k(q_k,\pbf_{-k})} \right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(q_k,\pbf_{-k})}  \right)
 \end{align}
@@
 (\ref{step-prod-sum}) and Eq.
-(\ref{step-sum-prod}) can be carried out by observing that when all the sums are multiplied out, one is left with sums of terms, each of which is a exponential with power equal to sum of payoffs that co-players of $j$ (here $k$) receive when they play their respective strategies from $\qbf$ (that is $\qbf_k$) against co-players that play $\pbf_{-k}$.
+(\ref{step-sum-prod}) can be carried out by observing that when all the sums are multiplied out, one is left with sums of terms, each of which is a exponential with power equal to sum of payoffs that co-players of $j$ (here $k$) receive when they play their respective strategies from $\qbf$ (that is $q_k$) against co-players that play $\pbf_{-k}$.
 This is the similar to the step between Eq.
@@
 \begin{align}
-&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \left( \pi_j(a',\pbf_{-j}) - \pi_j(\abf_j,\pbf_{-j})\right)} \right)^{-1}\\ \notag \\
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \left( \pi_j(a',\pbf_{-j}) - \pi_j(a_j,\pbf_{-j})\right)} \right)^{-1}\\ \notag \\
 \label{final-expression}
-&= \sum_{a' \in \A_j} \displaystyle e^{\beta f_j(a',\abf_j)}
+&= \sum_{a' \in \A_j} \displaystyle e^{\beta f_j(a',a_j)}
 \end{align} \\
@@
 \begin{equation}
-\prod_{j=1}^N \xi_{j:\abf_j} = \ubf_\abf
+\prod_{j=1}^N \xi_{j,a_j} = \mathrm{u}_\abf
 \end{equation} 
@@
 Here, we provide an independent proof.
-The idea behind this proof is identical to the proof of proof\ref{Th:additive-games-stationary-dist}.
-\\ \\
-\noindent Using Proposition \ref{Prop:unique-stationary-dist}, we can confirm that since $\beta$ is finite, the process will have a unique stationary distribution.
+The idea behind this proof is identical to the proof of Proposition \ref{Th:additive-games-stationary-dist}.
+\\ \\
+\noindent Again, since $\beta$ is finite, the process will have a unique stationary distribution.
 Before continuing with the rest of the proof where we show that our candidate stationary distribution is \emph{the} unique stationary distribution, we define the following short-cut notations for the ease of the proof:
 \begin{align}
-\bar{\abf}_j &:= \{\D,\C\} \setminus \{\abf_j\}  \\ \notag \\ 
+\bar{a}_j &:= \{\D,\C\} \setminus \{a_j\}  \\ \notag \\ 
 p_j &:= \frac{1}{1 + \displaystyle e^{\beta f_j(\D, \C)}} 
@@
 Using these notations and Eq.
-(\ref{Eq:introspection-update}) and (\ref{Eq:difference-payoffs-lpgg}) and utilizing our shortcut notation from above, we can write the probability that a player $j$ updates to $\abf_j$ from $\bar{\abf}_j$ while their co-players play $\abf_{-j}$ as: \\
-\begin{equation}
-p_{\displaystyle \bar{\abf}_j  \to \abf_j} (\abf_{-j}) = p_j \mathit{sign}(\abf_j) + \alpha(\bar{\abf}_j) 
+(\ref{Eq:introspection-update}) and (\ref{Eq:difference-payoffs-lpgg}) and utilizing our shortcut notation from above, we can write the probability that a player $j$ updates to $a_j$ from $\bar{a}_j$ while their co-players play $\abf_{-j}$ as: \\
+\begin{equation}
+p_{\displaystyle \bar{a}_j  \to a_j} (\abf_{-j}) = p_j \mathit{sign}(a_j) + \alpha(\bar{a}_j) 
 \end{equation}\\
@@
 \label{Eq:stationary-dist-shortcut}
-\ubf_\abf = \prod_{k = 1}^{N}  p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k)
+\mathrm{u}_\abf = \prod_{k = 1}^{N}  p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k)
 \end{equation}\\
@@
 \label{Eq:transition-in-proof}
-&\ubf_\abf = \T_{\abf,\abf} \ubf_\abf  + \sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf}  \\[10pt] 
+&\mathrm{u}_\abf = \mathrm{T}_{\abf,\abf} \mathrm{u}_\abf  + \sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf}  \\[10pt] 
 \label{Eq:normalization-in-proof}
-&\sum_{\abf \in \A} \ubf_{\abf}= 1
-\end{align}
-Where, the terms in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified using Eq. (\ref{Eq:introspection-update}) and (\ref{Eq:transition-matrix}) as follows:
+&\sum_{\abf \in \A} \mathrm{u}_{\abf}= 1
+\end{align}
+Where, the terms in the right hand side of Eq. (\ref{Eq:transition-in-proof}) can be simplified using Eq. (\ref{Eq:introspection-update}) and (\ref{Eq:transition-matrix}) as follows:
 \begin{eqnarray}
-\T_{\abf,\abf} = 1 - \sum_{k=1}^{N} \T_{(\abf_k, \abf_{-k}), (\bar{\abf}_k,\abf_{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p_k \textit{sign}(\bar{\abf}_k) + \alpha(\abf_k)
+\mathrm{T}_{\abf,\abf} = 1 - \sum_{k=1}^{N} \mathrm{T}_{(a_k, \abf_{-k}), (\bar{a}_k,\abf_{-k})} = 1 - \frac{1}{N} \sum_{k=1}^{N} p_k \textit{sign}(\bar{a}_k) + \alpha(a_k)
 \label{Eq:first-term-rhs-proof}
@@
 \begin{align}
-\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &= \sum_{k = 1}^N \T_{(\bar{\abf}_k,\abf_{-k}), (\abf_k, \abf_{-k})} \ubf_{(\bar{\abf}_k,\abf_{-k})} \\[10pt]
-&= \frac{1}{N} \sum_{k = 1}^N \left(p_k \textit{sign}(\abf_k) +\alpha(\bar{\abf}_k) \right) \ubf_{(\bar{\abf}_k,\abf_{-k})} \\[10pt] 
+\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &= \sum_{k = 1}^N \mathrm{T}_{(\bar{a}_k,\abf_{-k}), (a_k, \abf_{-k})} \mathrm{u}_{(\bar{a}_k,\abf_{-k})} \\[10pt]
+&= \frac{1}{N} \sum_{k = 1}^N \left(p_k \textit{sign}(a_k) +\alpha(\bar{a}_k) \right) \mathrm{u}_{(\bar{a}_k,\abf_{-k})} \\[10pt] 
 \label{Eq:second-term-rhs-proof}
-&= \frac{\ubf_\abf}{N} \sum_{k=1}^{N} p_k \textit{sign}(\bar{\abf}_k) + \alpha(\abf_k) 
+&= \frac{\mathrm{u}_\abf}{N} \sum_{k=1}^{N} p_k \textit{sign}(\bar{a}_k) + \alpha(a_k) 
 \end{align}
@@
 (\ref{Eq:first-term-rhs-proof}) and (\ref{Eq:second-term-rhs-proof}) one can show that the right hand side of Eq.
-(\ref{Eq:transition-in-proof}) is the element of the stationary distribution, corresponding to the state $\abf$, $\ubf_a$.
+(\ref{Eq:transition-in-proof}) is the element of the stationary distribution, corresponding to the state $\abf$, $\mathrm{u}_a$.
 Now, to complete the proof, we must show that Eq.
@@
 \begin{align}
-\sum_{\abf \in \A} u_{\abf} =& \displaystyle \sum_{\abf \in \A} \prod_{k=1}^N p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k) \\[10pt]
-=& \displaystyle \displaystyle \sum_{\abf \in \A_{-\!N}} (1-p_N)  \prod_{k=1}^{N-1} p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k)  + p_N  \prod_{k=1}^{N-1} p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k) \\[10pt]
-=& \displaystyle \sum_{\abf \in \A_{-\!N}} \prod_{k=1}^{N-1} p_k \mathit{sign}(\abf_k) + \alpha(\bar{\abf}_k)
+\sum_{\abf \in \A} \mathrm{u}_{\abf} =& \displaystyle \sum_{\abf \in \A} \prod_{k=1}^N p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k) \\[10pt]
+=& \displaystyle \displaystyle \sum_{\abf \in \A_{-\!N}} (1-p_N)  \prod_{k=1}^{N-1} p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k)  + p_N  \prod_{k=1}^{N-1} p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k) \\[10pt]
+=& \displaystyle \sum_{\abf \in \A_{-\!N}} \prod_{k=1}^{N-1} p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k)
 \end{align}
@@
 (\ref{Eq:stationary-dist-normalization-symm-2-stgs-state}) is a probability distribution since it satisfies the condition in Eq.
-(\ref{Eq:normalizationcondition}) and for any state $\abf$, $\ubf_{\abf}$ is between 0 and 1.
-Moreover, since $\beta$ is finite, by Proposition \ref{Prop:unique-stationary-dist}, the process will have a unique stationary distribution.
+(\ref{Eq:normalizationcondition}) and for any state $\abf$, $\mathrm{u}_{\abf}$ is between 0 and 1.
+Again, since $\beta$ is finite the process will have a unique stationary distribution.
 Again, to show that the candidate stationary distribution is the unique stationary distribution, we need to check if Eq.
@@
 \begin{align}
-\bar{\abf}^j &:= \{\D,\C\} \setminus \{\abf_j\} \\[10pt]
+\bar{a}^j &:= \{\D,\C\} \setminus \{a_j\} \\[10pt]
 \alpha(a)&:= 
@@
 \end{cases}\\[10pt]
-\mathcal{C}(\abf) &= \sum_{j=1}^N \alpha(\abf_j)
+\mathcal{C}(\abf) &= \sum_{j=1}^N \alpha(a_j)
 \end{align}
@@
 \begin{align}
-\ubf_{\abf} \T_{\abf,\abf}  &= \ubf_\abf - \ubf_{\abf} \sum_{k=1}^{N} \T_{(\abf_k, \abf_{-k}),(\bar{\abf}_{k}, \abf_{-k})} \\[10pt]
-&= \ubf_{\abf} - \frac{\ubf_{\abf}}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}_{k}) \beta f(N_k)}}
+\mathrm{u}_{\abf} \mathrm{T}_{\abf,\abf}  &= \mathrm{u}_\abf - \mathrm{u}_{\abf} \sum_{k=1}^{N} \mathrm{T}_{(a_k, \abf_{-k}),(\bar{a}_{k}, \abf_{-k})} \\[10pt]
+&= \mathrm{u}_{\abf} - \frac{\mathrm{u}_{\abf}}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{a}_{k}) \beta f(N_k)}}
 \label{Eq:T_aa_u_a term}
@@
 \begin{equation}
-N_k := \sum_{j \neq k} \alpha(\abf_j)
+N_k := \sum_{j \neq k} \alpha(a_j)
 \end{equation} \\
-The second term in the right hand side of Eq. \ref{Eq:transition-in-proof} can be simplified as, 
-\begin{align}
-\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &= \sum_{k=1}^N \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \ubf_{(\bar{\abf}_k, \abf_{-k})} \\[10pt]
+The second term in the right hand side of Eq. (\ref{Eq:transition-in-proof}) can be simplified as, 
+\begin{align}
+\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &= \sum_{k=1}^N \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \mathrm{u}_{(\bar{a}_k, \abf_{-k})} \\[10pt]
 \label{Eq:step-single-product}
-&= \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \displaystyle \prod_{j=1}^{\mathcal{C}((\bar{\abf}_k, \abf_{-k}))} e^{-\beta f(j-1)}\\[10pt]
-&=  \frac{1}{N \Gamma} \sum_{k=1}^N \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k})
+&= \frac{1}{N \Gamma} \sum_{k=1}^N \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \displaystyle \prod_{j=1}^{\mathcal{C}((\bar{a}_k, \abf_{-k}))} e^{-\beta f(j-1)}\\[10pt]
+&=  \frac{1}{N \Gamma} \sum_{k=1}^N \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k})
 \label{Eq:step-product-broken}
@@
 (\ref{Eq:step-product-broken}), we took out one term from the product that is present in our candidate distribution.
-This term accounts for the $k^{th}$ players action in the neighbouring state $(\bar{\abf}_k, \abf_{-k})$ of $\abf$.
-For simplicity, we replace $\T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})}$ with just $\T$ in the next steps.
+This term accounts for the $k^{th}$ players action in the neighbouring state $(\bar{a}_k, \abf_{-k})$ of $\abf$.
+For simplicity, we represent $\mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})}$ with just $\T$ in the next steps.
 We continue the simplification of Eq.
@@
 \begin{align}
-\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k)}}{e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) +N_k)}} \cdot e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) + N_k)}
+\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot \frac{e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k)}}{e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) +N_k)}} \cdot e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) + N_k)}
 \label{Eq:new-cancelable-term-introduced}
@@
 When this term is taken inside the product bracket, products of exponent $e^{-\beta f(j-1)}$ can be performed for $j$ ranging from $1$ to the number of cooperators in state $\abf$, $\mathcal{C}(\abf)$.
-This product is then the candidate stationary distribution probability $\ubf_\abf$.
+This product is then the candidate stationary distribution probability $\mathrm{u}_\abf$.
 That is,
 \begin{align}
-\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \cdot e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) + N_k)} \right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k)}}{e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) +N_k)}} \\[10pt]
-&= \frac{1}{N} \sum_{k=1}^N  \T \cdot \left( \frac{1}{\Gamma} \prod_{j=1}^{\mathcal{C}(\abf)} e^{-\beta f(j-1)}\right) \cdot \frac{e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k)}}{e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) +N_k)}} \\[10pt]
-&= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \cdot \ubf_\abf \cdot \frac{e^{-\beta \alpha(\bar{\abf}_k)f(-\alpha(\abf_k)+ N_k)}}{e^{-\beta \alpha(\abf_k)f(-\alpha(\bar{\abf}_k) +N_k)}} \label{Eq: last-step-w-fraction}
-\end{align}
-\\ \noindent The fraction inside the sum in  Eq. (\ref{Eq: last-step-w-fraction}) can be simplified as follows leading to further simplification of Eq. (\ref{Eq: last-step-w-fraction}):
-\begin{align}
-\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &= \frac{1}{N} \sum_{k=1}^N  \T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} \cdot \ubf_\abf \cdot e^{sign(\abf_k) \beta f(N_k)} 
+\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \cdot e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) + N_k)} \right) \cdot \frac{e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k)}}{e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) +N_k)}} \\[10pt]
+&= \frac{1}{N} \sum_{k=1}^N  \T \cdot \left( \frac{1}{\Gamma} \prod_{j=1}^{\mathcal{C}(\abf)} e^{-\beta f(j-1)}\right) \cdot \frac{e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k)}}{e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) +N_k)}} \\[10pt]
+&= \frac{1}{N} \sum_{k=1}^N  \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \cdot \mathrm{u}_\abf \cdot \frac{e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k)}}{e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) +N_k)}} \label{Eq: last-step-w-fraction}
+\end{align}
+\\ \noindent The fraction inside the sum in  Eq.
+(\ref{Eq: last-step-w-fraction}) can be simplified using the $\mathit{sign}(.)$ function (in \ref{Eq:sign-function}) leading to further simplification of Eq.
+(\ref{Eq: last-step-w-fraction}):
+\begin{align}
+\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &= \frac{1}{N} \sum_{k=1}^N  \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \cdot \mathrm{u}_\abf \cdot e^{sign(a_k) \beta f(N_k)}
 \label{Eq:only-need-to-replace-T-now}
 \end{align}
-\\ \noindent In Eq. (\ref{Eq:only-need-to-replace-T-now}) we can replace the element of the transition matrix $\T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})}$ by using the following: 
-\begin{equation}
-\T_{(\bar{\abf}_k, \abf_{-k}),(\abf_k, \abf_{-k})} = \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf_k) \beta f(N_k)}} 
+\\ \noindent In Eq. (\ref{Eq:only-need-to-replace-T-now}) we can replace the element of the transition matrix $\mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})}$ with,
+\begin{equation}
+\mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} = \frac{1}{1 + \displaystyle e^{\mathit{sign}(a_k) \beta f(N_k)}} 
 \label{Eq:transition-matrix-T-symm-2-stgs}
@@
 \begin{align}
-\sum_{\bbf \neq \abf} \T_{\bbf, \abf} \ubf_{\bbf} &= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\abf_k) \beta f(N_k)}} \cdot  e^{sign(\abf_k) \beta f(N_k)} \\[10pt]
-&= \frac{\ubf_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{\abf}_k) \beta f(N_k)}}  \\[10pt]
-&= \ubf_\abf - \ubf_\abf \T_{\abf,\abf}
+\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &= \frac{\mathrm{u}_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(a_k) \beta f(N_k)}} \cdot  e^{sign(a_k) \beta f(N_k)} \\[10pt]
+&= \frac{\mathrm{u}_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{a}_k) \beta f(N_k)}}  \\[10pt]
+&= \mathrm{u}_\abf - \mathrm{u}_\abf \mathrm{T}_{\abf,\abf}
 \end{align}
@@
 \ref{Eq:stationary-dist-symm-2-stgs-state}.
-Two distinct states $\abf, \abf'$ having the same number of cooperators (i.e., $\mathcal{C}(\abf') = \mathcal{C}(\abf)$), have the same stationary distribution probability (i.e., $\ubf_{\abf'} = \ubf_{\abf}$).
+Two distinct states $\abf, \abf'$ having the same number of cooperators (i.e., $\mathcal{C}(\abf') = \mathcal{C}(\abf)$), have the same stationary distribution probability (i.e., $\mathrm{u}_{\abf'} = \mathrm{u}_{\abf}$).
 \\ \\ 
@@
 As argued before, all of these states are identical and are also equiprobable in the stationary distribution.
-Therefore, the stationary distribution probability of having $k$, $\C$ players, $\ubf_{k}$, is,
-\begin{equation}
-\ubf_{k} = \sum_{\mathcal{C(\abf)} = k} \ubf_\abf = \frac{1}{\Gamma} {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)} \\[10pt]
+Therefore, the stationary distribution probability of having $k$, $\C$ players, $\mathrm{u}_{k}$, is,
+\begin{equation}
+\mathrm{u}_{k} = \sum_{\mathcal{C(\abf)} = k} \mathrm{u}_\abf = \frac{1}{\Gamma} {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)} \\[10pt]
 \end{equation} 
@@
 \textbf{Introspection dynamics in a symmetric linear public goods game.}
-The stationary distribution of the introspection dynamics for a linear public goods game with all identical players is shown in this figure.
+The stationary distribution of introspection dynamics for a linear public goods game with all identical players is shown in this figure.
 For all the panels in this figure, we use the following parameters: $N = 4$ (group size), $b = 2$ (benefit provided to the public good upon cooperation), $c = 1$ (cost of cooperation) a) Here we show the frequency of each state in the stationary distribution of introspection dynamics.
@@
 The results are shown for different values of selection strength, $\beta = 1, 5$ and $100$.
-For high $\beta$, stationary distribution of the introspection dynamics reflects the rational play.
+For high $\beta$, stationary distribution of introspection dynamics reflects the rational play.
 In the long-run player play the Nash equilibrium.
@@
 For all panels, the benefit of cooperation generated by each player is worth 2 units.
-The selection strength of the introspection dynamics is $\beta = 5$ for all panels.}
+The selection strength of introspection dynamics is $\beta = 5$ for all panels.}
 \label{Fig:GPGG-symmetric}
@@
 In this example, players 1 and 2 are identical in all aspects while player 3 is asymmetric to them in only a single aspect.
-In here, we plot the average frequency with which players cooperate and reward cooperation after a long time (after $10^5$ time steps of a computer simulation).
+In here, we use Eq.
+(\ref{Eq:explicit-stationary-dist-representation}) to plot the exact probability with which the asymmetric players cooperate and reward cooperation after a long run of introspection.
 We consider three types of asymmetry for player 3.

### 2023-02-28 code/article_with_bf_notation.tex

--- 2023-02-27 latex/article.tex
@@
 At $\beta = 0$, players update to a randomly chosen strategy with probablity $0.5$.
-For $\beta > 0$, players update to the alternate strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
+For $\beta > 0$, players update to the alternative strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
 The probability that the chosen player does not update the action to a new action is then, \\ \\
@@
 \noindent In the previous example, the index of difference between the neighbouring states $(\C,\C,\C)$ and $(\C,\C,\D)$ is $3$.
-Using the above definitions, one can formally define the transition matrix of the introspection dynamics with:
+Using the above definitions, one can formally define the transition matrix of introspection dynamics with:
 
@@
 \noindent The transition matrix is a row stochastic matrix (the sums of the rows are 1).
-This implies that the stationary distribution of $\T$: a left eigenvector of $\T$ corresponding to eigenvalue $1$, always exists.
+This implies that the stationary distribution of $\T$, a left eigenvector of $\T$ corresponding to eigenvalue $1$, always exists.
 The following proposition introduces a sufficient condition for the stationary distribution of $\T$ to be unique.
-\begin{Prop} When $\beta$ is finite, the transition matrix of the introspection dynamics has a unique stationary distribution. 
-\label{Prop:unique-stationary-dist}
-\end{Prop}
-\begin{proof}
+\\ \\
+\noindent When the selection strength, $\beta$ is finite, the transition matrix of introspection dynamics has a unique stationary distribution.
 A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
@@
 \noindent where $\mathbf{1}$ is the column vector with size same as $\ubf$ and has all elements as $1$.
-\end{proof}
+For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distribution of the processes are unique.
+\\ \\
+%\begin{Prop} When $\beta$ is finite, the transition matrix of the introspection dynamics has a unique stationary distribution. 
+%\label{Prop:unique-stationary-dist}
+%\end{Prop}
+%\begin{proof}
+%A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
+Since no state is isolated (i.e., every state belongs in the neighbourhood set of another state) and there are only finitely many states of the game, every state is reachable in a finite number of steps from any starting point with non-zero probability.
+The transition matrix, $\T$, is therefore primitive for a finite $\beta$.
+By the Perron-Frobenius theorem, a primitive matrix, $\T$ will have a unique and strictly positive stationary distribution $\ubf := (\ubf_\abf)_{\abf \in \A}$ which satisfies the conditions:
+%\begin{eqnarray}
+%\label{Eq:lefteigenvector}
+%\ubf \T &= \ubf \\ 
+%\label{Eq:normalizationcondition}
+%\ubf \mathbf{1} &= 1
+%\end{eqnarray}
+%\noindent where $\mathbf{1}$ is the column vector with size same as $\ubf$ and has all elements as $1$. 
+%\end{proof}
 \noindent The above equations only present an implicit representation of the stationary distribution $\ubf$.
 The stationary distribution can be explictly calculated by the following expression (which is derived using Eq.
-(\ref{Eq:lefteigenvector}) and (\ref{Eq:normalizationcondition}) as:
+(\ref{Eq:lefteigenvector}) and (\ref{Eq:normalizationcondition})) as:
 \begin{equation}
@@
 where $\mathbf{U}$ is a square matrix of the same size as $\T$ with all elements equal to 1 and $\mathbb{1}$ is the identity matrix.
-For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distribution of the processes are unique.
-\\
+The matrix $\mathbb{1} + \mathbf{U} - \T$ is invertible when $\T$ is a primitive matrix \cite{Couto:NJP:2022}.
+Using Eq.
+(\ref{Eq:explicit-stationary-dist-representation}) one can compute the stationary distribution of introspection dynamics for any normal form game (with arbitrary number of asymmetric players).\\
 
@@
 \section*{Additive games and their properties under introspection dynamics}
-In this section we discuss the stationary properties of the introspection dynamics when players learn to play strategies in a special class of games: the additive games \cite{McAvoy:PlosCB:2015, Pena:JTB:2014}.
+In this section we discuss the stationary properties of introspection dynamics when players learn to play strategies in a special class of games: additive games \cite{McAvoy:PlosCB:2015, Pena:JTB:2014}.
 In an additive game, the payoff difference that a player earns by making a unilateral switch in their actions is independent of what their co-players play.
@@
  \begin{Prop}
-When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of the introspection dynamics for the N-player additive game is given by: 
+When $\beta$ is finite, the unique stationary distribution, $\ubf = (\ubf_\abf)_{\abf \in \A}$, of introspection dynamics for the N-player additive game is given by: 
 \begin{equation}
@@
 \end{equation}
-where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play from $\abf_j$  to $a'$.
+where, $f_j(a', \abf_j)$ is the co-player independent payoff difference given by Eq. (\ref{Eq:coplayer-independent-payoffdiff}).
+
 \label{Th:additive-games-stationary-dist}
@@
 \begin{Prop}
-Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of the introspection dynamics with finite $\beta$ for the N-player additive game.
+Let $\ubf = (\ubf_\abf)_{\abf \in \A}$ be the unique stationary distribution of introspection dynamics with finite $\beta$ for the N-player additive game.
 Then, $\ubf_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$.
@@
 \end{equation}
-\noindent where, $f_j(a', \abf_j) = \pi_j(a', \qbf) - \pi_j(\abf_j, \qbf)$ is the co-player independent payoff difference that $j$  earns in an additive game when they unilaterally switch their play from $\abf_j$ to $a'$.
+\noindent where, $f_j(a', \abf_j)$ is the co-player independent payoff difference given by Eq. (\ref{Eq:coplayer-independent-payoffdiff}).
 \label{Th:additive-game-product-of-marginals}
 \end{Prop}
-\noindent The above proposition states that for additive games, the stationary distribution of the introspection dynamics can be factorized into its corresponding marginals.
+\noindent The above proposition states that for additive games, the stationary distribution of introspection dynamics can be factorized into its corresponding marginals.
 In the long run, the probability that players play the state ($\abf_1, \abf_2, ...,\abf_N$) is the product of the cumulative probabilities that player 1 plays $\abf_1$, player 2 plays $\abf_2$ and so on.
-For a proof, please see Appendix.
 This property of the additive game was already shown for the simple two-player, two-action donation game in Couto et al.
@@
 While this factorizing property of the stationary distribution appears for additive games, we do not show that this property is unique to additive games.
-In the next section we use the well-studied example of the linear public goods game to demonstrate the stationary properties of the introspection dynamics in additive games.
+In the next section we use the well-studied example of the linear public goods game to demonstrate the stationary properties of introspection dynamics in additive games.
 
@@
 \label{prop:stationary-dist-lpgg}
-When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for a $N-$player linear public goods game is given by: 
+When $\beta$ is finite, the unique stationary distribution of introspection dynamics for a $N-$player linear public goods game is given by: 
 \\
@@
 \end{equation}
-
-\noindent 
-The stationary distribution of a two-action symmetric game under introspection dynamics can be explictly computed using the following proposition,
+\\
+\noindent The stationary distribution of a two-action symmetric game under introspection dynamics can be explictly computed using the following proposition,
 
@@
 \label{Prop:Symmetric-2-strategies-state}
-When $\beta$ is finite, the unique stationary distribution of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\ubf_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
+When $\beta$ is finite, the unique stationary distribution of introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\ubf_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
 \begin{equation}
@@
 \end{equation}
-where $f(j) := \pi^\D(j) - \pi^\C(j)$ is the payoff difference earned by switching the play from $\D$ and $\C$ when there are $j$ co-players playing $\C$.
-The term $\Gamma$ is the normalization factor given by:
+where $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}). The term $\Gamma$ is the normalization factor given by:
 \begin{equation}
@@
 \label{Lemma: Symmetric-2-stg}
-When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of the introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
+When $\beta$ is finite, the unique stationary distribution, $(\ubf_k)_{k \in \{0,1,...,N\}}$, of introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
 \begin{equation}
@@
 \end{equation} \\ 
-where, $k$ represents the number of $\C$ players in the state and $f(j) := \pi^\D(j) - \pi^\C(j)$ is the payoff difference earned by switching the play $\D$ and $\C$ when there are $j$ co-players playing $\C$.
-The term $\Gamma$ is the normalization factor, given by, \\
+where, $k$ represents the number of $\C$ players in the state and $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}). The term $\Gamma$ is the normalization factor, given by, \\
 \begin{equation}
@@
 \noindent 
-We also study the introspection dynamics in general public goods game with asymmetric players.
+We also study introspection dynamics in general public goods game with asymmetric players.
 We use the same setup that we used for studying the linear public goods with three asymmetric players.
@@
 \textbf{Proof of Proposition} \ref{Th:additive-games-stationary-dist} \\ \\ 
-Since $\beta$ is finite,the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the process is unique by Proposition \ref{Prop:unique-stationary-dist}.
+Since $\beta$ is finite,the stationary distribution $\ubf = (\ubf_\abf)_{\abf \in \A}$ of the process is unique.
 The stationary distribution also satisfies the equalities in Eq.
@@
 \\ \\
-\noindent Using Proposition \ref{Prop:unique-stationary-dist}, we can confirm that since $\beta$ is finite, the process will have a unique stationary distribution.
+\noindent Again, since $\beta$ is finite, the process will have a unique stationary distribution.
 Before continuing with the rest of the proof where we show that our candidate stationary distribution is \emph{the} unique stationary distribution, we define the following short-cut notations for the ease of the proof:
@@
 (\ref{Eq:normalizationcondition}) and for any state $\abf$, $\ubf_{\abf}$ is between 0 and 1.
-Moreover, since $\beta$ is finite, by Proposition \ref{Prop:unique-stationary-dist}, the process will have a unique stationary distribution.
+Again, since $\beta$ is finite the process will have a unique stationary distribution.
 Again, to show that the candidate stationary distribution is the unique stationary distribution, we need to check if Eq.

### 2023-02-28 latex/article.tex
end of day Tuesday. Need to revise Applications and proof read once more and check marta stuff

@@
 %-----SP ABSTRACT-----%
-Social interactions are often modelled using simultaneous games.
-The simplest model involves two identical players.
-However, interactions in everyday life are complex and often involve more than two individuals that differ between themselves.
-Such interactions can be captured more realistically using asymmetric multiplayer games.
-Over the years, learning models and models from evolutionary game theory have studied how players may learn to play strategically in these games.
-Recently, introspection dynamics has proven to be a useful learning model for tackling complex games.
-In this dynamics, players compare their current strategy to an alternative strategy.
-If the update results in a payoff advantage, it is more likely adopted.
-This dynamics provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (the stationary distribution).
-In this paper, we extend some of the previous analytical results of introspection dynamics on games with two-players to games with more players.
-We obtain analytical expressions of the stationary distribution for multiplayer asymmetric games that have the special property of being additive in the payoffs.
-In such games, the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions that their co-players play.
-In addition, we derive the stationary distribution for symmetric multiplayer games with two strategies.
-We discuss several classical games like the general public goods game to illustrate our results.
+Evolutionary game theory and learning models have contributed to the understanding of social interactions and how individuals may learn to act strategically.
+The simplest models involve two identical players.
+However, many interactions in everyday life are often complex, occurring among more than two individuals that differ between themselves.
+Such interactions can be captured by asymmetric multiplayer games.
+Recently, introspection dynamics has proven to be a useful learning model for tackling asymmetric games.
+In this dynamics, at each time step, players compare their current strategy to an alternative strategy.
+If the update results in a payoff advantage, the new strategy is more likely adopted.
+This model provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (i.e., the stationary distribution).
+In this paper, we extend some of the previous results of introspection dynamics on 2-player asymmetric games to games with multiple players.
+First, we derive a general explicit formula that allows us to numerically compute the stationary distribution of any multiplayer asymmetric game.
+Second, we obtain analytical expressions of the stationary distribution for two special cases, i) additive games (where the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions of their co-players), and ii) symmetric multiplayer games with two strategies.
+Finally, we revisit several classical games like the general public goods game to illustrate our results.
 
@@
 In the state $(a_i, \abf_{-i})$, player $i$ plays the action $a_i \in \A_i$ and their co-players play the action $\abf_{-i} \in \A_{-i}$ where $\A_{-i}$ is defined as $\A_{-i}:= \prod_{j \neq i} \A_j$.
-The payoff of a player depends on the state of the game.
 In this paper, we use bold font letters to denote vectors and matrices.
 We use the corresponding normal font letters with subscripts to denote elements of the vectors (or matrices).
+The payoff of a player depends on the state of the game.
 We denote the payoff of player $i$ in the state $\abf$ with $\pi_i(\abf)$ or $\pi_i(a_i, \abf_{-i})$.
@@
 For $\beta > 0$, players update to the alternative strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
-The probability that the chosen player does not update the action to a new action is then, \\ \\
+\\ \\
 \noindent Introspection dynamics can be studied by analyzing properties of the transition matrix, $\T$ of the resulting dynamical process.
@@
 In order to formally define the transition matrix, we first need to introduce some notations and definitions.
-We define the neighbourhood set of $\abf$ as the following:
+We start by defining the neighbourhood set of $\abf$ as,
 
@@
 \noindent where $\mathbf{1}$ is the column vector with size same as $\ubf$ and has all elements as $1$.
-For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distribution of the processes are unique.
+For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distributions of the processes are unique.
 \\ \\
@@
 Using Eq.
-(\ref{Eq:explicit-stationary-dist-representation}) one can compute the stationary distribution of introspection dynamics for any normal form game (with arbitrary number of asymmetric players).\\
+(\ref{Eq:explicit-stationary-dist-representation}) one can compute the unique stationary distribution of (a finite $\beta$-) introspection dynamics for any normal form game (with arbitrary number of asymmetric players).\\
 
@@
 Using the stationary distribution, one can calculate the marginal probabilities corresponding to each player's actions.
-For example, the probability that player $i$ plays action $a \in \A_i$ in the long run, $\xi_{i,a}$, can be computed as,
+That is, the probability that player $i$ plays action $a \in \A_i$ in the long run, $\xi_{i,a}$, can be computed as,
 \begin{equation}
@@
 In the literature, this property is sometimes called the property of \emph{equal gains from switching} \cite{Pena:JTB:2014}.
-For games with this property, the stationary distribution of introspection dynamics takes a simple form;
+For games with this property, the stationary distribution of introspection dynamics takes a simple form,
 
@@
 \end{Prop}
-\noindent For any finite value of the selection strength parameter, $\beta$, the stationary distribution of the process for an additive game can be exactly computed using the expression in Eq.
-(\ref{Eq:additive-game-stationary-distribution}).
-For a proof of the propositions and corollaries, please see Appendix.
+\noindent For a proof of the Propositions and Corollaries, please see Appendix.
 Using the stationary distribution, one can also exactly compute the cumulative probabilities with which players play their actions in the long run (i.e., the marginal distribution) using Eq.
@@
 In this regard, introspection learning in additive games is particularly interesting.
-The stationary distribution and the marginal distributions of introspection learning in additive games are related in a special way,
+The stationary distribution and the marginal distributions of introspection dynamics in additive games are related in a special way,
 
@@
 
-\noindent where the marginal probability, $\xi_{j,a_j}$, is the cumulative probability that player $j$ plays $a_j$ at the stationary distribution.
-The marginal probability for the $N$-player additive game is given by:
+\noindent where the marginal probability, $\xi_{j,a_j}$, is the cumulative probability that player $j$ plays $a_j$ at the stationary distribution. For the $N$-player additive game, this is given by,
 
@@
 \cite{Couto:NJP:2022}.
-Here we extend that result for any number of players, each having an arbitrary number of strategies.
-In the next section we use the well-studied example of the linear public goods game to demonstrate the stationary properties of introspection dynamics in additive games.
+Here we extend that result for any additive game with arbitrary number of players, each having an arbitrary number of strategies.
+In the next section we use the well-studied example of the linear public goods game (an additive game) to illustrate these results.
 
@@
 The players differ in their cost of cooperation and the benefit they provide by contributing to the public good.
-We denote the cost of cooperation for player $i$ and the benefit that they provide to the public good by $c_i$ and $b_i$ respectively.
+We denote the cost of cooperation for player $i$ and the benefit that they provide by $c_i$ and $b_i$ respectively.
 We define an indicator function $\alpha(.)$ to map the action of cooperation to 1 and the action of defection to 0.
@@
 For player 1 and 2, the cost of cooperation is 1 unit ($c_1 = c_2 = 1$) while for the third player, the cost is slightly higher at 1.5 units ($c_3 = 1.5$).
-In the stationary distribution of the process with selection strength $\beta = 1$, the state where player 1 and 2 play $\C$ and player 3 plays $\D$, $\mathrm{u}_{\C\C\D}$, occurs with probability $\approx 0.121$ (rounded up to three decimal places).
-We calculate this probability exactly with Eq.
-(\ref{Eq:stationary_dist_lpgg}).
-The marginal probabilities that in the long run player 1 (or player 2) plays cooperation and player 3 plays defection are 0.417 and 0.697 respectively.
-That is, $\xi_{1,\C} = \xi_{2,\C} \approx 0.417$ and $\xi_{3,\D} \approx 0.697$ (rounded up to a three decimal places).
-With the exact values (and also with the approximations here), one can confirm the factorizing property of the stationary distribution for additive games in this example (i.e., Proposition \ref{Th:additive-game-product-of-marginals}).
-That is, $\mathrm{u}_{\C\C\D} = \xi_{1,\C} \cdot \xi_{2,\C} \cdot \xi_{3,\D}$.
-\\ \\
-\noindent First, we analyze the simplest case of the linear public goods game in which all players are symmetric to each other.
-We consider a game with 4 players.
-All players have the same cost of cooperation ($c_i = c$) and they all provide the same benefit to the public good ($b_i = b$).
+In the stationary distribution of the process with selection strength $\beta = 1$, the cumulative probability that player 1 (or 2) cooperates and player 3 defects are $\xi_{1,\C} = \xi_{2,\C}= 0.417$ and $\xi_{3,\D} = 0.697$ respectively.
+With the exact values, one can confirm the factorizing property of the stationary distribution for additive games in this example (i.e., Proposition \ref{Th:additive-game-product-of-marginals}).
+That is, $\mathrm{u}_{\C\C\D} = 0.121 = \xi_{1,\C} \cdot \xi_{2,\C} \cdot \xi_{3,\D}$.
+\\ \\
+\noindent We use the Eq.
+(\ref{Eq:stationary_dist_lpgg}) to analyze the stationary behaviour of players after a long run of introspection in a linear public goods game (LPGG).
+First, we study the simplest case where all players are symmetric (the cost and benefit for all the 4 players are $c$ and $b$).
 Since all players are identical, the states of the game can be enumerated by counting the number of cooperators in the state.
 There can only be 5 distinct states of the game (from 0 to 4 cooperators).
-In this case, one can show with Eq.
-(\ref{Eq:stationary_dist_lpgg}) that, between the states with $k$ and $k+1$ cooperators, the stationary distribution changes by a factor of $(k+1)/(4-k) \cdot \mathrm{exp}(\beta f_j(\D,\C))$.
 When the parameters of the game are such that defection dominates cooperation ($b = 2, c = 1$, Fig.
@@
 \ref{Fig:LPGG-symmetric}b).
-Naturally, $\beta$ plays an important role in determining the overall cooperation frequncy in the game.
-When $\beta$ is low, the average cooperation frequency varies weakly with the strength of the dilemma, $b/N - c$ (Fig.
+Since every possible state is equiprobable in the limit of $\beta \to 0$, the outcome with $2$ cooperators is most likely only because there are more states with 2 cooperators than states with any other number of cooperators.
+\\ \\
+\noindent Naturally, $\beta$ plays an important role in determining the overall cooperation in the long run.
+When $\beta$ is low, average cooperation varies weakly with the strength of the dilemma, $b/N - c$ (Fig.
 \ref{Fig:LPGG-symmetric}c).
-Even when the temptation to defect is high ($b/N - c \approx -2$), players cooperate with a non-zero probability in the long run ($\approx 0.1$).
-Similarly, when cooperation is highly beneficial and strictly dominates defection ($b/N - c \approx 2$), players defect with a non-zero probability ($\approx 0.1$).
-At higher values of $\beta$, the stationary behaviour of players is more responsive to the payoffs and thus reflects an abrupt change around the parameter region where the game transitions from defection-dominating to cooperation-dominating ($b/N - c = 0$).
+Even when the temptation to defect is high ($b/N - c = -2$), players cooperate with a non-zero probability.
+Similarly, when cooperation is highly beneficial and strictly dominates defection ($b/N - c = 2$), players defect sometimes.
+At higher values of $\beta$, the stationary behaviour of players is more responsive to the payoffs and thus reflects an abrupt change near the parameters where the game transitions from defection-dominating to cooperation-dominating ($b/N - c = 0$).
 \\ \\
 \noindent 
-For studying the asymmetric linear public goods game, we consider a setup with 3 players.
+To study what effects might appear due to asymmetry in the LPGG, we consider the game with 3 asymmetric players.
 All the players can differ in their cost of cooperation and the benefit they provide to the public goods.
@@
 For player 1, the cost and benefit are $1 + \delta_c$ and $2 + \delta_b$ respectively while for player 3, the cost and benefit are $1 - \delta_c$ and $2 - \delta_b$, respectively.
-First, we study a simple case in which players only differ in their cost of cooperation ($\delta_b = 0$ and $\delta_c = 0.5$, Fig \ref{Fig:LPGG-asymmetric}a, left).
-In the long run, the relative cooperation frequency of players reflect their relative ability to cooperate.
+The terms $\delta_b$ and $\delta_c$ represents the strength of asymmetry between the three players (a higher absolute value of $\delta$ indicating a bigger asymmetry).
+When the players only differ in their cost of cooperation ($\delta_b = 0$ and $\delta_c = 0.5$, Fig \ref{Fig:LPGG-asymmetric}a, left), their relative cooperation in the long run reflects their relative ability to cooperate.
 The player with the lowest cooperation cost (player 3), cooperates with the highest probability (and \emph{vice-versa},  Fig \ref{Fig:LPGG-asymmetric}a, right).
-Similarly, when players only differ in their ability to produce the public good ($\delta_b = 1$ and $\delta_c = 0$, Fig \ref{Fig:LPGG-asymmetric}b left), their relative cooperation in the long run reflects the relative benefits they provide with their cooperation.
-The player with the highest benefit value (player 1) cooperates with the highest probability (Fig \ref{Fig:LPGG-asymmetric}b, right).
-For this particular setup with three asymmetric players, defection dominates cooperation for player 1 if and only if $\delta_b < 1 + 3\delta_c$ .
-For player 3, defection dominates cooperation only when $\delta_b > 3\delta_c - 1$.
-For the parameter values $b = 2, c = 1$, defection always dominates cooperation for the reference player.
+Similarly, when players only differ in their ability to produce the public good ($\delta_b = 1$ and $\delta_c = 0$, Fig \ref{Fig:LPGG-asymmetric}b left), their relative cooperation in the long run reflects the relative benefits they provide with their cooperation (Fig \ref{Fig:LPGG-asymmetric}b, right).
+In this example, if we consider that the reference player provides a benefit of 2 units and has a cost of 1 unit (in which case, defection always dominates cooperation for them), defection dominates cooperation for player 1 if and only if $\delta_b < 1 + 3\delta_c$ and for player 3 only when $\delta_b > 3\delta_c - 1$.
 These regions in the $\delta_b-\delta_c$ parameter plane that correspond to defection dominating cooperation are circumscribed by white dashed lines in Fig.
@@
 This includes the case where players are symmetric ($\delta_b = \delta_c = 0$).
-A relatively high cooperation frequency is only assured if players are aligned in their asymmetries (i.e., either $\delta_b < 3\delta_c +1$ or $\delta_b > 3\delta_c - 1$).
-Or, in other words, if the player that has low cost of cooperation also provides a high benefit upon contribution, then cooperation frequencies are high in the long-run.
+A relatively high cooperation is only assured if players are aligned in their asymmetries (i.e., either $\delta_b < 3\delta_c +1$ or $\delta_b > 3\delta_c - 1$).
+Or, in other words, if the player that has low cost of cooperation also provides a high benefit upon contribution, then cooperation is high in the long-run.
 
@@
 
-\noindent From the previous section, we adopt the indicator function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to 0, and the notation $\mathcal{C}(\abf)$ to denote the number of cooperators in the state $\abf$.
+%\noindent From the previous section, we adopt the indicator function $\alpha(.)$ that maps the action $\C$ to 1 and the action $\D$ to 0, and the notation $\mathcal{C}(\abf)$ to denote the number of cooperators in the state $\abf$.
 That is,
-
-\begin{equation}
-\mathcal{C}(\abf) := \sum_{j=1}^N \alpha(a_j)
-\end{equation}
-\\
+%
+%\begin{equation}
+%\mathcal{C}(\abf) := \sum_{j=1}^N \alpha(a_j)
+%\end{equation}
+%\\
 \noindent The stationary distribution of a two-action symmetric game under introspection dynamics can be explictly computed using the following proposition,
@@
 \end{equation}
-where $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}). The term $\Gamma$ is the normalization factor given by:
+where $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}) and $\mathcal{C}(\abf)$ is the number of cooperators in state $\abf$. The term $\Gamma$ is the normalization factor given by:
 \begin{equation}
@@
 \end{Corollary}
-\noindent The above lemma follows directly from Proposition \ref{Prop:Symmetric-2-strategies-state}.
+\noindent The above corollary follows directly from Proposition \ref{Prop:Symmetric-2-strategies-state}.
 The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$, $\C$ players (and therefore $N-k$, $\D$ players).
 This count is simply the binomal coefficient $N \choose k$.
-In the next section, we study the stationary behaviour of introspection dynamics in a two-action general game with an example.
-To this end, we use the example of a non-linear public goods game to demonstrate the results.
+In the next section, we use the example of a non-linear public goods game to illustrate these results.
 
@@
 \cite{Hauert:JTB:2006a}.
-This framework introduces a normal form game with symmetric players.
+In the original paper, the authors propose a normal form game with symmetric players.
 The game's properties are determined by a parameter $w$ that determines the nature of the public good.
 The players have two actions: cooperation, $\C$ and defection, $\D$.
-In Hauert et al., authors introduce a symmetric public goods game.
 Here, we extend their framework to account for players with asymmetric payoffs.
@@
 Every additional cooperator's contribution is as valuable as the benefit that they can generate.
-When $w < 1$, the effective contribution of every new cooperator goes down by a factor of $w$ (compared to the last cooperator).
+When $w < 1$, the effective contribution of every new cooperator goes down by a factor, $w$ (compared to the last cooperator).
 The public goods is said to be discounting in this case.
 On the other hand when $w > 1$, every new contributor is more valuable than the previous one.
-These public goods are called synergistic.
-For the symmetric case, the relationship between the cost to benefit ratio, $cN/b$, and the discount/synergy factor, $w$, determines the type of social dilemma arising from this general public goods game.
-In principle, this framework can produce generalizations of the prisoner's dilemma (defection dominating cooperation), the snowdrift game (no dominance but coexistence under the replicator dynamics), the stag-hunt game (no dominance but existence of an internal equilibrium that is unstable under the replicator dynamics) and the harmony game (cooperation dominating defection) with respect to its evolutionary trajectories.
+The public good is said to be synergistic in this case.
+For the symmetric case, the relationship between the cost to benefit ratio, $cN/b$, and the discount/synergy factor, $w$, determines the type of social dilemma arising from the game.
+In principle, this framework can produce generalizations of the prisoner's dilemma ($\D$ dominating $\C$), the snowdrift game (coexistence between $\C$ and $\D$), the stag-hunt game (no dominance but existence of an internal unstable equilibrium) and the harmony game ($\C$ dominating $\D$) with respect to its evolutionary trajectories under the replicator dynamics.
 For more details see Hauert et al.
 \cite{Hauert:JTB:2006a}.
-We study the long term stationary behaviour of players in this game when they learn through introspection dynamics.
 \\
@@
 The benefit that they can generate for the public good is $b_i$.
-However, the benefit of cooperation generated by a player is either synergized (or discounted) by a factor depending on the number of cooperators already in the group and the synergy/discount factor, $w$ (just like the original model).
+The benefit of cooperation generated by a player is either synergized (or discounted) by a factor depending on the number of cooperators already in the group and the synergy/discount factor, $w$ (just like the original model).
 However, now, since players are asymmetric it is not entirely clear in which order the contributions of cooperators should be discounted (or synergized).
@@
 \end{align} \\
-\noindent where $\mathcal{C}(a,\abf_{-i})$ is the number of cooperators in the state $(a,\abf_{-i})$ and $\alpha(.)$ is the indicator function that maps the actions $\C$ and $\D$ to 1 and 0 respectively.
+\noindent where $\mathcal{C}(a,\abf_{-i})$ counts the number of cooperators in state $(a,\abf_{-i})$ and $\alpha(.)$ maps the actions $\C$ and $\D$ to 1 and 0 respectively.
 Note that the number of cooperators in the two states are related as: $\mathcal{C}(\D,\abf_{-i}) = \mathcal{C}(\C,\abf_{-i}) - 1$.
-In the following, we discuss results from the symmetric public goods game and then discuss results for the game with asymmetric players.\\
-
-\noindent To compute the stationary distribution of introspection dynamics in a symmetric (general) public goods game (PG), we use the closed for expression in Eq.
+We are interested in studying the long term stationary behaviour of players in this game when they learn through introspection.
+We first discuss results from the symmetric public goods game and then discuss results for the game with asymmetric players.\\
+
+\noindent To compute the stationary distribution of introspection dynamics in this game, we use Eq.
 (\ref{Eq:stationary-dist-symm-2-stgs}).
-We consider that every player in a 4-player game can generate a benefit $b$ of value $2$.
-Before exploring the $c-w-N$ parameter space, we study four specific cases.
+In our symmetric example, we consider that every player in a $N-$player game can generate a benefit $b$ of value $2$.
+Before exploring the $c-w-N$ parameter space, we study four specific cases (with a 4 player game).
 In two of these cases, the public goods is discounted ($w = 0.5$, Fig.
@@
 \ref{Fig:GPGG-symmetric}a right panels).
-For each case, we consider two sub-cases: one, in which cost is high ($c = 1$,  Fig.
-\ref{Fig:GPGG-symmetric}a top panels) and two, when cost is low ($c = 0.2$, Fig.
+For each case, we consider two sub-cases: first, in which cost is high ($c = 1$,  Fig.
+\ref{Fig:GPGG-symmetric}a top panels) and second, when cost is low ($c = 0.2$, Fig.
 \ref{Fig:GPGG-symmetric}a bottom panels).
-The four parameter combinations are chosen such that each of them represents a unique social dilemma under the replicator dynamics.
-When the PG is discounted ($w = 0.5$) and costs are high ($c = 1$) defection dominates cooperation (like the prisoner's dilemma).
+The four parameter combinations are chosen such that each of them corresponds to a unique social dilemma under the replicator dynamics.
+%When the PG is discounted ($w = 0.5$) and costs are high ($c = 1$) defection dominates cooperation (like the prisoner's dilemma).
 When the PG is discounted ($w = 0.5$) but costs are low ($c = 0.2$), the there is stable coexistence between cooperators and defectors under the replicator dynamics just like the snowdrift game.
@@
 \ref{Fig:GPGG-symmetric}a).
-As selection strength is intermediate ($\beta = 5$), in some cases, players learn to play actions that are not optimal for the dilemma with non-zero probability.
-For example, even when the parameters of the game make cooperation to be the dominated strategy, there is a single cooperator in the group with a sizeable chance ($\approx 20\%$) in the long run.
-When the parameters of the game reflect the stag-hunt dilemma, players are more likely to coordinate their actions in the long run.
+When selection strength is intermediate ($\beta = 5$), players sometimes play actions that are not optimal for the dilemma.
+For example, even when the parameters of the game make cooperation to be the dominated strategy ($w = 0.5, c = 1$), there is a single cooperator in the group in 20 $\%$ of the cases.
+When the parameters of the game reflect the stag-hunt dilemma ($c = 1, w = 1.5$), players are more likely to coordinate their actions in the long run.
 In the long-run, the probabilities that the whole group plays $\C$ or $\D$ is higher than the probabilities that there is a group with a mixture of $\C$ and $\D$ players.
-In contrast, when the parameters reflect the snowdrift game, we get the opposite effect.
+In contrast, when the parameters reflect the snowdrift game ($w = 0.5, c = 0.5$), we get the opposite effect.
 In the long run, mixed groups are more likely than homogeneous groups.
-In fact, the group with exactly 2 cooperators and 2 defectors is the most likely outcome in the long run.
-Finally, when the parameters of the game make defection the dominated action, all players in the group learn to cooperate in the long run.
+Finally, when the parameters of the game make defection the dominated action ($w = 1.5, c = 0.2$), all players learn to cooperate in the long run.
 \\ \\
@@
 First, let us consider the case when the group size is fixed at 4 players (the $c-w$ plane in Fig\ref{Fig:GPGG-symmetric}b).
-In that case if the cost of cooperation is too high, the average cooperation rate is negligible and does not change with the change in the nature of the public good.
-When the cost is not restrictively high, the discount/synergy parameter, $w$, determines the frequency with which players cooperate in the long run.
-A high $w$ for the public good would result in high cooperation in the long run (and \emph{vice-versa}).
-Next we consider the case where the cost of cooperation is fixed (the $N-w$ plane in Fig.
+In that case, if the cost of cooperation is restrictively high, the average cooperation rate is negligible and does not change with the change in the nature of the public good.
+In contrary, when the cost is not restrictively high, the discount/synergy parameter, $w$, determines the frequency with which players cooperate in the long run.
+A higher $w$ for the public good would result in higher cooperation (and \emph{vice-versa}).
+Next, we consider the case where the cost of cooperation is fixed (the $N-w$ plane in Fig.
 \ref{Fig:GPGG-symmetric}b).
-It is fixed to a value such that in a synergistic PG ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size.
+The cost is fixed to a value such that in a synergistic PG ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size.
 In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run.
-When the public good is discounted ($w < 1$), cooperation rates fall with larger group sizes.\\ \\
+In discounted public goods, cooperation rates fall with increase in group sizes.\\ \\
 \noindent 
-We also study introspection dynamics in general public goods game with asymmetric players.
-We use the same setup that we used for studying the linear public goods with three asymmetric players.
+We also study introspection dynamics in this game with asymmetric players.
+We use the same setup that we used for studying the asymmetric linear public goods.
 The average frequency of cooperation per player is summarized in Supplementary Figures 1 and 2.
-First, we study two cases, one in which the public good is synergistic ($w > 1$, and players have a high average cost) and two in which public good is discounted (and players have a lower average cost).
+In Supplementary Figure 1, we study two cases, first in which the public good is synergistic ($w > 1$, and players have a high average cost) and second in which public good is discounted (and players have a lower average cost).
 In both of these cases, players cooperate highly when they simultaneously have low cost and high benefit.

### 2023-03-01 latex/article.tex
Marta stuff added. Ready to be printed to review between us

@@
 \section*{Abstract}
+\section*{Abstract}
 
 % 150 to 250 words
-% 4 to 6 keywords: multiplayer games, asymmetric games, non-linear interactions, learning model, introspection dynamics, strategy abundance
-
-%-----SP ABSTRACT-----%
-Evolutionary game theory and learning models have contributed to the understanding of social interactions and how individuals may learn to act strategically.
-The simplest models involve two identical players.
+
+Evolutionary game theory and models of learning provide a powerful framework to describe strategic decision-making in social interactions. 
+In the simplest case, these models describe games among two identical players. 
+However, many interactions in everyday life are more complex. 
+They involve more than two players who may differ in their available actions and in their incentives to choose each action. 
+Such interactions can be captured by asymmetric multiplayer games. 
+Recently, introspection dynamics has been introduced to explore such asymmetric games. 
+According to this dynamics, at each time step players compare their current strategy to an alternative strategy. 
+If the alternative strategy results in a payoff advantage, it is more likely adopted. 
+This model provides a simple way to compute the players’ long-run probability of adopting each of their strategies. 
+In this paper, we extend some of the previous results of introspection dynamics for 2-player asymmetric games to games with arbitrarily many players. 
+First, we derive a formula that allows us to numerically compute the stationary distribution of introspection dynamics for any multiplayer asymmetric game. 
+Second, we obtain explicit expressions of the stationary distribution for two special cases.
+These cases are additive games (where the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions of their co-players), and symmetric multiplayer games with two strategies.
+To illustrate our results, we revisit several classical games such as the public goods game.\\
+
+% 4 to 6 keywords: multiplayer games, asymmetric games, non-linear interactions, learning model, introspection dynamics, strategy abundance, aditive games
+
+\noindent \textbf{Keywords}: multiplayer games, asymmetric games, non-linear interactions, introspection dynamics, strategy abundance, additive games.
+
+%Evolutionary game theory and learning models have contributed to the understanding of social interactions and how individuals learn to act strategically.
+%The simplest models involve two identical players.
 However, many interactions in everyday life are often complex, occurring among more than two individuals that differ between themselves.
 Such interactions can be captured by asymmetric multiplayer games.
-Recently, introspection dynamics has proven to be a useful learning model for tackling asymmetric games.
+%Recently, introspection dynamics has proven to be a useful learning model for tackling asymmetric games.
 In this dynamics, at each time step, players compare their current strategy to an alternative strategy.
@@
 This model provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (i.e., the stationary distribution).
-In this paper, we extend some of the previous results of introspection dynamics on 2-player asymmetric games to games with multiple players.
+%In this paper, we extend some of the previous results of introspection dynamics on 2-player asymmetric games to games with multiple players.
 First, we derive a general explicit formula that allows us to numerically compute the stationary distribution of any multiplayer asymmetric game.
@@
 Finally, we revisit several classical games like the general public goods game to illustrate our results.
+%%word count: 236
+
+%-----SP ABSTRACT-----%
+%Social interactions are often modelled using simultaneous games.
+The simplest model involves two identical players.
+However, interactions in everyday life are complex and often involve more than two individuals that differ between themselves.
+Such interactions can be captured more realistically using asymmetric multiplayer games.
+Over the years, learning models and models from evolutionary game theory have studied how players may learn to play strategically in these games.
+Recently, introspection dynamics has proven to be a useful learning model for tackling complex games.
+In this dynamics, players compare their current strategy to an alternative strategy.
+If the update results in a payoff advantage, it is more likely adopted.
+This dynamics provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (the stationary distribution).
+In this paper, we extend some of the previous analytical results of introspection dynamics on games with two-players to games with more players.
+We obtain analytical expressions of the stationary distribution for multiplayer asymmetric games that have the special property of being additive in the payoffs.
+In such games, the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions that their co-players play.
+In addition, we derive the stationary distribution for symmetric multiplayer games with two strategies.
+We discuss several classical games like the general public goods game to illustrate our results.
 
@@
 \end{comment}
+
 \newpage
@@
 % Pairwise vs Multiplayer Games
-The simplest form of social interaction occurs between two individuals.
-These pairwise interactions have been studied extensively \cite{Hofbauer:book:1998}.
-Despite their simplicity, they provide important insights, e.g., on how social species can maintain cooperation \cite{Axelrod:book:1984, Nowak:book:2011}.
-An ubiquitous example of a model game for two players is the prisoner's dilemma.
+Social behavior has been studied extensively through pairwise interactions \cite{Hofbauer:book:1998}.
+Despite their simplicity, they provide important insights, such as how populations can sustain cooperation \cite{Axelrod:book:1984, Nowak:Science:2006,  Nowak:book:2011}.
+%An ubiquitous example of a model game for two players is the prisoner's dilemma.
 Here, the two individuals have a temptation to cheat, but at the same time, players are better off if they help each other.
@@
 These studies provide several explanations for why one can expect cooperation in such interactions \cite{Nowak:Science:2006}.
-%some references
-\\ \\
-% non-linearity
-\noindent Yet, many interesting collective behaviors occur when multiple individuals interact simultaneously \cite{Palm:JMB:1984, Skyrms:book:2003, Pacheco:PRSB:2009, Archetti:EL:2011, Archetti:JTB:2012, Gokhale:DGAA:2014, Hilbe:JTB:2015, Venkateswaran:PRSB:2019}.
-Importantly, most of these situations cannot be captured by the sum of several pairwise interactions.
-Thus, to account for such non-linearities, we need to consider multiplayer games \cite{Gokhale:DGAA:2014}.
-One well-known effect that only emerges when more than two players are present is the ``second-order free-riding problem" \cite{Fowler:PNAS:2005}.
+Yet, many interesting collective behaviors occur when multiple individuals interact simultaneously \cite{Palm:JMB:1984, Skyrms:book:2003, Pacheco:PRSB:2009, Archetti:EL:2011, Archetti:JTB:2012, Gokhale:DGAA:2014, Hilbe:JTB:2015, Venkateswaran:PRSB:2019}.
+Most of these situations cannot be captured by the sum of several pairwise interactions.
+Thus, to account for such non-linearities, one needs to consider multiplayer games \cite{Gokhale:DGAA:2014}.
+A well-known effect that only emerges when more than two players are present is the ``second-order free-riding problem" \cite{Fowler:PNAS:2005}.
 A natural solution to maintain pro-social behavior in a community is to monitor and punish defectors (and/or reward cooperators).
@@
 As long as cooperation is incentivized by punishment (or rewards) of others, individuals can take advantage by defecting in this second-order dilemma.
-However, this tempts everyone to not engage in costly punishment (or rewarding).
-Cooperation can break down when there are not enough individuals punishing (or giving rewards).
-For this reason, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms or a suitable design \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.
+As such, this tempts everyone not to engage in costly punishment (or rewarding), and cooperation can break down.
+For this reason, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.
 \\ \\
@@
 In situations that require some sort of coordination and where expectations on others play an important role in one's decisions, a growing group size might hinder the optimal outcome \cite{Skyrms:book:2003}.
-Likewise, it has been shown that it is hard to cooperate in large groups for some conditions \cite{Santos:PNAS:2011, Hilbe:JTB:2015}.
+Likewise, it has been shown that it is hard to cooperate in large groups \cite{Santos:PNAS:2011, Hilbe:JTB:2015}.
 This is not a general effect, though.
 It can happen that adding more players actually promotes cooperation.
-In \cite{gokhale:JTB:2011}, authors investigate the 2-player and 3-player cases of a task allocation problem.
-Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, resulting in a decrease in freeloading.
+Gokhale and Traulsen (2011) investigate the 2-player and 3-player cases of a task allocation problem \cite{gokhale:JTB:2011}.
+Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, resulting in a decrease in free-riding.
 %As a biological example, consider a task allocation problem in a bacterial system.
@@
 With three players, the production of one of the enzymes increases while freeloading decreases, compared to the 2-player case.
-Additionally, not only the average group size can have an important effect, but also the variance of the group size distribution \cite{Pena:Evolution:2011, Broom:BMB:2019}.
+Additionally, interaction group size can vary in a population of players.
+There, not only the average group size can have an important effect, but also the variance of the group size distribution \cite{Pena:Evolution:2011, Broom:BMB:2019}.
 \\ \\ 
@@
 Thus, to fully characterise the state of the game, we only require to know the number of players playing each strategy.
-Conversely, in asymmetric games, players can be different in several ways.
-For example, players can have different types or roles, which can have consequences in the payoffs and strategies.
+Conversely, in asymmetric games, players can differ in their available actions and in their incentives to choose each action; players are of different types or roles.
 Therefore, they can have uneven effects on others' payoffs too.
-For example, in public goods games and collective-risk dilemmas, players can have different initial endowments (or wealth), productivitites, costs, risk perceptions, or risk exposures \cite{Milinski:CC:2011, Vasconcelos:PNAS:2014, Abouchakra:JTB:2014, Hauser:Nature:2019, Merhej:JAIR:2022}.
+For example, in public goods games and collective-risk dilemmas, players can have different initial endowments (or wealth), productivitites, costs, risk perceptions, or risk exposures \cite{Milinski:CC:2011, Vasconcelos:PNAS:2014, Abouchakra:JTB:2014, Hauser:Nature:2019, Merhej:JAIR:2022, Wang:PTRSB:2023}.
 Hence, to fully describe the state of the game, we need to know which of the players is doing what.
@@
 %meta communication; lit gap; our aim
-\noindent Due to these reasons, one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
+
+%\noindent Due to these reasons, one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
 Perhaps for that reason, there are not many studies on a general approach to multiplayer asymmetric games.
 As such, our aim here is to narrow that gap using introspection dynamics \cite{Couto:NJP:2022}.
-In the following section, we discuss several canonical frameworks from the literature that have been used to study both multiplayer games and asymmetric games.%, pointing out the gaps.
-
-%possibly new section \section*{Background} but then where to put "proposal"?
-
-\section*{Related Work}
+In the following section, we discuss several canonical frameworks from the literature that have been used to study both multiplayer games and asymmetric games.
+
+%\section*{Related Work}
 
@@
 % deterministic EGT
-From evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior.
-In evolutionary game theory, we assume a population of players and a mechanism by which strategies evolve over time.
+\noindent From evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior.
+%, in particular, in multiplayer and asymmetric games.
+%In evolutionary game theory, we assume a population of players and a mechanism by which strategies evolve over time.
 More successful strategies tend to persist in the population, either by genetic or cultural inheritance.
@@
 A (monomorphic) population playing an ESS cannot be invaded by mutants.
-The concept of ESS, originally proposed for parwise encounters, was already extended for multiplayer games \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}.
-Although suggestive of an evolutionary process, ESS does not really describe a dynamical system.
-In the more classical infinite population models (deterministic EGT), ordinary differential equations are the central mathematical tools \cite{Hofbauer:book:1998}.
-Among these the replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998} is the most popular model.
-Replicator equation has been widely used and easily comprises multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Pena:Evolution:2011, Cressman:PNAS:2014, Pena:JTB:2014}.
-More recently, also the replicator-mutator equation was applied to study the dynamics of multiplayer games \cite{Duong:DGAA:2020}.
+\noindent The concept of ``evolutionary stable strategy" (ESS), originally proposed for parwise encounters \cite{Maynard-Smith:Nature:1973}, was extended for multiplayer games \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}.
+Also the well-known replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998} easily comprises multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Pena:Evolution:2011, Cressman:PNAS:2014, Pena:JTB:2014}.
+More recently, the replicator-mutator equation was applied to study the dynamics of multiplayer games, too \cite{Duong:DGAA:2020}.
 As for asymmetric games, a few additional assumptions are needed.
@@
 The case of asymmetric games with more than two players is substantially less studied within deterministic EGT.
-Exceptions are  \cite{Gokhale:PRSB:2012, Zhang:arxiv:2022}.
+Gokhale and Traulsen (2012) and Zhang et al.
+(2022) are two exceptions \cite{Gokhale:PRSB:2012, Zhang:arxiv:2022}.
 Notably, although these works study multiplayer games, they consider, at most, two different types (drawn from two populations), which leaves out the exploration of full asymmetry.
@@
 % stochastic EGT
-\noindent To account for stochastic effects that are naturally present in finite populations, another set of tools was developed, known as stochastic evolutionary game dynamics.
-\cite{Nowak:Nature:2004, Traulsen:bookchapter:2009}.
-Besides the finiteness of population sizes, it also considers random mutations.
-Here, the quantities of interest are fixation probabilities and fixation times (i.e., the probability and the average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{Fudenberg:TPB:2006}, or the average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}.
-\\ \\
+\noindent Also stochastic evolutionary game dynamics \cite{Nowak:Nature:2004, Traulsen:bookchapter:2009} provides several models for studying multiplayer and asymmetric games. 
+%Here, the quantities of interest are fixation probabilities and fixation times (i.e., the probability and the average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{Fudenberg:TPB:2006}, or the average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}.
+%These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types. 
+Fixation probabilities \cite{Fudenberg:TPB:2006} for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived.
+Furthermore, average strategy abundances \cite{antal:JTB:2009a, antal:JTB:2009b} were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:JMB:2022}.
+For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to Gokhale and Traulsen (2014) \cite{Gokhale:DGAA:2014}.\\
+
 %When deriving fixation probabilities and times, it is assumed that mutations are rare, such that, no new mutant arises between the very first and its eventual fixation \cite{}. 
 %\cite{Chalub:BMB:2019}
-\noindent 
-These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types.
-Fixation probabilities for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived.
-Whereas with intermediate mutation, strategy abundances were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:JMB:2022}.
-For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to \cite{Gokhale:DGAA:2014}.\\
-%comment on the pervasiveness of weak selection
+
 %strategy abundance papers (intermediate mutation or mutation-selection equilibrium)
@@
 
-%[Learning models] IM NOT VERY HAPPY WITH HOW THIS SECTION READS YET
+%[Learning models]
 %learning models in general
-\noindent Different from evolutionary game theory, learning models (of strategic behavior) take another approach \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Hofbauer:GEB:2005, Tuyls:bookchapter:2005, Galla:PNAS:2013, Barfuss:PRE:2019, Barfuss:PNAS:2020, Pangallo:GEB:2022}.
+\noindent Learning models (of strategic behavior) take a different approach from EGT \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Hofbauer:GEB:2005, Tuyls:bookchapter:2005, Galla:PNAS:2013, Barfuss:PRE:2019, Barfuss:PNAS:2020, Pangallo:GEB:2022}.
 There is no evolution of strategies in a population necessarily, but a process by which individuals learn strategies dynamically.
-Despite the conceptual disparities, there have been already some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005, Bloembergen:JAIR:2015, Zhang:arxiv:2022}.
-\noindent Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from the classical game theory itself \cite{Fudenberg:book:1998b}.
+%Despite the conceptual disparities, there have been already some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005, Bloembergen:JAIR:2015, Zhang:arxiv:2022}.
+% Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from the classical game theory itself \cite{Fudenberg:book:1998b}.
 The ``theory of learning in games" was proposed as a refinement of classical equilibrium concepts, like Nash equilibrium, where strict assumptions of common knowledge of rationality are made.
@@
 In this context, several learning models were introduced, such as fictitious play \cite{Gaunersdorfer:GEB:1995} or perturbed best response dynamics \cite{Hofbauer:GEB:2005}.
-\\  \\
 %learning models for asymmetric and multiplayer games? fictious play for multiplayer games \cite{fudenberg:book:1998b} 
 %can we say most of learning models have no analytical or exact results?
-%quantal response equilibrium
-%introspection dynamics
-\noindent Introspection dynamics has proven to be a useful learning model for tackling asymmetric games \cite{Couto:NJP:2022, Hauser:Nature:2019, McAvoy:PNASnexus:2022, Schmid:PlosCB:2022}. 
-This feature comes from the fact that players update their strategies by exploring their own set of strategies in the following simple way: each time, after a round of the game, a player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, it is more likely adopted on the next round.
-We discuss the model formally in the next section.
+\noindent Introspection dynamics has recently proven to be a useful learning model for tackling asymmetric games \cite{Couto:NJP:2022, Hauser:Nature:2019, McAvoy:PNASnexus:2022, Schmid:PlosCB:2022}. 
+This feature comes from the fact that players update their strategies by exploring their own set of strategies in the following simple way: each time, after a round of the game, a random player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, it is more likely adopted on the next round.
+We describe the model formally in the next section.
 While in Couto et al.
-\cite{Couto:NJP:2022} only 2-player games were considered, this framework is general enough to account for multiple players.
-Indeed, as each player assumes that all others remain the same when doing the counterfactual comparison, introspection dynamics is an appropriate model to deal with the complexity introduced by multiple players.
-Particularly, it allows a natural exploration of full asymmetry in many-player games, compared to population models.
+(2022) \cite{Couto:NJP:2022} only 2-player games were considered, this framework is general enough to account for multiple players.
+Particularly, introspection dynamics allows a natural exploration of full asymmetry in many-player games compared to population models.
+For example, in imitation dynamics, one needs to specify who imitates who \cite{Vasconcelos:PNAS:2014}, as when players differ much, it might not make sense to assume they imitate any other player with the same likelihood.
+Introspection avoids this assumption because players' decisions only depend on their own payoffs.
 \\ \\
 %[Our proposal]
-\noindent Here, we extend previous analytical results of pairwise games under introspection dynamics to multiplayer games. 
-For general games, we obtain the analytical stationary distribution for 2-strategy symmetric games.
-For a particularly simple class of games -- additive games -- we derive the stationary distribution of strategies analytically, for any number of players and strategies, and with no restriction to symmetric games.
+\noindent Here, we extend previous results of pairwise games under introspection dynamics to multiplayer games. 
+First, we derive a formula that allows us to numerically compute the stationary distribution of introspection dynamics for any multiplayer asymmetric game. 
+Second, we obtain explicit expressions of the stationary distribution for two special cases.
+These cases are additive games (where the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions of their co-players), and symmetric multiplayer games with two strategies.
 To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas, extending the framework in \cite{Hauert:JTB:2006a} to asymmetric games.
@@
 \noindent For a proof of the Propositions and Corollaries, please see Appendix.
-Using the stationary distribution, one can also exactly compute the cumulative probabilities with which players play their actions in the long run (i.e., the marginal distribution) using Eq.
-(\ref{Eq:marginal-definition}).
+Using the stationary distribution and Eq.
+(\ref{Eq:marginal-definition}), one can also exactly compute the cumulative probabilities with which players play their actions in the long run (i.e., the marginal distributions).
 In this regard, introspection learning in additive games is particularly interesting.
@@
 
-\noindent where the marginal probability, $\xi_{j,a_j}$, is the cumulative probability that player $j$ plays $a_j$ at the stationary distribution. For the $N$-player additive game, this is given by,
+\noindent For the $N$-player additive game, $\xi_{j,a_j}$ is given by,
 
@@
 The average frequency of cooperation per player is summarized in Supplementary Figures 1 and 2.
-In Supplementary Figure 1, we study two cases, first in which the public good is synergistic ($w > 1$, and players have a high average cost) and second in which public good is discounted (and players have a lower average cost).
+In Supplementary Figure 1, we study two cases, first in which the public good is synergistic and players have a high average cost, and second in which public good is discounted and players have a lower average cost.
 In both of these cases, players cooperate highly when they simultaneously have low cost and high benefit.
@@
 Introspection dynamics is particularly useful when players can use larger strategy sets.
-In this section, we study the stationary behaviour of players in a game where each player has 16 possible actions (pure strategies).
+In this section, we study the stationary behaviour of players in a game where each player has 16 possible pure strategies.
 To this end, we adopt the multiplayer cooperation and rewarding game from Pal and Hilbe \cite{Pal:NatCom:2022}.
@@
 \\
-\noindent Combining the two stages, players can use one of 16 possible strategies.
+\noindent Combining the two stages, players can use one of 16 possible strategies (4 in stage 1 and 4 in stage 2).
 In the simple case where players are identical, one can characterize the Nash equilibria of the game and identify the conditions which allow an equilibrium where all players contribute in the first stage and reward peers in second stage \cite{Pal:NatCom:2022}.
@@
 We consider three cases.
-In each case the asymmetric player either has \textbf{a}) a higher cost of rewarding $\gamma_3 > \gamma_1$  or, \textbf{b}) low productivitiy  $r_3 < r_1$ or, \textbf{c}) or, less information about peers $\lambda_3 < \lambda_1$ than his peers.
+In each case the asymmetric player either has \textbf{a}) a higher cost of rewarding $\gamma_3 > \gamma_1$  or, \textbf{b}) low productivitiy  $r_3 < r_1$ or, \textbf{c}) or, less information about peers $\lambda_3 < \lambda_1$ than their peers.
 We use Eq.
@@
 Finally, we consider the case where the asymmetric individual differs from others in terms of the information players have about others' rewarding strategy (Fig \ref{Fig:SocialRewarding}c).
-In this case, the asymmetric player knows others' strategy with a considerably less chance than his peers.
+In this case, the asymmetric player knows others' strategy with a considerably less chance than their peers.
 In the long run, the asymmetric player cooperates less on average than their peers.
-This is because the individual with less information has less instances of opportunistically cooperating with his co-players.
+This is because the asymmetric individual faces less instances where they can opportunistically cooperate with their co-players.
 However, both types of player reward cooperation almost equally and just enough to sustain cooperation.
@@
 %[Short summary]
-Most previous evolutionary models focus on limiting regimes, namely low mutation rate and selection strength approximations, as they allow for analytical results. 
-Here, we show that it is possible to obtain analytical expressions for the long-run average strategy abundances for multiplayer games resorting to introspection dynamics, even for intermediate values of selection strength.
+
+We introduce introspection dynamics in $N$-player (a)symmetric games.
+In this learning model, at each time, one of the $N$ players updates (or not) their strategy by comparing the payoffs of two strategies only: the one being currently played and a random prospective one.
+Clearly, this assumption implies a simple cognitive process.
+Players do not optimize over the entire set of strategies as, for example, in best-responde models \cite{Gaunersdorfer:GEB:1995, Hofbauer:GEB:2005}.
+Furthermore, although conceptually similar, our model is also simpler than typical reinforcement learning models.
+For example, while we only have selection strength as a parameter (apart from payoffs), in Macy and Flache (2002) \cite{Macy:PNAS:2002}, there is a learning rate parameter (which could be comparable to our selection strength) but also an aspiration parameter which sets a payoff reference.
+In our model, the payoff reference is always the current one.
+All in all, whereas at each single time step, individuals are restricted to reason over two strategies only, as they iterate this step over time, they are able to fully explore the whole set of strategies, in a trial-and-error fashion.
+\\
+
+\noindent Importantly, our model is also much simpler than the stochastic evolutionary game theory framework.
+While they both can involve solving the stationary distribution of a Markov process, they differ greatly in the state space size.
+Population models typically assume individuals play multiple games against (potentially all) other players in a population.
+As such, the state is defined by the number of players playing each strategy in the population(s).
+The number of states rapidly increases with the population size, the number of strategies, of players and of different types (in the case of asymmetric games).
+One can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome.
+To deal with this issue, previous models frequently resorted to additional approximations, like low mutation rate \cite{Fudenberg:JET:2006, Veller:JET:2016} and weak selection \cite{Wild:JTB:2007}.
+%Most previous evolutionary models focus on limiting regimes, namely low mutation rate and selection strength approximations, as they allow for analytical results.
+On the contrary, in introspection dynamics, the states of the Markov process correspond to the outcome of a single (focal) game: for a $N$-player game, where player $i$ has $m_i$ possible actions, there are $m_1 \times m_2 \times ...
+\times m_N$ states.
+This feature hugely reduces our state space size, which is key for obtaining exact results.
+\\
+
+%Due to these reasons, one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
+Perhaps for that reason, there are not many studies on a general approach to multiplayer asymmetric games.
+As such, our aim here is to narrow that gap using introspection dynamics \cite{Couto:NJP:2022}.
+
+\noindent Here, we thus provide a general explicit formula (Eq.
+\ref{Eq:explicit-stationary-dist-representation}) that easily computes the stationary distribution of any multiplayer asymmetric game under introspection dynamics.
+Note that this formula is usefull for the exploration of many-strategy games in the full range of selection strenght.
+Additionally, we show that it is possible to obtain some analytical expressions for the long-run average strategy abundances.
 We start by analysing the set of additive games, for which the gain from switching between any two actions is constant, regardless of what co-players do. 
-Due to this simple feature, additive games allow for the most general close-form expression for the stationary distribution, regarding the number of players, strategies, and asymmetry of the game. 
+Due to this simple feature, additive games allow for the most general close-form expression for the stationary distribution (regarding the number of players, of strategies, and asymmetry of the game).
 Additionally, we find that for any additive game, the joint distribution of strategies factorizes over the marginal distribution of strategies. 
-For general games (for which additivity does not hold in general), we provide the stationary distribution formula for 2-strategy, symmetric games.
-By studying several examples of social dilemmas, we conclude that, generally, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently. \\ \\ 
+For more general games, we provide the stationary distribution formula for 2-strategy, symmetric games.
+Finally, we study several examples of social dilemmas.
+From those, we see that, despite the differences to other models pointed out above, we recover some previous qualitative results \cite{Hauert:JTB:2006a}.
+We also conlcude that players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
+\\
+
 \noindent Introspection dynamics is a rather broad model.
-Here, we mainly focused on introducing a general framework to the detriment of exploring more realistic, complex examples.
-Nevertheless, in the last section, we give one step forward in that direction, by studying a 2-stage game, where players can choose among $16$ strategies.
+Here, we mainly focused on introducing a general framework.
+Still, we provide some examples to illustrate how it can be applied.
+Besides the generic public goods game, we study a 2-stage game, where players can choose among $16$ strategies.
 There, individuals can reward their co-players condition on their previous cooperative (or not) behavior.
 %[What we didn't do, limitations, further work]
-\noindent Clearly, there are a number of ways in which we can further employ our model.
+\noindent Clearly, there are a number of ways in which our model can be further employed.
 For example, other researchers recently studied multiplayer games considering multiple games played concurrently \cite{Venkateswaran:PRSB:2019}, fluctuating environments \cite{Baron:JRSOP:2018}, continuous strategies \cite{Molina:JMB:2017}, or repeated interactions \cite{Hilbe:JTB:2015}.
-Finally, for the sake of mathematical tractability, introspection dynamics, as we present it here, does not consider a population, not to mention complex population structures \cite{Broom:JTB:2012, Wu:Games:2013, Perc:JRSI:2013, Pena:JTB:2015, Pena:JRSI:2016, Pattni:JTB:2017, Su:PNAS:2022}.
-However, it can be equally applicable to population models.
-In that case, players obtain average payoffs either from well-mixed or network-bounded interactions, as usual, but update their strategies introspectively.
+Also, a number of previous works considered complex population structures \cite{Broom:JTB:2012, Wu:Games:2013, Perc:JRSI:2013, Pena:JTB:2015, Pena:JRSI:2016, Pattni:JTB:2017, Su:PNAS:2022}.
+As discussed above, introspection dynamics does not consider a population of players, making it simple to work with.
+However, it could be equally applicable to population models.
+In that case, players would obtain average payoffs either from well-mixed or network-bounded interactions, as usual, but update their strategies introspectively.
+
+%Despite the conceptual disparities, there have been already some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005, Bloembergen:JAIR:2015, Zhang:arxiv:2022}.
+% Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from the classical game theory itself \cite{Fudenberg:book:1998b}.
+The ``theory of learning in games" was proposed as a refinement of classical equilibrium concepts, like Nash equilibrium, where strict assumptions of common knowledge of rationality are made.
+Instead, learning consists of ``\textit{an alternative explanation that equilibrium arises as the long-run outcome of a process in which less than fully rational players grope for optimality over time}" \cite{Fudenberg:book:1998b}.
+In this context, several learning models were introduced, such as fictitious play \cite{Gaunersdorfer:GEB:1995} or perturbed best response dynamics \cite{Hofbauer:GEB:2005}.
 

### 2023-03-01 latex/article.tex
Revised abstract, intro and discussion by Sap

@@
 \onehalfspacing
-\section*{Abstract}
 \section*{Abstract}
@@
 Thus, to account for such non-linearities, one needs to consider multiplayer games \cite{Gokhale:DGAA:2014}.
-A well-known effect that only emerges when more than two players are present is the ``second-order free-riding problem" \cite{Fowler:PNAS:2005}.
+For example, well-known effect that only emerges when more than two players are present is the ``second-order free-riding problem" \cite{Fowler:PNAS:2005}.
 A natural solution to maintain pro-social behavior in a community is to monitor and punish defectors (and/or reward cooperators).
 However, most forms of sanctioning are considerably costly \cite{Henrich:Science:2006}.
-Therefore, an additional (second-order) dilemma is at stake: deterring defection is beneficial for all, but an individual that does not pay the associated cost has an advantage over the ones that do.
+Therefore, an additional (second-order) dilemma
+%is at stake% 
+emerges: individuals would like cooperation to be incentivized but they prefer that others pay the associated costs.
+%deterring defection is beneficial for all, but an individual that does not pay the associated cost has an advantage over the ones that do.
 As long as cooperation is incentivized by punishment (or rewards) of others, individuals can take advantage by defecting in this second-order dilemma.
-As such, this tempts everyone not to engage in costly punishment (or rewarding), and cooperation can break down.
+%As such, this tempts everyone not to engage in costly punishment (or rewarding), and cooperation can break down.
 For this reason, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.
@@
 Likewise, it has been shown that it is hard to cooperate in large groups \cite{Santos:PNAS:2011, Hilbe:JTB:2015}.
-This is not a general effect, though.
+This is however, not a general effect in any interaction \cite{gokhale:JTB:2011}.
+%This is not a general effect, though.
 It can happen that adding more players actually promotes cooperation.
@@
 With three players, the production of one of the enzymes increases while freeloading decreases, compared to the 2-player case.
-Additionally, interaction group size can vary in a population of players.
+Additionally, 
+%interaction% 
+group size can vary in a population of players.
 There, not only the average group size can have an important effect, but also the variance of the group size distribution \cite{Pena:Evolution:2011, Broom:BMB:2019}.
@@
 Thus, to fully characterise the state of the game, we only require to know the number of players playing each strategy.
-Conversely, in asymmetric games, players can differ in their available actions and in their incentives to choose each action; players are of different types or roles.
+Conversely, in asymmetric games, players can differ in their available actions and in their incentives to choose each action.
+%;players are of different types or roles. 
 Therefore, they can have uneven effects on others' payoffs too.
 For example, in public goods games and collective-risk dilemmas, players can have different initial endowments (or wealth), productivitites, costs, risk perceptions, or risk exposures \cite{Milinski:CC:2011, Vasconcelos:PNAS:2014, Abouchakra:JTB:2014, Hauser:Nature:2019, Merhej:JAIR:2022, Wang:PTRSB:2023}.
-Hence, to fully describe the state of the game, we need to know which of the players is doing what.
+Hence, to fully describe the state of the game, we need to know the exact action of each player.
 This greatly increases the size of the game's state space; even more so, for more than two players.
-\\ \\
+\\
+%Hence, to fully describe the state of the game, we need to know which of the players is doing what.
+This greatly increases the size of the game's state space; even more so, for more than two players.
+\\
 %meta communication; lit gap; our aim
-
 %\noindent Due to these reasons, one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
@@
 % deterministic EGT
-\noindent From evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior.
+\noindent Models from evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} and learning theory \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, have been widely used to study strategic behavior.
+%From evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior.
 %, in particular, in multiplayer and asymmetric games.
@@
 A (monomorphic) population playing an ESS cannot be invaded by mutants.
-\noindent The concept of ``evolutionary stable strategy" (ESS), originally proposed for parwise encounters \cite{Maynard-Smith:Nature:1973}, was extended for multiplayer games \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}.
-Also the well-known replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998} easily comprises multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Pena:Evolution:2011, Cressman:PNAS:2014, Pena:JTB:2014}.
+\noindent The concept of evolutionary stable strategy, originally proposed for parwise encounters \cite{Maynard-Smith:Nature:1973}, was extended to multiplayer games \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}.
+Also the well-known replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998}
+%easily comprises 
+can easily account for multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Pena:Evolution:2011, Cressman:PNAS:2014, Pena:JTB:2014}.
 More recently, the replicator-mutator equation was applied to study the dynamics of multiplayer games, too \cite{Duong:DGAA:2020}.
-As for asymmetric games, a few additional assumptions are needed.
+As for asymmetric games, a few additional assumptions are needed in the description of the model.
 For example, if there are two different types of players, typically, either there are two populations co-evolving (``bimatrix games" \cite{Hofbauer:book:1998, Gokhale:PRSB:2012, Tuyls:SciRep:2018}) or there is a single population of players where each can play the two types or roles (``role games") \cite{Hofbauer:book:1998}.
-For role games, a strategy must include the action played in each of the two roles.
+%For role games, a strategy must include the action played in each of the two roles. 
 The case of asymmetric games with more than two players is substantially less studied within deterministic EGT.
@@
 % models of multiple populations seem unnatural
-\\ \\
 % stochastic EGT
-\noindent Also stochastic evolutionary game dynamics \cite{Nowak:Nature:2004, Traulsen:bookchapter:2009} provides several models for studying multiplayer and asymmetric games. 
+Also stochastic evolutionary game dynamics \cite{Nowak:Nature:2004, Traulsen:bookchapter:2009} provides several models for studying multiplayer and asymmetric games. 
 %Here, the quantities of interest are fixation probabilities and fixation times (i.e., the probability and the average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{Fudenberg:TPB:2006}, or the average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}.
 %These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types. 
-Fixation probabilities \cite{Fudenberg:TPB:2006} for asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived.
+Fixation probabilities \cite{Fudenberg:TPB:2006} in asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived.
 Furthermore, average strategy abundances \cite{antal:JTB:2009a, antal:JTB:2009b} were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:JMB:2022}.
-For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to Gokhale and Traulsen (2014) \cite{Gokhale:DGAA:2014}.\\
+For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to Gokhale and Traulsen (2014) \cite{Gokhale:DGAA:2014}.
+Learning models (of strategic behavior) take a different approach from EGT \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Hofbauer:GEB:2005, Tuyls:bookchapter:2005, Galla:PNAS:2013, Barfuss:PRE:2019, Barfuss:PNAS:2020, Pangallo:GEB:2022}.
+There is no evolution of strategies in a population necessarily, but a process by which individuals learn strategies dynamically.
+\\
 
@@
 %learning models in general
-\noindent Learning models (of strategic behavior) take a different approach from EGT \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Hofbauer:GEB:2005, Tuyls:bookchapter:2005, Galla:PNAS:2013, Barfuss:PRE:2019, Barfuss:PNAS:2020, Pangallo:GEB:2022}.
-There is no evolution of strategies in a population necessarily, but a process by which individuals learn strategies dynamically.
 %Despite the conceptual disparities, there have been already some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005, Bloembergen:JAIR:2015, Zhang:arxiv:2022}.
@@
 \noindent Introspection dynamics has recently proven to be a useful learning model for tackling asymmetric games \cite{Couto:NJP:2022, Hauser:Nature:2019, McAvoy:PNASnexus:2022, Schmid:PlosCB:2022}.
-This feature comes from the fact that players update their strategies by exploring their own set of strategies in the following simple way: each time, after a round of the game, a random player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, it is more likely adopted on the next round.
+In here, players update their strategies by exploring their own set of strategies in the following simple way: each time, after a round of the game, a random player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, it is more likely adopted on the next round.
 We describe the model formally in the next section.
@@
 Particularly, introspection dynamics allows a natural exploration of full asymmetry in many-player games compared to population models.
-For example, in imitation dynamics, one needs to specify who imitates who \cite{Vasconcelos:PNAS:2014}, as when players differ much, it might not make sense to assume they imitate any other player with the same likelihood.
+For example, in imitation dynamics, one needs to specify who is being imitated by whom \cite{Vasconcelos:PNAS:2014}.
+When players differ, it might not make sense to assume that they imitate others.
 Introspection avoids this assumption because players' decisions only depend on their own payoffs.
@@
 %[Our proposal]
-\noindent Here, we extend previous results of pairwise games under introspection dynamics to multiplayer games. 
+\noindent Here, we extend previous results \cite{Couto:NJP:2022} of pairwise games under introspection dynamics to multiplayer games. 
 First, we derive a formula that allows us to numerically compute the stationary distribution of introspection dynamics for any multiplayer asymmetric game. 
@@
 \noindent We use the Eq.
-(\ref{Eq:stationary_dist_lpgg}) to analyze the stationary behaviour of players after a long run of introspection in a linear public goods game (LPGG).
+(\ref{Eq:stationary_dist_lpgg}) to analyze the stationary behavior of players after a long run of introspection in a linear public goods game (LPGG).
 First, we study the simplest case where all players are symmetric (the cost and benefit for all the 4 players are $c$ and $b$).
@@
 Similarly, when cooperation is highly beneficial and strictly dominates defection ($b/N - c = 2$), players defect sometimes.
-At higher values of $\beta$, the stationary behaviour of players is more responsive to the payoffs and thus reflects an abrupt change near the parameters where the game transitions from defection-dominating to cooperation-dominating ($b/N - c = 0$).
+At higher values of $\beta$, the stationary behavior of players is more responsive to the payoffs and thus reflects an abrupt change near the parameters where the game transitions from defection-dominating to cooperation-dominating ($b/N - c = 0$).
 \\ \\
@@
 Note that the number of cooperators in the two states are related as: $\mathcal{C}(\D,\abf_{-i}) = \mathcal{C}(\C,\abf_{-i}) - 1$.
-We are interested in studying the long term stationary behaviour of players in this game when they learn through introspection.
+We are interested in studying the long term stationary behavior of players in this game when they learn through introspection.
 We first discuss results from the symmetric public goods game and then discuss results for the game with asymmetric players.\\
@@
 Introspection dynamics is particularly useful when players can use larger strategy sets.
-In this section, we study the stationary behaviour of players in a game where each player has 16 possible pure strategies.
+In this section, we study the stationary behavior of players in a game where each player has 16 possible pure strategies.
 To this end, we adopt the multiplayer cooperation and rewarding game from Pal and Hilbe \cite{Pal:NatCom:2022}.
@@
 
-\section*{Discussions and conclusion}
+\section*{Discussion and conclusion}
 
@@
 In our model, the payoff reference is always the current one.
-All in all, whereas at each single time step, individuals are restricted to reason over two strategies only, as they iterate this step over time, they are able to fully explore the whole set of strategies, in a trial-and-error fashion.
+All in all, while at each single time step individuals are restricted to reason over two strategies only, as they iterate this step over time, they are able to fully explore the whole set of strategies, in a trial-and-error fashion.
 \\
 
-\noindent Importantly, our model is also much simpler than the stochastic evolutionary game theory framework.
+\noindent Importantly, our model is also much simpler computationally than the stochastic evolutionary game theory framework.
 While they both can involve solving the stationary distribution of a Markov process, they differ greatly in the state space size.
@@
 As such, the state is defined by the number of players playing each strategy in the population(s).
-The number of states rapidly increases with the population size, the number of strategies, of players and of different types (in the case of asymmetric games).
+The number of states rapidly increases with the population size, the number of strategies, size of interaction and types of players (in the case of asymmetric games).
 One can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome.
@@
 
-\noindent Here, we thus provide a general explicit formula (Eq.
-\ref{Eq:explicit-stationary-dist-representation}) that easily computes the stationary distribution of any multiplayer asymmetric game under introspection dynamics.
-Note that this formula is usefull for the exploration of many-strategy games in the full range of selection strenght.
+\noindent Here, we thus provide a general explicit formula, Eq.
+(\ref{Eq:explicit-stationary-dist-representation}), that easily computes the stationary distribution of any multiplayer asymmetric game under introspection dynamics.
+Note that this formula is useful for the exploration of many-strategy games in the full range of selection strength.
 Additionally, we show that it is possible to obtain some analytical expressions for the long-run average strategy abundances.
@@
 Due to this simple feature, additive games allow for the most general close-form expression for the stationary distribution (regarding the number of players, of strategies, and asymmetry of the game).
-Additionally, we find that for any additive game, the joint distribution of strategies factorizes over the marginal distribution of strategies. 
+We also find that for additive games, the joint distribution of strategies factorizes over the marginal distribution of strategies. 
 For more general games, we provide the stationary distribution formula for 2-strategy, symmetric games.
@@
 
-\noindent Introspection dynamics is a rather broad model.
+\noindent Introspection dynamics is a rather broad in its scope.
 Here, we mainly focused on introducing a general framework.
@@
 Unless otherwise mentioned, the following parameters are maintained for all panels: $c_i = 1$ (individual cost of cooperation), $r_i = 2$ (individual productivity), $\gamma_i = 0.1$ (individual cost of rewarding), $\lambda_i = 0.9$ (individual information about co-players' strategies).
-In panels a and b, the reward value $\rho$ is 0.3 while for the last panel, c, the reward value $\rho = 1$.}
+In panels a and b, the reward value $\rho = 0.3$ while for the last panel, c, the reward value $\rho = 1$.}
 \label{Fig:SocialRewarding}

### 2023-03-01 latex/article.tex
figs caption by marta, all changes by me, supp info by marta

@@
 \section*{Model of introspection dynamics in multiplayer games}
-We consider a normal form game with $N$ players where $N \geq 2$.
+We consider a normal form game with $N (\geq 2)$ players.
 In the game, a player, say player $i$, can play actions from their action set, $\A_i := \{a_{i,1}, a_{i,2}, ..., a_{i,m_i} \}$.
@@
 In this model, players only use pure strategies.
-Therefore, there are only finitely many states of the game.
+Therefore, there are finitely many states of the game.
 More precisely, there are exactly $m_1 \times m_2 \times ...
@@
 We also use the notation, $\abf := (a_i, \abf_{-i})$ to denote the state from the perspective of player $i$.
-In the state $(a_i, \abf_{-i})$, player $i$ plays the action $a_i \in \A_i$ and their co-players play the action $\abf_{-i} \in \A_{-i}$ where $\A_{-i}$ is defined as $\A_{-i}:= \prod_{j \neq i} \A_j$.
+In the state $(a_i, \abf_{-i})$, player $i$ plays the action $a_i \in \A_i$ and their co-players play the actions $\abf_{-i} \in \A_{-i}$ where $\A_{-i}$ is defined as $\A_{-i}:= \prod_{j \neq i} \A_j$.
+The payoff of a player depends on the state of the game.
+We denote the payoff of player $i$ in the state $\abf$ with $\pi_i(\abf)$ or $\pi_i(a_i, \abf_{-i})$.
 In this paper, we use bold font letters to denote vectors and matrices.
 We use the corresponding normal font letters with subscripts to denote elements of the vectors (or matrices).
-The payoff of a player depends on the state of the game.
-We denote the payoff of player $i$ in the state $\abf$ with $\pi_i(\abf)$ or $\pi_i(a_i, \abf_{-i})$.
-\\ \\
-\noindent Since players only use pure strategies in this model, we use the terms strategies and actions interchangebly throughout the whole paper.
-In this model, players update their strategies over time using the introspection dynamics \cite{Couto:NJP:2022}.
+Since players only use pure strategies in this model, we use the terms strategies and actions interchangebly throughout the whole paper.
+\\ \\
+\noindent In this model, players update their strategies over time using introspection dynamics \cite{Couto:NJP:2022}.
 At every time step, one randomly chosen player can update their strategy.
-The randomly chosen player, say $i$, currently playing  action $a_{i,k}$, compares their current payoff to the payoff that they would obtain if they played a randomly selected action,  $a_{i,l} \neq a_{i,k}$, from their action set $\A_i$.
+The randomly chosen player, say $i$, currently playing  action $a_{i,k}$, compares their current payoff to the payoff that they would obtain if they played a randomly selected action $a_{i,l} \neq a_{i,k}$ from their action set $\A_i$.
 This comparison is done while assuming that the co-players do not change their respective actions.
-When the co-players of player $i$ play $\abf_{-i}$, player $i$ changes from action $a_{i,k}$ to the new action $a_{i,l}$ with the probability, \\
+When the co-players of player $i$ play $\abf_{-i}$, player $i$ changes from action $a_{i,k}$ to the new action $a_{i,l}$ in the next round with probability, \\
 \begin{equation}
@@
 \end{equation}
-\\ \\ \noindent in the next round.
-Here $\beta \in [0,\infty)$ is the selection strength parameter that represents the importance that players give to payoff differences while updating their actions.
-At $\beta = 0$, players update to a randomly chosen strategy with probablity $0.5$.
-For $\beta > 0$, players update to the alternative strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them a non-zero increase (or decrease) in the payoffs.
+\\ \\ \noindent Here $\beta \in [0,\infty)$ is the selection strength parameter that represents the importance that players give to payoff differences while updating their actions.
+For $\beta = 0$, players update to a randomly chosen strategy with probablity $0.5$.
+For $\beta > 0$, players update to the alternative strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them an increase (or decrease) in the payoffs.
 \\ \\
@@
 In order to formally define the transition matrix, we first need to introduce some notations and definitions.
-We start by defining the neighbourhood set of $\abf$ as,
+We start by defining the neighbourhood set of $\abf$,
 
@@
 \noindent In the previous example, the index of difference between the neighbouring states $(\C,\C,\C)$ and $(\C,\C,\D)$ is $3$.
-Using the above definitions, one can formally define the transition matrix of introspection dynamics with:
+Using the above definitions, one can formally define the transition matrix of introspection dynamics by:
 
@@
 \\ \\
-\noindent When the selection strength, $\beta$ is finite, the transition matrix of introspection dynamics has a unique stationary distribution.
+\noindent When the selection strength, $\beta$, is finite, the transition matrix of introspection dynamics has a unique stationary distribution.
 A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
@@
 The transition matrix, $\T$, is therefore primitive for a finite $\beta$.
-By the Perron-Frobenius theorem, a primitive matrix, $\T$ will have a unique and strictly positive stationary distribution $\ubf := (\mathrm{u}_\abf)_{\abf \in \A}$ which satisfies the conditions:
+By the Perron-Frobenius theorem, a primitive matrix, $\T$, will have a unique and strictly positive stationary distribution $\ubf := (\mathrm{u}_\abf)_{\abf \in \A}$ which satisfies the conditions:
 \begin{eqnarray}
@@
 \end{eqnarray}
-\noindent where $\mathbf{1}$ is the column vector with size same as $\ubf$ and has all elements as $1$.
+\noindent where $\mathbf{1}$ is the column vector with the same size as $\ubf$ and has all elements as $1$.
 For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distributions of the processes are unique.
@@
 The stationary distribution can be explictly calculated by the following expression (which is derived using Eq.
-(\ref{Eq:lefteigenvector}) and (\ref{Eq:normalizationcondition})) as:
+(\ref{Eq:lefteigenvector}) and (\ref{Eq:normalizationcondition})),
 \begin{equation}
@@
 Using Eq.
-(\ref{Eq:explicit-stationary-dist-representation}) one can compute the unique stationary distribution of (a finite $\beta$-) introspection dynamics for any normal form game (with arbitrary number of asymmetric players).\\
+(\ref{Eq:explicit-stationary-dist-representation}), one can compute the unique stationary distribution of introspection dynamics (with a finite $\beta$) for any normal form game (with arbitrary number of asymmetric players).\\
 
@@
 \noindent is independent of $\qbf$ and only dependent on $x$ and $y$.
-In the literature, this property is sometimes called the property of \emph{equal gains from switching} \cite{Pena:JTB:2014}.
+In the literature, this property is sometimes called \emph{equal gains from switching} \cite{Pena:JTB:2014}.
 For games with this property, the stationary distribution of introspection dynamics takes a simple form,
@@
 \end{Prop}
-\noindent For a proof of the Propositions and Corollaries, please see Appendix.
+\noindent For all proofs of Propositions and Corollaries, please see the Appendix.
 Using the stationary distribution and Eq.
@@
 Let $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$ be the unique stationary distribution of introspection dynamics with finite $\beta$ for the N-player additive game.
-Then, $\mathrm{u}_\abf$ is the product of the marginal probabilities that each player plays their respective actions in $\abf$.
+Then, $\mathrm{u}_\abf$ is the product of the marginal probabilities with which each player plays their respective actions in $\abf$.
 That is,
@@
 \subsection*{Example of an additive game: linear public goods game with 2 actions}
-In the simplest version of the linear public goods game with $N-$players, each player has two possible actions, to contribute (action $\C$, to cooperate), or to not contribute (action $\D$, to defect) to the public good.
-The players differ in their cost of cooperation and the benefit they provide by contributing to the public good.
+In the simplest version of the linear public goods game (LPGG) with $N-$players, each player has two possible actions, to contribute (action $\C$, to cooperate), or to not contribute (action $\D$, to defect) to the public good.
+The players may differ in their cost of cooperation and the benefit they provide by contributing to the public good.
 We denote the cost of cooperation for player $i$ and the benefit that they provide by $c_i$ and $b_i$ respectively.
@@
 This property of the game results in easily identifiable dominated strategies.
-Defection dominates cooperation when $c_i > b_i/N$ while cooperation dominates defection when $c_i < b_i/N$.
+For player $i$, defection dominates cooperation when $c_i > b_i/N$ while cooperation dominates defection when $c_i < b_i/N$.
 Using Proposition \ref{Th:additive-games-stationary-dist}, one can derive the closed form expression for the stationary distribution of a $N-$player linear public goods game with two strategies.
@@
 They differ, however, in their cost of cooperation.
-For player 1 and 2, the cost of cooperation is 1 unit ($c_1 = c_2 = 1$) while for the third player, the cost is slightly higher at 1.5 units ($c_3 = 1.5$).
+For player 1 and 2, the cost of cooperation is 1 unit ($c_1 = c_2 = 1$) while for the third player, the cost is 1.5 units ($c_3 = 1.5$).
 In the stationary distribution of the process with selection strength $\beta = 1$, the cumulative probability that player 1 (or 2) cooperates and player 3 defects are $\xi_{1,\C} = \xi_{2,\C}= 0.417$ and $\xi_{3,\D} = 0.697$ respectively.
@@
 \\ \\
-\noindent We use the Eq.
-(\ref{Eq:stationary_dist_lpgg}) to analyze the stationary behavior of players after a long run of introspection in a linear public goods game (LPGG).
+\noindent We now use Eq.
+(\ref{Eq:stationary_dist_lpgg}) to systematically analyze the LPGG under introspection dynamics.
 First, we study the simplest case where all players are symmetric (the cost and benefit for all the 4 players are $c$ and $b$).
 Since all players are identical, the states of the game can be enumerated by counting the number of cooperators in the state.
-There can only be 5 distinct states of the game (from 0 to 4 cooperators).
+There are only 5 distinct states of the game (from 0 to 4 cooperators).
 When the parameters of the game are such that defection dominates cooperation ($b = 2, c = 1$, Fig.
@@
 In the previous section we studied the properties of additive games under introspection dynamics.
-In this section, we study the stationary properties of games that are a) not necessarily additive and b) have only two actions for each player.
+In this section, we study games that are a) not necessarily additive and b) have only two actions for each player.
 First, we study the symmetric version of such a game.
@@
 \begin{enumerate}
-\item  All players have the same action set $\mathcal{A}$. That is, $\A_1 = \A_2 = ... = \A_N := \mathcal{A}$. We denote this set by, $\mathcal{A} := \{\C,\D\}$.
+\item  All players have the same action set $\mathcal{A} := \{\C,\D\}$. That is, $\A_1 = \A_2 = ... = \A_N := \mathcal{A}$. 
 \item Players have the same payoff when they play against the same composition of co-players. That is, for any $i,j \in \{1,2,...,N\}$, $a \in \mathcal{A}$ and $\bbf \in \mathcal{A}^{N-1}$,
@@
 
-\noindent The number of unique states of the game can be reduced to $N+1$ from $2^N$ due to symmetry.
+\noindent The number of unique states of the game can be reduced from $2^N$ to $N+1$  due to symmetry.
 In the reduced state space, the state, $k$, corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
@@
 In the original paper, the authors propose a normal form game with symmetric players.
-The game's properties are determined by a parameter $w$ that determines the nature of the public good.
+The game's properties depend on a parameter $w$ that determines the nature of the public good.
 The players have two actions: cooperation, $\C$ and defection, $\D$.
@@
 \begin{align}
-\pi^{\D}_i(k) &= \frac{b}{N}(1 + w + w^2 + ... + w^{k-1}) \\[15pt]
-\pi^{\C}_i(k) &= \pi^{\D}_i(k) - c
+\pi^{\D}(k) &= \frac{b}{N}(1 + w + w^2 + ... + w^{k-1}) \\[15pt]
+\pi^{\C}(k) &= \pi^{\D}_i(k) - c
 \label{Eq:payoff-synergistic-symmetric}
@@
 \noindent The parameter $w$ represents the non-linearity of the public good.
-The nature is linear when $w = 1$.
-Every additional cooperator's contribution is as valuable as the benefit that they can generate.
-When $w < 1$, the effective contribution of every new cooperator goes down by a factor, $w$ (compared to the last cooperator).
+The game is linear when $w = 1$.
+Every cooperator's contribution is as valuable as the benefit that they can generate.
+When $w < 1$, the effective contribution of every additional cooperator goes down by a factor, $w$ (compared to the last cooperator).
 The public goods is said to be discounting in this case.
-On the other hand when $w > 1$, every new contributor is more valuable than the previous one.
+On the other hand when $w > 1$, every new contribution is more valuable than the previous one.
 The public good is said to be synergistic in this case.
@@
 When selection strength is intermediate ($\beta = 5$), players sometimes play actions that are not optimal for the dilemma.
-For example, even when the parameters of the game make cooperation to be the dominated strategy ($w = 0.5, c = 1$), there is a single cooperator in the group in 20 $\%$ of the cases.
+For example, even when the parameters of the game make cooperation to be the dominated strategy ($w = 0.5, c = 1$), there is a single cooperator in the group in around 20 $\%$ of the cases.
 When the parameters of the game reflect the stag-hunt dilemma ($c = 1, w = 1.5$), players are more likely to coordinate their actions in the long run.
-In the long-run, the probabilities that the whole group plays $\C$ or $\D$ is higher than the probabilities that there is a group with a mixture of $\C$ and $\D$ players.
+In the long-run, the probabilities that the whole group plays $\C$ or $\D$ are higher than the probabilities that there is a group with a mixture of $\C$ and $\D$ players.
 In contrast, when the parameters reflect the snowdrift game ($w = 0.5, c = 0.5$), we get the opposite effect.
@@
 \\ \\
-\noindent The average cooperation frequency of the group in the long run are shown in the $c-w$ and $N-w$ parameter planes in Fig \ref{Fig:GPGG-symmetric}b.
+\noindent The average cooperation frequency of the group in the long run is shown in the $c-w$ and $N-w$ parameter planes in Fig \ref{Fig:GPGG-symmetric}b.
 First, let us consider the case when the group size is fixed at 4 players (the $c-w$ plane in Fig\ref{Fig:GPGG-symmetric}b).
-In that case, if the cost of cooperation is restrictively high, the average cooperation rate is negligible and does not change with the change in the nature of the public good.
-In contrary, when the cost is not restrictively high, the discount/synergy parameter, $w$, determines the frequency with which players cooperate in the long run.
+In that case, if the cost of cooperation is restrictively high, the average cooperation rate is negligible and does not change with the the nature of the public good.
+In contrast, when the cost is not restrictively high, the discount/synergy parameter, $w$, determines the frequency with which players cooperate in the long run.
 A higher $w$ for the public good would result in higher cooperation (and \emph{vice-versa}).
@@
 \ref{Fig:GPGG-symmetric}b).
-The cost is fixed to a value such that in a synergistic PG ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size.
+The cost is fixed to a value such that in a synergistic public good ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size.
 In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run.
@@
 \textbf{Introspection dynamics in a symmetric linear public goods game.}
-The stationary distribution of introspection dynamics for a linear public goods game with all identical players is shown in this figure.
-For all the panels in this figure, we use the following parameters: $N = 4$ (group size), $b = 2$ (benefit provided to the public good upon cooperation), $c = 1$ (cost of cooperation) a) Here we show the frequency of each state in the stationary distribution of introspection dynamics.
+We show the stationary distribution of the introspection dynamics for a linear public goods game with four identical players.
+For all the panels in this figure, we use the following parameters: $N = 4$ (group size), $b = 2$ (benefit provided to the public good upon cooperation), $c = 1$ (cost of cooperation).
+a) Here, we show the frequency of each state in the stationary distribution of introspection dynamics.
 As players are identical, each state can be defined by the number of cooperators.
-We use a selection strength of $\beta = 5$ for the introspection dynamics.
-For this strength of selection, states with more cooperators are less likely than states with less cooperators in the stationary distribution b) Here we show the frequency of each state for varying selection strength, $\beta$.
-We use the same color code as the previous panel.
+We use a selection strength of $\beta = 5$.
+For this strength of selection, states with more cooperators are less likely than states with less cooperators.
+b) Here, we show the frequency of each state for varying selection strength, $\beta$.
+We use the same color code as panel a).
 Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators.
 Indeed, up to $\beta \approx 3$, state $0$ is not the most frequent state in the long run.
-c) Average cooperation frequency for varying dilemma strength depends on the selection strength, $\beta$, and the parameters of the linear public goods game: $b,c, N$.
+c) Average cooperation frequency for varying dilemma strength depends on the selection strength, $\beta$.
 We use the marginal gain of choosing cooperation over defection, $b/N - c$, as a measure of the dilemma strength.
@@
 The results are shown for different values of selection strength, $\beta = 1, 5$ and $100$.
-For high $\beta$, stationary distribution of introspection dynamics reflects the rational play.
-In the long-run player play the Nash equilibrium.
+For high $\beta$, stationary distribution of the introspection dynamics reflects the rational play.
+In the long-run players play the Nash equilibrium.
 When marginal gain is negative, defection is played with almost certainty (and \emph{vice-versa}).
@@
 \caption{\onehalfspacing
-\textbf{Introspection dynamics in an asymmetric linear public goods game.} Three asymmetric players learn to play the linear public goods game through introspection dynamics.
-The cooperation probabilities in the stationary distribution are displayed here.
+\textbf{Introspection dynamics in an asymmetric linear public goods game.} We show the cooperation probabilities of the introspection dynamics for a linear public goods game with three asymmetric players.
 For each of the upper panels (a and b), we show the cost of cooperation and the benefit provided upon cooperation for the players on the left and the average cooperation frequency in the long-run on the right.
-In this example, the cost of cooperation for players 1, 2 and 3 are $1 + \delta_c, 1$ and $1 - \delta_c$ respectively.
+%In this example, the cost of cooperation for players 1, 2 and 3 are $1 + \delta_c, 1$ and $1 - \delta_c$ respectively.
 The benefits that player 1, 2 and 3 provide upon cooperation are $2 + \delta_b, 2$ and $2 - \delta_b$ respectively.
@@
 The area within the white dashed lines represents the parameter values for which the marginal gain of choosing cooperation over defection is negative, for each single player and, in the right-most panel, for all players simultaneously.
-In this example, with this specific asymmetrical players, cooperation is only feasible in the long run if the asymmetries of players are aligned.
+In this example, cooperation is only feasible in the long run if the asymmetries of players are aligned.
 That is, overall cooperation is high only when the individual with a low cost of cooperation has a high benefit value.
-For panels a and b we use a selection strength of $\beta = 2$ while for panel c, we use a selection strength of $\beta = 5$.
+For panels a) and b) we use a selection strength of $\beta = 2$ while for panel c), we use a selection strength of $\beta = 5$.
 }
@@
 The upper panels refer to a high cost of cooperation ($c=1$) while the bottom panels to a low cost of cooperation ($c = 0.2$); left panels refer to a discounted public good ($w = 0.5$), and the right panels refer to a synergistic public good ($w = 1.5$).
-Each case is tagged with a symbol that places the particular case in the contour plot in panel b, b) Average cooperation frequency for varying discount/synergy factor, $w$, and varying cost of cooperation, $c$.
+Each case is tagged with a symbol that places the particular case in the contour plot in panel b).
+b) On the left, we show the average cooperation frequency for varying discount/synergy factor, $w$, and varying cost of cooperation, $c$.
 Cooperation is feasible when costs are not restrictively high and the public good is not too discounted.
-c) Here we show the average cooperation frequency for varying discount/synergy factor, $w$, and group size $N$.
+On the right, we show the average cooperation frequency for varying discount/synergy factor, $w$, and group size $N$.
 For this plot, the cost of cooperation for each player is $c = 0.4$.
 The feasibility of cooperation drops with larger group sizes when the public good is discounted.
-For all panels, the benefit of cooperation generated by each player is worth 2 units.
-The selection strength of introspection dynamics is $\beta = 5$ for all panels.}
+For all panels, $b=2$ and $\beta = 5$.}
 \label{Fig:GPGG-symmetric}
@@
 For a full description of the model, please see the section on rewarding.
-In this example, players 1 and 2 are identical in all aspects while player 3 is asymmetric to them in only a single aspect.
+In this example, players 1 and 2 are identical in all aspects while player 3 differs from them in only a single aspect.
 In here, we use Eq.
-(\ref{Eq:explicit-stationary-dist-representation}) to plot the exact probability with which the asymmetric players cooperate and reward cooperation after a long run of introspection.
+(\ref{Eq:explicit-stationary-dist-representation}) to plot the exact probability with which players cooperate and reward cooperation in the long run.
 We consider three types of asymmetry for player 3.
@@
 b) Then, we consider the case where player 3 is less productive than their co-players, $1.2 = r_3 < r_1 = 2$.
-c) Finally, we consider the case where player 3 has less information about co-players' rewarding strategies than their peers, that is, $0.1 = \lambda_3 < \lambda_1 = 0.9$.
+c) Finally, we consider the case where player 3 has less information about co-players' rewarding strategies than the others, that is, $0.1 = \lambda_3 < \lambda_1 = 0.9$.
 For all plots, we consider a high value for the selection strenght, $\beta = 10$.
 Unless otherwise mentioned, the following parameters are maintained for all panels: $c_i = 1$ (individual cost of cooperation), $r_i = 2$ (individual productivity), $\gamma_i = 0.1$ (individual cost of rewarding), $\lambda_i = 0.9$ (individual information about co-players' strategies).
-In panels a and b, the reward value $\rho = 0.3$ while for the last panel, c, the reward value $\rho = 1$.}
+In panels a) and b), the reward value is $\rho=0.3$ while for panel c), the reward value $\rho = 1$.}
 \label{Fig:SocialRewarding}

### 2023-03-01 latex/supp.tex
figs caption by marta, all changes by me, supp info by marta

@@
 
-\title{\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}}
+\title{\vspace{0pt} \sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}}
 \date{\empty}
@@
 \onehalfspacing
-\section*{Supplementary Figures: Asymmetric general public goods game}
+%\newpage
+%\section*{Supplementary Figures: Asymmetric general public goods game}
 
@@
 In here, we look at the cooperation probability for each player (and also overall cooperation) in stationary distribution of the introspection process.
-Players use a selection strength of $\beta = 5$.
-In the top row, we i) set the public good to be synergistic $w = 1.5$ and ii) allow a high reference cost, $c = 1$.
-In the bottom row, we i) set the public good to be discounted $w = 0.5$ and ii) allow a low reference cost $c = 0.2$.
-}
+In the top row, we set i) the public good to be synergistic $w = 1.5$ and ii) a high reference cost, $c = 1$.
+In the bottom row, we set i) the public good to be discounted $w = 0.5$ and ii) a low reference cost $c = 0.2$.
+For all panels, $\beta = 5$.}
 
@@
 The setup is the same as Supplementary Figure \ref{Fig:Supp-Fig1}.
-In here, we show the cooperation probability of each player (and also the overall cooperation) in the stationary distribution of the introspection process versus the reference cost $c$ (cost of player 2) and tthe synergy/discount factor of the public good, $w$.
+In here, we show the cooperation probability of each player (and also the overall cooperation) in the stationary distribution of the introspection process versus the reference cost $c$ (cost of player 2) and the synergy/discount factor of the public good, $w$.
 For each row, the strength of asymmetry between the players is fixed.
 In the top row, the players do not differ in their benefits (they all have a benefit of value 2) but player 1 and player 3 have their cost of cooperation 0.5 units higher and lower respectively than player 2 (cost of cooperation for player 2 is varied in the y-axis).
-In the bottom row, all the players have the same cost of cooperation, $c$ (which is varied in the y-axis).
-In this case, player 1, 2 and 3 generate asymmetric benefits.
-Player 1,2 and 3 generate, 3, 2 and 1 units of benefits.
+In the bottom row, all the players have the same cost of cooperation, $c$ (which is varied in the y-axis) but player 1 and player 3 have their benefit to the public good 1 unit higher and lower respectively than player 2.
 }

### 2023-03-02 latex/article.tex

@@
 
-%\title{\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}}
+\title{\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}}
 \title{\sffamily \Large {\bfseries Introspection dynamics in asymmetric multiplayers games}}
 \date{\empty}
-\author{\parbox[c]{16cm}{\centering \onehalfspacing \fontsize{11}{12}\selectfont Marta Couto$^{1*}$ and Saptarshi Pal$^{1*}$\\[0.2cm]
+\author{\parbox[c]{16cm}{\centering \onehalfspacing \fontsize{11}{12}\selectfont Marta C. Couto$^{1*}$ and Saptarshi Pal$^{1*}$\\[0.2cm]
 $^1$Max Planck Research Group Dynamics of Social Behavior, Max Planck Institute for Evolutionary Biology, 24306~Ploen, Germany}\\ \\
@@
 \onehalfspacing
+\section*{Author Information}
+\textbf{First co-author:} Marta C. Couto \\
+\noindent \textbf{Affiliation:} \\Max Planck Research Group Dynamics of Social Behavior, \\Max Planck Institute for Evolutionary Biology, 24306~Ploen, Germany \\ 
+\noindent \textbf{Email:} mccouto@evolbio.mpg.de \\
+\noindent \textbf{ORCID:} 0000-0002-2868-9685  \\ \\
+\textbf{Second co-author:} Saptarshi Pal \\
+\noindent \textbf{Affiliation:} \\Max Planck Research Group Dynamics of Social Behavior, \\Max Planck Institute for Evolutionary Biology, 24306~Ploen, Germany \\ 
+\noindent \textbf{Email:} pal@evolbio.mpg.de \\
+\noindent \textbf{ORCID:} 0000-0003-3805-1295
+\newpage 
 \section*{Abstract}
@@
 
-\section*{Introduction}
+\section{Introduction}
 
@@
 
-\section*{Model of introspection dynamics in multiplayer games}
+\section{Model of introspection dynamics in multiplayer games}
 We consider a normal form game with $N (\geq 2)$ players.
@@
 %\end{equation}
-\section*{Additive games and their properties under introspection dynamics}
+\section{Additive games and their properties under introspection dynamics}
 In this section we discuss the stationary properties of introspection dynamics when players learn to play strategies in a special class of games: additive games \cite{McAvoy:PlosCB:2015, Pena:JTB:2014}.
@@
 
-\subsection*{Example of an additive game: linear public goods game with 2 actions}
+\subsection{Example of an additive game: linear public goods game with 2 actions}
 In the simplest version of the linear public goods game (LPGG) with $N-$players, each player has two possible actions, to contribute (action $\C$, to cooperate), or to not contribute (action $\D$, to defect) to the public good.
@@
 
-\section*{Games with two actions and their properties under introspection dynamics}
+\section{Games with two actions and their properties under introspection dynamics}
 
@@
 
-\subsection*{An example of a  game with two actions: the general public goods game}
+\subsection{An example of a  game with two actions: the general public goods game}
 
@@
 
-\section*{Application: Introspection learning in a game with cooperation and rewards}
+\section{Application: Introspection learning in a game with cooperation and rewards}
 
@@
 
-\section*{Discussion and conclusion}
+\section{Discussion and conclusion}
 
@@
 We would like to thank Christian Hilbe and the members of the Research Group Dynamics of Social Behavior for valuable feedback.
+\section*{Statements and Declarations}
+The authors declare that they have no competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.
 \newpage
@@
 \centering
-\includegraphics[width =  \textwidth]{figures/figure1.eps}~\\[0.4cm]
+\includegraphics[width =  \textwidth]{figures/Fig1.eps}~\\[0.4cm]
 \caption{\onehalfspacing
@@
 \centering
-\includegraphics[width =  \textwidth]{figures/figure2.eps}~\\[0.4cm]
+\includegraphics[width =  \textwidth]{figures/Fig2.eps}~\\[0.4cm]
 \caption{\onehalfspacing
@@
 \centering
-\includegraphics[width =  0.65\textwidth, keepaspectratio]{figures/figure3.eps}~\\[0.4cm]
+\includegraphics[width =  0.65\textwidth, keepaspectratio]{figures/Fig3.eps}~\\[0.4cm]
 \caption{\onehalfspacing
@@
 \centering
-\includegraphics[width =  \textwidth]{figures/figure4.eps}~\\[0.4cm]
+\includegraphics[width =  \textwidth]{figures/Fig4.eps}~\\[0.4cm]
 \caption{\onehalfspacing

### 2023-07-12 latex/article.tex
checking if github push works

@@
 \newcommand{\D}{\mathrm{D}}
-
-\title{\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayers games}}
-\title{\sffamily \Large {\bfseries Introspection dynamics in asymmetric multiplayers games}}
+\newcommand{\LD}{\mathrm{LD}}
+\newcommand{\ID}{\mathrm{ID}}
+
+\title{\sffamily \Large Supplementary Information\\[0.1cm] {\bfseries Introspection dynamics in asymmetric multiplayer games}}
+\title{\sffamily \Large {\bfseries Introspection dynamics in asymmetric multiplayer games}}
 \date{\empty}
@@
 
-Evolutionary game theory and models of learning provide a powerful framework to describe strategic decision-making in social interactions. 
+Evolutionary game theory and models of learning provide powerful frameworks to describe strategic decision-making in social interactions. 
 In the simplest case, these models describe games among two identical players. 
@@
 This model provides a simple way to compute the players’ long-run probability of adopting each of their strategies. 
-In this paper, we extend some of the previous results of introspection dynamics for 2-player asymmetric games to games with arbitrarily many players. 
+In this paper, we extend some of the previous results of introspection dynamics for $2-$player asymmetric games to games with arbitrarily many players. 
 First, we derive a formula that allows us to numerically compute the stationary distribution of introspection dynamics for any multiplayer asymmetric game. 
@@
 
-% 4 to 6 keywords: multiplayer games, asymmetric games, non-linear interactions, learning model, introspection dynamics, strategy abundance, aditive games
-
 \noindent \textbf{Keywords}: multiplayer games, asymmetric games, non-linear interactions, introspection dynamics, strategy abundance, additive games.
-
-%Evolutionary game theory and learning models have contributed to the understanding of social interactions and how individuals learn to act strategically.
-%The simplest models involve two identical players.
-However, many interactions in everyday life are often complex, occurring among more than two individuals that differ between themselves.
-Such interactions can be captured by asymmetric multiplayer games.
-%Recently, introspection dynamics has proven to be a useful learning model for tackling asymmetric games.
-In this dynamics, at each time step, players compare their current strategy to an alternative strategy.
-If the update results in a payoff advantage, the new strategy is more likely adopted.
-This model provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (i.e., the stationary distribution).
-%In this paper, we extend some of the previous results of introspection dynamics on 2-player asymmetric games to games with multiple players.
-First, we derive a general explicit formula that allows us to numerically compute the stationary distribution of any multiplayer asymmetric game.
-Second, we obtain analytical expressions of the stationary distribution for two special cases, i) additive games (where the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions of their co-players), and ii) symmetric multiplayer games with two strategies.
-Finally, we revisit several classical games like the general public goods game to illustrate our results.
-%%word count: 236
-
-%-----SP ABSTRACT-----%
-%Social interactions are often modelled using simultaneous games.
-The simplest model involves two identical players.
-However, interactions in everyday life are complex and often involve more than two individuals that differ between themselves.
-Such interactions can be captured more realistically using asymmetric multiplayer games.
-Over the years, learning models and models from evolutionary game theory have studied how players may learn to play strategically in these games.
-Recently, introspection dynamics has proven to be a useful learning model for tackling complex games.
-In this dynamics, players compare their current strategy to an alternative strategy.
-If the update results in a payoff advantage, it is more likely adopted.
-This dynamics provides a simple way to compute the probability with which players play the different combinations of strategies in the long-run (the stationary distribution).
-In this paper, we extend some of the previous analytical results of introspection dynamics on games with two-players to games with more players.
-We obtain analytical expressions of the stationary distribution for multiplayer asymmetric games that have the special property of being additive in the payoffs.
-In such games, the payoff difference that a player gains by unilaterally switching to a different action is independent of the actions that their co-players play.
-In addition, we derive the stationary distribution for symmetric multiplayer games with two strategies.
-We discuss several classical games like the general public goods game to illustrate our results.
-
-%------MC ABSTRACT------%
-%The simplest form of social interaction occurs between two nearly similar individuals. This scenario can be stylized in a pairwise symmetric game. 
-%More complex behavior emerges when instead we consider multiple interacting individuals, and they may differ significantly among themselves.
-This case can be captured by a multiplayer asymmetric game.
-The complexity of these games increases both with the number and diversity of players.
-%From evolutionary dynamics to learning models, game theoretic frameworks have been widely used to study strategic behavior. 
-%Introspection dynamics has proven to be a useful learning model for tackling complex games. 
-%It provides a simple way to compute the average abundance of each combination of strategies (or actions), that is, the stationary distribution of strategies.
-%Here, our aim is to analyse multiplayer and (a)symmetric games.
-%We extend previous analytical results on pairwise games under introspection dynamics to multiplayer games. 
-%For general games, we obtain the analytical stationary distribution for 2 strategies, symmetric games.
-%Moreover, we consider a particular class of games -- additive games. 
-%In additive games, for any player, the difference between the payoffs provided by any two actions is constant, regardless of the co-players' actions. 
-%For these games, we derive the stationary distribution analytically, for any number of players and strategies, with no restriction to symmetric games. 
-%To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas. 
-%In general, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
-% 244 words
-
-%In addition, we find that the frequency of a state (a combination of actions played by each player) corresponds to the product of the frequencies of each player playing their respective strategy.
-
-\begin{comment}
-The simplest form of social interaction occurs between two nearly similar individuals. This scenario can be stylized in a pairwise symmetric game. 
-More complex behavior emerges when instead we consider multiple interacting individuals, and they may differ significantly among themselves.
-This case, in turn, can be captured by a multiplayer asymmetric game.
-The complexity of these games increases both with the number and diversity of players.
-From evolutionary dynamics to learning models, game theoretic frameworks have been widely used to study strategic behavior. 
-Introspection dynamics has proven to be a useful learning model to tackle complex games.
-%To analyse more complex games, researchers typically use approximations, e.g. weak selection, small mutation. 
-Here, our aim is to analyse multiplayer and (a)symmetric games. We extend previous analytical results of pairwise games under introspection dynamics to multiplayer games. 
-We divide games into two main categories: additive and non-additive (or general) games.
-In additive games, for any player, the difference between the payoffs provided by any two actions (or strategies) is constant, regardless of the co-players' actions. 
-Non-additive are all games that do not hold this property; hence, general games.
-For additive games, we derive the stationary distribution of strategies analytically, for any number of players and strategies. 
-%Additionally, we find that the joint distribution of strategies factorizes over the marginal distribution of strategies.
-Additionally, we find that the frequency of a state (a combination of actions played by each player) corresponds to the product of the frequencies of each player playing their respective strategy.
-For non-additive games, we obtain the analytical stationary distribution for 2-strategies symmetric games. For other cases, we provide numerical results. 
-To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas. 
-In general, players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
-%add rewarding game
-\end{comment}
 
@@
 Despite their simplicity, they provide important insights, such as how populations can sustain cooperation \cite{Axelrod:book:1984, Nowak:Science:2006,  Nowak:book:2011}.
-%An ubiquitous example of a model game for two players is the prisoner's dilemma.
-Here, the two individuals have a temptation to cheat, but at the same time, players are better off if they help each other.
-Solving this paradox has been the focus of many studies.
-These studies provide several explanations for why one can expect cooperation in such interactions \cite{Nowak:Science:2006}.
-Yet, many interesting collective behaviors occur when multiple individuals interact simultaneously \cite{Palm:JMB:1984, Skyrms:book:2003, Pacheco:PRSB:2009, Archetti:EL:2011, Archetti:JTB:2012, Gokhale:DGAA:2014, Hilbe:JTB:2015, Venkateswaran:PRSB:2019}.
+Yet, many interesting collective behaviors occur when multiple individuals interact simultaneously \cite{Palm:JMB:1984, Skyrms:book:2003, Pacheco:PRSB:2009, Archetti:EL:2011, Archetti:JTB:2012, Gokhale:DGAA:2014, Pena:JTB:2014, Hilbe:JTB:2015, Venkateswaran:PRSB:2019}.
 Most of these situations cannot be captured by the sum of several pairwise interactions.
 Thus, to account for such non-linearities, one needs to consider multiplayer games \cite{Gokhale:DGAA:2014}.
-For example, well-known effect that only emerges when more than two players are present is the ``second-order free-riding problem" \cite{Fowler:PNAS:2005}.
+For example, a well-known effect that only emerges when more than two players are present is the ``second-order free-riding problem" \cite{Fowler:PNAS:2005}.
 A natural solution to maintain pro-social behavior in a community is to monitor and punish defectors (and/or reward cooperators).
 However, most forms of sanctioning are considerably costly \cite{Henrich:Science:2006}.
-Therefore, an additional (second-order) dilemma
-%is at stake% 
-emerges: individuals would like cooperation to be incentivized but they prefer that others pay the associated costs.
-%deterring defection is beneficial for all, but an individual that does not pay the associated cost has an advantage over the ones that do.
-As long as cooperation is incentivized by punishment (or rewards) of others, individuals can take advantage by defecting in this second-order dilemma.
-%As such, this tempts everyone not to engage in costly punishment (or rewarding), and cooperation can break down.
-For this reason, peer-punishment and sanctioning institutions can be hard to sustain without additional mechanisms \cite{Panchanathan:Nature:2004, Perc:SciRep:2012, Hilbe:SciRep:2012, Couto:JTB:2020, Pal:NatCom:2022}.
+Therefore, an additional (second-order) dilemma emerges: individuals would like cooperation to be incentivized but they prefer that others pay the associated costs.
 \\ \\
@@
 In situations that require some sort of coordination and where expectations on others play an important role in one's decisions, a growing group size might hinder the optimal outcome \cite{Skyrms:book:2003}.
-Likewise, it has been shown that it is hard to cooperate in large groups \cite{Santos:PNAS:2011, Hilbe:JTB:2015}.
-This is however, not a general effect in any interaction \cite{gokhale:JTB:2011}.
-%This is not a general effect, though.
-It can happen that adding more players actually promotes cooperation.
-Gokhale and Traulsen (2011) investigate the 2-player and 3-player cases of a task allocation problem \cite{gokhale:JTB:2011}.
-Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, resulting in a decrease in free-riding.
-%As a biological example, consider a task allocation problem in a bacterial system.
-A strain of bacteria can do any of three actions: to specialize in producing one of two kinds of enzymes (at some personal cost) or not to produce any enzyme.
-The bacteria need two different types of enzymes at the same time to obtain resources from the environment.
-In \cite{gokhale:JTB:2011}, authors investigate both the 2-player and 3-player cases of this scenario.
-Although the underlying rules defining the interactions are the same for the two cases, simply introducing a third player changes the overall game, and hence the outcomes.
-With three players, the production of one of the enzymes increases while freeloading decreases, compared to the 2-player case.
-Additionally, 
-%interaction% 
-group size can vary in a population of players.
-There, not only the average group size can have an important effect, but also the variance of the group size distribution \cite{Pena:Evolution:2011, Broom:BMB:2019}.
+Likewise, it has been shown that it is hard to cooperate in large groups \cite{Santos:PNAS:2011, Hilbe:JTB:2015,Pena:jtb:2018}.
+This is not, however, a general effect \cite{gokhale:JTB:2011}.
+Additionally, group size can vary in a population of players.
+There, not only the average group size can have an important effect, but also the variance of the group size distribution \cite{Pena:Evolution:2011, Broom:BMB:2019} and the group size distribution itself \cite{Pena:JTB:2016}.
 \\ \\ 
@@
 Conversely, in asymmetric games, players can differ in their available actions and in their incentives to choose each action.
-%;players are of different types or roles. 
 Therefore, they can have uneven effects on others' payoffs too.
 For example, in public goods games and collective-risk dilemmas, players can have different initial endowments (or wealth), productivitites, costs, risk perceptions, or risk exposures \cite{Milinski:CC:2011, Vasconcelos:PNAS:2014, Abouchakra:JTB:2014, Hauser:Nature:2019, Merhej:JAIR:2022, Wang:PTRSB:2023}.
-Hence, to fully describe the state of the game, we need to know the exact action of each player.
+Hence, to fully describe the state of the game, we need to know the action of each player.
 This greatly increases the size of the game's state space; even more so, for more than two players.
 \\
-%Hence, to fully describe the state of the game, we need to know which of the players is doing what.
-This greatly increases the size of the game's state space; even more so, for more than two players.
-\\
-%meta communication; lit gap; our aim
-%\noindent Due to these reasons, one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
-Perhaps for that reason, there are not many studies on a general approach to multiplayer asymmetric games.
-As such, our aim here is to narrow that gap using introspection dynamics \cite{Couto:NJP:2022}.
-In the following section, we discuss several canonical frameworks from the literature that have been used to study both multiplayer games and asymmetric games.
-
-%\section*{Related Work}
 
@@
 \noindent Models from evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} and learning theory \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, have been widely used to study strategic behavior.
-%From evolutionary game theory (EGT) \cite{Maynard-Smith:Nature:1973, Maynard-Smith:book:1982, Hofbauer:book:1998, Nowak:book:2006} to learning models \cite{Sandholm:BioSys:1996, Fudenberg:book:1998b, Macy:PNAS:2002, Pangallo:GEB:2022}, game theoretic frameworks have been widely used to study strategic behavior.
-%, in particular, in multiplayer and asymmetric games.
-%In evolutionary game theory, we assume a population of players and a mechanism by which strategies evolve over time.
-More successful strategies tend to persist in the population, either by genetic or cultural inheritance.
-The first key concept in evolutionary game theory is ``evolutionary stable strategy" (ESS),  introduced in 1973, in the seminal paper of John Maynard Smith and George Price \cite{Maynard-Smith:Nature:1973}.
-A (monomorphic) population playing an ESS cannot be invaded by mutants.
-\noindent The concept of evolutionary stable strategy, originally proposed for parwise encounters \cite{Maynard-Smith:Nature:1973}, was extended to multiplayer games \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}.
-Also the well-known replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998}
-%easily comprises 
-can easily account for multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Pena:Evolution:2011, Cressman:PNAS:2014, Pena:JTB:2014}.
+ The concept of evolutionary stable strategy, originally proposed for parwise encounters \cite{Maynard-Smith:Nature:1973}, was extended to multiplayer games \cite{Palm:JMB:1984, Broom:BMB:1997, Bukowski:IJGT:2004}.
+Also the well-known replicator equation \cite{Taylor:MB:1978, Hofbauer:book:1998} can easily account for multiplayer games \cite{Hauert:JTB:2006a, gokhale:PNAS:2010, Cressman:PNAS:2014, Pena:JTB:2014}.
 More recently, the replicator-mutator equation was applied to study the dynamics of multiplayer games, too \cite{Duong:DGAA:2020}.
@@
 For example, if there are two different types of players, typically, either there are two populations co-evolving (``bimatrix games" \cite{Hofbauer:book:1998, Gokhale:PRSB:2012, Tuyls:SciRep:2018}) or there is a single population of players where each can play the two types or roles (``role games") \cite{Hofbauer:book:1998}.
-%For role games, a strategy must include the action played in each of the two roles. 
 The case of asymmetric games with more than two players is substantially less studied within deterministic EGT.
@@
 Notably, although these works study multiplayer games, they consider, at most, two different types (drawn from two populations), which leaves out the exploration of full asymmetry.
-% models of multiple populations seem unnatural
 % stochastic EGT
 Also stochastic evolutionary game dynamics \cite{Nowak:Nature:2004, Traulsen:bookchapter:2009} provides several models for studying multiplayer and asymmetric games. 
-%Here, the quantities of interest are fixation probabilities and fixation times (i.e., the probability and the average time that a single mutant overtakes an initially monomorphic population) for when mutations are rare \cite{Fudenberg:TPB:2006}, or the average strategy abundance (i.e., the stationary distribution of strategy frequencies) for when mutation rates take intermediate values \cite{antal:JTB:2009a, antal:JTB:2009b}.
-%These frameworks have been applied to asymmetric games assuming co-evolving (finite) subpopulations of different player types. 
-Fixation probabilities \cite{Fudenberg:TPB:2006} in asymmetric 2-player \cite{Sekiguchi:DGA:2017}, asymmetric 3-player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived.
-Furthermore, average strategy abundances \cite{antal:JTB:2009a, antal:JTB:2009b} were obtained only for 2-player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:JMB:2022}.
+Fixation probabilities \cite{Fudenberg:TPB:2006} in asymmetric $2-$player \cite{Sekiguchi:DGA:2017}, asymmetric $3-$player games \cite{Sekiguchi:DGAA:2022}, and symmetric multiplayer games \cite{Kurokawa:PRSB:2009, gokhale:PNAS:2010} were recently derived.
+Furthermore, average strategy abundances \cite{antal:JTB:2009a, antal:JTB:2009b} were obtained only for $2-$player asymmetric games \cite{Ohtsuki:JTB:2010, Sekiguchi:PA:2013} or multiplayer symmetric games \cite{gokhale:JTB:2011, Wu:Games:2013, Kroumi:JMB:2022}.
 For a review on evolutionary multiplayer games both in infinitely large populations as well as in finite populations, we refer to Gokhale and Traulsen (2014) \cite{Gokhale:DGAA:2014}.
@@
 
-%When deriving fixation probabilities and times, it is assumed that mutations are rare, such that, no new mutant arises between the very first and its eventual fixation \cite{}. 
-%\cite{Chalub:BMB:2019}
-
-%strategy abundance papers (intermediate mutation or mutation-selection equilibrium)
-%2-player symmetric and asymmetric games, any number of strategies, Birth-death process \cite{ohtsuki:JTB:2010}
-%2-player symmetric and asymmetric games, any number of strategies, Death-birth process \cite{Sekiguchi:PA:2013}
-
-% multiplayer 
-%\cite{gokhale:PNAS:2010}
-%\cite{gokhale:JTB:2011} extends the approach in \cite{antal:JTB:2009b} for 2-player to multiplayer (symmetric) games. 
-%\cite{Wu:Games:2013} symmetric, any number of strategies, Birth-death process (equations connections?)
-%\cite{Gokhale:DGAA:2014} review on evolutionary multiplayer games both for infinitely large populations as well as finite population
-
-% nice multiplayer applications
-
 %[Learning models]
-%learning models in general
-%Despite the conceptual disparities, there have been already some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005, Bloembergen:JAIR:2015, Zhang:arxiv:2022}.
-% Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from the classical game theory itself \cite{Fudenberg:book:1998b}.
-The ``theory of learning in games" was proposed as a refinement of classical equilibrium concepts, like Nash equilibrium, where strict assumptions of common knowledge of rationality are made.
-Instead, learning consists of ``\textit{an alternative explanation that equilibrium arises as the long-run outcome of a process in which less than fully rational players grope for optimality over time}" \cite{Fudenberg:book:1998b}.
-In this context, several learning models were introduced, such as fictitious play \cite{Gaunersdorfer:GEB:1995} or perturbed best response dynamics \cite{Hofbauer:GEB:2005}.
-%learning models for asymmetric and multiplayer games? fictious play for multiplayer games \cite{fudenberg:book:1998b} 
-%can we say most of learning models have no analytical or exact results?
-\noindent Introspection dynamics has recently proven to be a useful learning model for tackling asymmetric games \cite{Couto:NJP:2022, Hauser:Nature:2019, McAvoy:PNASnexus:2022, Schmid:PlosCB:2022}.
+\noindent Introspection dynamics has recently proven to be a useful learning model for tackling (a)symmetric games \cite{Couto:NJP:2022, Hauser:Nature:2019, McAvoy:PNASnexus:2022, Schmid:PlosCB:2022, Ramirez:SciRep:2023}.
 In here, players update their strategies by exploring their own set of strategies in the following simple way: each time, after a round of the game, a random player considers a random alternative strategy; they compare the payoff that it would have given them to their current payoff; if the new strategy would provide a higher payoff, it is more likely adopted on the next round.
@@
 While in Couto et al.
-(2022) \cite{Couto:NJP:2022} only 2-player games were considered, this framework is general enough to account for multiple players.
+(2022) \cite{Couto:NJP:2022} only $2-$player games were considered, this framework is general enough to account for multiple players.
 Particularly, introspection dynamics allows a natural exploration of full asymmetry in many-player games compared to population models.
@@
 Introspection avoids this assumption because players' decisions only depend on their own payoffs.
+An existing model that shares this same property is the logit-response dynamics or, simply, logit dynamics \cite{Blume:GEB:1993, Alos-Ferrer:GEB:2010,Auletta:Annual:2011}.
+Unlike introspection dynamics, at each time, the randomly drawn player to update their strategy, can switch to any other strategy with a non-zero probability.
+This probability grows with the payoff provided by each strategy at the (possible) future state.
+The probability of switching functions of introspection dynamics and logit dynamics are similar in their exponential shape; hence, the two processes have some interesting connections.
 \\ \\
 %[Our proposal]
-\noindent Here, we extend previous results \cite{Couto:NJP:2022} of pairwise games under introspection dynamics to multiplayer games. 
+\noindent Here, we extend previous results of pairwise games under introspection dynamics  \cite{Couto:NJP:2022} to multiplayer games. 
 First, we derive a formula that allows us to numerically compute the stationary distribution of introspection dynamics for any multiplayer asymmetric game. 
@@
 To illustrate our theoretical results, we analyse various multiplayer asymmetric social dilemmas, extending the framework in \cite{Hauert:JTB:2006a} to asymmetric games.
-Finally, we also study the asymmetric version of a public goods game with a rewarding stage \cite{Pal:NatCom:2022}.
+We also study the asymmetric version of a public goods game with a rewarding stage \cite{Pal:NatCom:2022}.
+Finally, we compare introspection dynamics with logit dynamics, in the Appendix, where we show that the two processes have equivalent stationary distributions for some particular games (namely, 2-strategy, potential and additive games).
 
@@
 \times m_N$ states.
-We denote a state of the game by collecting the actions of all the players in the game in a vector, $\abf := (a_1, a_2, ..., a_N)$ where $\abf \in \A := \A_1 \times \A_2 \times ...
+We denote a state of the game by collecting the actions of all the players in a vector, $\abf := (a_1, a_2, ..., a_N)$ where $\abf \in \A := \A_1 \times \A_2 \times ...
 \times \A_N$ and $a_i \in \A_i$.
-We also use the notation, $\abf := (a_i, \abf_{-i})$ to denote the state from the perspective of player $i$.
+We also use the common notation, $\abf := (a_i, \abf_{-i})$ to denote the state from the perspective of player $i$.
 In the state $(a_i, \abf_{-i})$, player $i$ plays the action $a_i \in \A_i$ and their co-players play the actions $\abf_{-i} \in \A_{-i}$ where $\A_{-i}$ is defined as $\A_{-i}:= \prod_{j \neq i} \A_j$.
@@
 \begin{equation}
- p_{a_{i,k} \to a_{i,l}} (\abf_{-i})= \frac{1}{1 + e^{\displaystyle -\beta(\pi_i(a_{i,l}, \abf_{-i}) - \pi_i(a_{i,k}, \abf_{-i}))}}
+ p_{a_{i,k} \to a_{i,l}} (\abf_{-i})= \frac{1}{1 + e^{\displaystyle -\beta(\pi_i(a_{i,l}, \abf_{-i}) - \pi_i(a_{i,k}, \abf_{-i}))}} .
  \label{Eq:introspection-update}
@@
 For $\beta = 0$, players update to a randomly chosen strategy with probablity $0.5$.
-For $\beta > 0$, players update to the alternative strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them an increase (or decrease) in the payoffs.
-\\ \\
-\noindent Introspection dynamics can be studied by analyzing properties of the transition matrix, $\T$ of the resulting dynamical process.
+For $\beta > 0$, players update to the alternative strategy under consideration with probablity greater than $0.5$ (or less than $0.5$) if the switch gives them an increase (or decrease) in the payoff.
+\\ \\
+\noindent Introspection dynamics comprises a Markov chain and can be studied by analyzing the properties of the corresponding transition matrix $\T$.
 The transition matrix element $\mathrm{T}_{\abf,\bbf}$ denotes the conditional probability that the game goes to the state $\bbf$ in the next round if it is in state $\abf$ in the current round.
 In order to formally define the transition matrix, we first need to introduce some notations and definitions.
-We start by defining the neighbourhood set of $\abf$,
+We start by defining the neighbourhood set of state $\abf$.
 
@@
 \begin{equation}
-\mathrm{Neb}(\abf) := \{\bbf \in \A  \big| \quad \exists j:  b_{j} \neq a_{j} \land \bbf_{-j} = \abf_{-j}  \}
+\mathrm{Neb}(\abf) := \{\bbf \in \A  \big| \quad \exists j:  b_{j} \neq a_{j} \land \bbf_{-j} = \abf_{-j}  \}.
 \label{Eq:neighbourhood-states}
@@
 \begin{equation}
-a_{\mathrm{I}(\abf, \bbf)} \neq b_{\mathrm{I}(\abf, \bbf)}
+a_{\mathrm{I}(\abf, \bbf)} \neq b_{\mathrm{I}(\abf, \bbf)}.
 \end{equation} 
@@
 \noindent In the previous example, the index of difference between the neighbouring states $(\C,\C,\C)$ and $(\C,\C,\D)$ is $3$.
-Using the above definitions, one can formally define the transition matrix of introspection dynamics by:
+Using the above definitions, one can formally define the transition matrix of introspection dynamics by
 
@@
 1 - \sum_{\cbf \neq \bbf} \mathrm{T}_{\abf,\cbf} \quad &\text{ if } \abf = \bbf
-\end{cases}
+\end{cases}.
 \label{Eq:transition-matrix}
@@
 \noindent When the selection strength, $\beta$, is finite, the transition matrix of introspection dynamics has a unique stationary distribution.
-A finite value of $\beta$ results in non-zero probability of transition between neighbouring states.
-Since no state is isolated (i.e., every state belongs in the neighbourhood set of another state) and there are only finitely many states of the game, every state is reachable in a finite number of steps from any starting point with non-zero probability.
+A finite value of $\beta$ results in a transition of non-zero probability between neighbouring states.
+Since no state is isolated (i.e., every state belongs in the neighbourhood set of another state) and there are only finitely many states of the game, every state is reachable in a finite number of steps from any starting point.
 The transition matrix, $\T$, is therefore primitive for a finite $\beta$.
@@
 \end{eqnarray}
-\noindent where $\mathbf{1}$ is the column vector with the same size as $\ubf$ and has all elements as $1$.
+\noindent where $\mathbf{1}$ is the column vector with the same size as $\ubf$ and has all elements equal to $1$.
 For all the analytical results in this paper, we consider $\beta$ to be finite so that stationary distributions of the processes are unique.
@@
 Using Eq.
-(\ref{Eq:explicit-stationary-dist-representation}), one can compute the unique stationary distribution of introspection dynamics (with a finite $\beta$) for any normal form game (with arbitrary number of asymmetric players).\\
-
-\noindent The stationary distribution element $\mathrm{u}_\abf$ is the probability that state $\abf$ will be played by the players in the long run.
+(\ref{Eq:explicit-stationary-dist-representation}), one can compute the unique stationary distribution of introspection dynamics (with a finite $\beta$) for any normal form game (with arbitrary number of asymmetric players and strategies).\\
+
+\noindent The stationary distribution element $\mathrm{u}_\abf$ is the probability that the state $\abf$ will be played by the players in the long-run.
 Using the stationary distribution, one can calculate the marginal probabilities corresponding to each player's actions.
-That is, the probability that player $i$ plays action $a \in \A_i$ in the long run, $\xi_{i,a}$, can be computed as,
-\begin{equation}
-\mathbf{\xi}_{i,a} := \sum_{\qbf \in \A_{-i}} \mathrm{u}_{(a, \qbf)}
+That is, the probability that player $i$ plays action $a \in \A_i$ in the long-run, $\xi_{i,a}$, can be computed as
+\begin{equation}
+\mathbf{\xi}_{i,a} := \sum_{\qbf \in \A_{-i}} \mathrm{u}_{(a, \qbf)}.
 \label{Eq:marginal-definition}
@@
 \section{Additive games and their properties under introspection dynamics}
-In this section we discuss the stationary properties of introspection dynamics when players learn to play strategies in a special class of games: additive games \cite{McAvoy:PlosCB:2015, Pena:JTB:2014}.
+In this section we discuss the stationary properties of introspection dynamics when players learn to play strategies in a special class of games: additive games.
 In an additive game, the payoff difference that a player earns by making a unilateral switch in their actions is independent of what their co-players play.
@@
 \noindent is independent of $\qbf$ and only dependent on $x$ and $y$.
-In the literature, this property is sometimes called \emph{equal gains from switching} \cite{Pena:JTB:2014}.
-For games with this property, the stationary distribution of introspection dynamics takes a simple form,
+In the literature, this property is sometimes called \emph{equal gains from switching} \cite{Nowak:AAM:1990, Van-Veelen:JTB:2009}.
+For games with this property, the stationary distribution of introspection dynamics takes a simple form.
 
  \begin{Prop}
-When $\beta$ is finite, the unique stationary distribution, $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$, of introspection dynamics for the N-player additive game is given by: 
+When $\beta$ is finite, the unique stationary distribution, $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$, of introspection dynamics for an $N-$player additive game is given by
 \begin{equation}
@@
 \end{Prop}
-\noindent For all proofs of Propositions and Corollaries, please see the Appendix.
+\noindent For all proofs of Propositions and Corollaries, please see the Appendix 2.
 Using the stationary distribution and Eq.
-(\ref{Eq:marginal-definition}), one can also exactly compute the cumulative probabilities with which players play their actions in the long run (i.e., the marginal distributions).
+(\ref{Eq:marginal-definition}), one can also exactly compute the cumulative probabilities with which players play their actions in the long-run (i.e., the marginal distributions).
 In this regard, introspection learning in additive games is particularly interesting.
@@
 \begin{Prop}
-Let $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$ be the unique stationary distribution of introspection dynamics with finite $\beta$ for the N-player additive game.
+Let $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$ be the unique stationary distribution of introspection dynamics with finite $\beta$ for an $N-$player additive game.
 Then, $\mathrm{u}_\abf$ is the product of the marginal probabilities with which each player plays their respective actions in $\abf$.
@@
 \begin{equation}
-\mathrm{u}_\abf = \prod_{j = 1}^N \xi_{j,a_j}
+\mathrm{u}_\abf = \prod_{j = 1}^N \xi_{j,a_j}.
 \label{Eq:additive-game-products}
@@
 
-\noindent For the $N$-player additive game, $\xi_{j,a_j}$ is given by,
+\noindent For an $N$-player additive game, $\xi_{j,a_j}$ is given by
 
@@
 \noindent The above proposition states that for additive games, the stationary distribution of introspection dynamics can be factorized into its corresponding marginals.
-In the long run, the probability that players play the state $\abf = (a_1, a_2, ...,a_N)$ is the product of the cumulative probabilities that player 1 plays $a_1$, player 2 plays $a_2$ and so on.
-This property of the additive game was already shown for the simple two-player, two-action donation game in Couto et al.
+In the long-run, the probability that players play the state $\abf = (a_1, a_2, ...,a_N)$ is the product of the cumulative probabilities that player 1 plays $a_1$, player 2 plays $a_2$ and so on.
+This property of the additive game was already shown for the simple $2-$player, $2-$action donation game in Couto et al.
 \cite{Couto:NJP:2022}.
-Here we extend that result for any additive game with arbitrary number of players, each having an arbitrary number of strategies.
-In the next section we use the well-studied example of the linear public goods game (an additive game) to illustrate these results.
+Here, we extend that result for any additive game with arbitrary number of players, each having an arbitrary number of strategies.
+In the next section, we use the well-studied example of the linear public goods game (an additive game) to illustrate these results.
 
 \subsection{Example of an additive game: linear public goods game with 2 actions}
-In the simplest version of the linear public goods game (LPGG) with $N-$players, each player has two possible actions, to contribute (action $\C$, to cooperate), or to not contribute (action $\D$, to defect) to the public good.
+In the simplest version of the linear public goods game (LPGG) with $N$ players, each player has two possible actions, to contribute (action $\C$, to cooperate), or to not contribute (action $\D$, to defect) to the public good.
 The players may differ in their cost of cooperation and the benefit they provide by contributing to the public good.
@@
 We define an indicator function $\alpha(.)$ to map the action of cooperation to 1 and the action of defection to 0.
-That is $\alpha(\C) = 1$ and $\alpha(\D) = 0$.
-The payoff of player $i$ when the state of the game is $\abf$ is given by: \\
-\begin{equation}
-\pi_i(\abf) = \frac{1}{N}\sum_{j=1}^N \displaystyle \alpha(a_j) b_j - \alpha(a_i) c_i
+That is, $\alpha(\C) = 1$ and $\alpha(\D) = 0$.
+The payoff of player $i$ when the state of the game is $\abf$ is given by \\
+\begin{equation}
+\pi_i(\abf) = \frac{1}{N}\sum_{j=1}^N \displaystyle \alpha(a_j) b_j - \alpha(a_i) c_i .
 \label{Eq:linear-pgg-payoff}
@@
 \\
-\noindent The payoff difference that a player earns by unilaterally switching from $\C$ to $\D$ (or \emph{vice-versa}) in the linear public goods game is independent of what the other co-players play in the game.
+\noindent The payoff difference that a player earns by unilaterally switching from $\C$ to $\D$ (or \emph{vice-versa}) in the linear public goods game is independent of what the other players play in the game.
 That is, for every player $i$,
@@
 For player $i$, defection dominates cooperation when $c_i > b_i/N$ while cooperation dominates defection when $c_i < b_i/N$.
-Using Proposition \ref{Th:additive-games-stationary-dist}, one can derive the closed form expression for the stationary distribution of a $N-$player linear public goods game with two strategies.
+Using Proposition \ref{Th:additive-games-stationary-dist}, one can derive the closed form expression for the stationary distribution of an $N-$player linear public goods game with two strategies.
 \begin{Prop}
 \label{prop:stationary-dist-lpgg}
-When $\beta$ is finite, the unique stationary distribution of introspection dynamics for a $N-$player linear public goods game is given by: 
+When $\beta$ is finite, the unique stationary distribution of introspection dynamics for an $N-$player linear public goods game is given by
 \\
@@
 -&1 \quad \text{if} \quad a = \D
-\end{cases}
+\end{cases}.
 \end{equation} \\
@@
 \noindent We use a simple example to illustrate the above result.
-Consider a 3-player linear public goods game.
-All players provide a benefit of 2 units when they contribute to the public good ($b_1 = b_2 = b_3 = 2$).
+Consider a $3-$player linear public goods game.
+All players provide a benefit of $2$ units when they contribute to the public good ($b_1 = b_2 = b_3 = 2$).
 They differ, however, in their cost of cooperation.
-For player 1 and 2, the cost of cooperation is 1 unit ($c_1 = c_2 = 1$) while for the third player, the cost is 1.5 units ($c_3 = 1.5$).
-In the stationary distribution of the process with selection strength $\beta = 1$, the cumulative probability that player 1 (or 2) cooperates and player 3 defects are $\xi_{1,\C} = \xi_{2,\C}= 0.417$ and $\xi_{3,\D} = 0.697$ respectively.
+For player $1$ and $2$, the cost of cooperation is $1$ unit ($c_1 = c_2 = 1$) while for the third player, the cost is $1.5$ units ($c_3 = 1.5$).
+In the stationary distribution of the process with selection strength $\beta = 1$, the cumulative probability that player $1$ (or $2$) cooperates and player $3$ defects are $\xi_{1,\C} = \xi_{2,\C}= 0.417$ and $\xi_{3,\D} = 0.697$, respectively.
 With the exact values, one can confirm the factorizing property of the stationary distribution for additive games in this example (i.e., Proposition \ref{Th:additive-game-product-of-marginals}).
@@
 (\ref{Eq:stationary_dist_lpgg}) to systematically analyze the LPGG under introspection dynamics.
-First, we study the simplest case where all players are symmetric (the cost and benefit for all the 4 players are $c$ and $b$).
+First, we study the simple case of $4-$player symmetric LPGG (the cost and benefit for all the $4$ players are $c$ and $b$).
 Since all players are identical, the states of the game can be enumerated by counting the number of cooperators in the state.
-There are only 5 distinct states of the game (from 0 to 4 cooperators).
+There are only $5$ distinct states of the game (from $0$ to $4$ cooperators).
 When the parameters of the game are such that defection dominates cooperation ($b = 2, c = 1$, Fig.
@@
 \ref{Fig:LPGG-symmetric}b).
-Since every possible state is equiprobable in the limit of $\beta \to 0$, the outcome with $2$ cooperators is most likely only because there are more states with 2 cooperators than states with any other number of cooperators.
-\\ \\
-\noindent Naturally, $\beta$ plays an important role in determining the overall cooperation in the long run.
+Since every possible state is equiprobable in the limit of $\beta \to 0$, the outcome with $2$ cooperators is most likely only because there are more states with $2$ cooperators than states with any other number of cooperators.
+\\ \\
+\noindent Naturally, $\beta$ plays an important role in determining the overall cooperation in the long-run.
 When $\beta$ is low, average cooperation varies weakly with the strength of the dilemma, $b/N - c$ (Fig.
@@
 \noindent 
-To study what effects might appear due to asymmetry in the LPGG, we consider the game with 3 asymmetric players.
+To study what effects might appear due to asymmetry in the LPGG, we consider the game with $3$ asymmetric players.
 All the players can differ in their cost of cooperation and the benefit they provide to the public goods.
-In this setup, the reference player's (player 2) cost and benefit values are $1$ and $2$ units respectively.
+In this setup, the cost and benefit values of the reference player (player 2) are $1$ and $2$ units, respectively.
 Player 1 and player 3 differ from the reference player in opposite directions.
-For player 1, the cost and benefit are $1 + \delta_c$ and $2 + \delta_b$ respectively while for player 3, the cost and benefit are $1 - \delta_c$ and $2 - \delta_b$, respectively.
+For player 1, the cost and benefit are $1 + \delta_c$ and $2 + \delta_b$, respectively, while for player 3, the cost and benefit are $1 - \delta_c$ and $2 - \delta_b$, respectively.
 The terms $\delta_b$ and $\delta_c$ represents the strength of asymmetry between the three players (a higher absolute value of $\delta$ indicating a bigger asymmetry).
-When the players only differ in their cost of cooperation ($\delta_b = 0$ and $\delta_c = 0.5$, Fig \ref{Fig:LPGG-asymmetric}a, left), their relative cooperation in the long run reflects their relative ability to cooperate.
+When the players only differ in their cost of cooperation ($\delta_b = 0$ and $\delta_c = 0.5$, Fig \ref{Fig:LPGG-asymmetric}a, left), their relative cooperation in the long-run reflects their relative ability to cooperate.
 The player with the lowest cooperation cost (player 3), cooperates with the highest probability (and \emph{vice-versa},  Fig \ref{Fig:LPGG-asymmetric}a, right).
-Similarly, when players only differ in their ability to produce the public good ($\delta_b = 1$ and $\delta_c = 0$, Fig \ref{Fig:LPGG-asymmetric}b left), their relative cooperation in the long run reflects the relative benefits they provide with their cooperation (Fig \ref{Fig:LPGG-asymmetric}b, right).
-In this example, if we consider that the reference player provides a benefit of 2 units and has a cost of 1 unit (in which case, defection always dominates cooperation for them), defection dominates cooperation for player 1 if and only if $\delta_b < 1 + 3\delta_c$ and for player 3 only when $\delta_b > 3\delta_c - 1$.
+Similarly, when players only differ in their ability to produce the public good ($\delta_b = 1$ and $\delta_c = 0$, Fig \ref{Fig:LPGG-asymmetric}b left), their relative cooperation in the long-run reflects the relative benefits they provide with their cooperation (Fig \ref{Fig:LPGG-asymmetric}b, right).
+In this example, if we consider that the reference player provides a benefit of $2$ units and has a cost of $1$ unit (in which case, defection always dominates cooperation for them), defection dominates cooperation for player 1 if and only if $\delta_b < 1 + 3\delta_c$ and, for player 3, only when $\delta_b > 3\delta_c - 1$.
 These regions in the $\delta_b-\delta_c$ parameter plane that correspond to defection dominating cooperation are circumscribed by white dashed lines in Fig.
@@
 \ref{Fig:LPGG-asymmetric}c).
-In the long run, the average cooperation frequency of the group is low if the asymmetry in the benefit value is bounded, $3\delta_c - 1 < \delta_b < 3\delta_c + 1$.
+In the long-run, the average cooperation frequency of the group is low if the asymmetry in the benefit value is bounded as $3\delta_c - 1 < \delta_b < 3\delta_c + 1$.
 This includes the case where players are symmetric ($\delta_b = \delta_c = 0$).
@@
 
-In the previous section we studied the properties of additive games under introspection dynamics.
-In this section, we study games that are a) not necessarily additive and b) have only two actions for each player.
+In the previous section, we studied the properties of additive games under introspection dynamics.
+In this section, we study games that are\textit{ a}) not necessarily additive and \textit{b}) have only two actions for each player.
 First, we study the symmetric version of such a game.
-A $N$-player symmetric normal form game with two actions has the following properties:
+An $N$-player symmetric normal form game with two actions has the following properties:
 
@@
 \item  All players have the same action set $\mathcal{A} := \{\C,\D\}$. That is, $\A_1 = \A_2 = ... = \A_N := \mathcal{A}$. 
-\item Players have the same payoff when they play against the same composition of co-players. That is, for any $i,j \in \{1,2,...,N\}$, $a \in \mathcal{A}$ and $\bbf \in \mathcal{A}^{N-1}$,
-\begin{equation}
-\pi_i(a,\bbf) = \pi_j(a,\bbf)
+\item Players have the same payoff when they play the same action against the same composition of co-players.
+That is, for any $i,j \in \{1,2,...,N\}$, $a \in \mathcal{A}$ and $\bbf \in \mathcal{A}^{N-1}$,
+\begin{equation}
+\pi_i(a,\bbf) = \pi_j(a,\bbf).
 \end{equation} 
@@
 \begin{equation}
-f(j) := \pi^\D(j) - \pi^\C(j)
+f(j) := \pi^\D(j) - \pi^\C(j).
 \label{Eq:f-switching-CtoD}
@@
 %\\
-\noindent The stationary distribution of a two-action symmetric game under introspection dynamics can be explictly computed using the following proposition,
+\noindent The stationary distribution of a $2-$action symmetric game under introspection dynamics can be explictly computed using the following proposition.
 
@@
 \label{Prop:Symmetric-2-strategies-state}
-When $\beta$ is finite, the unique stationary distribution of introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\mathrm{u}_{\abf})_{\abf \in \mathcal{A}^N}$, is given by:
+When $\beta$ is finite, the unique stationary distribution of introspection dynamics for an $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, $(\mathrm{u}_{\abf})_{\abf \in \mathcal{A}^N}$, is given by
 \begin{equation}
@@
 \end{equation}
-where $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}) and $\mathcal{C}(\abf)$ is the number of cooperators in state $\abf$. The term $\Gamma$ is the normalization factor given by:
+where $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}) and $\mathcal{C}(\abf)$ is the number of cooperators in state $\abf$. The term $\Gamma$ is the normalization factor given by
 \begin{equation}
 \label{Eq:stationary-dist-normalization-symm-2-stgs-state}
-\Gamma = \displaystyle \sum_{\abf' \in \mathcal{A}^N} \prod_{j = 1}^{\mathcal{C}(\abf')} \displaystyle e^{-\beta f(j-1)}
+\Gamma = \displaystyle \sum_{\abf' \in \mathcal{A}^N} \prod_{j = 1}^{\mathcal{C}(\abf')} \displaystyle e^{-\beta f(j-1)}.
 \end{equation}
@@
 \noindent The number of unique states of the game can be reduced from $2^N$ to $N+1$  due to symmetry.
-In the reduced state space, the state, $k$, corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
+In the reduced state space, the state $k$ corresponds to $k$ players playing $\C$ and $N-k$ players playing $\D$.
 Then, Proposition \ref{Prop:Symmetric-2-strategies-state} can be simply reformulated by relabelling the states as follows,
@@
 \label{Lemma: Symmetric-2-stg}
-When $\beta$ is finite, the unique stationary distribution, $(\mathrm{u}_k)_{k \in \{0,1,...,N\}}$, of introspection dynamics for the $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
+When $\beta$ is finite, the unique stationary distribution, $(\mathrm{u}_k)_{k \in \{0,1,...,N\}}$, of introspection dynamics for an $N-$player symmetric normal form game with two actions, $\mathcal{A} = \{\C, \D \}$, is given by \\
 \begin{equation}
@@
 \end{equation} \\ 
-where, $k$ represents the number of $\C$ players in the state and $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}). The term $\Gamma$ is the normalization factor, given by, \\
+where $k$ represents the number of $\C$ players in the state and $f(j)$ is defined as in Eq. (\ref{Eq:f-switching-CtoD}). The term $\Gamma$ is the normalization factor, given by, \\
 \begin{equation}
 \label{Eq:normalization-Tk}
-\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)}
+\Gamma = \displaystyle \sum_{k=0}^N {N \choose k} \cdot \displaystyle \prod_{j=1}^{k} \displaystyle e^{-\beta f(j-1)} .
 \end{equation}
@@
 \noindent The above corollary follows directly from Proposition \ref{Prop:Symmetric-2-strategies-state}.
-The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$, $\C$ players (and therefore $N-k$, $\D$ players).
+The key step is to count the number of states in the state space $\mathcal{A}^N$ that corresponds to exactly $k$ $\C$ players (and therefore $N-k$ $\D$ players).
 This count is simply the binomal coefficient $N \choose k$.
@@
 
-To study general public goods game, we adopt the framework of general social dilemmas from Hauert et al.
+To study general public goods games, we adopt the framework of general social dilemmas from Hauert et al.
 \cite{Hauert:JTB:2006a}.
@@
 Before we explain the asymmetric setup, we describe the original model briefly.
-In the symmetric case, all $N$ players have the same cost of cooperation, $c$ and they all generate the same benefit $b$ for the public good.
+In the symmetric case, all $N$ players have the same cost of cooperation $c$ and they all generate the same benefit $b$ for the public good.
 Unlike the linear public goods game, contributions to the public good are scaled by a factor that is determined by $w$ and the number of cooperators in the group.
@@
 \begin{align}
-\pi^{\D}(k) &= \frac{b}{N}(1 + w + w^2 + ... + w^{k-1}) \\[15pt]
-\pi^{\C}(k) &= \pi^{\D}_i(k) - c
+\pi^{\D}(k) &= \frac{b}{N}(1 + w + w^2 + ... + w^{k-1}), \\[15pt]
+\pi^{\C}(k) &= \pi^{\D}_i(k) - c .
 \label{Eq:payoff-synergistic-symmetric}
@@
 Every cooperator's contribution is as valuable as the benefit that they can generate.
-When $w < 1$, the effective contribution of every additional cooperator goes down by a factor, $w$ (compared to the last cooperator).
-The public goods is said to be discounting in this case.
-On the other hand when $w > 1$, every new contribution is more valuable than the previous one.
+When $w < 1$, the effective contribution of every additional cooperator goes down by a factor $w$ (compared to the last cooperator).
+The public good is said to be discounting in this case.
+On the other hand, when $w > 1$, every new contribution is more valuable than the previous one.
 The public good is said to be synergistic in this case.
@@
 However, now, since players are asymmetric it is not entirely clear in which order the contributions of cooperators should be discounted (or synergized).
-For example, consider that there are three cooperators in the group: player $p, q$ and $r$.
+For example, consider that there are $3$ cooperators in the group: player $p, q$ and $r$.
 The total benefit that they provide to the public good can be one of the six possibilities from $x + y w + z w^2$, where $x,y$ and $z$ are permutations  of $b_p, b_q$ and $b_r$.
@@
 \noindent The complete state space of the game with asymmetric players is $\A = \{\C,\D\}^N$.
-The payoff of a defector in a state $(\D, \abf_{-i})$ and that of a cooperator in state $(\C,\abf_{-i})$ where $\abf_{-i} \in \{\C,\D\}^{N-1}$ are respectively given by:
+The payoff of a defector in a state $(\D, \abf_{-i})$ and that of a cooperator in state $(\C,\abf_{-i})$ where $\abf_{-i} \in \{\C,\D\}^{N-1}$ are respectively given by
 
@@
 \end{align} \\
-\noindent where $\mathcal{C}(a,\abf_{-i})$ counts the number of cooperators in state $(a,\abf_{-i})$ and $\alpha(.)$ maps the actions $\C$ and $\D$ to 1 and 0 respectively.
+\noindent where $\mathcal{C}(a,\abf_{-i})$ counts the number of cooperators in state $(a,\abf_{-i})$ and $\alpha(.)$, as before, maps the actions $\C$ and $\D$ to $1$ and $0$ respectively.
 Note that the number of cooperators in the two states are related as: $\mathcal{C}(\D,\abf_{-i}) = \mathcal{C}(\C,\abf_{-i}) - 1$.
@@
 (\ref{Eq:stationary-dist-symm-2-stgs}).
-In our symmetric example, we consider that every player in a $N-$player game can generate a benefit $b$ of value $2$.
-Before exploring the $c-w-N$ parameter space, we study four specific cases (with a 4 player game).
+In our symmetric example, we consider that every player in an $N-$player game can generate a benefit $b$ of value $2$.
+Before exploring the $c-w-N$ parameter space, we study four specific cases (with a $4-$player game).
 In two of these cases, the public goods is discounted ($w = 0.5$, Fig.
@@
 When selection strength is intermediate ($\beta = 5$), players sometimes play actions that are not optimal for the dilemma.
-For example, even when the parameters of the game make cooperation to be the dominated strategy ($w = 0.5, c = 1$), there is a single cooperator in the group in around 20 $\%$ of the cases.
-When the parameters of the game reflect the stag-hunt dilemma ($c = 1, w = 1.5$), players are more likely to coordinate their actions in the long run.
-In the long-run, the probabilities that the whole group plays $\C$ or $\D$ are higher than the probabilities that there is a group with a mixture of $\C$ and $\D$ players.
+For example, even when the parameters of the game make cooperation to be the dominated strategy ($w = 0.5, c = 1$), there is a single cooperator in the group in around 20$\%$ of the cases.
+When the parameters of the game reflect the stag-hunt dilemma ($c = 1, w = 1.5$), players are more likely to coordinate their actions in the long-run.
+The probabilities that the whole group plays $\C$ or $\D$ are higher than the probabilities that there is a group with a mixture of $\C$ and $\D$ players.
 In contrast, when the parameters reflect the snowdrift game ($w = 0.5, c = 0.5$), we get the opposite effect.
-In the long run, mixed groups are more likely than homogeneous groups.
-Finally, when the parameters of the game make defection the dominated action ($w = 1.5, c = 0.2$), all players learn to cooperate in the long run.
-\\ \\
-\noindent The average cooperation frequency of the group in the long run is shown in the $c-w$ and $N-w$ parameter planes in Fig \ref{Fig:GPGG-symmetric}b.
-First, let us consider the case when the group size is fixed at 4 players (the $c-w$ plane in Fig\ref{Fig:GPGG-symmetric}b).
+In the long-run, mixed groups are more likely than homogeneous groups.
+Finally, when the parameters of the game make defection the dominated action ($w = 1.5, c = 0.2$), all players learn to cooperate in the long-run.
+\\ \\
+\noindent The average cooperation frequency of the group in the long-run is shown in the $c-w$ and $N-w$ parameter planes in Fig \ref{Fig:GPGG-symmetric}b.
+First, let us consider the case when the group size is fixed at $4$ players (the $c-w$ plane in Fig\ref{Fig:GPGG-symmetric}b).
 In that case, if the cost of cooperation is restrictively high, the average cooperation rate is negligible and does not change with the the nature of the public good.
-In contrast, when the cost is not restrictively high, the discount/synergy parameter, $w$, determines the frequency with which players cooperate in the long run.
+In contrast, when the cost is not restrictively high, the discount/synergy parameter, $w$, determines the frequency with which players cooperate in the long-run.
 A higher $w$ for the public good would result in higher cooperation (and \emph{vice-versa}).
@@
 \ref{Fig:GPGG-symmetric}b).
-The cost is fixed to a value such that in a synergistic public good ($w > 1$), the cooperation frequency is almost 1 in the long run for any group size.
-In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long run.
-In discounted public goods, cooperation rates fall with increase in group sizes.\\ \\
+The cost is fixed to a value such that in a synergistic public good ($w > 1$), the cooperation frequency is almost $1$ in the long-run for any group size.
+In this case, when the public good is discounted, group size $N$ and the discounting factor $w$ jointly determine the cooperation frequency in the long-run.
+In discounted public goods, cooperation rates fall with the increase in group size.\\ \\
 \noindent 
@@
 The average frequency of cooperation per player is summarized in Supplementary Figures 1 and 2.
-In Supplementary Figure 1, we study two cases, first in which the public good is synergistic and players have a high average cost, and second in which public good is discounted and players have a lower average cost.
+In Supplementary Figure 1, we study two cases, a first in which the public good is synergistic and players have a high average cost, and a second in which public good is discounted and players have a lower average cost.
 In both of these cases, players cooperate highly when they simultaneously have low cost and high benefit.
-The only noticebale difference between the two cases is the minimum relationship between the asymmetries $\delta_b$ and $\delta_c$ that results in high cooperation for the player with low cost and high benefit.
+The only noticebale difference between the two cases is the minimum relation between the asymmetries $\delta_b$ and $\delta_c$ that results in high cooperation for the player with low cost and high benefit.
 When we observe individual cooperation frequency versus the synergy/discount factor, $w$ (Supplementary Figure 2), we find that when players are symmetric with respect to just benefits (or just costs), the one with the lowest cost (or highest benefit) cooperates with a high probability across all types of public goods, even for a high value of average cost.
@@
 Introspection dynamics is particularly useful when players can use larger strategy sets.
-In this section, we study the stationary behavior of players in a game where each player has 16 possible pure strategies.
-To this end, we adopt the multiplayer cooperation and rewarding game from Pal and Hilbe \cite{Pal:NatCom:2022}.
+As such, in this section, we study the stationary behavior of players in the $N-$player, $16-$strategy cooperation and rewarding game from Pal and Hilbe \cite{Pal:NatCom:2022}.
 In this game, there are two stages: in stage 1, players decide whether or not they contribute to a linear public good and in stage 2, they decide whether or not they reward their peers.
 When a player contributes to the public good, they pay a cost $c_i$ but generate a benefit worth $r_i c_i$ that is equally shared by everyone.
-When a player rewards a peer, they provide them a benefit of $\rho$ while incurring the cost of rewarding, $\gamma_i$ to self.
+When a player rewards a peer, they provide them a benefit of $\rho$ while incurring the cost of rewarding, $\gamma_i$, to themselves.
 In between the stages, players get full information about the contribution of their peers.
@@
 Conditional cooperators (or defectors) contribute (or do not contribute) when they have no information about their peers (which happens with probability $1 - \lambda_i$).
-When a conditional player, $i$, knows the rewarding strategy of all their peers (which happens with probability $\lambda_i$) and finds that there are $n_{\mathrm{SR}}$ social rewarders and $n_{\mathrm{AR}}$ antisocial rewarders among his peers, they cooperate if and only if the marginal gain from rewards for choosing cooperation over defection outweighs the effective cost of cooperation.
+When a conditional player, $i$, knows the rewarding strategy of all their peers (which happens with probability $\lambda_i$) and finds that there are $n_{\mathrm{SR}}$ social rewarders and $n_{\mathrm{AR}}$ antisocial rewarders among their peers, they cooperate if and only if the marginal gain from rewards for choosing cooperation over defection outweighs the effective cost of cooperation.
 That is,
@@
 \begin{equation}
-\rho(n_{\mathrm{SR}} - n_{\mathrm{AR}}) \geq c_i \left( 1 - \frac{r_i}{N} \right)
+\rho(n_{\mathrm{SR}} - n_{\mathrm{AR}}) \geq c_i \left( 1 - \frac{r_i}{N} \right) .
 \label{Eq:palrewardsequation}
@@
 \\
-\noindent Combining the two stages, players can use one of 16 possible strategies (4 in stage 1 and 4 in stage 2).
+\noindent Combining the two stages, players can use one of $16$ possible strategies ($4$ in stage 1 and $4$ in stage 2).
 In the simple case where players are identical, one can characterize the Nash equilibria of the game and identify the conditions which allow an equilibrium where all players contribute in the first stage and reward peers in second stage \cite{Pal:NatCom:2022}.
@@
 In this section, we study three simple cases of asymmetry between players to demonstrate how these asymmetric players may learn to play the game through introspection dynamics.
-The three specific examples that we show demonstrate that with introspection dynamics, asymmetric players can end up taking different roles in the long run to produce the public good.
-To this end, we consider a 3-player game in which player 1 and 2 are identical but player 3 is asymmetric to them in some aspect.
-We consider three cases.
-In each case the asymmetric player either has \textbf{a}) a higher cost of rewarding $\gamma_3 > \gamma_1$  or, \textbf{b}) low productivitiy  $r_3 < r_1$ or, \textbf{c}) or, less information about peers $\lambda_3 < \lambda_1$ than their peers.
+The three specific examples that we show demonstrate that with introspection dynamics, asymmetric players can end up taking different roles in the long-run to produce the public good.
+To this end, we consider a $3-$player game in which player 1 and 2 are identical but player 3 is asymmetric to them in some aspect.
+In each case, the asymmetric player either has \textit{a}) a higher cost of rewarding $\gamma_3 > \gamma_1$, \textit{b}) low productivitiy  $r_3 < r_1$, or \textit{c}) less information about peers $\lambda_3 < \lambda_1$ than their peers.
 We use Eq.
-(\ref{Eq:explicit-stationary-dist-representation}) to exactly compute the expected abundances of the 16 strategies for each player.
+(\ref{Eq:explicit-stationary-dist-representation}) to exactly compute the expected abundances of the $16$ strategies for each player.
 \\ \\
@@
 \ref{Fig:SocialRewarding}a).
-The players, to whom rewarding is less costly (player 1 and player 2), reward cooperation with a higher probability than to whom rewarding is very costly (player 3).
+The players to whom rewarding is less costly (player 1 and player 2), reward cooperation with a higher probability than to whom rewarding is very costly (player 3).
 In return, player 3 learns to respond by contributing with more probability than their co-players.
 With these specific parameters, one player takes up the role of providing the highest per-capita contribution while the others compensate with costly rewarding.
-When the asymmetric player differs only in their productivity, a different effect may appear in the long run (Fig \ref{Fig:SocialRewarding}b).
+When the asymmetric player differs only in their productivity, a different effect may appear in the long-run (Fig \ref{Fig:SocialRewarding}b).
 In this case, the less productive player free-rides on the cooperation of their higher productive peers, but eventually reward the cooperation of their peers nonetheless.
 The asymmetric player free-rides but does not second-order free ride.
-The probability with which the less productive player rewards others in the long run is slightly higher than the probability with which the contributing individuals reward each other.
+The probability with which the less productive player rewards others in the long-run is slightly higher than the probability with which the contributing individuals reward each other.
 Finally, we consider the case where the asymmetric individual differs from others in terms of the information players have about others' rewarding strategy (Fig \ref{Fig:SocialRewarding}c).
 In this case, the asymmetric player knows others' strategy with a considerably less chance than their peers.
-In the long run, the asymmetric player cooperates less on average than their peers.
+In the long-run, the asymmetric player cooperates less on average than their peers.
 This is because the asymmetric individual faces less instances where they can opportunistically cooperate with their co-players.
@@
 Clearly, this assumption implies a simple cognitive process.
-Players do not optimize over the entire set of strategies as, for example, in best-responde models \cite{Gaunersdorfer:GEB:1995, Hofbauer:GEB:2005}.
-Furthermore, although conceptually similar, our model is also simpler than typical reinforcement learning models.
-For example, while we only have selection strength as a parameter (apart from payoffs), in Macy and Flache (2002) \cite{Macy:PNAS:2002}, there is a learning rate parameter (which could be comparable to our selection strength) but also an aspiration parameter which sets a payoff reference.
+Players do not optimize over the entire set of strategies as, for example, in best-responde models \cite{Blume:GEB:1993, Gaunersdorfer:GEB:1995, Hofbauer:GEB:2005}.
+One such model of particular interest due to its connections to introspection dynamics is the logit dynamics \cite{Blume:GEB:1993, Alos-Ferrer:GEB:2010,Auletta:Annual:2011}.
+In Appendix 1, we compare introspection dynamics and logit dynamics.
+We show that the two processes have equivalent stationary distributions for 2-strategy games, potential games and additive games.
+We also note that there are games for which the stationary distributions do not match.
+For example, we find coordination games with multiple Nash equilibria for which introspection dynamics and logit dynamics select a different equilibrium.
+Interestingly, whether one of the dynamics is better at selecting the higher payoff equilibrium in coordination games has no trivial answer and remains to be investigated.
+\\
+
+\noindent Furthermore, although conceptually similar, our model is also simpler than typical reinforcement learning models.
+For example, while we only have selection strength as a parameter (apart from the payoffs), in Macy and Flache (2002) \cite{Macy:PNAS:2002}, there is a learning rate parameter (which could be comparable to our selection strength) but also an aspiration parameter which sets a payoff reference.
 In our model, the payoff reference is always the current one.
@@
 To deal with this issue, previous models frequently resorted to additional approximations, like low mutation rate \cite{Fudenberg:JET:2006, Veller:JET:2016} and weak selection \cite{Wild:JTB:2007}.
-%Most previous evolutionary models focus on limiting regimes, namely low mutation rate and selection strength approximations, as they allow for analytical results.
 On the contrary, in introspection dynamics, the states of the Markov process correspond to the outcome of a single (focal) game: for a $N$-player game, where player $i$ has $m_i$ possible actions, there are $m_1 \times m_2 \times ...
@@
 \\
-
-%Due to these reasons, one can see how the mathematical analysis of multiplayer asymmetric games can become cumbersome, the extreme cases being many-player games where all individuals are different.
-Perhaps for that reason, there are not many studies on a general approach to multiplayer asymmetric games.
-As such, our aim here is to narrow that gap using introspection dynamics \cite{Couto:NJP:2022}.
 
@@
 Finally, we study several examples of social dilemmas.
-From those, we see that, despite the differences to other models pointed out above, we recover some previous qualitative results \cite{Hauert:JTB:2006a}.
+From those, we see that, despite the differences to other models pointed out above, we recover some previous results qualitatively \cite{Hauert:JTB:2006a}.
 We also conlcude that players that have a lower cost or a higher benefit of cooperation learn to cooperate more frequently.
@@
 
-\noindent Introspection dynamics is a rather broad in its scope.
-Here, we mainly focused on introducing a general framework.
+\noindent Introspection dynamics is rather broad in its scope.
+Here, we mainly focus on introducing a general framework.
 Still, we provide some examples to illustrate how it can be applied.
-Besides the generic public goods game, we study a 2-stage game, where players can choose among $16$ strategies.
+Besides the generic public goods game, we study a $2$-stage game, where players can choose among $16$ strategies.
 There, individuals can reward their co-players condition on their previous cooperative (or not) behavior.
-%[What we didn't do, limitations, further work]
-\noindent Clearly, there are a number of ways in which our model can be further employed.
-For example, other researchers recently studied multiplayer games considering multiple games played concurrently \cite{Venkateswaran:PRSB:2019}, fluctuating environments \cite{Baron:JRSOP:2018}, continuous strategies \cite{Molina:JMB:2017}, or repeated interactions \cite{Hilbe:JTB:2015}.
+Clearly, there are a number of ways in which our model can be further employed.
+For example, other researchers recently studied multiplayer games considering multiple games played concurrently \cite{Venkateswaran:PRSB:2019}, fluctuating environments \cite{Baron:JRSOP:2018}, continuous strategies \cite{Molina:JMB:2017}, or repeated interactions \cite{Hilbe:JTB:2015, Wang:PTRSB:2023}.
 Also, a number of previous works considered complex population structures \cite{Broom:JTB:2012, Wu:Games:2013, Perc:JRSI:2013, Pena:JTB:2015, Pena:JRSI:2016, Pattni:JTB:2017, Su:PNAS:2022}.
-As discussed above, introspection dynamics does not consider a population of players, making it simple to work with.
+As defined above, introspection dynamics does not consider a population of players, making it simple to work with.
 However, it could be equally applicable to population models.
 In that case, players would obtain average payoffs either from well-mixed or network-bounded interactions, as usual, but update their strategies introspectively.
-
-%Despite the conceptual disparities, there have been already some efforts in unifying the two lines of research of evolutionary game theory and multiagent reinforcement learning \cite{Macy:PNAS:2002, Tuyls:bookchapter:2005, Bloembergen:JAIR:2015, Zhang:arxiv:2022}.
-% Clearly, we can distinguish two different pathways that led to ``learning in games": one which stemmed from the broad field of reinforcement learning \cite{Sandholm:BioSys:1996} and the other from the classical game theory itself \cite{Fudenberg:book:1998b}.
-The ``theory of learning in games" was proposed as a refinement of classical equilibrium concepts, like Nash equilibrium, where strict assumptions of common knowledge of rationality are made.
-Instead, learning consists of ``\textit{an alternative explanation that equilibrium arises as the long-run outcome of a process in which less than fully rational players grope for optimality over time}" \cite{Fudenberg:book:1998b}.
-In this context, several learning models were introduced, such as fictitious play \cite{Gaunersdorfer:GEB:1995} or perturbed best response dynamics \cite{Hofbauer:GEB:2005}.
-
-%[Comparison to other models]
-%see e.g Hofbauer:GEB:2005
-
-% examples
-%\cite{Baron:JRSOP:2018} multiplayer games with fluctuating environments
-%\cite{Molina:JMB:2017} multiplayer games continuous strategies
-%\cite{Venkateswaran:PRSB:2019} multiplayer in multiple games
-%\cite{Hilbe:JTB:2015} explore the evolution of direct reciprocity in groups of multiple players; in small groups, generosity allows the evolution of cooperation, whereas, in large groups, cooperation is unlikely to evolve.
-
-%networks/structure
-%\cite{Broom:JTB:2012, Wu:Games:2013, Pena:JTB:2015, Pena:JRSI:2016, Pattni:JTB:2017, Su:PNAS:2022}
-% broom territorial
 
@@
 \newpage
-\section*{Appendix: Proofs}
+\section*{Appendix 1: Comparison between introspection and logit-response dynamics}
+
+In this section, we discuss some similarties between introspection dynamics and the widely studied logit-response dynamics (or perturbed best-response dynamics) \cite{Blume:GEB:1993, Alos-Ferrer:GEB:2010}.
+In the logit-response dynamics, at every time step, some set of players are chosen to update their strategies.
+The new strategy that a player adopts is drawn from a probability mass function over all of their strategies.
+The players construct this probability distribution by exponentially weighing the payoffs that they would receive if they switch to the new strategy (conditioned on all co-players' strategies remaining fixed).
+Mathematically, the probability that player $i$ switches to action $a_i \in \A_i$ when the co-players are currently playing $\abf_{-i}$, is given by
+
+\begin{equation}
+p^{\LD}_{a_i}(\abf_{-i}) := \frac{\displaystyle e^{\beta \pi_i(a_i,\abf_{-i})}}{\displaystyle \sum_{a' \in \A_i} e^{\beta \pi_i(a',\abf_{-i})}}
+\end{equation}
+\\
+\noindent where the scalar $\beta$ is akin to selection strength in the introspection dynamics. \\ \\
+\noindent Note that while making comparisons between the two processes, we only consider a special case of the logit-response dynamics called the asynchronous learning logit-response dynamics \cite{Blume:GEB:1993}.
+From here on, we refer to the asynchronous learning logit-response dynamics as simply \emph{logit-response dynamics}.
+In this process, at every time step, exactly one player is uniform randomly chosen to update their strategy.
+The transition probability of going from state $\abf$ to state $\bbf$ in the logit-response dynamics can thus be expressed as
+
+\begin{align}
+\mathrm{T}^\LD_{\abf, \bbf} = 
+\begin{cases}
+\frac{1}{N}  \cdot p^\LD_{b_{j}} (\abf_{-j}) \quad  \quad &\text{ if }\bbf \in \mathrm{Neb}(\abf) \quad \text{and,} \quad j = \mathrm{I}(\abf,\bbf)\\ \\ 
+0 \quad &\text{ if } \bbf \notin \mathrm{Neb}(\abf) \\ \\
+1 - \sum_{\cbf \neq \bbf} \mathrm{T}_{\abf,\cbf} \quad &\text{ if } \abf = \bbf
+\end{cases}.
+\label{Eq:transition-matrix-logit}
+\end{align} \\
+
+\noindent Throughout the rest of this section, we will refer to the transition matrix of the logit-response dynamics with $\T^{\LD}$ and the transition matrix of the introspection dynamics, as given by Eq.
+(\ref{Eq:transition-matrix}), with $\T^{\ID}$.
+We refer to the respective unique stationary distributions at finite $\beta$ with $\ubf^\LD$ and $\ubf^\ID$.
+Our first comparison between the two processes is for games with two actions.
+
+\begin{Prop}
+In games where $m_i = 2$, for all $i \in \{1,2,...,N\}$, the transition matrix and the stationary distribution for introspection dynamics and logit-response dynamics are the same.
+That is, $\T^\LD = \T^\ID$ and $\ubf^\LD = \ubf^\ID$.
+\label{Prop:2-strategy-logit}
+\end{Prop}
+\noindent This proposition states that for games where every player has two available actions (strategies), the processes of introspection and logit-response are equivalent. \\ \\ 
+\noindent We also compare the two processes on two more classes of games -- additive and potential games \cite{Monderer:GEB:1996}.
+We have already defined an additive game earlier.
+Monderer and Shapley (1996) \cite{Monderer:GEB:1996} define potential games as any game where a scalar function $\phi: \A \mapsto \mathbb{R}$ exists such that for all $i$, $a_i, a'_i \in \A_i$ and $\abf_{-i} \in \A_{-i}$,
+
+\begin{equation}
+\pi_i(a_i, \abf_{-i}) - \pi_i(a'_i, \abf_{-i}) = \phi(a_i, \abf_{-i}) - \phi(a'_i, \abf_{-i}).
+\label{Eq:potential-game}
+\end{equation} \\
+\noindent Here, the scalar function $\phi$ is called the potential of the game. Following this definition, one can see a potential game as a game where it follows that
+\begin{equation}
+\pi_i(a_i, \abf_{-i}) = \phi(a_i, \abf_{-i}) + \sigma(\abf_{-i}),
+\label{Eq:potential-game-second-def}
+\end{equation} \\
+\noindent where $ \sigma(\abf_{-i}) := \pi_i(a', \abf_{-i}) - \phi(a',\abf_{-i})$, for a fixed $a' \in \A_i$, is independent of $a_i$.
+We show that, for potential games, introspection dynamics and logit-response dynamics have the same stationary distribution.
+
+\begin{Prop} For a potential game with potential $\phi$, the stationary distributions of introspection dynamics (with a finite $\beta$) and logit-response dynamics (with the same finite parameter $\beta$) are the same and given by
+\begin{equation}
+\ubf^\ID_\abf = \ubf^\LD_\abf = \frac{\displaystyle e^{\beta \phi(\abf)}}{\displaystyle \sum_{\abf' \in \A} e^{\beta \phi(\abf')}}.
+\label{Eq:logit-potential-stationary-dist}
+\end{equation}
+\label{Prop:potential-logit}
+\end{Prop}
+\noindent The above proposition states that both the processes (with the same finite $\beta$) lead to identical stationary distribution for any potential game.
+The proof of this proposition relies on proposition 1 from Al\'{o}s-Ferrer and Netzer (2010) \cite{Alos-Ferrer:GEB:2010} where a closed form expression of the stationary distribution of the logit-response dynamics for a potential game was provided.
+We obtain a similar result for additive games.
+
+\begin{Prop}
+\label{Prop:additive-logit}
+For an $N-$player additive game, the stationary distributions of introspection dynamics (with a finite $\beta$) and logit-response dynamics (with the same finite $\beta$), are the same and given by
+\begin{equation}
+\ubf^\ID_\abf = \ubf^\LD_\abf =  \prod_{j=1}^N \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a', a_j)}} 
+\label{Eq:logit-potential-stationary-dist}
+\end{equation}
+where, $f_j(a', a_j)$ is the co-player independent payoff difference given by Eq. (\ref{Eq:coplayer-independent-payoffdiff}).
+\end{Prop}
+\noindent To summarize, the two propositions above state that while the transition matrices of the two processes may be different from each other, the long-run stationary behaviour of the players in potential and additive games are the same.
+\section*{Appendix 2: Proofs}
 \label{Section:Appendix}
@@
 \textbf{Proof of Proposition} \ref{Th:additive-games-stationary-dist} \\ \\ 
-Since $\beta$ is finite,the stationary distribution $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$ of the process is unique.
+Since $\beta$ is finite, the stationary distribution $\ubf = (\mathrm{u}_\abf)_{\abf \in \A}$ of the process is unique.
 The stationary distribution also satisfies the equalities in Eq.
@@
 \label{Eq:shortcut-tau}
-\tau_{j,a_j} &:= \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a',  a_j)}} 
+\tau_{j,a_j} &:= \frac{1}{\displaystyle \sum_{a' \in \A_j} e^{\beta f_j(a',  a_j)}} .
 \end{align}
@@
 \label{step-two}
-&\sum_{\abf \in \A} \mathrm{u}_\abf  = 1
+&\sum_{\abf \in \A} \mathrm{u}_\abf  = 1 .
 \end{align} 
@@
 \begin{equation}
-\mathrm{u}_\abf = \prod_{j=1}^N \tau_{j,a_j}
+\mathrm{u}_\abf = \prod_{j=1}^N \tau_{j,a_j} .
 \label{Eq:additive-stat-shortcut}
@@
 \label{eq:important-step}
-&= \mathrm{u}_\abf +  \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \left( \prod_{k \neq I_\bbf} \tau_{k,a_k} \right) \left( p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, a_{\mathrm{I}_\bbf}} -  p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, b_{\mathrm{I}_\bbf}} \right) \cdot \left(  \frac{1}{m_{\mathrm{I}_\bbf}-1} \right)
+&= \mathrm{u}_\abf +  \frac{1}{N} \sum_{\bbf \in \mathrm{Neb}(\abf)} \left( \prod_{k \neq I_\bbf} \tau_{k,a_k} \right) \left( p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, a_{\mathrm{I}_\bbf}} -  p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, b_{\mathrm{I}_\bbf}} \right) \cdot \left(  \frac{1}{m_{\mathrm{I}_\bbf}-1} \right) .
 \end{align}
@@
 p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}} &=\frac{1}{1 + \displaystyle e^{\beta f_{\mathrm{I}_\bbf}(b_{\mathrm{I}_\bbf}, a_{\mathrm{I}_\bbf})}} \\[10pt] 
-p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} &= \frac{1}{1 + \displaystyle e^{\beta f_{\mathrm{I}_\bbf}(a_{\mathrm{I}_\bbf}, b_{\mathrm{I}_\bbf})}} 
+p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} &= \frac{1}{1 + \displaystyle e^{\beta f_{\mathrm{I}_\bbf}(a_{\mathrm{I}_\bbf}, b_{\mathrm{I}_\bbf})}} .
 \end{align} \\
@@
 \begin{equation}
- \left( p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, a_{\mathrm{I}_\bbf}} -  p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, b_{\mathrm{I}_\bbf}} \right) = 0
+ \left( p_{b_{\mathrm{I}_\bbf} \to a_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, a_{\mathrm{I}_\bbf}} -  p_{a_{\mathrm{I}_\bbf} \to b_{\mathrm{I}_\bbf}} \cdot \tau_{\mathrm{I}_\bbf, b_{\mathrm{I}_\bbf}} \right) = 0 .
 \label{important-step-is-zero}
@@
 \end{align} \\
-\noindent Multiplying out the sums in the denominator of the above expression, we get that:
+\noindent Multiplying out the sums in the denominator of the above expression, we get
 \begin{align}
@@
 \label{Eq:OG_sum-of-prod}
-=& \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})}  \right)^{-1} \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})}  \right) = 1
+=& \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})}  \right)^{-1} \left( \sum_{\abf \in \A} \displaystyle \prod_{k=1}^N e^{\beta \pi_k(a_k, \qbf_{-k})}  \right) = 1 .
 \end{align} \\ 
@@
 &= \sum_{\qbf \in \A_{-j}} \left( \sum_{a' \in \A_j} \displaystyle e^{\beta f_j(a',a_j)}\right)^{-1} \prod_{k \neq j} \left( \sum_{a' \in \A_k} \displaystyle e^{\beta f_k(a',q_k)}\right)^{-1} \\ \notag \\
-&= \left( \prod_{k=1}^N \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k (a', \pbf_{-k})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(a_j, \pbf_{-j})} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(q_k, l_{-k})} \right) \\ \notag \\
-\label{step-prod-sum}
-&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(a_j, \pbf_{-j})}\cdot \left( \prod_{k\neq j} \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k(a',\pbf_{-k})}\right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(q_k,\pbf_{-k})} \right)
-\end{align}
-\newpage
-\begin{align}
-\label{step-sum-prod}
-&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(a_j, \pbf_{-j})}\cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi_k(q_k,\pbf_{-k})} \right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(q_k,\pbf_{-k})}  \right)
+&= \left( \prod_{k=1}^N \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k (a', \pbf_{-k})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(a_j, \pbf_{-j})} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(q_k, \pbf_{-k})} \right) \\ \notag \\
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(a_j, \pbf_{-j})}\cdot \left( \prod_{k\neq j} \sum_{a' \in \A_k} \displaystyle e^{\beta \pi_k(a',\pbf_{-k})}\right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(q_k,\pbf_{-k})} \right) \label{Eq:step-prod-sum} \\ \notag \\
+&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \pi_j(a',\pbf_{-j})}\right)^{-1} \cdot \displaystyle e^{\beta \pi_j(a_j, \pbf_{-j})}\cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k\neq j}  \displaystyle e^{\beta \pi_k(q_k,\pbf_{-k})} \right)^{-1} \cdot \left( \sum_{\qbf \in \A_{-j}} \prod_{k \neq j} e^{\beta \pi_k(q_k,\pbf_{-k})}  \right) \label{Eq:step-sum-prod}.
 \end{align}
 \noindent The interchange of the sum and the product between the expressions in Eq.
-(\ref{step-prod-sum}) and Eq.
-(\ref{step-sum-prod}) can be carried out by observing that when all the sums are multiplied out, one is left with sums of terms, each of which is a exponential with power equal to sum of payoffs that co-players of $j$ (here $k$) receive when they play their respective strategies from $\qbf$ (that is $q_k$) against co-players that play $\pbf_{-k}$.
-This is the similar to the step between Eq.
+(\ref{Eq:step-prod-sum}) and Eq.
+(\ref{Eq:step-sum-prod}) can be carried out by observing that when all the sums are multiplied out, one is left with sums of terms, each of which is a exponential with power equal to sum of payoffs that co-players of $j$ (here $k$) receive when they play their respective strategies from $\qbf$ (that is $q_k$) against co-players that play $\pbf_{-k}$.
+This is similar to the step between Eq.
 (\ref{Eq:OG_prod-of-sum}) and Eq.
 (\ref{Eq:OG_sum-of-prod}) in the proof of Proposition 2.
-\begin{align}
-&= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \left( \pi_j(a',\pbf_{-j}) - \pi_j(a_j,\pbf_{-j})\right)} \right)^{-1}\\ \notag \\
+Thus,
+\begin{align}
+\xi_{j,a_j} &= \left( \sum_{a' \in \A_j} \displaystyle e^{\beta \left( \pi_j(a',\pbf_{-j}) - \pi_j(a_j,\pbf_{-j})\right)} \right)^{-1}\\ \notag \\
 \label{final-expression}
-&= \sum_{a' \in \A_j} \displaystyle e^{\beta f_j(a',a_j)}
+&=  \left( \sum_{a' \in \A_j} \displaystyle e^{\beta f_j(a',a_j)} \right)^{-1} .
 \end{align} \\
@@
 \begin{equation}
-\prod_{j=1}^N \xi_{j,a_j} = \mathrm{u}_\abf
+\prod_{j=1}^N \xi_{j,a_j} = \mathrm{u}_\abf .
 \end{equation} 
@@
 \bar{a}_j &:= \{\D,\C\} \setminus \{a_j\}  \\ \notag \\ 
-p_j &:= \frac{1}{1 + \displaystyle e^{\beta f_j(\D, \C)}} 
+p_j &:= \frac{1}{1 + \displaystyle e^{\beta f_j(\D, \C)}} .
 \end{align} \\
@@
 \begin{equation}
-p_{\displaystyle \bar{a}_j  \to a_j} (\abf_{-j}) = p_j \mathit{sign}(a_j) + \alpha(\bar{a}_j) 
+p_{\displaystyle \bar{a}_j  \to a_j} (\abf_{-j}) = p_j \mathit{sign}(a_j) + \alpha(\bar{a}_j) .
 \end{equation}\\
@@
 \label{Eq:stationary-dist-shortcut}
-\mathrm{u}_\abf = \prod_{k = 1}^{N}  p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k)
+\mathrm{u}_\abf = \prod_{k = 1}^{N}  p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k) .
 \end{equation}\\
@@
 \label{Eq:normalization-in-proof}
-&\sum_{\abf \in \A} \mathrm{u}_{\abf}= 1
+&\sum_{\abf \in \A} \mathrm{u}_{\abf}= 1 .
 \end{align}
@@
 \end{eqnarray} 
-and additionally, using Eq. (\ref{Eq:stationary-dist-shortcut}) the second term can be simplified too:
+and additionally, using Eq. (\ref{Eq:stationary-dist-shortcut}) the second term can be simplified to
 \begin{align}
@@
 \label{Eq:second-term-rhs-proof}
-&= \frac{\mathrm{u}_\abf}{N} \sum_{k=1}^{N} p_k \textit{sign}(\bar{a}_k) + \alpha(a_k) 
+&= \frac{\mathrm{u}_\abf}{N} \sum_{k=1}^{N} p_k \textit{sign}(\bar{a}_k) + \alpha(a_k) .
 \end{align}
@@
 (\ref{Eq:normalization-in-proof}) is also true for our candidate stationary distribution.
-This can be done by decomposing the sum of the elements of the stationary distribution as follows:
+This can be done by decomposing the sum of the elements of the stationary distribution as follows
 \begin{align}
@@
 =& \displaystyle \displaystyle \sum_{\abf \in \A_{-\!N}} (1-p_N)  \prod_{k=1}^{N-1} p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k)  + p_N  \prod_{k=1}^{N-1} p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k) \\[10pt]
-=& \displaystyle \sum_{\abf \in \A_{-\!N}} \prod_{k=1}^{N-1} p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k)
-\end{align}
-When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This prooves that the candidate stationary distribution is also a probability distribution.\\
+=& \displaystyle \sum_{\abf \in \A_{-\!N}} \prod_{k=1}^{N-1} p_k \mathit{sign}(a_k) + \alpha(\bar{a}_k) .
+\end{align}
+When the above decomposition is perfomed $N-1$ more times, the sum of the right hand side becomes 1. This proves that the candidate stationary distribution is also a probability distribution.\\
 \end{proof}
@@
 \end{cases}\\[10pt]
-\mathcal{C}(\abf) &= \sum_{j=1}^N \alpha(a_j)
-\end{align}
-For this process, since there are only two actions, the first term in the right hand side of Eq. (\ref{Eq:transition-in-proof}) can be simplified as: 
+\mathcal{C}(\abf) &= \sum_{j=1}^N \alpha(a_j) .
+\end{align}
+For this process, since there are only two actions, the first term in the right hand side of Eq. (\ref{Eq:transition-in-proof}) can be simplified as 
 \begin{align}
 \mathrm{u}_{\abf} \mathrm{T}_{\abf,\abf}  &= \mathrm{u}_\abf - \mathrm{u}_{\abf} \sum_{k=1}^{N} \mathrm{T}_{(a_k, \abf_{-k}),(\bar{a}_{k}, \abf_{-k})} \\[10pt]
-&= \mathrm{u}_{\abf} - \frac{\mathrm{u}_{\abf}}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{a}_{k}) \beta f(N_k)}}
+&= \mathrm{u}_{\abf} - \frac{\mathrm{u}_{\abf}}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{a}_{k}) \beta f(N_k)}} .
 \label{Eq:T_aa_u_a term}
@@
 \begin{equation}
-N_k := \sum_{j \neq k} \alpha(a_j)
+N_k := \sum_{j \neq k} \alpha(a_j) .
 \end{equation} \\
@@
 &= \frac{1}{N \Gamma} \sum_{k=1}^N \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \displaystyle \prod_{j=1}^{\mathcal{C}((\bar{a}_k, \abf_{-k}))} e^{-\beta f(j-1)}\\[10pt]
-&=  \frac{1}{N \Gamma} \sum_{k=1}^N \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k})
+&=  \frac{1}{N \Gamma} \sum_{k=1}^N \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k}) .
 \label{Eq:step-product-broken}
@@
 We continue the simplification of Eq.
-(\ref{Eq:step-product-broken}) in the next steps by introducing terms that cancel each other.
-\\[10pt]
-\begin{align}
-\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot \frac{e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k)}}{e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) +N_k)}} \cdot e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) + N_k)}
+(\ref{Eq:step-product-broken}) in the next steps by introducing terms that cancel each other, \\[10pt]
+\begin{align}
+\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &=  \frac{1}{N \Gamma} \sum_{k=1}^N \T \cdot \displaystyle \left( \prod_{j=1}^{N_k}  e^{-\beta f(j-1)} \right) \cdot \frac{e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k)}}{e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) +N_k)}} \cdot e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) + N_k)} .
 \label{Eq:new-cancelable-term-introduced}
@@
 &= \frac{1}{N} \sum_{k=1}^N  \T \cdot \left( \frac{1}{\Gamma} \prod_{j=1}^{\mathcal{C}(\abf)} e^{-\beta f(j-1)}\right) \cdot \frac{e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k)}}{e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) +N_k)}} \\[10pt]
-&= \frac{1}{N} \sum_{k=1}^N  \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \cdot \mathrm{u}_\abf \cdot \frac{e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k)}}{e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) +N_k)}} \label{Eq: last-step-w-fraction}
+&= \frac{1}{N} \sum_{k=1}^N  \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \cdot \mathrm{u}_\abf \cdot \frac{e^{-\beta \alpha(\bar{a}_k)f(-\alpha(a_k)+ N_k)}}{e^{-\beta \alpha(a_k)f(-\alpha(\bar{a}_k) +N_k)}} .
+\label{Eq: last-step-w-fraction}
 \end{align}
@@
 \begin{align}
-\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &= \frac{1}{N} \sum_{k=1}^N  \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \cdot \mathrm{u}_\abf \cdot e^{sign(a_k) \beta f(N_k)}
+\sum_{\bbf \neq \abf} \mathrm{T}_{\bbf, \abf} \mathrm{u}_{\bbf} &= \frac{1}{N} \sum_{k=1}^N  \mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} \cdot \mathrm{u}_\abf \cdot e^{sign(a_k) \beta f(N_k)} .
 \label{Eq:only-need-to-replace-T-now}
 \end{align}
-\\ \noindent In Eq. (\ref{Eq:only-need-to-replace-T-now}) we can replace the element of the transition matrix $\mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})}$ with,
-\begin{equation}
-\mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} = \frac{1}{1 + \displaystyle e^{\mathit{sign}(a_k) \beta f(N_k)}} 
+\\ \noindent In Eq. (\ref{Eq:only-need-to-replace-T-now}) we can replace the element of the transition matrix $\mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})}$ with
+\begin{equation}
+\mathrm{T}_{(\bar{a}_k, \abf_{-k}),(a_k, \abf_{-k})} = \frac{1}{1 + \displaystyle e^{\mathit{sign}(a_k) \beta f(N_k)}} .
 \label{Eq:transition-matrix-T-symm-2-stgs}
@@
 &= \frac{\mathrm{u}_\abf}{N} \sum_{k=1}^N \frac{1}{1 + \displaystyle e^{\mathit{sign}(\bar{a}_k) \beta f(N_k)}}  \\[10pt]
-&= \mathrm{u}_\abf - \mathrm{u}_\abf \mathrm{T}_{\abf,\abf}
+&= \mathrm{u}_\abf - \mathrm{u}_\abf \mathrm{T}_{\abf,\abf} .
 \end{align}
@@
 As argued before, all of these states are identical and are also equiprobable in the stationary distribution.
-Therefore, the stationary distribution probability of having $k$, $\C$ players, $\mathrm{u}_{k}$, is,
-\begin{equation}
-\mathrm{u}_{k} = \sum_{\mathcal{C(\abf)} = k} \mathrm{u}_\abf = \frac{1}{\Gamma} {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)} \\[10pt]
-\end{equation} 
-\noindent Where the normalization factor $\Gamma$ can also be simplified as: 
-\begin{equation}
-\Gamma = \sum_{k=0}^N {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)}
+Therefore, the stationary distribution probability of having $k$, $\C$ players, $\mathrm{u}_{k}$, is
+\begin{equation}
+\mathrm{u}_{k} = \sum_{\mathcal{C(\abf)} = k} \mathrm{u}_\abf = \frac{1}{\Gamma} {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)} . \\[10pt]
+\end{equation} 
+\noindent Where the normalization factor $\Gamma$ can also be simplified as
+\begin{equation}
+\Gamma = \sum_{k=0}^N {N \choose k} \prod_{j=1}^k e^{-\beta f(j-1)} .
 \end{equation}
 \end{proof}
+
+\begin{proof}
+\textbf{Proof of Proposition} \ref{Prop:2-strategy-logit} \\ \\
+We consider two arbitrary states $\abf$ and $\bbf$ such that $\abf \in \mathrm{Neb}(\bbf)$.
+Let $j = \mathrm{I}(\abf,\bbf)$ be the index of difference between these neighbouring states.
+Taking into account that $m_i = 2, \forall i \in \{1,2,...,N\}$, it follows that $a_j$ and $b_j$ are the only two actions in the action set of player $j$, $\A_j$.
+It can be shown that,
+\begin{align}
+\mathrm{T}^\ID_{\abf,\bbf} = \frac{1}{N} \frac{1}{m_j - 1} p_{a_j \to b_j} (\abf_{-j}) &= \frac{1}{N} \cdot \frac{1}{1 + \displaystyle e^{\beta (\pi_j(a_j, \abf_{-j}) - \pi_j(b_j,\abf_{-j}))}} \\[10pt]
+&=\frac{1}{N} \cdot \frac{ \displaystyle e^{\beta \pi_j(b_j, \abf_{-j})}}{\displaystyle e^{\beta \pi_j(b_j, \abf_{-j})} + \displaystyle e^{\beta \pi_j(a_j, \abf_{-j})}}  \\[10pt]
+&= \frac{1}{N} \cdot \frac{\displaystyle e^{\beta \pi_j(b_j, \abf_{-j})}}{\displaystyle \sum_{a' \in \A_j} e^{\beta \pi_j(a',\abf_{-j})}} \\[10pt]
+&= \frac{1}{N} \cdot p^{\LD}_{b_j} (\abf_{-j}) = \mathrm{T}^\LD_{\abf,\bbf}.
+\end{align} \\ 
+\noindent The above equality is sufficient to show that $\T^\LD = \T^\ID$ (the other cases of the matrix \ref{Eq:transition-matrix-logit} are trivial).
+Furthermore, when $\beta$ is finite, both the processes will also have identical stationary distributions.
+That is, $\ubf^\LD = \ubf^\ID$.
+\end{proof}
+
+\begin{proof}
+\textbf{Proof of Proposition} \ref{Prop:potential-logit} \\ \\
+In this proof, we will use the result from proposition 1 in Al\'{o}s-Ferrer and Netzer (2010) \cite{Alos-Ferrer:GEB:2010}.
+There, it was shown that the stationary distribution of the logit-response dynamics for a potential game with potential $\phi$ (for a finite $\beta$) takes the form,
+\begin{equation}
+\ubf^\LD_\abf = \frac{\displaystyle e^{\beta \phi(\abf)}}{\displaystyle \sum_{\abf' \in \A} e^{\beta \phi(\abf')}}.
+\end{equation}
+\noindent We will use this stationary distribution as the candidate stationary distribution for introspection dynamics and show that $\ubf^\LD \T^\ID = \ubf^\LD$.
+This is sufficient to prove that, with finite $\beta$, $\ubf^\LD = \ubf^\ID$.
+We will look at the value of the following expression for two arbitrary neighbouring states, $\abf$ and $\bbf$ (with $j$ as the index of difference between the two states), \\
+\begin{align}
+&\ubf^\LD_\abf \mathrm{T}^\ID_{\abf,\bbf} - \ubf^\LD_\bbf \mathrm{T}^\ID_{\bbf,\abf} \\[15pt]
+&= \frac{1}{N(m_j - 1)} \cdot \frac{1}{\displaystyle \sum_{\abf' \in \A} e^{\beta \phi(\abf')}} \cdot (e^{\beta \phi(\abf)}p_{a_j \to b_j}(\abf_{-j}) - e^{\beta\phi(\bbf)} p_{b_j \to a_j}(\abf_{-j})) \\[10pt]
+&= \frac{1}{N(m_j - 1)\displaystyle \sum_{\abf' \in \A} e^{\beta \phi(\abf')}} \cdot \frac{1}{\displaystyle e^{\beta \pi_j(\bbf)} + e^{\beta \pi_j(\abf)}} \bigg( e^{\beta \phi(\abf)} e^{\beta \pi_j(\bbf)} - e^{\beta \phi(\bbf)} e^{\beta \pi_j(\abf)} \bigg) \\[10pt]
+&= \frac{1}{N(m_j - 1)\displaystyle \sum_{\abf' \in \A} e^{\beta \phi(\abf')}} \cdot \frac{e^{\beta\sigma(\abf_{-j})}}{\displaystyle e^{\beta \pi_j(\bbf)} + e^{\beta \pi_j(\abf)}} \bigg( e^{\beta \phi(\abf)} e^{\beta \phi(\bbf)} - e^{\beta \phi(\bbf)} e^{\beta \phi(\abf)} \bigg) \\[10pt]
+&= 0
+\end{align}
+\noindent Using the above result, one can then show that, 
+\begin{align}
+\label{Eq:step-1-detailed-balance}
+\ubf^\LD_\abf \mathrm{T}^\ID_{\abf,\bbf} - \ubf^\LD_\bbf \mathrm{T}^\ID_{\bbf,\abf} &= 0 \\[10pt]
+\implies \sum_{c \in \mathrm{Neb}(\abf)} \ubf^\LD_\abf \mathrm{T}^\ID_{\abf,\cbf} - \ubf^\LD_\cbf \mathrm{T}^\ID_{\cbf,\abf} &= 0 \\[10pt]
+\implies  \ubf^\LD_\abf \bigg( 1 -  \sum_{c \in \mathrm{Neb}(\abf)} \mathrm{T}^\ID_{\abf,\cbf} \bigg) + \sum_{c \in \mathrm{Neb}(\abf)}  \ubf^\LD_\cbf \mathrm{T}^\ID_{\cbf,\abf} &=  \ubf^\LD_\abf \\[10pt]
+\implies \ubf^\LD_\abf \mathrm{T}^\ID_{\abf,\abf} + \sum_{c \in \mathrm{Neb}(\abf)}  \ubf^\LD_\cbf \mathrm{T}^\ID_{\cbf,\abf} &=  \ubf^\LD_\abf \\[10pt]
+\label{Eq:step-2-detailed-balance}
+\implies \ubf^\LD \T^\ID &= \ubf^\LD
+\end{align}
+\noindent The candidate $\ubf^\LD$ is indeed the unique stationary distribution of introspection dynamics too. Therefore, the two processes have the same stationary distribution.
+\end{proof}
+
+\begin{proof}
+\textbf{Proof of Proposition} \ref{Prop:additive-logit} \\ \\
+The idea behind the proof of this proposition is similar to the proof of Proposition \ref{Prop:potential-logit}.
+We consider the stationary distribution of introspection dynamics for additive games, $\ubf^\ID$, from Eq.
+(\ref{Eq:additive-game-stationary-distribution}), to be the candidate stationary distribution of the logit-response dynamics.
+Then, showing that $\ubf^\ID \T^\LD = \ubf^\ID$ is equivalent to showing that $\ubf^\LD = \ubf^\ID$.
+Again, like in the previous proof, we look at the value of the following expression for two arbitrary neighbouring states $\abf$ and $\bbf$ (with $j$ as the index of difference between the states), \\
+\begin{align}
+&\ubf^\ID_\abf \mathrm{T}^\LD_{\abf,\bbf} - \ubf^\ID_\bbf \mathrm{T}^\LD_{\bbf,\abf} \\[15pt]
+&= \underbrace{\frac{1}{N \displaystyle \sum_{a' \in \A_j} e^{\beta \pi_j(a',\abf_{-j})}} \Bigg( \displaystyle \prod_{l \neq j} \frac{1}{\displaystyle \sum_{a^{''} \in \A_l} e^{\beta f_l(a^{''}, \abf_l)}} \Bigg)}_{\mathrm{L} > 0} \Bigg(
+\frac{\displaystyle e^{\beta \pi_j(b_j, \abf_{-j})}}{\displaystyle \sum_{a \in \A_j}  e^{\beta f_j(a,a_j)}}  - \frac{\displaystyle e^{\beta \pi_j(a_j, \abf_{-j})}}{\displaystyle \sum_{a \in \A_j} e^{\beta f_j(a,b_j)}} \Bigg)
+\end{align}
+\noindent The product of the first two terms, which we denote as $\mathrm{L}$ is stricltly greater than $0$.
+We focus on the rest of the expression.
+Since, $f_j(a,a_j) = \pi_j(a,\pbf) - \pi_j(a_j,\pbf)$, is independent of $\pbf$ irrespective of the choice of $\pbf \in \A_{-j}$, we use $\pbf = \abf_{-j}$ in the steps below,\\
+\begin{align}
+&\ubf^\ID_\abf \mathrm{T}^\LD_{\abf,\bbf} - \ubf^\ID_\bbf \mathrm{T}^\LD_{\bbf,\abf} \\[15pt]
+&= \mathrm{L} \cdot \frac{1}{\displaystyle \sum_{a \in \A_j} e^{\beta \pi_j(a,\abf_{-j})}} \bigg( e^{\beta \pi_j(b_j, \abf_{-j})} e^{\beta \pi_j(a_j, \abf_{-j})}  - e^{\beta \pi_j(a_j, \abf_{-j})} e^{\beta \pi_j(b_j, \abf_{-j})} \bigg) \\[10pt]
+&= 0
+\end{align}
+\noindent Now, following the exact same steps from Eq.
+(\ref{Eq:step-1-detailed-balance}) to Eq.
+(\ref{Eq:step-2-detailed-balance}), we can show that $\ubf^\ID \T^\LD = \ubf^\ID$.
+Therefore, the two processes have the same stationary distribution, $\ubf^\ID = \ubf^\LD$.
+\end{proof}
+
 \newpage
@@
 \textbf{Introspection dynamics in a symmetric linear public goods game.}
-We show the stationary distribution of the introspection dynamics for a linear public goods game with four identical players.
-For all the panels in this figure, we use the following parameters: $N = 4$ (group size), $b = 2$ (benefit provided to the public good upon cooperation), $c = 1$ (cost of cooperation).
-a) Here, we show the frequency of each state in the stationary distribution of introspection dynamics.
+Stationary distribution of the introspection dynamics for a linear public goods game with four identical players.
+For all the panels in this figure, the following parameters are used: $N = 4$ (group size), $b = 2$ (benefit provided to the public good upon cooperation), $c = 1$ (cost of cooperation).
+a) Frequency of each state in the stationary distribution of introspection dynamics.
 As players are identical, each state can be defined by the number of cooperators.
-We use a selection strength of $\beta = 5$.
-For this strength of selection, states with more cooperators are less likely than states with less cooperators.
-b) Here, we show the frequency of each state for varying selection strength, $\beta$.
-We use the same color code as panel a).
-Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, we see that selection favors states other than 0 cooperators.
-Indeed, up to $\beta \approx 3$, state $0$ is not the most frequent state in the long run.
+For a selection strength of $\beta = 5$, states with more cooperators are less likely than states with less cooperators.
+b) Frequency of each state for varying selection strength, $\beta$.
+The color code is the same as panel a).
+Comparing neutrality ($\beta = 0$) with low to intermediate $\beta$ values, selection favors states other than 0 cooperators.
+Indeed, up to $\beta \approx 3$, state $0$ is not the most frequent state in the long-run.
 c) Average cooperation frequency for varying dilemma strength depends on the selection strength, $\beta$.
@@
 Typically, a linear public goods dilemma is defined to have a negative marginal gain.
-Here, we show the dilemma strength varying from $-2$ to $2$.
+Here, the dilemma strength varies from $-2$ to $2$.
 The results are shown for different values of selection strength, $\beta = 1, 5$ and $100$.
 For high $\beta$, stationary distribution of the introspection dynamics reflects the rational play.
-In the long-run players play the Nash equilibrium.
+In the long-run, players play the Nash equilibrium.
 When marginal gain is negative, defection is played with almost certainty (and \emph{vice-versa}).
-For low $\beta$, however, we see that some cooperation is possible even when the dilemma is strong.
+For low $\beta$, however, some cooperation is possible even when the dilemma is strong.
 }
@@
 \caption{\onehalfspacing
-\textbf{Introspection dynamics in an asymmetric linear public goods game.} We show the cooperation probabilities of the introspection dynamics for a linear public goods game with three asymmetric players.
+\textbf{Introspection dynamics in an asymmetric linear public goods game.} Cooperation probabilities of the introspection dynamics for a linear public goods game with three asymmetric players.
 For each of the upper panels (a and b), we show the cost of cooperation and the benefit provided upon cooperation for the players on the left and the average cooperation frequency in the long-run on the right.
@@
 The cost of cooperation is the same for all players ($c = 1$).
-In c), we vary the asymmetry strengths between the players, $\delta_c $ and $\delta_b$, simultaneously and show both average individual cooperation frequency and the overall average cooperation frequency in the long-run.
+In c), the asymmetry strengths between the players,$\delta_c $ and $\delta_b$, varies simultaneously.
+Both average individual cooperation frequency and the overall average cooperation frequency in the long-run is shown.
 The reference player's cost and benefit are again 1 and 2 units respectively.
 The area within the white dashed lines represents the parameter values for which the marginal gain of choosing cooperation over defection is negative, for each single player and, in the right-most panel, for all players simultaneously.
-In this example, cooperation is only feasible in the long run if the asymmetries of players are aligned.
+In this example, cooperation is only feasible in the long-run if the asymmetries of players are aligned.
 That is, overall cooperation is high only when the individual with a low cost of cooperation has a high benefit value.
-For panels a) and b) we use a selection strength of $\beta = 2$ while for panel c), we use a selection strength of $\beta = 5$.
+For panels a) and b) selection strength is $\beta = 2$ while for panel c), $\beta = 5$.
 }
@@
 \textbf{Introspection dynamics in a symmetric general public goods game}.
-We study introspection dynamics in the general public goods game with 4 symmetric players, each having two possible actions - cooperation and defection.
+Introspection dynamics in the general public goods game with 4 symmetric players, each having two possible actions - cooperation and defection.
 For a detailed description of the game, please see the main text.
@@
 Each case is tagged with a symbol that places the particular case in the contour plot in panel b).
-b) On the left, we show the average cooperation frequency for varying discount/synergy factor, $w$, and varying cost of cooperation, $c$.
+b) On the left, the average cooperation frequency for varying discount/synergy factor, $w$, and varying cost of cooperation, $c$ is shown.
 Cooperation is feasible when costs are not restrictively high and the public good is not too discounted.
-On the right, we show the average cooperation frequency for varying discount/synergy factor, $w$, and group size $N$.
+On the right, the average cooperation frequency for varying discount/synergy factor, $w$, and group size $N$.
 For this plot, the cost of cooperation for each player is $c = 0.4$.
@@
 \caption{\onehalfspacing
-\textbf{Intropection dynamics in the linear public goods game with peer rewarding.} Here we study a game with three asymmetric players, each having 16 possible strategies.
+\textbf{Intropection dynamics in the linear public goods game with peer rewarding.} Here, a game with three asymmetric players, each having 16 possible strategies, is studied.
 Players cooperate in a linear public goods and then reward each other in the next stage after everyone's contribution is revealed.
@@
 In this example, players 1 and 2 are identical in all aspects while player 3 differs from them in only a single aspect.
-In here, we use Eq.
-(\ref{Eq:explicit-stationary-dist-representation}) to plot the exact probability with which players cooperate and reward cooperation in the long run.
-We consider three types of asymmetry for player 3.
-a) First, we consider the case where player 3 has a high cost of rewarding compared to player 1 and 2, $0.7 = \gamma_3 > \gamma_1 = 0.1$.
-b) Then, we consider the case where player 3 is less productive than their co-players, $1.2 = r_3 < r_1 = 2$.
-c) Finally, we consider the case where player 3 has less information about co-players' rewarding strategies than the others, that is, $0.1 = \lambda_3 < \lambda_1 = 0.9$.
-For all plots, we consider a high value for the selection strenght, $\beta = 10$.
+Here, Eq.
+(\ref{Eq:explicit-stationary-dist-representation}) is used to plot the exact probability with which players cooperate and reward cooperation in the long-run.
+There are three types of asymmetry for player 3.
+a) First, the case where player 3 has a high cost of rewarding compared to player 1 and 2, $0.7 = \gamma_3 > \gamma_1 = 0.1$.
+b) Then, the case where player 3 is less productive than their co-players, $1.2 = r_3 < r_1 = 2$.
+c) Finally, the case where player 3 has less information about co-players' rewarding strategies than the others, that is, $0.1 = \lambda_3 < \lambda_1 = 0.9$.
+For all plots, a high value for the selection strength, $\beta = 10$, is considered.
 Unless otherwise mentioned, the following parameters are maintained for all panels: $c_i = 1$ (individual cost of cooperation), $r_i = 2$ (individual productivity), $\gamma_i = 0.1$ (individual cost of rewarding), $\lambda_i = 0.9$ (individual information about co-players' strategies).
